---
title: "F2_DryWeights_analysis"
author: "Samuel Gurr"
date: "2024-01-05"
output: html_document
---

# Objectives: 

* (i) view the mean, variation, and number of samples

* (ii) plot the data 

* (iii) run stats

### set up load libraries and set working dir for the script 
```{r setup, include= FALSE, echo = FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(performance)
library(car)
library(ggpubr)
library(SciViews)
library(Rmisc)
library(ggpmisc)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis")

```

## Load data 

```{r, load data}

# F2s
F2_dryweights <- read.csv(file="Data/Physiology/Dry_weights/F2/cumulative_raw/F2_dry_weights_raw_2.csv",
                          header=T,stringsAsFactors=FALSE, fileEncoding="latin1") 
F2_dryweights <- F2_dryweights[!is.na(F2_dryweights$Tank_Replicate),]      # seven indivuals did not have tnak ID on the bag (Gabby P. review google doc!" and are omitted

# unique dates for the dry weight data 
unique(F2_dryweights$Date_sampled)
# View(F1_dryweights)

F2_dryweights <- F2_dryweights[!is.na(F2_dryweights$pH),] %>% # master data file
                    dplyr::mutate(pCO2 = as.factor(case_when(pH == 8 ~ "500 μatm", # add column for pCO2
                                                   pH == 7.5 ~ "800 μatm",
                                                   pH == 7 ~ "1200 μatm"))) %>% 
                    dplyr::mutate(Age = case_when(Date_sampled == "11/16/2022" ~  93, # A- D for each treatment 
                                                  Date_sampled == "1/27/2023" ~  165, # A- D for each treatment 
                                                  #NOTE: A-G started on 2/3/2023 unlike F1s, this was note A - E and B to F, 
                                                  # the bins are separate reps, G disappears from the chemistry data at 2/28/2023
                                                  Date_sampled == "2/27/2023" ~  196, # A-G 
                                                  Date_sampled == "3/23/2023" ~  220, # A-F 
                                                  Date_sampled == "3/28/2023" ~  225)) %>%  # A-F 
                    dplyr::mutate(pCO2 = fct_relevel(pCO2, c("500 μatm","800 μatm","1200 μatm")))# relevel for plotting!

```



```{r Steps 1-3 to acheive master means data}

# first, lets reshape to assist in calculating all the means in LONG format
library(tidyr)

F2_dryweights$Shell_length_mm <- as.numeric(F2_dryweights$Shell_length_mm)
colnames(F2_dryweights)
F2_dryweights_long <- F2_dryweights %>% 
                                  dplyr::mutate(row = row_number()) %>% 
                                  # because there are duplicates - complicates pivot_wider later
                                  dplyr::select(Age, pCO2, Tank_Replicate, row,
                                                Shell_length_mm,
                                                Dry_Shell_weight_g, Dry_Gonad_weight_g, 
                                                Dry_Muscle_weight_g, Dry_Tissue_weight_g 
                                                #Tissue_AFDW_g, Total_Dry_Tissue_g, Total_AFDW_g, Whole_animal_dry_weight_g
                                                ) %>% 
                                  dplyr::rename(Dry_Adductor_Tissue_g = Dry_Muscle_weight_g) %>% 
                                  dplyr::mutate(Dry_Somatic_Tissue_g = case_when(Dry_Gonad_weight_g %in% NA ~ NA,
                                                                                 TRUE ~ Dry_Tissue_weight_g),
                                                Total_Dry_Tissue_g = case_when( Dry_Gonad_weight_g %in% NA ~ Dry_Tissue_weight_g,
                                                                                TRUE ~ (Dry_Gonad_weight_g +
                                                                                         Dry_Adductor_Tissue_g +
                                                                                           Dry_Tissue_weight_g)),
                                                Dry_Tissue_weight_g = case_when(Dry_Gonad_weight_g %in% NA ~ Dry_Tissue_weight_g,
                                                                                TRUE ~ NA)) %>% 
                                  dplyr::select(!Dry_Tissue_weight_g) %>% 
                                  tidyr::pivot_longer(
                                    cols = c('Shell_length_mm',
                                             'Dry_Shell_weight_g', 'Dry_Gonad_weight_g', 
                                             'Dry_Adductor_Tissue_g', 'Dry_Somatic_Tissue_g', 'Total_Dry_Tissue_g'#, 
                                             #'Tissue_AFDW_g', 'Total_Dry_Tissue_g', 'Total_AFDW_g', 'Whole_animal_dry_weight_g'
                                             ), 
                                    names_to = "measurement",
                                    values_to = "value"
                                  ) %>% 
                                    na.omit()

## step 1 calc means by replicate tank 


F2_dryweights_calc.long.MEANS    <- F2_dryweights_long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)

write.csv(F2_dryweights_calc.long.MEANS, "Output/DryWeights/F2/F2_N_per_Replicate_MeanSE.csv")

## step 3:  convert E-H to A-D and summarise again to get the median 
# * note: ignore sd, se, etc, as there as N now ==1 or 2 in all cases, refer to the output file above 
# if you want the actual N for each replicate along with the variation within replicate!

F2_dryweights_calc.long.MEANS_master <- F2_dryweights_calc.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate) %>% 
                        dplyr::select(-c(sd, se, ci)) # N = number of means!!! N = 2 means there awas a A+E, etc and mean == median

```

```{r all diagnostic plotting}

#plot all data by replicate 

Raw_all_data <-ggplot(F2_dryweights_long,
                                 aes(x=paste0(pCO2,Tank_Replicate), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           geom_violin() +
                           labs(x ="Age (dpf)", y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~Age*measurement, scales="free")

pdf("Output/DryWeights/F2/all_raw/Raw_data_bytank.pdf", height=15, width =30)
print(Raw_all_data)
dev.off()

Raw_MeanSE <-ggplot(F2_dryweights_calc.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")

pdf("Output/DryWeights/F2/all_raw/MeanSE_data.pdf", height=8, width =8)
print(Raw_MeanSE)
dev.off()


```

## Statistics function 'runstats' and 'run_ttest'
```{r Statistic function}


runstats <- function(datafilename,  outputfilename) {
            # variables for both for loops
            DF_loop           <- data.frame(matrix(nrow = 1, ncol = 11)) # create dataframe to save during for loop
            colnames(DF_loop) <- c('Age_DPF', 'ShapiroWilk', 'ResidNorm', 
                                   'Levenes', 'HomogVar', 'model', 
                                   'DF.num' , 'DF.denom', 
                                   'F_val','P_val', 'SigDif') # names for comuns in the for loop
            
            unique(datafilename$Age)
            outputfilename <- data.frame()

            
            for (i in 1:length(unique(datafilename$Age))) {
              GROUPvar_loop <- unique(datafilename$GROUPvar)[i]
              Data_all      <- datafilename %>% dplyr::filter(GROUPvar %in% GROUPvar_loop)
              # Data_mean   <- Data_all %>% summarySE(measurevar="DPvar", 
              #                                       groupvars=c("group1","Tank_Replicate", "INDvar")) 
              
              AOVmod      <- aov(lm(Data_all$DPvar ~ as.factor(Data_all$INDvar))) # CHANGE HERE!
              KWmod       <- kruskal.test(Data_all$DPvar  ~ as.factor(Data_all$INDvar)) # CHANGE HERE!
              
              # DF_loop$About <- paste0("Gonad: All bfactor + mean by replicate")
              # DF_loop$About <- paste0("Gonad: All bfactor + all data")  # normality tests for the anova model - asign
              
              
              DF_loop$ShapiroWilk <- shapiro.test(resid(AOVmod))[[2]]
              DF_loop$ResidNorm   <- if( shapiro.test(resid(AOVmod))[[2]] > 0.05) {
                  'YES'} else {'NO'}
              DF_loop$Levenes     <- leveneTest(AOVmod)[[3]][[1]]
              DF_loop$HomogVar    <- if( leveneTest(AOVmod)[[3]][[1]] > 0.05) {
                  'YES'} else {'NO'}
                
              if(shapiro.test(resid(AOVmod))[[2]] > 0.05 & leveneTest(AOVmod)[[3]][[1]] > 0.05) {
                    DF_loop$model       <- 'one-way AOV; x ~ treatment'
                    DF_loop$DF.num      <- summary(AOVmod)[[1]][["Df"]][1]
                    DF_loop$DF.denom    <- summary(AOVmod)[[1]][["Df"]][2]
                    DF_loop$F_val       <- summary(AOVmod)[[1]][["F value"]][1]
                    DF_loop$P_val       <- summary(AOVmod)[[1]][["Pr(>F)"]][1]
                    DF_loop$SigDif      <- if( (summary(AOVmod)[[1]][["Pr(>F)"]][1]) > 0.05) {
                      'NO'} else {'YES'}
            
                  } else {
                    DF_loop$model       <- 'kruskal-wallis; x ~ treatment'
                    DF_loop$DF.num      <- (KWmod)[[2]][["df"]][1]
                    DF_loop$DF.denom    <- NA
                    DF_loop$F_val       <- NA
                    DF_loop$P_val       <- (KWmod)[[3]]
                    DF_loop$SigDif      <- if( ((KWmod)[[3]]) > 0.05) {
                      'NO'} else {'YES'}
                  }
              DF_loop$Age_DPF     <- GROUPvar_loop
              # asign loop and cumulative output table
              df                        <- data.frame(DF_loop) # name dataframe for this single row
              outputfilename <- rbind(outputfilename,DF_loop) #bind to a cumulative list dataframe
              # print(outputfilename) # print to monitor progress
              
            }
return(outputfilename)
}




run_ttest <- function(datafilename,  outputfilename) {
            # variables for both for loops
            DF_loop           <- data.frame(matrix(nrow = 1, ncol = 12)) # create dataframe to save during for loop
            colnames(DF_loop) <- c('Age_DPF', 'model', 'ShapiroWilk', 'ResidNorm', 'Variance', 
                                   'HomogVar', 'DF.num' , 'DF.denom', 
                                   'Tstat','P_val', 'SigDif') # names for comuns in the for loop
            
            unique(datafilename$Age)
            outputfilename <- data.frame()

            
            for (i in 1:length(unique(datafilename$Age))) {
              GROUPvar_loop <- unique(datafilename$GROUPvar)[i]
              Data_all      <- datafilename %>% dplyr::filter(GROUPvar %in% GROUPvar_loop)
              # Data_mean   <- Data_all %>% summarySE(measurevar="DPvar", 
              #                                       groupvars=c("group1","Tank_Replicate", "INDvar")) 
              
            # run assumptions 
            # normality of data 
            normality_A <- (Data_all %>% 
                                  group_by(as.factor(INDvar)) %>% 
                                  rstatix::shapiro_test(DPvar))$p[1]
            
            normality_B <- (Data_all %>% 
                                  group_by(as.factor(INDvar)) %>% 
                                  rstatix::shapiro_test(DPvar))$p[2]
            
            # equal variance 
            variance <- (Data_all %>% rstatix::levene_test(DPvar ~ as.factor(INDvar)))$p[1]
            
            # run all modles
            Ttestmod.eqvar      <- t.test(Data_all$DPvar ~ (as.factor(Data_all$INDvar)), 
                                           alternative = "greater",
                                           var.equal = TRUE)
            
            Ttestmod.noneqvar   <- t.test(Data_all$DPvar ~ (as.factor(Data_all$INDvar)), 
                                           alternative = "greater",
                                           var.equal = FALSE)
            
            Wilcoxmod           <- wilcox.test(Data_all$DPvar ~ 
                                                 as.numeric(as.factor(Data_all$INDvar)))
            
            # normality tests for the anova model - asign 
            DF_loop$ShapiroWilk <- paste0(normality_A, '; ',normality_B)
            
            DF_loop$ResidNorm   <- if(normality_A > 0.05 & normality_B > 0.05) {
              'YES'} else {'NO'}
            
            DF_loop$Variance     <- variance
            
            DF_loop$HomogVar    <- if( variance > 0.05) {
              'YES'} else {'NO'}
            
            if(normality_A > 0.05 & normality_B > 0.05 & variance > 0.05) {
                DF_loop$model       <- 'Welchs T test, equal variance'
                DF_loop$DF.num      <- map_df(list(Ttestmod.eqvar), tidy)$parameter[[1]]
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Ttestmod.eqvar), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Ttestmod.eqvar), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Ttestmod.eqvar), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}
        
              } else if (normality_A > 0.05 & normality_B > 0.05 & variance < 0.05) {
                DF_loop$model       <- 'Welchs T test, non-equal variance'
                DF_loop$DF.num      <- map_df(list(Ttestmod.noneqvar), tidy)$parameter[[1]]
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Ttestmod.noneqvar), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Ttestmod.noneqvar), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Ttestmod.noneqvar), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}
              } else {
                DF_loop$model       <- 'Wilcoxon rank sum exact test'
                DF_loop$DF.num      <- 'NA'
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Wilcoxmod), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Wilcoxmod), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Wilcoxmod), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}            
              }
                  DF_loop$Age_DPF     <- GROUPvar_loop
                  # asign loop and cumulative output table
                  df                        <- data.frame(DF_loop) # name dataframe for this single row
                  outputfilename <- rbind(outputfilename,DF_loop) #bind to a cumulative list dataframe
                  # print(outputfilename) # print to monitor progress
                  
                }
return(outputfilename)
}


```



# Proportion Gonad to Total tissue weight 

* here we do no require a bfactor becuase we are already scalling to the individual!

### Build poroprtion dataset 
```{r Proportion calculate}


Proportion_master <- F2_dryweights_long %>% 
                             #F2_dryweights_calc.long.MEANS_master %>% 
                             dplyr::filter(measurement %in% c('Dry_Gonad_weight_g', 
                                                              'Dry_Somatic_Tissue_g', 
                                                              'Dry_Adductor_Tissue_g',
                                                              'Total_Dry_Tissue_g')) %>%
                            tidyr::pivot_wider(
                                                names_from = measurement,
                                                values_from = value
                            ) %>% 
                            na.omit() %>% # omit cases where we do not have gonad weight (there are a few!)
                            dplyr::mutate(Proportion_Gonad    = Dry_Gonad_weight_g/Total_Dry_Tissue_g,
                                          Proportion_Adductor = Dry_Adductor_Tissue_g/Total_Dry_Tissue_g,
                                          Proportion_Somatic  = Dry_Somatic_Tissue_g/Total_Dry_Tissue_g,
                                          Sanity_check_prop_total = (Proportion_Gonad +  
                                                                       Proportion_Adductor + 
                                                                       Proportion_Somatic)) 

```

### Plot porportion dataset
```{r Propotion stacked bar plot}

Proportion_master_long <- Proportion_master[,c(1:2,9:11)] %>%  
                              tidyr::pivot_longer(cols = c(3:5), names_to='prop_metric', values_to='value') 



#convert metric to ordered factor
Proportion_master_long_ordered             <- Proportion_master_long[order(Proportion_master_long$prop_metric ),]
Proportion_master_long_ordered$prop_metric <- factor(Proportion_master_long_ordered$prop_metric, 
                                                     levels = rev(c(rep("Proportion_Somatic",1), 
                                                                    rep("Proportion_Adductor",1), 
                                                                    rep("Proportion_Gonad",1))))

Proportion_master_long_MEANS <- Proportion_master_long_ordered %>%
                                    dplyr::mutate(prop_metric = 
                                                    forcats::fct_relevel(prop_metric,
                                                                         "Proportion_Somatic",
                                                                         "Proportion_Gonad",
                                                                         "Proportion_Adductor")) %>% 
                                    group_by(Age, pCO2, prop_metric) %>% 
                                    dplyr::summarise(mean = mean(value), sd =sd(value)) %>% 
                                    mutate(y_pos = cumsum(mean)) 


Proportion_master_long_MEANS$prop_metric <- factor(Proportion_master_long_MEANS$prop_metric, 
                                                     levels = rev(c(rep("Proportion_Somatic",1), 
                                                                    rep("Proportion_Gonad",1), 
                                                                    rep("Proportion_Adductor",1))))

# stacked proportion plot
pd <- position_dodge2(width = 0.2)
Proportion_master_long_MEANS$prop_metric <- as.character(Proportion_master_long_MEANS$prop_metric)


Proportion_StackedBarplot <- Proportion_master_long_MEANS %>% 
  ggplot(aes(x = as.factor(Age), 
             y = mean, 
             fill = prop_metric)) + 
  geom_bar(stat = "identity", width=0.7) + 
  scale_fill_manual(values = c("grey80","grey40", "grey20")) +
  #scale_fill_manual(values = c("#0072B2", "#D55E00")) + # colorblindness palette blue and orange
  geom_errorbar(aes(ymax = y_pos + sd, ymin=y_pos - sd), stat = "identity", width = 0.1, alpha = 0.7, position = pd) + 
  facet_wrap(~pCO2) + 
  scale_alpha_manual(values=c(seq(0.3,1, length.out = 3))) + 
  theme_bw() + 
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10)) + 
  ylim(0,1.1)+
  ylab("Dry Tissue Proportions (%)") 
Proportion_StackedBarplot


pdf("Output/DryWeights/F2/Proportion_DryWeight_StakedBarplot.pdf", height=4, width =6)
print(Proportion_StackedBarplot)
dev.off()

```

```{r Proportion mean SE plot}

Proportion_Gonad_plot <- Proportion_master %>% 
                          # dplyr::filter((!value > 20)) %>% 
                          ggplot(aes(x=factor(Age), y=Proportion_Gonad, colour=factor(pCO2)),stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Proportion Gonad to Total Tissue", 
                               x ="Age (dpf)", 
                               y = "Dry gonad (proportion)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")


Proportion_Adductor_plot <- Proportion_master %>% 
                          # dplyr::filter((!value > 20)) %>% 
                          ggplot(aes(x=factor(Age), y=Proportion_Adductor, colour=factor(pCO2)),stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Proportion Adductor to Total Tissue", x ="Age (dpf)", y = "Dry Adductor (proportion)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")


Proportion_Somatic_plot <- Proportion_master %>% 
                          # dplyr::filter((!value > 20)) %>% 
                          ggplot(aes(x=factor(Age), y=Proportion_Somatic, colour=factor(pCO2)),stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Proportion Somatic to Total Tissue", x ="Age (dpf)", y = "Dry Somatic (proportion)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")


# Lets look at shell length for good measure.. Remember to omit lines that did not have gonad! 
Shell_Length_plot <- F2_dryweights_long %>% 
                            dplyr::filter(measurement %in% c('Dry_Gonad_weight_g', 'Shell_length_mm')) %>%
                            tidyr::pivot_wider(
                                                names_from = measurement,
                                                values_from = value
                            ) %>% 
                            na.omit() %>% # omit cases where we do not have gonad weight (there are a few!)
                            ggplot(aes(x=factor(Age), y=Shell_length_mm, colour=factor(pCO2)),stat="identity") +
                            scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                            stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                            stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                            labs(title="Shell length", x ="Age (dpf)", y = "shell length (mm)") +
                            theme_classic() +
                            theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")



# pdf("Output/DryWeights/F2/length_scaling/Dry_Gonad_byLength.pdf", height=8, width =8)
# ggarrange(bfactorGonad.Length.all, bfactorGonad.Length.pCO2,Gonad_bfactor.MeanSE, nrow=3)
# dev.off()

pdf("Output/DryWeights/F2/Proportion_DryWeight_MeanSE.pdf", height=6, width =8)
ggarrange(Proportion_Gonad_plot, Proportion_Adductor_plot , Proportion_Somatic_plot,Shell_Length_plot, nrow = 2, ncol = 2)
dev.off()


```

### Statistics on proportion data
```{r Proportion stats}
library(purrr)
library(rstatix)

# Gonad (to total tissue)
F2_Proportion_Gonad_MEANS <- Proportion_master %>% 
                                    dplyr::select(Age,pCO2, Tank_Replicate,
                                                  Proportion_Gonad) %>% 
                                    summarySE(measurevar="Proportion_Gonad", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate")) %>% 
                                    dplyr::arrange(as.numeric(Age))


F2_Proportion_Gonad_MEANS %>% summarySE(measurevar="Proportion_Gonad", 
                                               groupvars=c("Age","pCO2"))
# 220	500 μatm	5	0.11154640	0.064620441	0.028899140	0.080236875
# 220	800 μatm	6	0.25291354	0.089489351	0.036533874	0.093913314
# 
# 0.25291354 - 0.11154640 # at 220 dpf 14 % more of the total tissue weight comprised of gonad under moderate OA

F2_Proportion_Gonad_MEANS$DPvar    <- F2_Proportion_Gonad_MEANS$Proportion_Gonad
F2_Proportion_Gonad_MEANS$INDvar   <- F2_Proportion_Gonad_MEANS$pCO2
F2_Proportion_Gonad_MEANS$GROUPvar <- F2_Proportion_Gonad_MEANS$Age

ProportionGonad_stats <- as.data.frame(runstats(F2_Proportion_Gonad_MEANS)) # sig effect on Age 196 and 220
ProportionGonad_ttest <- as.data.frame(run_ttest(F2_Proportion_Gonad_MEANS %>% 
                                                   dplyr::filter(!(pCO2 %in% '1200 μatm')))) # sig for all
# Gonad posthoc
aov_Gonad196             <- aov(lm(Proportion_Gonad~pCO2, data = (F2_Proportion_Gonad_MEANS %>% dplyr::filter(Age %in% 196))))
summary(aov(aov_Gonad196)) # significnat as known already
aov_Gonad196_means_contr <- emmeans::emmeans(object = aov_Gonad196, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
aov_Gonad196_mod_means   <- multcomp::cld(object = aov_Gonad196_means_contr$emmeans, Letters = letters) # letter display\


aov_Gonad220             <- aov(lm(Proportion_Gonad~pCO2, data = (F2_Proportion_Gonad_MEANS %>% dplyr::filter(Age %in% 220))))
summary(aov(aov_Gonad220)) # significnat as known already
aov_Gonad220_means_contr <- emmeans::emmeans(object = aov_Gonad220, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
aov_Gonad220_mod_means   <- multcomp::cld(object = aov_Gonad220_means_contr$emmeans, Letters = letters) # letter display\







# Adductpr (to total tissue)
F2_Proportion_Adductor_MEANS <- Proportion_master %>% 
                                    dplyr::select(Age,pCO2, Tank_Replicate,
                                                  Proportion_Adductor) %>% 
                                    summarySE(measurevar="Proportion_Adductor", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate")) %>% 
                                    dplyr::arrange(as.numeric(Age))

F2_Proportion_Adductor_MEANS %>% summarySE(measurevar="Proportion_Adductor", 
                                               groupvars=c("Age","pCO2"))

# 220	500 μatm	5	0.3227584	0.027336394	0.012225207	0.033942616
# 220	800 μatm	6	0.2371311	0.047686561	0.019467957	0.050043976
# 
# 0.3227584 - 0.2371311 # at 220 dpf 8 % more of the total tissue weight comprised of adductor under low OA

F2_Proportion_Adductor_MEANS$DPvar    <- F2_Proportion_Adductor_MEANS$Proportion_Adductor

F2_Proportion_Adductor_MEANS$INDvar   <- F2_Proportion_Adductor_MEANS$pCO2
F2_Proportion_Adductor_MEANS$GROUPvar <- F2_Proportion_Adductor_MEANS$Age

ProportionAdductor_stats <- as.data.frame(runstats(F2_Proportion_Adductor_MEANS)) # 165, 196, 220 (220 is Kruskal Wallis!)
ProportionAdductor_ttest <- as.data.frame(run_ttest(F2_Proportion_Adductor_MEANS %>% 
                                                   dplyr::filter(!(pCO2 %in% '1200 μatm')))) # sig for all
# Adductor posthoc
aov_Adductor165             <- aov(lm(Proportion_Adductor~pCO2, data = 
                                        (F2_Proportion_Adductor_MEANS %>% dplyr::filter(Age %in% 165))))
summary(aov(aov_Adductor165)) # significnat as known already
aov_Adductor165_means_contr <- emmeans::emmeans(object = aov_Adductor165, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
aov_Adductor165_mod_means   <- multcomp::cld(object = aov_Adductor165_means_contr$emmeans, Letters = letters) # letter display\



aov_Adductor196             <- aov(lm(Proportion_Adductor~pCO2, data = 
                                        (F2_Proportion_Adductor_MEANS %>% dplyr::filter(Age %in% 196))))
summary(aov(aov_Adductor196)) # significnat as known already
aov_Adductor196_means_contr <- emmeans::emmeans(object = aov_Adductor196, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
aov_Adductor196_mod_means   <- multcomp::cld(object = aov_Adductor196_means_contr$emmeans, Letters = letters) # letter display\



kw_Adductor220             <- kruskal.test(Proportion_Adductor~pCO2, data = 
                                              (F2_Proportion_Adductor_MEANS %>% dplyr::filter(Age %in% 220)))
dunnTest(Proportion_Adductor~pCO2, data = (F2_Proportion_Adductor_MEANS %>% dplyr::filter(Age %in% 220)))
# 1200 uatm b
# 800 uatm b
# 500 uatm a






# Somatic (to total tissue)
F2_Proportion_Somatic_MEANS <- Proportion_master %>% 
                                    dplyr::select(Age,pCO2, Tank_Replicate,
                                                  Proportion_Somatic) %>% 
                                    summarySE(measurevar="Proportion_Somatic", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate")) %>% 
                                    dplyr::arrange(as.numeric(Age))

F2_Proportion_Somatic_MEANS$DPvar    <- F2_Proportion_Somatic_MEANS$Proportion_Somatic
F2_Proportion_Somatic_MEANS$INDvar   <- F2_Proportion_Somatic_MEANS$pCO2
F2_Proportion_Somatic_MEANS$GROUPvar <- F2_Proportion_Somatic_MEANS$Age

ProportionSomatic_stats <- as.data.frame(runstats(F2_Proportion_Somatic_MEANS)) # 165, 196, 220 (220 is Kruskal Wallis!)
ProportionSomatic_ttest <- as.data.frame(run_ttest(F2_Proportion_Somatic_MEANS %>% 
                                                   dplyr::filter(!(pCO2 %in% '1200 μatm')))) # sig for all
```



# Dry Gonad: b factor calc and plot
```{r Gonad b factor calc and plot}
# b factor for gonad? 
LogDryGonadvShell <- F2_dryweights_long %>% 
                     #F2_dryweights_calc.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% c('Dry_Gonad_weight_g', 'Shell_length_mm')) %>%
                          # dplyr::group_by(measurement) %>% 
                          tidyr::pivot_wider(
                                              names_from = measurement,
                                              values_from = value
                          ) %>% 
                          # dplyr::select(-row) %>% 
                          dplyr::group_by(Age, pCO2, Tank_Replicate) %>%    
                          dplyr::filter(!Dry_Gonad_weight_g < 0) %>% 
                          dplyr::mutate(log10_Gonad   = log10(Dry_Gonad_weight_g),
                                        log10_Length = log10(Shell_length_mm)) %>% 
                          na.omit() %>% # we only have gonad for later life stage - omit rows without it
                          dplyr::filter(!log10_Gonad %in% '-Inf') # ommit instances when gonad weight == 0


bfactorGonad.Length.pCO2 <- LogDryGonadvShell %>% 
                          ggplot(aes(x=log10_Length, y=log10_Gonad, color = pCO2)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2")), size =3) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Gonad scaling: log10_Gonad = log10_a + 
                                      (b.factor * log10_Length)") +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(method = "SMA",
                             #                       parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") +
                             facet_wrap(~pCO2)


bfactorGonad.Length.all <- LogDryGonadvShell %>% 
                          ggplot(aes(x=log10_Length, y=log10_Gonad)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2"))) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Gonad scaling: log10_Gonad = log10_a + 
                                      (b.factor * log10_Length)") # +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") 

# call dataset - omit data without gonad weights
F2_DryGonad <- F2_dryweights %>% 
    dplyr::filter(!Dry_Gonad_weight_g < 0) %>% 
    dplyr::select(Age, pCO2, Tank_Replicate, Dry_Gonad_weight_g, Shell_length_mm) %>% 
    na.omit()
# call the mean gonad dry weight
meanLength.all <- mean(as.numeric(F2_DryGonad$Shell_length_mm))# 34.44198
seLength.all   <- sd(F2_DryGonad$Shell_length_mm)/sqrt(length((F2_DryGonad$Shell_length_mm))) # 0.4063575
# age range of animals 
print(paste0('youngest = ', min(F2_DryGonad$Age), '; oldest = ', max(F2_DryGonad$Age)))

#assign bfactors
bLength.all  <- 9.96 # 
bLength.low  <- 9.28 #  
bLength.mod  <- 9.52 #  
bLength.high <- 10.2 #  

# standardize gonad dry weight using bfactors
## follow the equation for scaling weights to length inbivalves 
### a = (weight of indiv / (height of indivisual)^bfactor )
### standardized weight == [a * (standard height)^bfactor ] *100
### /note: stnadard height is the mean of all individuals measured
F2_DryGonad.bfactor <- F2_DryGonad %>% 
                          dplyr::mutate(
                           Gonad_bFactorLength.all  =  ( (Dry_Gonad_weight_g * (Shell_length_mm^-bLength.all)) * # == a,  mass index Bonardelli and Himmelman 1995 
                                                                    (meanLength.all^bLength.all) )*100, # multiplied by the mean length as the standard raised to the b factor
                           Gonad_bFactorLength.pCO2 =  case_when(pCO2 == '500 μatm' ~
                                                                  ( (Dry_Gonad_weight_g * (Shell_length_mm^-bLength.low)) * # == a,  mass index Bonardelli and Himmelman 1995
                                                                      (meanLength.all^bLength.low) )*100, # multiplied by the mean length as the standard raised to the b factor
                                                                 pCO2 == '800 μatm' ~ 
                                                                  ( (Dry_Gonad_weight_g * (Shell_length_mm^-bLength.mod))* # == a,  mass index Bonardelli and Himmelman 1995
                                                                      (meanLength.all^bLength.mod) )*100, # multiplied by the mean length as the standard raised to the b factor
                                                                 pCO2 == '1200 μatm' ~ 
                                                                  ( (Dry_Gonad_weight_g * (Shell_length_mm^-bLength.high))* # == a,  mass index Bonardelli and Himmelman 1995
                                                                      (meanLength.all^bLength.high) )*100 # multiplied by the mean length as the standard raised to the b factor

                           ) # case when for pCO2 
                          ) # mutate
# pivot longer and plot 
F2_DryGonad.bfactor.long <- F2_DryGonad.bfactor %>% 
                              dplyr::select(-Shell_length_mm) %>% 
                              tidyr::pivot_longer(
                                cols = c(Dry_Gonad_weight_g, Gonad_bFactorLength.all, Gonad_bFactorLength.pCO2),
                                names_to = "measurement",
                                values_to = "value"
                              )
# means by replicate tank 
F2_DryGonad.bfactor.long.MEANS <- F2_DryGonad.bfactor.long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age))
# mmeans master - median for E-H as A-D!
F2_DryGonad.bfactor.long.MEANS_master <- F2_DryGonad.bfactor.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)
  
# 
Gonad_bfactor.MeanSE <-ggplot(F2_DryGonad.bfactor.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")


pdf("Output/DryWeights/F2/length_scaling/Dry_Gonad_byLength.pdf", height=8, width =10)
ggarrange(bfactorGonad.Length.all, bfactorGonad.Length.pCO2,Gonad_bfactor.MeanSE, nrow=3)
dev.off()
# View(F2_DryGonad.bfactor.long.MEANS_master)

Gonad_final_plot <- F2_DryGonad.bfactor.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% 'Gonad_bFactorLength.pCO2') %>% 
                          dplyr::filter((!value > 20)) %>% 
                          ggplot(aes(x=factor(Age), y=value, colour=factor(pCO2)),stat="identity") +
                           scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                           values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Gonad: Length b factor pCO2", x ="Age (dpf)", y = "Dry gonad (mg Lengthbfactor_all)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")
```

# Dry Gonad stats
```{r Gonad Stats raw - no standardization}

F2_DryGonad.raw.MEAN <- F2_DryGonad.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Dry_Gonad_weight_g')
F2_DryGonad.raw.MEAN$DPvar    <- F2_DryGonad.raw.MEAN$value
F2_DryGonad.raw.MEAN$INDvar   <- F2_DryGonad.raw.MEAN$pCO2
F2_DryGonad.raw.MEAN$GROUPvar <- F2_DryGonad.raw.MEAN$Age

Stats_GonadMEAN_raw <- as.data.frame(runstats(F2_DryGonad.raw.MEAN))
Ttest_GonadMEAN_raw <- as.data.frame(run_ttest(F2_DryGonad.raw.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_GonadMEAN_raw$About <- paste0("Gonad: raw, NO BFACTOR + mean data")
```

```{r Mean Gonad Stats bfactor all - length standardized}

F2_DryGonad.bfactor.MEAN <- F2_DryGonad.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Gonad_bFactorLength.all') %>% 
                                dplyr::filter(!value > 25)
F2_DryGonad.bfactor.MEAN$DPvar    <- F2_DryGonad.bfactor.MEAN$value
F2_DryGonad.bfactor.MEAN$INDvar   <- F2_DryGonad.bfactor.MEAN$pCO2
F2_DryGonad.bfactor.MEAN$GROUPvar <- F2_DryGonad.bfactor.MEAN$Age

Stats_GonadMEAN_bfactor.all <- as.data.frame(runstats(F2_DryGonad.bfactor.MEAN))
Ttest_GonadMEAN_bfactor_raw <- as.data.frame(run_ttest(F2_DryGonad.bfactor.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_GonadMEAN_bfactor.all$About <- paste0("Gonad: one bfactor + mean data")
```

```{r Mean Gonad Stats bfactor pCO2 - length standardized}

# means by replicate tank within treamtent and day/age
F2_DryGonad.bfactor.MEAN <- F2_DryGonad.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Gonad_bFactorLength.pCO2') %>% 
                                dplyr::filter(!value > 25)
F2_DryGonad.bfactor.MEAN$DPvar    <- F2_DryGonad.bfactor.MEAN$value
F2_DryGonad.bfactor.MEAN$INDvar   <- F2_DryGonad.bfactor.MEAN$pCO2
F2_DryGonad.bfactor.MEAN$GROUPvar <- F2_DryGonad.bfactor.MEAN$Age

Stats_GonadMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DryGonad.bfactor.MEAN))
Ttest_GonadMEAN_bfactor.pCO2 <- as.data.frame(run_ttest(F2_DryGonad.bfactor.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_GonadMEAN_bfactor.pCO2$About <- paste0("Gonad: two pCO2 bfactors + mean data")
```


```{r Dry Gonad output master stats} 

DryGonad_stats_master <- do.call("rbind", 
                                          list(Stats_GonadMEAN_bfactor.pCO2,
                                              Stats_GonadMEAN_bfactor.all,
                                              Stats_GonadMEAN_raw
                                              ))
write.csv(DryGonad_stats_master, "Output/DryWeights/F2/F2_Gonad_DryWeight_ANOVA_table.csv")

```


# Dry Adductor: b factor calc and plot
```{r Adductor b factor calc and plot}
# b factor for adductor? 
LogDryAdductorvShell <- F2_dryweights_calc.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% c('Dry_Adductor_Tissue_g', 'Shell_length_mm')) %>%
                          # dplyr::group_by(measurement) %>% 
                          tidyr::pivot_wider(
                                              names_from = measurement,
                                              values_from = value
                          ) %>% 
                          # dplyr::select(-row) %>% 
                          dplyr::group_by(Age, pCO2, Tank_Replicate) %>%    
                          dplyr::mutate(log10_Adductor   = log10(Dry_Adductor_Tissue_g),
                                        log10_Length = log10(Shell_length_mm)) %>% 
                          na.omit() %>% # we only have adductor for later life stage - omit rows without it
                          dplyr::filter(!log10_Adductor %in% '-Inf') # ommit instances when adductor weight == 0

bfactorAdductor.Length.pCO2 <- LogDryAdductorvShell %>% 
                          ggplot(aes(x=log10_Length, y=log10_Adductor, color = pCO2)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2")), size = 3) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Adductor; in g)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Adductor scaling: log10_adductor = log10_a + 
                                      (b.factor * log10_Length)") +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") +
                             facet_wrap(~pCO2)


bfactorAdductor.Length.all <- LogDryAdductorvShell %>% ggplot(aes(x=log10_Length, y=log10_Adductor)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2"))) +
                          theme(panel.grid.major = element_blank(), 
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())) + 
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Adductor; in g") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("adductor scaling: log10_adductor = log10_a + 
                                      (b.factor * log10_Length)") #+
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") 

# call dataset - omit data without adductor weights
F2_DryAdductor <- F2_dryweights %>% 
    dplyr::select(Age, pCO2, Tank_Replicate, Dry_Muscle_weight_g, Shell_length_mm) %>% 
    na.omit()
# call the mean adductor dry weight
meanLength.all <- mean(F2_DryAdductor$Shell_length_mm) # 34.23718
seLength.all   <- sd(F2_DryAdductor$Shell_length_mm)/sqrt(length((F2_DryAdductor$Shell_length_mm))) # 0.4108748
# age range of animals 
print(paste0('youngest = ', min(F2_DryAdductor$Age), '; oldest = ', max(F2_DryAdductor$Age)))
#assign bfactors
bLength.all <- 4.16#
bLength.low <- 4.42#
bLength.mod <- 3.8#3
bLength.high <- 4.15#

# standardize adductor dry weight using bfactors
F2_DryAdductor.bfactor <- F2_DryAdductor %>% 
                          dplyr::mutate(
                           Adductor_bFactorLength.all  =  ( (Dry_Muscle_weight_g * (Shell_length_mm^-bLength.all))* # a
                                                                    (meanLength.all^bLength.all) ) * 100,
                           Adductor_bFactorLength.pCO2 =  case_when(pCO2 == '500 μatm' ~
                                                                   ( (Dry_Muscle_weight_g * (Shell_length_mm^-bLength.low))* # a
                                                                      (meanLength.all^bLength.low) ) * 100,
                                                                 pCO2 == '800 μatm' ~ 
                                                                   ( (Dry_Muscle_weight_g * (Shell_length_mm^-bLength.mod))* # a
                                                                      (meanLength.all^bLength.mod) ) * 100,
                                                                 pCO2 == '1200 μatm' ~ 
                                                                   ( (Dry_Muscle_weight_g * (Shell_length_mm^-bLength.high))* # a
                                                                      (meanLength.all^bLength.high) ) * 100
                           ) # case when for pCO2 
                          ) # mutate
# pivot longer and plot 
F2_DryAdductor.bfactor.long <- F2_DryAdductor.bfactor %>% 
                              dplyr::select(-Shell_length_mm) %>% 
                              tidyr::pivot_longer(
                                cols = c(Dry_Muscle_weight_g, Adductor_bFactorLength.all, Adductor_bFactorLength.pCO2),
                                names_to = "measurement",
                                values_to = "value"
                              )
# means by replicate tank 
F2_DryAdductor.bfactor.long.MEANS <- F2_DryAdductor.bfactor.long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age))
# mmeans master - median for E-H as A-D!
F2_DryAdductor.bfactor.long.MEANS_master <- F2_DryAdductor.bfactor.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)
  
Adductor_bfactor.MeanSE <-ggplot(F2_DryAdductor.bfactor.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")


pdf("Output/DryWeights/F2/length_scaling/Dry_Adductor_byLength.pdf", height=8, width =8)
ggarrange(bfactorAdductor.Length.all, bfactorAdductor.Length.pCO2,Adductor_bfactor.MeanSE, nrow=3)
dev.off()


Adductor_final_plot <- F2_DryAdductor.bfactor.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% 'Adductor_bFactorLength.pCO2') %>% 
                          ggplot(aes(x=factor(Age), y=value, colour=factor(pCO2)),stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Adductor: Length b factor pCO2", x ="Age (dpf)", y = "Dry adductor (mg Lengthbfactor_all)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")
```

# Dry Adductor stats
```{r Adductor Stats raw - no standardization}

F2_DryAdductor.raw.MEAN <- F2_DryAdductor.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Dry_Muscle_weight_g')
F2_DryAdductor.raw.MEAN$DPvar    <- F2_DryAdductor.raw.MEAN$value
F2_DryAdductor.raw.MEAN$INDvar   <- F2_DryAdductor.raw.MEAN$pCO2
F2_DryAdductor.raw.MEAN$GROUPvar <- F2_DryAdductor.raw.MEAN$Age

Stats_AdductorMEAN_raw <- as.data.frame(runstats(F2_DryAdductor.raw.MEAN))
Ttest_AdductorMEAN_raw <- as.data.frame(runstats(F2_DryAdductor.raw.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_AdductorMEAN_raw$About <- paste0("Adductor: raw, NO BFACTOR + mean data")
```

```{r Mean Adductor Stats bfactor all - length standardized}

F2_DryAdductor.bfactor.MEAN <- F2_DryAdductor.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Adductor_bFactorLength.all')
F2_DryAdductor.bfactor.MEAN$DPvar    <- F2_DryAdductor.bfactor.MEAN$value
F2_DryAdductor.bfactor.MEAN$INDvar   <- F2_DryAdductor.bfactor.MEAN$pCO2
F2_DryAdductor.bfactor.MEAN$GROUPvar <- F2_DryAdductor.bfactor.MEAN$Age

Stats_AdductorMEAN_bfactor.all <- as.data.frame(runstats(F2_DryAdductor.bfactor.MEAN))
Ttest_AdductorMEAN_bfactor.all  <- as.data.frame(runstats(F2_DryAdductor.bfactor.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_AdductorMEAN_bfactor.all$About <- paste0("Adductor: one bfactor + mean data")
```


```{r Mean Adductor Stats bfactor all - length standardized}

F2_DryAdductor.bfactor.MEAN <- F2_DryAdductor.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Adductor_bFactorLength.pCO2')
F2_DryAdductor.bfactor.MEAN$DPvar    <- F2_DryAdductor.bfactor.MEAN$value
F2_DryAdductor.bfactor.MEAN$INDvar   <- F2_DryAdductor.bfactor.MEAN$pCO2
F2_DryAdductor.bfactor.MEAN$GROUPvar <- F2_DryAdductor.bfactor.MEAN$Age

Stats_AdductorMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DryAdductor.bfactor.MEAN))
Ttest_AdductorMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DryAdductor.bfactor.MEAN %>% dplyr::filter(!pCO2 %in% '1200 μatm')))

# About column
Stats_AdductorMEAN_bfactor.pCO2$About <- paste0("Adductor: two pCO2 bfactors + mean data")
```

```{r Dry Adductor output master stats} 

DryAdductor_stats_master <- do.call("rbind", 
                                          list(Stats_AdductorMEAN_bfactor.pCO2,
                                              Stats_AdductorMEAN_bfactor.all,
                                              Stats_AdductorMEAN_raw
                                              ))
write.csv(DryAdductor_stats_master, "Output/DryWeights/F2/F2_Adductor_DryWeight_ANOVA_table.csv")

```

# Dry Somatic: b factor calc and plot
```{r Somatic b factor calc and plot}
# b factor for Somatic? 
LogDrySomaticvShell <- F2_dryweights_long %>% 
                          dplyr::filter(measurement %in% c('Dry_Somatic_Tissue_g', 'Shell_length_mm')) %>%
                          # dplyr::group_by(measurement) %>% 
                          tidyr::pivot_wider(
                                              names_from = measurement,
                                              values_from = value
                          ) %>% 
                          # dplyr::select(-row) %>% 
                          dplyr::group_by(Age, pCO2, Tank_Replicate) %>%    
                          dplyr::mutate(log10_Somatic   = log10(Dry_Somatic_Tissue_g),
                                        log10_Length = log10(Shell_length_mm)) %>% 
                          na.omit() %>% # we only have Somatic for later life stage - omit rows without it
                          dplyr::filter(!log10_Somatic %in% '-Inf') # ommit instances when Somatic weight == 0

bfactorSomatic.Length.pCO2 <- LogDrySomaticvShell %>% 
                          ggplot(aes(x=log10_Length, y=log10_Somatic, color = pCO2)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2")), size = 3) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Somatic; in g)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Somatic scaling: log10_Somatic = log10_a + 
                                      (b.factor * log10_Length)") +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") +
                             facet_wrap(~pCO2)


bfactorSomatic.Length.all <- LogDrySomaticvShell %>% ggplot(aes(x=log10_Length, y=log10_Somatic)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2"))) +
                          theme(panel.grid.major = element_blank(), 
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())) + 
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Somatic; in g") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Somatic scaling: log10_Somatic = log10_a + 
                                      (b.factor * log10_Length)") #+
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") 

# call dataset - omit data without Somatic weights
F2_DrySomatic <- F2_dryweights %>% 
    dplyr::select(Age, pCO2, Tank_Replicate, Dry_Tissue_weight_g, Shell_length_mm) %>% 
    na.omit()
# call the mean Somatic dry weight
meanLength.all <- mean(F2_DrySomatic$Shell_length_mm) # 32.88486
seLength.all   <- sd(F2_DrySomatic$Shell_length_mm)/sqrt(length((F2_DrySomatic$Shell_length_mm))) # 0.4762848
# age range of animals 
print(paste0('youngest = ', min(F2_DrySomatic$Age), '; oldest = ', max(F2_DrySomatic$Age)))
#assign bfactors
bLength.all  <- 2.51#
bLength.low  <- 2.63#
bLength.mod  <- 2.38 #3
bLength.high <- 2.49#

# standardize Somatic dry weight using bfactors
F2_DrySomatic.bfactor <- F2_DrySomatic %>% 
                          dplyr::mutate(
                           Somatic_bFactorLength.all  =  ( (Dry_Tissue_weight_g * (Shell_length_mm^-bLength.all))* # a
                                                                    (meanLength.all^bLength.all) ) * 100,
                           Somatic_bFactorLength.pCO2 =  case_when(pCO2 == '500 μatm' ~
                                                                   ( (Dry_Tissue_weight_g * (Shell_length_mm^-bLength.low))* # a
                                                                      (meanLength.all^bLength.low) ) * 100,
                                                                 pCO2 == '800 μatm' ~ 
                                                                   ( (Dry_Tissue_weight_g * (Shell_length_mm^-bLength.mod))* # a
                                                                      (meanLength.all^bLength.mod) ) * 100,
                                                                 pCO2 == '1200 μatm' ~ 
                                                                   ( (Dry_Tissue_weight_g * (Shell_length_mm^-bLength.high))* # a
                                                                      (meanLength.all^bLength.high) ) * 100
                           ) # case when for pCO2 
                          ) # mutate
# pivot longer and plot 
F2_DrySomatic.bfactor.long <- F2_DrySomatic.bfactor %>% 
                              dplyr::select(-Shell_length_mm) %>% 
                              tidyr::pivot_longer(
                                cols = c(Dry_Tissue_weight_g, Somatic_bFactorLength.all, Somatic_bFactorLength.pCO2),
                                names_to = "measurement",
                                values_to = "value"
                              )
# means by replicate tank 
F2_DrySomatic.bfactor.long.MEANS <- F2_DrySomatic.bfactor.long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age))
# mmeans master - median for E-H as A-D!
F2_DrySomatic.bfactor.long.MEANS_master <- F2_DrySomatic.bfactor.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)
  
Somatic_bfactor.MeanSE <-ggplot(F2_DrySomatic.bfactor.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")


pdf("Output/DryWeights/F2/length_scaling/Dry_Somatic_byLength.pdf", height=8, width =8)
ggarrange(bfactorSomatic.Length.all, bfactorSomatic.Length.pCO2,Somatic_bfactor.MeanSE, nrow=3)
dev.off()


Somatic_final_plot <- F2_DrySomatic.bfactor.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% 'Somatic_bFactorLength.pCO2' & Age > 93) %>% 
                          ggplot(aes(x=factor(Age), y=value, colour=factor(pCO2)),stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Somatic: Length b factor pCO2", x ="Age (dpf)", y = "Dry Somatic (mg Lengthbfactor_all)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")
```

# Dry Somatic stats
```{r Somatic Stats raw - no standardization}

F2_DrySomatic.raw.MEAN <- F2_DrySomatic.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Dry_Tissue_weight_g')
F2_DrySomatic.raw.MEAN$DPvar    <- F2_DrySomatic.raw.MEAN$value
F2_DrySomatic.raw.MEAN$INDvar   <- F2_DrySomatic.raw.MEAN$pCO2
F2_DrySomatic.raw.MEAN$GROUPvar <- F2_DrySomatic.raw.MEAN$Age

Stats_SomaticMEAN_raw <- as.data.frame(runstats(F2_DrySomatic.raw.MEAN))
# About column
Stats_SomaticMEAN_raw$About <- paste0("Somatic: raw, NO BFACTOR + mean data")
```

```{r Mean Somatic Stats bfactor all - length standardized}

F2_DrySomatic.bfactor.MEAN <- F2_DrySomatic.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Somatic_bFactorLength.all')
F2_DrySomatic.bfactor.MEAN$DPvar    <- F2_DrySomatic.bfactor.MEAN$value
F2_DrySomatic.bfactor.MEAN$INDvar   <- F2_DrySomatic.bfactor.MEAN$pCO2
F2_DrySomatic.bfactor.MEAN$GROUPvar <- F2_DrySomatic.bfactor.MEAN$Age

Stats_SomaticMEAN_bfactor.all <- as.data.frame(runstats(F2_DrySomatic.bfactor.MEAN))
# About column
Stats_SomaticMEAN_bfactor.all$About <- paste0("Somatic: one bfactor + mean data")
```

```{r Mean Somatic Stats bfactor pCO2 - length standardized}

F2_DrySomatic.bfactor.MEAN <- F2_DrySomatic.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Somatic_bFactorLength.pCO2')
F2_DrySomatic.bfactor.MEAN$DPvar    <- F2_DrySomatic.bfactor.MEAN$value
F2_DrySomatic.bfactor.MEAN$INDvar   <- F2_DrySomatic.bfactor.MEAN$pCO2
F2_DrySomatic.bfactor.MEAN$GROUPvar <- F2_DrySomatic.bfactor.MEAN$Age

Stats_SomaticMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DrySomatic.bfactor.MEAN))
# About column
Stats_SomaticMEAN_bfactor.pCO2$About <- paste0("Somatic: two pCO2 bfactors + mean data")
```

```{r Dry Somatic output master stats} 

DrySomatic_stats_master <- do.call("rbind", 
                                          list(Stats_SomaticMEAN_bfactor.pCO2,
                                              Stats_SomaticMEAN_bfactor.all,
                                              Stats_SomaticMEAN_raw
                                              ))
write.csv(DrySomatic_stats_master, "Output/DryWeights/F2/F2_Somatic_DryWeight_ANOVA_table.csv")

```




# Total tissue weight: b factor calc and plot
```{r Total tissue b factor calc and plot}
# b factor for Shell? 
LogDryTissue <- F2_dryweights_long %>% 
                          dplyr::filter(measurement %in% c('Total_Dry_Tissue_g', 'Shell_length_mm')) %>%
                          # dplyr::group_by(measurement) %>% 
                          tidyr::pivot_wider(
                                              names_from = measurement,
                                              values_from = value
                          ) %>% 
                          # dplyr::select(-row) %>% 
                          dplyr::group_by(Age, pCO2, Tank_Replicate) %>%    
                          dplyr::mutate(log10_Tissue   = log10(Total_Dry_Tissue_g),
                                        log10_Length = log10(Shell_length_mm)) %>% 
                          na.omit() %>% # we only have shell for later life stage - omit rows without it
                          dplyr::filter(!log10_Tissue %in% '-Inf') # ommit instances when shell weight == 0

bfactorTissue.Length.pCO2 <- LogDryTissue %>% ggplot(aes(x=log10_Length, y=log10_Tissue, color = pCO2)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2")), size = 3) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Tissue; in g)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Total Tissue scaling: log10_Tissue = log10_a + 
                                      (b.factor * log10_Length)") +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") +
                             facet_wrap(~pCO2)


bfactorTissue.Length.all <- LogDryTissue %>% ggplot(aes(x=log10_Length, y=log10_Tissue)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2"))) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Tissue; in g") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Total tissue scaling: log10_Tissue = log10_a + 
                                      (b.factor * log10_Length)") +
                             geom_smooth(method = lm, color = 'red')# +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") 

# call dataset - omit data without Shell weights
F2_DryTissue <- F2_dryweights %>% 
    dplyr::select(Age, pCO2, Tank_Replicate, Total_Dry_Tissue_g, Shell_length_mm) %>% 
    na.omit()
# call the mean Shell dry weight
meanLength.all <- mean(F2_DryTissue$Shell_length_mm) # 32.88486
seLength.all   <- sd(F2_DryTissue$Shell_length_mm)/sqrt(length((F2_DryTissue$Shell_length_mm))) # 0.4762848

StandardShellSize = 40

# age range of animals 
print(paste0('youngest = ', min(F2_DryTissue$Age), '; oldest = ', max(F2_DryTissue$Age)))
#assign bfactors
bLength.all  <- 3.53#
bLength.low  <- 3.42#
bLength.mod  <- 3.65 #3
bLength.high <- 3.53#

# standardize Shell dry weight using bfactors
F2_DryTissue.bfactor <- F2_DryTissue %>% 
                          dplyr::mutate(
                           Tissue_bFactorLength.all  =  ( (Total_Dry_Tissue_g * (Shell_length_mm^-bLength.all))* # a
                                                                    (meanLength.all^bLength.all) ) * 100,
                           Tissue_bFactorLength.pCO2 =  case_when(pCO2 == '500 μatm' ~
                                                                   ( (Total_Dry_Tissue_g *
                                                                        (Shell_length_mm^-bLength.low))* # a
                                                                      (meanLength.all^bLength.low) ) * 100,
                                                                 pCO2 == '800 μatm' ~ 
                                                                   ( (Total_Dry_Tissue_g *
                                                                        (Shell_length_mm^-bLength.mod))* # a
                                                                      (meanLength.all^bLength.mod) ) * 100,
                                                                 pCO2 == '1200 μatm' ~ 
                                                                   ( (Total_Dry_Tissue_g *
                                                                        (Shell_length_mm^-bLength.high))* # a
                                                                      (meanLength.all^bLength.high) ) * 100
                           ) # case when for pCO2 
                          ) # mutate
# pivot longer and plot 
F2_DryTissue.bfactor.long <- F2_DryTissue.bfactor %>% 
                              dplyr::select(-Shell_length_mm) %>% 
                              tidyr::pivot_longer(
                                cols = c(Total_Dry_Tissue_g, Tissue_bFactorLength.all, Tissue_bFactorLength.pCO2),
                                names_to = "measurement",
                                values_to = "value"
                              )
# means by replicate tank 
F2_DryTissue.bfactor.long.MEANS <- F2_DryTissue.bfactor.long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age))
# mmeans master - median for E-H as A-D!
F2_DryTissue.bfactor.long.MEANS_master <- F2_DryTissue.bfactor.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)
  
Tissue_bfactor.MeanSE <-ggplot(F2_DryTissue.bfactor.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")


pdf("Output/DryWeights/F2/length_scaling/Dry_TotalTissue_byLength.pdf", height=8, width =8)
ggarrange(bfactorTissue.Length.all, bfactorTissue.Length.pCO2, Tissue_bfactor.MeanSE, nrow=3)
dev.off()

Tissue_final_plot <- F2_DryTissue.bfactor.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% 'Tissue_bFactorLength.pCO2' & Age > 93) %>% 
                          ggplot(aes(x=factor(Age), y=value, colour=factor(pCO2)),stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Tissue: Length b factor pCO2", x ="Age (dpf)", y = "Dry Tissue (mg Lengthbfactor_all)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")
```


# Dry Tissue stats
```{r Tissue Stats raw - no standardization}

F2_DryTissue.raw.MEAN <- F2_DryTissue.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Total_Dry_Tissue_g')
F2_DryTissue.raw.MEAN$DPvar    <- F2_DryTissue.raw.MEAN$value
F2_DryTissue.raw.MEAN$INDvar   <- F2_DryTissue.raw.MEAN$pCO2
F2_DryTissue.raw.MEAN$GROUPvar <- F2_DryTissue.raw.MEAN$Age

Stats_TissueMEAN_raw <- as.data.frame(runstats(F2_DryTissue.raw.MEAN))
# About column
Stats_TissueMEAN_raw$About <- paste0("Tissue: raw, NO BFACTOR + mean data")
```

```{r Mean Tissue Stats bfactor all - length standardized}

F2_DryTissue.bfactor.MEAN <- F2_DryTissue.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Tissue_bFactorLength.all')
F2_DryTissue.bfactor.MEAN$DPvar    <- F2_DryTissue.bfactor.MEAN$value
F2_DryTissue.bfactor.MEAN$INDvar   <- F2_DryTissue.bfactor.MEAN$pCO2
F2_DryTissue.bfactor.MEAN$GROUPvar <- F2_DryTissue.bfactor.MEAN$Age

Stats_TissueMEAN_bfactor.all <- as.data.frame(runstats(F2_DryTissue.bfactor.MEAN))
# About column
Stats_TissueMEAN_bfactor.all$About <- paste0("Tissue: one bfactor + mean data")
```

```{r Mean Tissue Stats bfactor pCO2 specific - length standardized}

F2_DryTissue.bfactor.MEAN <- F2_DryTissue.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Tissue_bFactorLength.pCO2')
F2_DryTissue.bfactor.MEAN$DPvar    <- F2_DryTissue.bfactor.MEAN$value
F2_DryTissue.bfactor.MEAN$INDvar   <- F2_DryTissue.bfactor.MEAN$pCO2
F2_DryTissue.bfactor.MEAN$GROUPvar <- F2_DryTissue.bfactor.MEAN$Age

Stats_TissueMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DryTissue.bfactor.MEAN))
# About column
Stats_TissueMEAN_bfactor.pCO2$About <- paste0("Tissue: two pCO2 bfactors + mean data")
```


```{r Dry Total Tissue output master stats} 

DryTissue_stats_master <- do.call("rbind", 
                                          list(Stats_TissueMEAN_bfactor.pCO2,
                                              Stats_TissueMEAN_bfactor.all,
                                              Stats_TissueMEAN_raw
                                              ))
write.csv(DryTissue_stats_master, "Output/DryWeights/F2/F2_Tissue_DryWeight_ANOVA_table.csv")

```













# Dry Shell: b factor calc and plot
```{r Shell b factor calc and plot}
library(ggpmisc)
# b factor for Shell? 
LogDryShellvShell <- F2_dryweights_long %>% 
                          dplyr::filter(measurement %in% c('Dry_Shell_weight_g', 'Shell_length_mm')) %>%
                          # dplyr::group_by(measurement) %>% 
                          tidyr::pivot_wider(
                                              names_from = measurement,
                                              values_from = value
                          ) %>% 
                          # dplyr::select(-row) %>% 
                          dplyr::group_by(Age, pCO2, Tank_Replicate) %>%    
                          dplyr::mutate(log10_Shell   = log10(Dry_Shell_weight_g),
                                        log10_Length = log10(Shell_length_mm)) %>% 
                          na.omit() %>% # we only have Shell for later life stage - omit rows without it
                          dplyr::filter(!log10_Shell %in% '-Inf') # ommit instances when Shell weight == 0

bfactorShell.Length.pCO2 <- LogDryShellvShell %>% 
                          ggplot(aes(x=log10_Length, y=log10_Shell, color = pCO2)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2")), size = 3) +
                          theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Shell; in g)") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Shell scaling: log10_Shell = log10_a + 
                                      (b.factor * log10_Length)") +
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") +
                             facet_wrap(~pCO2)


bfactorShell.Length.all <- LogDryShellvShell %>% ggplot(aes(x=log10_Length, y=log10_Shell)) +
                          geom_point() +
                          ggpmisc::stat_ma_line(method = "SMA") + # model 2 regression Standard major axis!
                          ggpmisc::stat_ma_eq(use_label(c("eq", "n", "R2"))) +
                          theme(panel.grid.major = element_blank(), 
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())) + 
                             scale_x_continuous(name ="log10_Length; in mm") +
                             scale_y_continuous(name ="log10_Shell; in g") +
                             theme_classic() +
                             theme(legend.position="none",axis.title.y=element_text(size=7)) +
                             ggtitle("Shell scaling: log10_Shell = log10_a + 
                                      (b.factor * log10_Length)") #+
                             # geom_smooth(method = lm, color = 'red') +
                             # ggpmisc::stat_poly_eq(parse=T, 
                             #                       aes(label = paste(..eq.label.., ..rr.label.., 
                             #                                       sep = "~~~")),
                             #                          label.x.npc = "left") 

# call dataset - omit data without Shell weights
F2_DryShell <- F2_dryweights %>% 
    dplyr::select(Age, pCO2, Tank_Replicate, Dry_Shell_weight_g, Shell_length_mm) %>% 
    na.omit()
# call the mean Shell dry weight
meanLength.all <- mean(F2_DryShell$Shell_length_mm) # 33.58173
seLength.all   <- sd(F2_DryShell$Shell_length_mm)/sqrt(length((F2_DryShell$Shell_length_mm))) # 0.4933574
# age range of animals 
print(paste0('youngest = ', min(F2_DryShell$Age), '; oldest = ', max(F2_DryShell$Age)))
#assign bfactors
bLength.all  <- 2.95#
bLength.low  <- 2.9#
bLength.mod  <- 2.93 #3
bLength.high <- 3.01#

# standardize Shell dry weight using bfactors
F2_DryShell.bfactor <- F2_DryShell %>% 
                          dplyr::mutate(
                           Shell_bFactorLength.all  =  ( (Dry_Shell_weight_g * (Shell_length_mm^-bLength.all))* # a
                                                                    (meanLength.all^bLength.all) ) * 100,
                           Shell_bFactorLength.pCO2 =  case_when(pCO2 == '500 μatm' ~
                                                                   ( (Dry_Shell_weight_g * (Shell_length_mm^-bLength.low))* # a
                                                                      (meanLength.all^bLength.low) ) * 100,
                                                                 pCO2 == '800 μatm' ~ 
                                                                   ( (Dry_Shell_weight_g * (Shell_length_mm^-bLength.mod))* # a
                                                                      (meanLength.all^bLength.mod) ) * 100,
                                                                 pCO2 == '1200 μatm' ~ 
                                                                   ( (Dry_Shell_weight_g * (Shell_length_mm^-bLength.high))* # a
                                                                      (meanLength.all^bLength.high) ) * 100
                           ) # case when for pCO2 
                          ) # mutate
# pivot longer and plot 
F2_DryShell.bfactor.long <- F2_DryShell.bfactor %>% 
                              dplyr::select(-Shell_length_mm) %>% 
                              tidyr::pivot_longer(
                                cols = c(Dry_Shell_weight_g, Shell_bFactorLength.all, Shell_bFactorLength.pCO2),
                                names_to = "measurement",
                                values_to = "value"
                              )
# means by replicate tank 
F2_DryShell.bfactor.long.MEANS <- F2_DryShell.bfactor.long %>% 
                                    summarySE(measurevar="value", 
                                               groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% 
                                    dplyr::arrange(as.numeric(Age))
# mmeans master - median for E-H as A-D!
F2_DryShell.bfactor.long.MEANS_master <- F2_DryShell.bfactor.long.MEANS %>%  # noew convert and resummarize by tank
                        # dplyr::mutate(Tank_Replicate = case_when(
                        #               Tank_Replicate == 'E' ~ 'A', #convert E to A
                        #               Tank_Replicate == 'F' ~ 'B', #convert F to B
                        #               Tank_Replicate == 'G' ~ 'C', #convert G to C
                        #               Tank_Replicate == 'H' ~ 'D', #convert H to D
                        #               .default = (as.character(Tank_Replicate)) # for cases A-D, keep em my mans
                        #             )) %>% 
                        summarySE(measurevar="value", 
                                  groupvars=c("Age","pCO2", "Tank_Replicate", "measurement")) %>% # summarize again
                        dplyr::arrange(as.numeric(Age), measurement, pCO2, Tank_Replicate)
  
Shell_bfactor.MeanSE <-ggplot(F2_DryShell.bfactor.long.MEANS_master,
                                 aes(x=factor(Age), 
                                     y=value, 
                                     colour=factor(pCO2)),
                                      stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                           geom_point(aes(colour = pCO2), 
                                            position = position_dodge2(width = 0.5)) + 
                           stat_summary(fun.y="mean", size = 0.8,
                                              position = position_dodge2(width = 0.5)) +
                           stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                              fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                              geom = 'errorbar', width = 0.25, size = 1,
                                              position = position_dodge2(width = 0.5)) + 
                           labs(title="Mean + SE data", 
                                                      x ="Age (dpf)", 
                                                      y = "value") +
                          # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                # axis.title.y=element_blank(),
                                # axis.title.x=element_blank(),
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none") +
                          facet_wrap(~measurement, scales = "free_y")


pdf("Output/DryWeights/F2/length_scaling/Dry_Shell_byLength.pdf", height=8, width =8)
ggarrange(bfactorShell.Length.all, bfactorShell.Length.pCO2,Shell_bfactor.MeanSE, nrow=3)
dev.off()


Shell_final_plot <- F2_DryShell.bfactor.long.MEANS_master %>% 
                          dplyr::filter(measurement %in% 'Shell_bFactorLength.pCO2' & Age > 93) %>% 
                          ggplot(aes(x=factor(Age), y=value, colour=factor(pCO2)),stat="identity") +
                             scale_colour_manual(breaks=c("500 μatm", "800 μatm", "1200 μatm"), 
                                             values=c("forestgreen","darkorange2", "purple")) +
                          stat_summary(fun.y="mean", size = 0.8,
                                        position = position_dodge2(width = 0.25)) +
                          stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                        fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                        geom = 'errorbar', width = 0.25, size = 1,
                                        position = position_dodge2(width = 0.5)) + 
                          labs(title="Shell: Length b factor pCO2", x ="Age (dpf)", 
                               y = "Dry Shell (mg Lengthbfactor_pCO2)") +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1),
                                axis.text=element_text(size=8),
                                plot.title = element_text(size=12),
                                legend.position="none")
```

# Dry Shell stats
* significantly different at 165 and 192 DPF (low and moderate > high) - still need to verify with posthoc emmeans
```{r Shell Stats raw - no standardization}

F2_DryShell.raw.MEAN <- F2_DryShell.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Dry_Shell_weight_g')
F2_DryShell.raw.MEAN$DPvar    <- F2_DryShell.raw.MEAN$value
F2_DryShell.raw.MEAN$INDvar   <- F2_DryShell.raw.MEAN$pCO2
F2_DryShell.raw.MEAN$GROUPvar <- F2_DryShell.raw.MEAN$Age

Stats_ShellMEAN_raw <- as.data.frame(runstats(F2_DryShell.raw.MEAN))
# About column
Stats_ShellMEAN_raw$About <- paste0("Shell: raw, NO BFACTOR + mean data")
```

```{r Mean Shell Stats bfactor all - length standardized}

F2_DryShell.bfactor.MEAN <- F2_DryShell.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Shell_bFactorLength.all')
F2_DryShell.bfactor.MEAN$DPvar    <- F2_DryShell.bfactor.MEAN$value
F2_DryShell.bfactor.MEAN$INDvar   <- F2_DryShell.bfactor.MEAN$pCO2
F2_DryShell.bfactor.MEAN$GROUPvar <- F2_DryShell.bfactor.MEAN$Age

Stats_ShellMEAN_bfactor.all <- as.data.frame(runstats(F2_DryShell.bfactor.MEAN))
# About column
Stats_ShellMEAN_bfactor.all$About <- paste0("Shell: one bfactor + mean data")
```

```{r Mean Shell Stats bfactor pCO2 specific - length standardized}

F2_DryShell.bfactor.MEAN <- F2_DryShell.bfactor.long.MEANS_master %>% 
                                dplyr::filter(measurement %in% 'Shell_bFactorLength.pCO2')
F2_DryShell.bfactor.MEAN$DPvar    <- F2_DryShell.bfactor.MEAN$value
F2_DryShell.bfactor.MEAN$INDvar   <- F2_DryShell.bfactor.MEAN$pCO2
F2_DryShell.bfactor.MEAN$GROUPvar <- F2_DryShell.bfactor.MEAN$Age

Stats_ShellMEAN_bfactor.pCO2 <- as.data.frame(runstats(F2_DryShell.bfactor.MEAN))
# About column
Stats_ShellMEAN_bfactor.pCO2$About <- paste0("Shell: two pCO2 b factors + mean data")
```


```{r Dry Somatic output master stats} 

DryShell_stats_master <- do.call("rbind", 
                                          list(Stats_ShellMEAN_bfactor.pCO2,
                                              Stats_ShellMEAN_bfactor.all,
                                              Stats_ShellMEAN_raw
                                              ))
write.csv(DryShell_stats_master, "Output/DryWeights/F2/F2_Shell_DryWeight_ANOVA_table.csv")

```


# Manuscript plot! 
* If we decide to go with the 'Two pCO2 bfactors data b factor'
then this is what we will use - in the above chunks I made a figure for each metric 
* NOTE: for shell weight, whole tissue and whole animal we have more timepoints, here we subset these to overlap with the 
full dissection of different compartments 
```{r Final Panel Plot}


pdf("Output/DryWeights/F2/DryWeights_bFactorLengthpCO2.pdf", height=7, width =10)
print(ggarrange(Gonad_final_plot, Adductor_final_plot,
               Somatic_final_plot, Tissue_final_plot,
               Shell_final_plot,
          ncol = 3, nrow = 2
          ))
dev.off()


```


































# (i) summary of data 

```{r dry weights, echo = FALSE}
F2_dryweights$Shell_length_mm <- as.numeric(F2_dryweights$Shell_length_mm)
F2_dryweights[!is.na(F2_dryweights$Shell_length_mm),] %>%  # ommit rows with NA for shell length - if not you get errors here
            summarySE(measurevar="Shell_length_mm", groupvars=c("Age","pCO2")) %>% 
            dplyr::arrange(Shell_length_mm)

F2_dryweights[!is.na(F2_dryweights$Shell_length_mm),] %>%  # ommit rows with NA for shell length - if not you get errors here
            summarySE(measurevar="Shell_length_mm", groupvars=c("Age","pCO2","Tank_Replicate")) %>% 
            dplyr::arrange(Shell_length_mm) %>% 
            dplyr::arrange(Age, pCO2, Tank_Replicate)

```


# (ii) plot data 

### Dry weights data

* raw data 

* normalized to shell size 

```{r, F1 dry shell weight master file}

# data - clean up the master file, calc length normalized weight for plotting
# select only necessary columns 
# filter for those with > 0 weight
# as numeric for plotting and stats

F2_dry_weights_master <- F2_dryweights %>% 
                              dplyr::select(c('Age','pH','Tank_Replicate', 'pCO2', # sample metadata
                                              'Shell_length_mm', # length to normalize
                                              'Dry_Shell_weight_g' , 'Dry_Tissue_weight_g', 
                                              'Dry_Gonad_weight_g', 'Dry_Muscle_weight_g')) %>% 
                              # dplyr::filter(!Shell_length_mm == 'MEASURE THIS') %>%  # check this row, omit for now
                              dplyr::filter(!Dry_Shell_weight_g < 0) %>%  # one sample with a negative value here,.. omit!
                              #na.omit() %>% 
                              dplyr::mutate(Dry_Shell_weight_g = as.numeric(Dry_Shell_weight_g)) %>% 
                              dplyr::mutate(Shell_length_mm = as.numeric(Shell_length_mm)) %>% 
            # NOTE: for F2s, we have data on 11/16 that was solely measured for dry tissue and dry shell weights. Tissue including the adductor and remaining somatic
            # however all data thereafter separates out gonad and muscle from remaining tissue (as the same 'tissue' columns on 11/16) thereafore we need 
            # do be diligent here to not confound these data comparisons - below I remedied this matter
                              dplyr::mutate(Dry_Somatic_weight_g = case_when(Age == 93 ~ Dry_Tissue_weight_g, # age 93 is "11/16/2022" - done above in prev cluster
                                                                            .default = Dry_Tissue_weight_g + Dry_Muscle_weight_g)) %>% # in all other cases add tissue and muscle
                              # length normalize all data
                              dplyr::mutate(Dry_Shell_weight_g_LENGTHnormalized    = Dry_Shell_weight_g/Shell_length_mm, # nromalized dry weights to length
                                            Dry_Somatic_weight_g_LENGTHnormalized  = Dry_Somatic_weight_g/Shell_length_mm,
                                            Dry_Gonad_weight_g_LENGTHnormalized    = Dry_Gonad_weight_g/Shell_length_mm,
                                            Dry_Muscle_weight_g_LENGTHnormalized   = Dry_Muscle_weight_g/Shell_length_mm) %>% 
                              dplyr::mutate(Prop_Gonad_weight = Dry_Gonad_weight_g_LENGTHnormalized /
                                                               (Dry_Gonad_weight_g_LENGTHnormalized + Dry_Somatic_weight_g_LENGTHnormalized))

```


# Raw dry shell weights 

```{r Figures - raw dry shell weigts}

# Not normalized to shell length
F2_dry_shell_Summ <-summarySE(F2_dry_weights_master, measurevar="Dry_Shell_weight_g", 
                              groupvars=c("Age", "pCO2"))
F2_dry_shell_Summ # print the summary table 


DryShellWeight_Boxplot <- F2_dry_weights_master %>% 
                          ggplot(aes(x=as.factor(Age), 
                                     y=Dry_Shell_weight_g, 
                                     color=as.factor(pCO2))) +
                          geom_boxplot(position=position_dodge(.8))+ 
                          geom_point(position=position_jitterdodge(0.8))+
                          scale_color_manual(values=c("forestgreen",
                                                      "darkorange2",
                                                      "purple3"))+
                          ggtitle("Raw Dry Shell Weights (g) - all data") +
                          theme_classic() +  
                          xlab("Age (dpf)") +
                         #xlab("Age (d)") +
                          theme(panel.grid.major = element_blank(),
                                panel.grid.minor = element_blank())+ 
                          scale_y_continuous(name ="Dry shell weight (g)")+
                          theme(text = element_text(size=10))
                          
DryShellWeight_MeanSE <- F2_dry_shell_Summ %>% 
                          ggplot(aes(x=as.factor(Age), 
                                     y=Dry_Shell_weight_g, 
                                     color=as.factor(pCO2))) +
                          geom_point(position=position_dodge(.5))+ 
                          scale_color_manual(values=c("forestgreen",
                                                      "darkorange2",
                                                      "purple3"))+
                          geom_errorbar(aes(ymin=Dry_Shell_weight_g-se, 
                                            ymax=Dry_Shell_weight_g+se), width=.2,
                                        position=position_dodge(.5))+
                          ggtitle("Raw Dry Shell Weights (g) - mean+-SE") +
                          theme_classic() +  
                          xlab("Age (dpf)") +
                         #xlab("Age (d)") +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank())+ 
                          scale_y_continuous(name ="Dry shell weight (g)")+
                          geom_line(stat = "identity", size=1.0)+
                          theme(text = element_text(size=10))

ggarrange(DryShellWeight_Boxplot, DryShellWeight_MeanSE, nrow=2)


```


#  NORMALIZED to shell length

```{r Figures - normalized to length dry shell weigts}



F2_dry_shell_NORM_Summ <- F2_dry_weights_master[!is.na(F2_dry_shell$Dry_Shell_weight_g_LENGTHnormalized),] %>% 
                            summarySE(measurevar="Dry_Shell_weight_g_LENGTHnormalized", 
                                      groupvars=c("Age", "pCO2" ,"Tank_Replicate"))
F2_dry_shell_NORM_Summ # print the summary table 

# points are the mean for each replicate tank 
DryShellWeight_NORM_Boxplot <- F2_dry_shell_NORM_Summ %>% 
                                ggplot(aes(x=as.factor(Age), 
                                           y=Dry_Shell_weight_g_LENGTHnormalized, 
                                           color=as.factor(pCO2))) +
                                geom_boxplot(position=position_dodge(.8))+ 
                                geom_point(position=position_jitterdodge(0.8))+
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("Length-normalized Dry Shell Weights (g) - all data") +
                                theme_classic() +  
                                xlab("Age (dpf)") +
                               #xlab("Age (d)") +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                scale_y_continuous(name ="Dry shell weight (g)")+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10))

# now take the means by Date pCO2  and tank and remove the tank group - means and st error by date and pCO2
F2_dry_shell_NORM_MEAN <- F2_dry_shell_NORM_Summ %>% 
                            summarySE(measurevar="Dry_Shell_weight_g_LENGTHnormalized", 
                                      groupvars=c("Age", "pCO2"))


DryShellWeight_NORM_MeanSE <- F2_dry_shell_NORM_MEAN %>% 
                                ggplot(aes(x=as.factor(Age), 
                                           y=Dry_Shell_weight_g_LENGTHnormalized, 
                                           color=as.factor(pCO2))) +
                                geom_point(position=position_dodge(.5))+ 
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                geom_errorbar(aes(ymin=Dry_Shell_weight_g_LENGTHnormalized-se, 
                                                  ymax=Dry_Shell_weight_g_LENGTHnormalized+se), 
                                              width=.2,
                                              position=position_dodge(.5))+
                                ggtitle("Length-normalized Dry Shell Weights (g) - mean+-SE") +
                                theme_classic() +  
                                xlab("Age (dpf)") +
                               #xlab("Age (d)") +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                scale_y_continuous(name ="Dry shell weight (g)")+
                                geom_line(stat = "identity", size=1.0)+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10)) 

ggarrange(DryShellWeight_NORM_Boxplot, DryShellWeight_NORM_MeanSE, nrow=2)


```


#  Shell weight by length association

```{r Figures - normalized to length dry shell weigts}
F2_DryShell_ShellLength_Regression <- F2_dry_weights_master %>%
                                dplyr::filter(!Shell_length_mm > 70) %>% 
                                ggplot(aes(x=Shell_length_mm, 
                                           y=Dry_Shell_weight_g, 
                                           color=as.factor(pCO2))) +
                                geom_point(position=position_dodge(.5))+ 
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("F2 (Age 93-295 DPF): Dry SHELL weights v. shell length") +
                                theme_classic() +  
                                xlab("Shell length (mm)") +
                               #xlab("Age (d)") +
                                scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                geom_smooth(method = "loess", se=TRUE)+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10))  +
                                scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) 



F2_DrySomatic_ShellLength_Regression <- F2_dry_weights_master %>%
                                dplyr::filter(!Shell_length_mm > 70) %>% 
                                ggplot(aes(x=Shell_length_mm, 
                                           y=Dry_Somatic_weight_g, 
                                           color=as.factor(pCO2))) +
                                geom_point(position=position_dodge(.5))+ 
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("F2 (Age 93-295 DPF): Dry SOMATIC weights v. shell length") +
                                theme_classic() +  
                                xlab("Shell length (mm)") +
                               #xlab("Age (d)") +
                                scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                geom_smooth(method = "loess", se=TRUE)+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10))  +
                                scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) 


F2_DryGonad_ShellLength_Regression <- F2_dry_weights_master %>%
                                dplyr::filter(!Shell_length_mm > 70) %>% 
                                ggplot(aes(x=Shell_length_mm, 
                                           y=Dry_Gonad_weight_g, 
                                           color=as.factor(pCO2))) +
                                geom_point(position=position_dodge(.5))+ 
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("F2 (Age 93-295 DPF): Dry GONAD weights v. shell length") +
                                theme_classic() +  
                                xlab("Shell length (mm)") +
                               #xlab("Age (d)") +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                scale_y_continuous(name ="Dry somatic tissue weight (g)")+
                                geom_smooth(method = "loess", se=TRUE)+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10)) +
                                scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) 


F2_Prop_ShellLength_Regression <- F2_dry_weights_master %>%
                                      dplyr::filter(!Shell_length_mm > 70) %>% 
                                      dplyr::filter(!Prop_Gonad_weight < 0) %>% 
                                      ggplot(aes(x=as.numeric(Shell_length_mm), 
                                                 y=as.numeric(Prop_Gonad_weight), 
                                                 color=as.factor(pCO2),
                                                 group=as.factor(pCO2))) +
                                      geom_point()+ 
                                      scale_color_manual(values=c("forestgreen",
                                                                  "darkorange2",
                                                                  "purple3"))+
                                      ggtitle("F2 (Age 93-295 DPF): Proportion gonad weight") +
                                      theme_classic() +  
                                      xlab("Shell length (mm)") +
                                     #xlab("Age (d)") +
                                      theme(panel.grid.major = element_blank(), 
                                            panel.grid.minor = element_blank())+ 
                                      scale_y_continuous(name ="Proportion dry gonad weight (% fraction)")+
                                      stat_smooth(method = 'nls', 
                                                  method.args = list(start = c(a=0.1, b=0.001)), 
                                                  formula = y~a*exp(b*x), colour = 'grey10', se = FALSE) +
                                      #geom_smooth(method = "lm", se=FALSE) +
                                      labs(color='pCO2 treatment') +
                                      theme(text = element_text(size=10)) +
                                      scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                      #10 % gonad tissue in individuals 7 mm smaller 
                                      geom_hline(yintercept = 0.1, color = "grey30", size = 1, linetype = "dashed", alpha = 0.5) +
                                      geom_vline(xintercept = 31, color = "purple3", size = 1, linetype = "dashed", alpha = 0.5) + 
                                      geom_vline(xintercept = 40, color = "forestgreen", size = 1, linetype = "dashed", alpha = 0.5) +
                                      # 15 % gonad tissue in individuals 10 mm smaller 
                                      geom_hline(yintercept = 0.2, color = "grey30", size = 1, linetype = "dotted", alpha = 0.5) +
                                      geom_vline(xintercept = 40, color = "purple3", size = 1, linetype = "dotted", alpha = 0.5) + 
                                      geom_vline(xintercept = 48, color = "forestgreen", size = 1, linetype = "dotted", alpha = 0.5) 
# F2_Prop_ShellLength_Regression

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/DryWeights/F2/F2_DryWeights.pdf"), width = 12, height = 8)
ggarrange(F2_DryShell_ShellLength_Regression, F2_DrySomatic_ShellLength_Regression, 
          F2_DryGonad_ShellLength_Regression, F2_Prop_ShellLength_Regression)
dev.off()
```


```{r}
# PORPORTION GONAD WEIGHT

F2_gonad_prop_summ <- F2_dry_weights_master[!is.na(F2_dry_weights_master$Prop_Gonad_weight),] %>% 
                            summarySE(measurevar="Prop_Gonad_weight", 
                                      groupvars=c("Age", "pCO2" ,"Tank_Replicate"))
F2_gonad_prop_summ # print the summary table 

# points are the mean for each replicate tank 
Prop_Gonad_Boxplot <- F2_gonad_prop_summ %>% 
                                ggplot(aes(x=as.factor(Age), 
                                           y=Prop_Gonad_weight, 
                                           color=as.factor(pCO2))) +
                                geom_boxplot(position=position_dodge(.8))+ 
                                geom_point(position=position_jitterdodge(0.8))+
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("F2 (Age 93-295 DPF): Proportion Gonad Weight") +
                                theme_classic() +  
                                xlab("Age (dpf)") +
                               #xlab("Age (d)") +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                scale_y_continuous(name ="Proportion gonad weight (g)")+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10))

F2_PropGonad_Regression <- F2_gonad_prop_summ %>%
                                ggplot(aes(x=as.factor(Age), 
                                           y=Prop_Gonad_weight, 
                                           color=as.factor(pCO2))) +
                                geom_point(position=position_dodge(.5))+ 
                                scale_color_manual(values=c("forestgreen",
                                                            "darkorange2",
                                                            "purple3"))+
                                ggtitle("F2 (Age 93-295 DPF):  Proportion Gonad Weight") +
                                theme_classic() +  
                                xlab("Age (dpf)") +
                               #xlab("Age (d)") +
                                theme(panel.grid.major = element_blank(), 
                                      panel.grid.minor = element_blank())+ 
                                scale_y_continuous(name ="Proportion gonad weight (g)")+
                                geom_smooth(method = "loess", se=FALSE)+
                                labs(color='pCO2 treatment') +
                                theme(text = element_text(size=10)) 

```