---
title: "F2_Scope_for_growth"
author: "Samuel Gurr"
date: "2023-03-18"
output: html_document
---

# F2s: scope for growth

-   **objective**: to merge all data for F2s in which standard metabolic rates (resp), excretion rates, and biodeposition were completed **on the same individual(s)!**

    -   Create 'F2_Master' file: merge together respiration, excretion and biodepsotion data by a unique identifier for the individual

        -   i.e. date \* pH_treatment \* replicate tank \* dry tissue weight (mg)

        -   Note! master file data are limited by the biodeposition runs - there's pleeenty of data for respiration and excretion in which biodeposition *was not* completed

        -   these 'master' data use allometric scaling (b factor and mean correction) via **tissue dry weight** since *all* individuals used for biodeposition were large enough to separate tissue from shell for drying

            -   important to state because the cumulative respiration and excretion data (both including individuals with and without biodeposition runs) is corrected via **shell length** applicable to all life stages, like those too small/fragile to obtatin accurate estimation of dry tissue

    -   Calculate scope for growth

    -   Plot data

    -   Run statistics

    -   (*Optional*) Adjust plots to emphasize significant effect(s)

### load packages and set directory for this markdown file

```{r setup}


library(devtools) # devtools::install_github # use devtools to instlal github link

# library(LoLinR) # install_github('colin-olito/LoLinR') # install LoLinR from github
library(dplyr)
library(lubridate)
library(rMR) 
library(dplyr)
library(stringr)
library(rlang)
library(ggplot2)
library(ggfortify)
library(DESeq2)
library(devtools)


# set wd
knitr::opts_knit$set(root.dir = 'C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/RAnalysis')
#knitr::opts_knit$set(root.dir = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis')


```

# (1) Create 'F2 Master' file

## Load biodeposition, respiration, and excretion data

```{r}

Biodeposition    <- read.csv("Output/Biodeposition/F2/F2_Biodeposition_master.csv", header = T)
nrow(Biodeposition) # 61

RespirationRates <- read.csv(file="Output/Respiration/F2/F2_RR_calc_master.csv", header=T)
nrow(RespirationRates) # 143
ExcretionRates   <- read.csv(file="Output/ExcretionRates/F2/F2_ExcretionRates_master.csv", header=T) %>% dplyr::filter(!Date %in% 20221116)
nrow(ExcretionRates) # 63


```

## Add minor adjustments to these files to assist merging

-   importantly, we adjust the excretion data for b factor normalization below, other datasets are already prepped with this correction
-   Note: : biodep does not have the columns to merge by including the Run, Vhamber_Tank, Replicate, etc. However... we can merge by the equal length and tissue dry weight in the RR dataset below! first we need to reformat a few things here
-   b factor TDW from use of all data in both F1 and F2
-   TDW correction to 1 g TDW (as opposed to a mean or median within the dataset)
    -   biodeposition.R and RR_calc scripts contain this correction, excretion corrects in the chunk below

```{r}

# biodep
Biodeposition_adj    <- Biodeposition %>% 
                          dplyr::select(-c(X, tank_ID.y)) %>% 
                          dplyr::rename(tank_ID = tank_ID.x) %>% 
                          dplyr::mutate(Date = format(strptime(Date, format = "%Y%m%d"), 
                                                      "%m/%d/%Y")) %>% # format to mm/dd/yyy as RR dataset
                          dplyr::mutate(Replicate = gsub("[^a-zA-Z]", "", tank_ID)) %>% # new replicate column - reflects RR dataset 
                          dplyr::rename(Dry_Tissue_weight = animal_dry_weight_g) %>% # change name to match RR
                          dplyr::rename(Length_mm = animal_length_mm) %>% # change name to match RR
                          dplyr::rename(pH = treatment) %>% # rename to match 
                          dplyr::select(-c(tank_ID, animal_number, initial_filter_weight_mg, 
                                           dry_filter_weight_mg,ash_filter_weight_mg, inclubation_time_hours)) %>% 
                          dplyr::mutate(Date = case_when(Date == "02/01/2023" ~ '1/31/2023',
                                                         Date == "02/24/2023" ~ '2/23/2023',
                                                         Date == "03/28/2023" ~ '3/27/2023')) %>% 
                          dplyr::select(-Length_mm) # lenngth is the exact same as the resp and Excretion data except diff sig figs and some missing
nrow(Biodeposition_adj) # nrow 61

# RR
RespirationRates_adj <- RespirationRates %>% 
                          dplyr::filter(Date %in% c('1/31/2023','2/23/2023', '3/27/2023')) %>% # , '3/27/2023'
                          dplyr::mutate(Replicate = 
                                        gsub("[^a-zA-Z]", "", Chamber_tank)) %>% # new replicate column - reflects RR dataset 
                          dplyr::select(c(Date, 
                                          Age,  
                                          pH, 
                                          pCO2,
                                          Replicate,
                                          Length_mm, 
                                          Dry_Tissue_weight,
                                          resp_umol_hr_bFactorNormTDW.MEAN_all,
                                          resp_umol_hr_bFactorNormTDW.MEAN_LvM,
                                          resp_umol_hr_bFactorNormTDW.MEAN_LvH)) %>% 
  
                          dplyr::rename(RR_umol_hr_bfactorTDW_all = 
                                          resp_umol_hr_bFactorNormTDW.MEAN_all,
                                        
                                        RR_umol_hr_bfactorTDW_LvM = 
                                          resp_umol_hr_bFactorNormTDW.MEAN_LvM,
                                        
                                        RR_umol_hr_bfactorTDW_LvH = 
                                          resp_umol_hr_bFactorNormTDW.MEAN_LvH,
                                        )  


RespirationRates_adj$Dry_Tissue_weight <- as.numeric(RespirationRates_adj$Dry_Tissue_weight)                     
nrow(RespirationRates_adj) # 63

# ER
# note - we will bfctor and mean corret for TDW)
# bTDW    <- 0.979 # FR_bfactor script using ALL F1 and F2 data!

ExcretionRates_adj  <- ExcretionRates  %>% 
                          dplyr::mutate(Date = format(strptime(Date, format = "%Y%m%d"), "%m/%d/%Y")) %>% # format to mm/dd/yyy as RR dataset
                          dplyr::mutate(Date = case_when(Date == "01/31/2023" ~ '1/31/2023',
                                                         Date == "02/23/2023" ~ '2/23/2023',
                                                         Date == "03/27/2023" ~ '3/27/2023',)) %>% 
                          # dplyr::mutate(ExcretionRate_mg_hr = ExcretionRate_ug_hr/1000) %>% 
                          # dplyr::rename(ExcretionRate_umol_hr = ExcretionRate_umol_hr) %>% 
                          # 
                          # dplyr::mutate(ExcretionRate_mg_hr_bFactorNormTDW = 
                          #                 (ExcretionRate_mg_hr)*((1/Dry_Tissue_weight)^bTDW)) %>% # TDW b factor - mg
                          # 
                          # dplyr::mutate(ExcretionRate_umol_hr_bFactorNormTDW = 
                          #                 (ExcretionRate_umol_hr)*((1/Dry_Tissue_weight)^bTDW)) %>% # TDW b factor - umol
                          # dplyr::mutate(Length_mm = as.numeric(Length_um / 1000)) %>% # Length_mm matched biodep and RR 
                          dplyr::select(c(Date, 
                                          pH, 
                                          Replicate, 
                                          # Chamber_tank,
                                          Length_mm,
                                          Dry_Tissue_weight,
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_all,
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_LvM,
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_LvH))  %>% 
  
                          dplyr::rename(ER_umol_hr_bfactorTDW_all = 
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_all,
                                        
                                        ER_umol_hr_bfactorTDW_LvM = 
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_LvM,
                                        
                                        ER_umol_hr_bfactorTDW_LvH = 
                                          ExcretionRate_umol_hr_bFactorNormTDW.MEAN_LvH,
                                        ) 
# sanity check before we merge
nrow(ExcretionRates_adj)          == (nrow(RespirationRates_adj)  + nrow(Biodeposition_adj)) / 2 # FLASE becuase there were 2 outliers removed for biodep
unique(ExcretionRates_adj$Date)   == unique(RespirationRates_adj$Date) # should be TRUE
unique(RespirationRates_adj$Date) ==  unique(Biodeposition_adj$Date)  # should be TRUE
```

### Unique identifier

-   Date \* pH \* dry tissue weight

```{r}

Biodeposition_adj$uniqueID <- paste(Biodeposition_adj$Date,
                                 Biodeposition_adj$pH,
                                 Biodeposition_adj$Dry_Tissue_weight, 
                                 sep = '_')

RespirationRates_adj$uniqueID <- paste(RespirationRates_adj$Date,
                             RespirationRates_adj$pH,
                             RespirationRates_adj$Dry_Tissue_weight, 
                             sep = '_')

ExcretionRates_adj$uniqueID <- paste(ExcretionRates_adj$Date,
                             ExcretionRates_adj$pH,
                             ExcretionRates_adj$Dry_Tissue_weight, 
                             sep = '_')
```

### Test the unique identifier before merging

```{r}
# subset the ER data removing all instances that contain the same unique identifier 
# returns nothing == we are good to merge!

# btwn RR and ER
nrow(subset(ExcretionRates_adj, 
       !(uniqueID %in% RespirationRates_adj$uniqueID))) # no discrepancies btwn files (yay!)

# now btwn RR and biodep
nrow(subset(RespirationRates_adj, 
            !(uniqueID %in% Biodeposition_adj$uniqueID))) #  2 discrepancies, these are the removed outliers from biodep
```

### Let's merge this thang!

```{r}

# merge RR and ER - check the number of rows == 42
RR_ER_merge <- merge(RespirationRates_adj,ExcretionRates_adj) %>% dplyr::select(!pCO2)
# ommitted pCO2 because biodep has the correct micro symbol and is merged below 
nrow(RR_ER_merge) # 63 - no rows lost! 

# merge this data with the biodep - adjust the columns to be our master file!
F2_Masterfile <- merge(RR_ER_merge, Biodeposition_adj, 
                    by = c('Date','uniqueID','Dry_Tissue_weight', 'Replicate', 'pH')) %>% 
                  dplyr::select(c(Date, 
                                  Age,
                                  pCO2,
                                  pH,
                                  Replicate,
                                  Length_mm,
                                  Dry_Tissue_weight,
                                  
                                  ER_umol_hr_bfactorTDW_all,
                                  RR_umol_hr_bfactorTDW_all,
                                  
                                  ER_umol_hr_bfactorTDW_LvM,
                                  RR_umol_hr_bfactorTDW_LvM,
                                  
                                  ER_umol_hr_bfactorTDW_LvH,
                                  RR_umol_hr_bfactorTDW_LvH,
                                  
                                  IER_correct,
                                  IRR_correct,
                                  OER_correct,
                                  ORR_correct,
                                  CR_correct,
                                  FR_correct,
                                  RR_correct,
                                  p,
                                  f,
                                  i,
                                  SE,
                                  AR,
                                  AE))
nrow(F2_Masterfile) # 61 rows as expected!!!!!
# View(F2_Masterfile)


```

### Write the file to output folder

```{r}

write.csv(F2_Masterfile, "Output/F2_RR_ER_Biodep_master.csv")
```

# Scope for growth calc

* Pousee et al. 
The bioenergetics status of a bivalve can be assessed by calculating the “scope for growth” (SFG, [15,16]). 
This estimator is based upon mathematical expressions that incorporate feeding functions such as clearance rate 
(CR, the volume of water totally filtered per time unit) and assimilation efficiency (AE, the fraction of organic matter consumed that is assimilated), 
and food availability to calculate the energy intake. Energy expenditures are estimated through respiration (RR) and excretion rates (ER) that are used 
to determine the catabolized energy. The subtraction of this catabolized energy from the energy intake is the SFG. 

(RR + ER) = energy expenditures
(RR + ER) = energy expenditures




RR was converted to oxygen-catabolized energy (R) using 14.0 J mg-1 O2, 
ER converted to U using 24.83 J mg-1 NH4-N [45]. 
The absorbed energy (A, J h-1) calculated as A = CR*AE*Δfood, with CR (L h-1) and AE (no unit) obtained from the biodeposition method and 
Δfood the energetic content of the food (J mg-1) obtained from Δfood = (0.632+0.086 (%C))×4.184, where %C was the organic matter of the seston
caloric value of dried phytoplankton = (0.632+0.086 *(%C)) where %C is the % of organic carbon 



## SFG or P = A - (R + U)

-   Widdows and Johnson 1988 " Physiological energetics of *Mytilus edulis*: Scope for Growth
-   **P** = production - estimated from the difference between the energy absorbed from the food and energy expenditure via respiration and excretion - referred to as Scope for Growth (SGF)
-   **A** = C x absorption efficiency
    -   C = Clearnace rate (l g-1 h-1) x POM (mg L-1) x 23 J mg-1 ash free dry weight
-   **R** = VO2 (ml O2 g-1 hr-1) x 20.33 J ml-1 O2
-   **U** = mg NH4 g-1 hr-1 x 19.4 J mg-1 NH4




```{r}

Biodep_blanks <- read.csv("Output/Biodeposition/Biodeposition_input_blank.csv", 
                          h=T, sep =",") %>% 
                            dplyr::filter(Date %in% c(20230201,20230224,20230328)) %>% 
                            dplyr::mutate(Date = case_when(Date == 20230201 ~ '1/31/2023',
                                                           Date == 20230224 ~ '2/23/2023',
                                                           Date == 20230328 ~ '3/27/2023')) %>% 
                            dplyr::select(c(Date,treatment,Perc_ORG_1)) %>% 
                            dplyr::rename(pH = treatment)
unique(Biodep_blanks$Date) # "1/31/2023" "2/23/2023" "3/27/2023"


nrow(F2_Masterfile) == nrow(merge(Biodep_blanks,F2_Masterfile, by = c("Date", "pH"))) # TRUE = YAY!

F2_Masterfile_2.0_all <- merge(Biodep_blanks,F2_Masterfile, by = c("Date", "pH")) %>% 
                dplyr::mutate(
                # RR
                RR_mgO2_hr_bfactorTDW = ((RR_umol_hr_bfactorTDW_all/1000)*32),# convert umol to mg O2
                RR_Joules_hr          = RR_mgO2_hr_bfactorTDW*14, # convert to joules
                # ER
                ExcretionRate_mgNH4_bFactorNormTDW =
                  ((ER_umol_hr_bfactorTDW_all/1000)*18.04), # convert umol to mg NH4
                
                ER_Joules_hr                       = ExcretionRate_mgNH4_bFactorNormTDW*24.83, # convert o Joules
                # caloric value of dried phytoplankton
                Food_Joules_mg = (0.632+0.086 *(Perc_ORG_1))*4.184, # caloric value of dried phytoplaknton following 
                #Pousee et al. -referenced paper below for calculation
                #Platt T, Irwin B. Caloric content of phytoplankton. Limnology and Oceanography. 1973;18(2)
                A_Joules_hr = (CR_correct*AE)*Food_Joules_mg,
                # FINALLY SCOPE FOR GROWTH YALL
                SFG = A_Joules_hr - (RR_Joules_hr + ER_Joules_hr)
  )
                
F2_Masterfile_2.0_LvM <- merge(Biodep_blanks,F2_Masterfile, by = c("Date", "pH")) %>% # 
                tidyr::drop_na(RR_umol_hr_bfactorTDW_LvM) %>% 
                dplyr::mutate(
                # RR RR_umol_hr_bfactorTDW_LvM
                RR_mgO2_hr_bfactorTDW = ((RR_umol_hr_bfactorTDW_LvM/1000)*32),# convert umol to mg O2
                RR_Joules_hr          = RR_mgO2_hr_bfactorTDW*14, # convert to joules
                # ER ER_umol_hr_bfactorTDW_LvM
                ExcretionRate_mgNH4_bFactorNormTDW =
                  ((ER_umol_hr_bfactorTDW_LvM/1000)*18.04), # convert umol to mg NH4
                
                ER_Joules_hr                       = ExcretionRate_mgNH4_bFactorNormTDW*24.83, # convert o Joules
                # caloric value of dried phytoplankton
                Food_Joules_mg = (0.632+0.086 *(Perc_ORG_1))*4.184, # caloric value of dried phytoplaknton following 
                #Pousee et al. -referenced paper below for calculation
                #Platt T, Irwin B. Caloric content of phytoplankton. Limnology and Oceanography. 1973;18(2)
                A_Joules_hr = (CR_correct*AE)*Food_Joules_mg,
                # FINALLY SCOPE FOR GROWTH YALL
                SFG = A_Joules_hr - (RR_Joules_hr + ER_Joules_hr)
  )
       

F2_Masterfile_2.0_LvH <- merge(Biodep_blanks,F2_Masterfile, by = c("Date", "pH")) %>% # 
                tidyr::drop_na(RR_umol_hr_bfactorTDW_LvH) %>% 
                dplyr::mutate(
                # RR RR_umol_hr_bfactorTDW_LvH
                RR_mgO2_hr_bfactorTDW = ((RR_umol_hr_bfactorTDW_LvH/1000)*32),# convert umol to mg O2
                RR_Joules_hr          = RR_mgO2_hr_bfactorTDW*14, # convert to joules
                # ER ER_umol_hr_bfactorTDW_LvH
                ExcretionRate_mgNH4_bFactorNormTDW =
                  ((ER_umol_hr_bfactorTDW_LvH/1000)*18.04), # convert umol to mg NH4
                
                ER_Joules_hr                       = ExcretionRate_mgNH4_bFactorNormTDW*24.83, # convert o Joules
                # caloric value of dried phytoplankton
                Food_Joules_mg = (0.632+0.086 *(Perc_ORG_1))*4.184, # caloric value of dried phytoplaknton following 
                #Pousee et al. -referenced paper below for calculation
                #Platt T, Irwin B. Caloric content of phytoplankton. Limnology and Oceanography. 1973;18(2)
                A_Joules_hr = (CR_correct*AE)*Food_Joules_mg,
                # FINALLY SCOPE FOR GROWTH YALL
                SFG = A_Joules_hr - (RR_Joules_hr + ER_Joules_hr)
  )

```

```{r, F2_Masterfile_2.0_all stats 1-31-23}

# stats
library(car)
F2_Masterfile_1_31_23 <- F2_Masterfile_2.0_all %>% dplyr::filter(Date %in% '1/31/2023')
SGFmod_131 <- aov(lm(SFG ~ pCO2 , data =F2_Masterfile_1_31_23 ))
shapiro.test(resid(SGFmod_131)) # 0.7896
leveneTest(SGFmod_131)# 0.1664
summary(SGFmod_131)
#             Df Sum Sq Mean Sq F value  Pr(>F)    
# pCO2         2  41072   20536   21.52 2.2e-05 ***
# Residuals   17  16226     954 

TukeyHSD(SGFmod_131)
# $pCO2
#                         diff       lwr      upr     p adj
# 500 μatm-1200 μatm  -3.92091 -80.53572  72.6939 0.9905478
# 800 μatm-1200 μatm  96.90813  20.29332 173.5229 0.0125474
# 800 μatm-500 μatm  100.82904  27.21991 174.4382 0.0071161

SGFmod_131.tukey <- emmeans::emmeans(object = SGFmod_131, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
SGFmod_131.tukey.letters   <- multcomp::cld(object = SGFmod_131.tukey$emmeans, Letters = letters) # letter display\
 # pCO2      emmean   SE df lower.CL upper.CL .group
 # 500 μatm     140 20.3 17     97.5      183  a    
 # 1200 μatm    144 21.9 17     98.0      190  a    
 # 800 μatm     241 20.3 17    198.4      284   b   
```


```{r, F2_Masterfile_2.0_all stats 2-23-23}

F2_Masterfile_2_23_23 <- F2_Masterfile_2.0_all %>% dplyr::filter(Date %in% '2/23/2023')
SGFmod_223 <- aov(lm(SFG ~ pCO2 , data =F2_Masterfile_2_23_23 ))
shapiro.test(resid(SGFmod_223)) # 0.6276
leveneTest(SGFmod_223)# 0.244
summary(SGFmod_223)
#             Df Sum Sq Mean Sq F value  Pr(>F)   
# pCO2         2   5991  2995.7    7.92 0.00371 **
# Residuals   17   6431   378.3 
# TukeyHSD(SGFmod_223)
# $pCO2
#                         diff       lwr       upr     p adj
# 500 μatm-1200 μatm -31.47811 -59.23644 -3.719785 0.0251343
# 800 μatm-1200 μatm  10.23495 -16.43438 36.904290 0.5961931
# 800 μatm-500 μatm   41.71306  13.95474 69.471390 0.0034461
SGFmod_223.tukey <- emmeans::emmeans(object = SGFmod_223, # run tukey
                                    pairwise ~ "pCO2",
                                    adjust = "tukey")
SGFmod_223.tukey.letters   <- multcomp::cld(object = SGFmod_223.tukey$emmeans, Letters = letters) # letter display\
 # pCO2      emmean   SE df lower.CL upper.CL .group
 # 500 μatm    1.08 7.94 17    -15.7     17.8  a    
 # 1200 μatm  32.56 7.35 17     17.0     48.1   b   
 # 800 μatm   42.79 7.35 17     27.3     58.3   b   
```


```{r, stats 3-27-23}

F2_Masterfile_3_27_23 <- F2_Masterfile_2.0_all %>% dplyr::filter(Date %in% '3/27/2023')
SGFmod_327 <- aov(lm(SFG ~ pCO2 , data =F2_Masterfile_3_27_23 ))
shapiro.test(resid(SGFmod_327)) # 0.1604
leveneTest(SGFmod_327)# 0.005288 **
SGFmod_327_KW <- kruskal.test(SFG ~ pCO2, data =F2_Masterfile_3_27_23)
# ?kruskal.test
# Kruskal-Wallis chi-squared = 6.4526, df = 2, p-value = 0.0397
library(FSA)
dunnTest(SFG ~ pCO2, data =F2_Masterfile_3_27_23)
# 1200 μatm - 500 μatm	1.5438267	0.12263033	0.24526065	
# 1200 μatm - 800 μatm	-0.9233805	0.35580894	0.35580894	
# 500 μatm - 800 μatm	-2.5020639	0.01234716	0.03704149	**

```


```{r plotting - all treatments}


F2_Masterfile_2.0_all$pCO2 <- factor(F2_Masterfile_2.0_all$pCO2, levels= c('500 μatm','800 μatm','1200 μatm'))

F2_SGF_Means_by_tank <- F2_Masterfile_2.0_all %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2", "Replicate"))

SFG_Pousse_F2       <- ggplot(data=F2_SGF_Means_by_tank, aes(x=pCO2, y=SFG, colour=pCO2)) +
                        scale_colour_manual(values=c("forestgreen","orange", "purple"))+
                        theme_classic() +  
                        geom_boxplot(fill="white", 
                                     outlier.colour=NA, 
                                     position=position_dodge(width=0.9)) +
                        geom_point(position=position_jitterdodge()) +
                        theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                        labs(title="F2 Bay Scallops: Scope for Growth ", x ="Month", y = "Scope for Growth") + 
                        facet_wrap(~Age)

# convert meand by tank to summrizing means by treatment and age 

F2_SGF_Means_plotting <- F2_SGF_Means_by_tank %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2"))

F2_SGF_MeanSE <-  F2_SGF_Means_plotting %>%
                                 ggplot(aes(x=(as.factor(Age)), 
                                               y=SFG, 
                                               color=as.factor(pCO2))) +
                                    geom_point(position=position_dodge(.5))+ 
                                    scale_color_manual(values=c("forestgreen",
                                                                "darkorange2",
                                                                "purple"))+
                                    geom_errorbar(aes(ymin=SFG-se, 
                                                      ymax=SFG+se), width=.2,
                                                  position=position_dodge(.5)) +
                                    ggtitle("SFG (mean+-SE)") +
                                    theme_classic() +  
                                    xlab("Age (dpf)") +
                                    ylab("SFG") +
                                   #xlab("Age (d)") +
                                    theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                                    # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                    # labs(color='pCO2 treatment') + # legend name
                                    theme(text = element_text(size=10))


pdf("Output/F2_SFG_all_treatments.pdf", width = 6, height = 8)
print(ggpubr::ggarrange(SFG_Pousse_F2,F2_SGF_MeanSE,nrow=2))
dev.off()
```

```{r plotting - L v M}


F2_Masterfile_2.0_LvM$pCO2 <- factor(F2_Masterfile_2.0_LvM$pCO2, levels= c('500 μatm','800 μatm'))

F2_SGF_Means_by_tank_LvM <- F2_Masterfile_2.0_LvM %>% 
                            dplyr::filter(!SFG < 0) %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2", "Replicate"))

SFG_Pousse_F2       <- ggplot(data=F2_SGF_Means_by_tank_LvM, aes(x=pCO2, y=SFG, colour=pCO2)) +
                        scale_colour_manual(values=c("forestgreen","orange"))+
                        theme_classic() +  
                        geom_boxplot(fill="white", 
                                     outlier.colour=NA, 
                                     position=position_dodge(width=0.9)) +
                        geom_point(position=position_jitterdodge()) +
                        theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                        labs(title="F2 Bay Scallops: Scope for Growth ", x ="Month", y = "Scope for Growth") + 
                        facet_wrap(~Age)

# convert meand by tank to summrizing means by treatment and age 

F2_SGF_Means_plotting_LvM <- F2_SGF_Means_by_tank_LvM %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2"))

F2_SGF_MeanSE <-  F2_SGF_Means_plotting_LvM %>%
                                 ggplot(aes(x=(as.factor(Age)), 
                                               y=SFG, 
                                               color=as.factor(pCO2))) +
                                    geom_point(position=position_dodge(.5))+ 
                                    scale_color_manual(values=c("forestgreen",
                                                                "darkorange2"))+
                                    geom_errorbar(aes(ymin=SFG-se, 
                                                      ymax=SFG+se), width=.2,
                                                  position=position_dodge(.5)) +
                                    ggtitle("SFG (mean+-SE)") +
                                    theme_classic() +  
                                    xlab("Age (dpf)") +
                                    ylab("SFG") +
                                   #xlab("Age (d)") +
                                    theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                                    # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                    # labs(color='pCO2 treatment') + # legend name
                                    theme(text = element_text(size=10))


pdf("Output/F2_SFG_LvM.pdf", width = 6, height = 8)
print(ggpubr::ggarrange(SFG_Pousse_F2,F2_SGF_MeanSE,nrow=2))
dev.off()
```


```{r plotting - L v H}


F2_Masterfile_2.0_LvH$pCO2 <- factor(F2_Masterfile_2.0_LvH$pCO2, levels= c('500 μatm','1200 μatm'))

F2_SGF_Means_by_tank_LvH <- F2_Masterfile_2.0_LvH %>% 
                            dplyr::filter(!SFG < 0) %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2", "Replicate")) 

SFG_Pousse_F2       <- ggplot(data=F2_SGF_Means_by_tank_LvH, aes(x=pCO2, y=SFG, colour=pCO2)) +
                        scale_colour_manual(values=c("forestgreen","purple"))+
                        theme_classic() +  
                        geom_boxplot(fill="white", 
                                     outlier.colour=NA, 
                                     position=position_dodge(width=0.9)) +
                        geom_point(position=position_jitterdodge()) +
                        theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                        labs(title="F2 Bay Scallops: Scope for Growth ", x ="Month", y = "Scope for Growth") + 
                        facet_wrap(~Age)

# convert meand by tank to summrizing means by treatment and age 

F2_SGF_Means_plotting <- F2_SGF_Means_by_tank_LvH %>% 
                            Rmisc::summarySE(measurevar="SFG", 
                                      groupvars=c("Age", "pCO2"))

F2_SGF_MeanSE <-  F2_SGF_Means_plotting %>%
                                 ggplot(aes(x=(as.factor(Age)), 
                                               y=SFG, 
                                               color=as.factor(pCO2))) +
                                    geom_point(position=position_dodge(.5))+ 
                                    scale_color_manual(values=c("forestgreen",
                                                                "purple"))+
                                    geom_errorbar(aes(ymin=SFG-se, 
                                                      ymax=SFG+se), width=.2,
                                                  position=position_dodge(.5)) +
                                    ggtitle("SFG (mean+-SE)") +
                                    theme_classic() +  
                                    xlab("Age (dpf)") +
                                    ylab("SFG") +
                                   #xlab("Age (d)") +
                                    theme(panel.grid.major = element_blank(), 
                                          panel.grid.minor = element_blank(),
                                          legend.position="none")+ 
                                    # scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
                                    # labs(color='pCO2 treatment') + # legend name
                                    theme(text = element_text(size=10))


pdf("Output/F2_SFG_LvH.pdf", width = 6, height = 8)
print(ggpubr::ggarrange(SFG_Pousse_F2,F2_SGF_MeanSE,nrow=2))
dev.off()
```

#### Runttest 

* why? we may have separate manuscript for Lo v M and Low v H, in this case
we need to run two sample t tests, and when not 
meeting assumptions,the wilkcox ranksum 

```{r run_ttest}


run_ttest <- function(datafilename,  outputfilename) {
            # variables for both for loops
            DF_loop           <- data.frame(matrix(nrow = 1, ncol = 12)) # create dataframe to save during for loop
            colnames(DF_loop) <- c('Age_DPF', 'model', 'ShapiroWilk', 'ResidNorm', 'Variance', 
                                   'HomogVar', 'DF.num' , 'DF.denom', 
                                   'Tstat','P_val', 'SigDif') # names for comuns in the for loop
            
            unique(datafilename$Age)
            outputfilename <- data.frame()

            
            for (i in 1:length(unique(datafilename$Age))) {
              GROUPvar_loop <- unique(datafilename$GROUPvar)[i]
              Data_all      <- datafilename %>% dplyr::filter(GROUPvar %in% GROUPvar_loop)
              # Data_mean   <- Data_all %>% summarySE(measurevar="DPvar", 
              #                                       groupvars=c("group1","Tank_Replicate", "INDvar")) 
              
            # run assumptions 
            # normality of data 
            normality_A <- (Data_all %>% 
                                  group_by(as.factor(INDvar)) %>% 
                                  rstatix::shapiro_test(DPvar))$p[1]
            
            normality_B <- (Data_all %>% 
                                  group_by(as.factor(INDvar)) %>% 
                                  rstatix::shapiro_test(DPvar))$p[2]
            
            # equal variance 
            variance <- (Data_all %>% rstatix::levene_test(DPvar ~ as.factor(INDvar)))$p[1]
            
            # run all modles
            Ttestmod.eqvar      <- t.test(Data_all$DPvar ~ (as.factor(Data_all$INDvar)), 
                                           alternative = "greater",
                                           var.equal = TRUE)
            
            Ttestmod.noneqvar   <- t.test(Data_all$DPvar ~ (as.factor(Data_all$INDvar)),
                                           alternative = "greater",
                                           var.equal = FALSE)
            
            Wilcoxmod           <- wilcox.test(Data_all$DPvar ~ 
                                                 as.numeric(as.factor(Data_all$INDvar)))
            
            # normality tests for the anova model - asign 
            DF_loop$ShapiroWilk <- paste0(normality_A, '; ',normality_B)
            
            DF_loop$ResidNorm   <- if(normality_A > 0.05 & normality_B > 0.05) {
              'YES'} else {'NO'}
            
            DF_loop$Variance     <- variance
            
            DF_loop$HomogVar    <- if( variance > 0.05) {
              'YES'} else {'NO'}
            
            if(normality_A > 0.05 & normality_B > 0.05 & variance > 0.05) {
                DF_loop$model       <- 'Welchs T test, equal variance'
                DF_loop$DF.num      <- map_df(list(Ttestmod.eqvar), tidy)$parameter[[1]]
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Ttestmod.eqvar), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Ttestmod.eqvar), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Ttestmod.eqvar), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}
        
              } else if (normality_A > 0.05 & normality_B > 0.05 & variance < 0.05) {
                DF_loop$model       <- 'Welchs T test, non-equal variance'
                DF_loop$DF.num      <- map_df(list(Ttestmod.noneqvar), tidy)$parameter[[1]]
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Ttestmod.noneqvar), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Ttestmod.noneqvar), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Ttestmod.noneqvar), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}
              } else {
                DF_loop$model       <- 'Wilcoxon rank sum exact test'
                DF_loop$DF.num      <- 'NA'
                DF_loop$DF.denom    <- 'NA'
                DF_loop$Tstat       <- map_df(list(Wilcoxmod), tidy)$statistic[[1]]
                DF_loop$P_val       <- map_df(list(Wilcoxmod), tidy)$p.value[[1]]
                DF_loop$SigDif      <- if( (map_df(list(Wilcoxmod), tidy)$p.value[[1]]) > 0.05) {
                  'NO'} else {'YES'}            
              }
                  DF_loop$Age_DPF     <- GROUPvar_loop
                  # asign loop and cumulative output table
                  df                        <- data.frame(DF_loop) # name dataframe for this single row
                  outputfilename <- rbind(outputfilename,DF_loop) #bind to a cumulative list dataframe
                  # print(outputfilename) # print to monitor progress
                  
                }
return(outputfilename)
}


```


```{r Low v Moderate execuate runttest for stats}

# Run the full model NOTE that temperature WAS THE SMAE ACROSS ALL SFG MEASUREMENTS so this has SOUND RATIONALE
# considering that temperature largely affects metabolism and therefore scope for growth 

library(rcompanion)
library(FSA)
F2_SGF_Means_by_tank_LvM$Age <- as.factor(F2_SGF_Means_by_tank_LvM$Age)
TwoWayANOVA_LvM <- lm(SFG ~ pCO2 * Age, data = F2_SGF_Means_by_tank_LvM)
shapiro.test(resid(TwoWayANOVA_LvM)) # 0.0339 no pass 
leveneTest(TwoWayANOVA_LvM) # 0.002765   ** no pass

scheirerRayHare(SFG ~ pCO2 * Age, data = F2_SGF_Means_by_tank_LvM)
#           Df  Sum Sq       H p.value
# pCO2       1  740.07  8.9525 0.00277
# Age        2 1057.06 12.7870 0.00167
# pCO2:Age   2   12.14  0.1468 0.92922
# Residuals 25  843.43   
SRH_LvM_Age = dunnTest(SFG ~ Age,
              data = F2_SGF_Means_by_tank_LvM,
              method="bh")      # Adjusts p-values for multiple comparisons;
SRH_LvM_Age
# 167 - 190	3.270772	0.001072545	0.003217634	
# 167 - 222	1.927726	0.053889168	0.080833752	
# 190 - 222	-1.533010	0.125273273	0.125273273		

# measure effects of OA binary within date (ttest wilcox if needed)
library(purrr)
library(rstatix)
library(tidyverse)
F2_SGF_Means_by_tank_LvM$GROUPvar <- F2_SGF_Means_by_tank_LvM$Age 
F2_SGF_Means_by_tank_LvM$DPvar    <- F2_SGF_Means_by_tank_LvM$SFG 
F2_SGF_Means_by_tank_LvM$INDvar   <- F2_SGF_Means_by_tank_LvM$pCO2 


as.data.frame(run_ttest(F2_SGF_Means_by_tank_LvM))

write.csv( 
          as.data.frame(run_ttest(F2_SGF_Means_by_tank_LvM)),
          "Output/F2_SFG_Ttests_LOWvMOD.csv"
         )


F2_SGF_Means_by_tank_LvH$GROUPvar <- as.factor(F2_SGF_Means_by_tank_LvH$Age) 
F2_SGF_Means_by_tank_LvH$DPvar    <- F2_SGF_Means_by_tank_LvH$SFG 
F2_SGF_Means_by_tank_LvH$INDvar   <- F2_SGF_Means_by_tank_LvH$pCO2 


as.data.frame(run_ttest(F2_Masterfile_2.0_LvH))

write.csv( 
          as.data.frame(run_ttest(F2_Masterfile_2.0_LvH)),
          "Output/F2_SFG_Ttests_LOWvHIGH.csv"
         )


```
