---
title: "DESeq2"
author: "Samuel Gurr"
date: "2023-02-13"
output: pdf_document
---


## Setup: 

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      cache = TRUE)

knitr::opts_knit$set(root.dir = "~/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis")


```

#### Load libraries

```{r load_libraries, include = TRUE}
# load libraries - notes show the install command needed to install (pre installed)
library(DESeq2) # note: this was previously installed with the command `BiocManager::install("DESeq2")`
library(edgeR)
library(goseq)
library(dplyr)
library(GenomicFeatures)
library(data.table)
library(calibrate)
library(affycoretools) # note: this was previously installed with the BiocManager::install("affycoretools")
library(data.table)
library(vsn)
# Plotting
library(ggplot2)
library(cowplot)
library(pheatmap)
library(gplots)
library(RColorBrewer)
library(EnhancedVolcano)  # note: this was previously installed with the command `BiocManager::install("EnhancedVolcano")`
library(pcaExplorer) # note: this was previously installed with the command `BiocManager::install("pcaExplorer")
library(ggpubr)
library(stringr)
```

#### Set path

```{r set the path out, include = TRUE}
path_out = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Transcriptomics/DESeq2'
```





# LOAD DATA: choose ONE of the counts clusters (filtered raw reads or unfiltered raw reads)



### Gene count data - convert to matrix - NOTE ONLY RUN ONE (FILTERED  versus UNFILTERED)
I include both filtered and unfiltered here to compare the results. 
DESEq2 mentions that pre-filtering is not necessary however will reduce the memory/time to run dds and rlog of the models 
Below are both RAW counts filtered and unfiltered to run DESeq2 

# FILTERED COUNTS:  3 CPM (with edgeR) and 50% of samples 
```{r call the count matrices, include = TRUE}
getwd()
# gather the 3CPM filtered read matrices 
All_filtered_counts <-
  read.csv(file="../../Output/Transcriptomics/Filtered_counts_matrix/filtered_3cpm50perc.csv", 
                                               sep=',', 
                                               header=TRUE)  %>% 
  dplyr::rename(transcript_id = X) %>% 
  tibble::column_to_rownames(var = "transcript_id") %>% 
  as.matrix()  

F1_filtered_counts <-
  read.csv(file="../../Output/Transcriptomics/Filtered_counts_matrix/F1_filtered_3cpm50perc.csv", 
                                               sep=',', 
                                               header=TRUE)  %>% 
  dplyr::rename(transcript_id = X) %>% 
  tibble::column_to_rownames(var = "transcript_id") %>% 
  as.matrix() 


F2_filtered_counts <-
  read.csv(file="../../Output/Transcriptomics/Filtered_counts_matrix/F2_filtered_3cpm50perc.csv", 
                                               sep=',', 
                                               header=TRUE)   %>% 
  dplyr::rename(transcript_id = X) %>% 
  tibble::column_to_rownames(var = "transcript_id") %>% 
  as.matrix() 
                      
           
```



### Sample metadata - Experimental treatments/groups
```{r experiment_data, include = TRUE}
### experiment metadata [from Count_Matrix_Stats.Filter.R]  - convert characaters to factors for DESeq2
exp_data  <- read.csv(file="../../Data/Transcriptomics/exp.metadata.csv", sep=',', header=TRUE)
```



### Design DESeqDatasets - All - F1s - F2s
```{r build_dds_datasets}
# ========================================================== 
#  FULL MODEL ==  design = ~ pCO2
# ========================================================== #
#####
Exp.metadata       <- exp_data %>% 
                      dplyr::select(c('SampleName_readmatrix', 'pCO2')) %>% 
                      dplyr::rename(Sample.Name = SampleName_readmatrix) %>% # coondense dataset to build target matrix
                      dplyr::filter(Sample.Name %in% colnames(All_filtered_counts))
Exp.metadata.df    <- data.frame(Exp.metadata[,-1], row.names=Exp.metadata[,1]) # move Sample.Name column as row names  
Exp.metadata.mtx   <- as.matrix(Exp.metadata.df, row.names="BayScallop.ID") # create matrix 

# check for 'TRUE' in each - check before proceeding  design
Exp.metadata.mtx_2 <- as.data.frame(Exp.metadata.mtx[match(colnames(All_filtered_counts),rownames(Exp.metadata.mtx)), ]) %>% dplyr::rename(pCO2 = 1)
all(rownames(Exp.metadata.mtx_2) %in% colnames(All_filtered_counts)) # should be TRUE
all(rownames(Exp.metadata.mtx_2) == colnames(All_filtered_counts)) # should be TRUE

# build dds
dds <- DESeqDataSetFromMatrix(countData = All_filtered_counts,
                                      colData = Exp.metadata.mtx_2,
                                      design = ~pCO2) # DESeq Data Set (dds) - design as ~Primary_Treatment

# ========================================================== 
#  F1s ONLY ==  design = ~ pCO2
# ========================================================== #

Exp.metadata_F1       <- exp_data %>% 
                      dplyr::filter(Date %in% 20211027) %>% 
                      dplyr::select(c('SampleName_readmatrix', 'pCO2')) %>% 
                      dplyr::rename(Sample.Name = SampleName_readmatrix) %>% # coondense dataset to build target matrix
                      dplyr::filter(Sample.Name %in% colnames(F1_filtered_counts))
Exp.metadata_F1.df    <- data.frame(Exp.metadata_F1[,-1], row.names=Exp.metadata_F1[,1]) # move Sample.Name column as row names  
Exp.metadata_F1.mtx   <- as.matrix(Exp.metadata_F1.df, row.names="BayScallop.ID") # create matrix 

# check for 'TRUE' in each - check before proceeding  design
Exp.metadata_F1.mtx_2 <- as.data.frame(Exp.metadata_F1.mtx[match(colnames(F1_filtered_counts),
                                                                 rownames(Exp.metadata_F1.mtx)), ]) %>%
                          dplyr::rename(pCO2 = 1)
all(rownames(Exp.metadata_F1.mtx_2) %in% colnames(F1_filtered_counts)) # should be TRUE
all(rownames(Exp.metadata_F1.mtx_2) == colnames(F1_filtered_counts)) # should be TRUE

# build dds
dds_F1 <- DESeqDataSetFromMatrix(countData = F1_filtered_counts,
                                      colData = Exp.metadata_F1.mtx_2,
                                      design = ~pCO2) # DESeq Data Set (dds) - design as ~Primary_Treatment

# ========================================================== 
#  F2s ONLY ==  design = ~ pCO2
# ========================================================== #

Exp.metadata_F2       <- exp_data %>% 
                      dplyr::select(c('SampleName_readmatrix', 'pCO2')) %>% 
                      dplyr::rename(Sample.Name = SampleName_readmatrix) %>% # coondense dataset to build target matrix
                      dplyr::filter(Sample.Name %in% colnames(F2_filtered_counts))
Exp.metadata_F2.df    <- data.frame(Exp.metadata_F2[,-1], row.names=Exp.metadata_F2[,1]) # move Sample.Name column as row names  
Exp.metadata_F2.mtx   <- as.matrix(Exp.metadata_F2.df, row.names="BayScallop.ID") # create matrix 

# check for 'TRUE' in each - check before proceeding  design
Exp.metadata_F2.mtx_2 <- as.data.frame(Exp.metadata_F2.mtx[match(colnames(F2_filtered_counts),
                                                                 rownames(Exp.metadata_F2.mtx)), ]) %>% 
                          dplyr::rename(pCO2 = 1)
all(rownames(Exp.metadata_F2.mtx_2) %in% colnames(F2_filtered_counts)) # should be TRUE
all(rownames(Exp.metadata_F2.mtx_2) == colnames(F2_filtered_counts)) # should be TRUE

# build dds
dds_F2 <- DESeqDataSetFromMatrix(countData = F2_filtered_counts,
                                      colData = Exp.metadata_F2.mtx_2,
                                      design = ~pCO2) # DESeq Data Set (dds) - design as ~Primary_Treatment

```

### run DESeq model - All - F1s - F2s
```{r, Run DESeq}
dds.run_all <- DESeq(dds) # wait for this to complete.... ALL data not parsed by generation, not very useful
dds.run_F1  <- DESeq(dds_F1) # data for just F1s
dds.run_F2  <- DESeq(dds_F2) # data for just F2s
```

## Transform Exp data 

* Why?
 - the transformed data can be used to run simple PCA 
 - identify whether samples appear as outliers sufficient for omission and rerun dds.run

```{r expression data transformation}

# vstExp  :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
vstExp     <- vst(dds.run_all)
vstExp_F1  <- vst(dds.run_F1)
vstExp_F2  <- vst(dds.run_F2)

# rlog  :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
rlogExp     <- rlogTransformation(dds.run_all)
rlogExp_F1  <- rlogTransformation(dds.run_F1)
rlogExp_F2  <- rlogTransformation(dds.run_F2)

# install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
dds.run_F2_df <- as.data.frame(assay(dds.run_F2))
chart.Correlation(dds.run_F2_df[,c(1:4,15:19)], histogram=TRUE, pch=19)
```


## Run diagnostic plots
```{r, Diagnostic plotting}

# ========================================================== 
#  F1s  
# ==========================================================
# VST DIAGNOSTICS ::::::::::::::
# Histogram
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_vstExp_histogram.png", 1000, 1000, pointsize=20)# diagnostics of transformation 
hist(assay(vstExp_F1)) # view histogram 
dev.off() # write
# Histogram mean sd
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_vstExp_mean_sd.png", 1000, 1000, pointsize=20)
meanSdPlot(assay(vstExp_F1)) # shows the sd y axis (sq root of varaince in all samples) 
# flat curve may seem like the goal, BUT may be unreasonable in cases with MANY true DEGs from experimental conditions
dev.off() # write
# PCA plot vst
pcaData_vstExp_F1    <- plotPCA(vstExp_F1, intgroup = "pCO2", returnData = TRUE)
percentVar_vstExp_F1 <- round(100 * attr(pcaData_vstExp_F1, "percentVar"))
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_vstExp_PCA.png", 1000, 1000, pointsize=20)
ggplot(pcaData_vstExp_F1, aes(x = PC1, y = PC2, color = pCO2, label=name)) +
  #scale_shape_manual(values = c(4, 19, 17)) +
  #geom_text(aes(label=name),hjust=0.2, vjust=1.4, size=5) +
  geom_point(size =3) +
  theme_classic() +
  stat_ellipse() +
  #theme(text = element_text(size=15)) +
  theme_classic() +
  theme(text = element_text(size=15)) +
  ggtitle("F1 PCA: vst expression data") +
  xlab(paste0("PC1: ", percentVar_vstExp_F1[1], "% variance")) + 
  ylab(paste0("PC2: ", percentVar_vstExp_F1[2], "% variance")) +
  coord_fixed()
dev.off()
# RLOG DIAGNOSTICS ::::::::::::::
# Histogram
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_rlogExp_histogram.png", 1000, 1000, pointsize=20)# diagnostics of transformation 
hist(assay(rlogExp_F1)) # view histogram 
dev.off() # write
# Histogram mean sd
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_rlogExp_mean_sd.png", 1000, 1000, pointsize=20)
meanSdPlot(assay(rlogExp)) # shows the sd y axis (sq root of varaince in all samples) - flat curve may seem like a goals, BUT may be unreasonable in cases with MANY true DEGs from experimental conditions
dev.off() # write
# PCA plot rlog
pcaData_rlogExp_F1    <- plotPCA(rlogExp_F1, intgroup = "pCO2", returnData = TRUE)
percentVar_rlogExp_F1  <- round(100 * attr(pcaData_rlogExp_F1, "percentVar"))
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_rlogExp_PCA.png", 1000, 1000, pointsize=20)
ggplot(pcaData_rlogExp_F1, aes(x = PC1, y = PC2, color = pCO2, label=name)) +
  #scale_shape_manual(values = c(4, 19, 17)) +
  #geom_text(aes(label=name),hjust=0.2, vjust=1.4, size=5) +
  geom_point(size =3) +
  theme_classic() +
  stat_ellipse() +
  #theme(text = element_text(size=15)) +
  theme_classic() +
  ggtitle("F1 PCA: rlog expression data") +
  xlab(paste0("PC1: ", percentVar_rlogExp_F1[1], "% variance")) +
  ylab(paste0("PC2: ", percentVar_rlogExp_F1[2], "% variance")) +
  coord_fixed()
dev.off()



# ========================================================== 
#  F2s  
# ==========================================================
# VST DIAGNOSTICS ::::::::::::::
# Histogram
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_vstExp_histogram.png", 1000, 1000, pointsize=20)# diagnostics of transformation 
hist(assay(vstExp_F2)) # view histogram 
dev.off() # write
# Histogram mean sd
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_vstExp_mean_sd.png", 1000, 1000, pointsize=20)
meanSdPlot(assay(vstExp_F2)) # shows the sd y axis (sq root of varaince in all samples) 
# flat curve may seem like the goal, BUT may be unreasonable in cases with MANY true DEGs from experimental conditions
dev.off() # write
# PCA plot vst
pcaData_vstExp_F2    <- plotPCA(vstExp_F2, intgroup = "pCO2", returnData = TRUE)
percentVar_vstExp_F2 <- round(100 * attr(pcaData_vstExp_F2, "percentVar"))
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_vstExp_PCA.png", 1000, 1000, pointsize=20)
ggplot(pcaData_vstExp_F2, aes(x = PC1, y = PC2, color = pCO2, label=name)) +
  #scale_shape_manual(values = c(4, 19, 17)) +
  #geom_text(aes(label=name),hjust=0.2, vjust=1.4, size=5) +
  geom_point(size =3) +
  theme_classic() +
  stat_ellipse() +
  #theme(text = element_text(size=15)) +
  ggtitle("F2 PCA: vst expression data") +
  xlab(paste0("PC1: ", percentVar_vstExp_F2[1], "% variance")) + 
  ylab(paste0("PC2: ", percentVar_vstExp_F2[2], "% variance")) +
  coord_fixed()
dev.off()
# RLOG DIAGNOSTICS ::::::::::::::
# Histogram
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_rlogExp_histogram.png", 1000, 1000, pointsize=20)# diagnostics of transformation 
hist(assay(rlogExp_F2)) # view histogram 
dev.off() # write
# Histogram mean sd
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_rlogExp_mean_sd.png", 1000, 1000, pointsize=20)
meanSdPlot(assay(rlogExp_F2)) # shows the sd y axis (sq root of varaince in all samples) - flat curve may seem like a goals, BUT may be unreasonable in cases with MANY true DEGs from experimental conditions
dev.off() # write
# PCA plot rlog
pcaData_rlogExp_F2     <- plotPCA(rlogExp_F2, intgroup = "pCO2", returnData = TRUE)
percentVar_rlogExp_F2  <- round(100 * attr(pcaData_rlogExp_F2, "percentVar"))
png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_rlogExp_PCA.png", 1000, 1000, pointsize=20)
ggplot(pcaData_rlogExp_F2, aes(x = PC1, y = PC2, color = pCO2, label=name)) +
  geom_point(size =3) +
  theme_classic() +
  stat_ellipse() +
 # geom_text(aes(label=name),hjust=0.2, vjust=1.4, size=5) +
 # theme(text = element_text(size=15)) +
  ggtitle("F2 PCA: rlog expression data") +
  xlab(paste0("PC1: ", percentVar_rlogExp_F2[1], "% variance")) +
  ylab(paste0("PC2: ", percentVar_rlogExp_F2[2], "% variance")) +
  coord_fixed()
dev.off()


```


## DEGs - data tables
```{r Examine DEGs how many? what are they?}

# Edit the annotation file (Cvirg blasted to annotate draft genome contigs of Airradians)
Airr_Cvirg_annotation <- read.csv(file="../../Output/Transcriptomics/Raw_counts_matrix/raw_count_matrix_WITH_ANNOTATION.csv",
                                  sep = ',', 
                                  header = T) %>% 
                        dplyr::select(c('Airradians_TranscriptID',
                                 "blastxEval_CvirgTranscriptID",
                                 "blastxEval_CvirgProteinID",
                                 "blastxEval_CvirgGeneID",
                                 "blastxEval_CvirgGOterms"))


# ========================================================== 
#  F1s  
# ==========================================================
# Grab DEGs from  the 'dds.run' model
DEGresults_F1         <- results(dds.run_F1, contrast=c("pCO2", "High", "Low"), alpha = 0.05) # FDR is the alpha 0.05
numDEGs_pval_F1       <- data.frame(table(DEGresults_F1$pvalue<0.05))[2,2] # DEGs - NOT considering LFC - just p adj
numDEGs_padj_F1       <- data.frame(table(DEGresults_F1$padj<0.05))[2,2] # DEGs - NOT considering LFC - just p adj
DEGresults.ordered_F1 <- DEGresults_F1[order(DEGresults_F1$padj), ] # Order by adjusted p-value
num.UpReg_F1          <- sum((DEGresults.ordered_F1$log2FoldChange[1:numDEGs_padj_F1] > 0) == TRUE) #  LFC >= 1
num.DownReg_F1        <- sum((DEGresults.ordered_F1$log2FoldChange[1:numDEGs_padj_F1] < 0) == TRUE) # LFC >= 1
total_F1              <- sum(num.DownReg_F1,num.UpReg_F1) # sum of DEGs with the criteria pdj < 0.05 + LFC>1 (< -1)
# Write results - covert to as.data.frame for the ordered results
resdata.F1           <- merge(as.data.frame(DEGresults.ordered_F1), 
                                    as.data.frame(counts(dds.run_F1, normalized=TRUE)), 
                                    by="row.names", 
                                    sort=FALSE) ## Merge with normalized count data
names(resdata.F1)[1] <- "Airradians_TranscriptID"
resdata.F1.annot     <- merge(Airr_Cvirg_annotation,resdata.F1, by = 'Airradians_TranscriptID')
resdata.F1.annot     <- resdata.F1.annot[order(resdata.F1.annot$padj), ]  # Order by adjusted p-value
# write out annotated DESeq2 DEGs
write.csv(resdata.F1.annot, "../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_DESeq2results_F1s.csv") # write
# What are the Protein names of these DEGs?
# first gather gene IDs for the DEGs (note: this is also used for the pheatmap in the transformed Exp heatmap)
numDEGs_padj_F1 # 150 - number of DEGs (from above) - use as integer in call below
topgenes.IDs_F1 <- head(rownames(DEGresults.ordered_F1),numDEGs_padj_F1) # call gene IDs for DEGs: pdj < 0.05 FDR < 0.05 
length(topgenes.IDs_F1) == numDEGs_padj_F1 # must be TRUE
# DEGs Protein IDs - lets take a look shall we! 
DEGs_annotated_F1s <- Airr_Cvirg_annotation %>% filter(Airradians_TranscriptID %in% topgenes.IDs_F1)
# nrow(DEGs_annotated_F1s) # 169 - all are present! 


# ========================================================== 
#  F2s  
# ==========================================================
# Grab DEGs from  the 'dds.run' model
DEGresults_F2         <- results(dds.run_F2, contrast=c("pCO2", "High", "Low"), alpha = 0.05) # FDR is the alpha 0.05
numDEGs_pval_F2       <- data.frame(table(DEGresults_F2$pvalue<0.05))[2,2] # DEGs - NOT considering LFC - just p adj
numDEGs_padj_F2       <- data.frame(table(DEGresults_F2$padj<0.05))[2,2] # DEGs - NOT considering LFC - just p adj
DEGresults.ordered_F2 <- DEGresults_F2[order(DEGresults_F2$padj), ] # Order by adjusted p-value
num.UpReg_F2          <- sum((DEGresults.ordered_F2$log2FoldChange[1:numDEGs_padj_F2] > 0) == TRUE) #  LFC >= 1
num.DownReg_F2        <- sum((DEGresults.ordered_F2$log2FoldChange[1:numDEGs_padj_F2] < 0) == TRUE) # LFC >= 1
total_F2              <- sum(num.DownReg_F2,num.UpReg_F2) # sum of DEGs with the criteria pdj < 0.05 + LFC>1 (< -1)
# Write results - covert to as.data.frame for the ordered results
resdata.F2           <- merge(as.data.frame(DEGresults.ordered_F2), 
                                    as.data.frame(counts(dds.run_F2, normalized=TRUE)), 
                                    by="row.names", 
                                    sort=FALSE) ## Merge with normalized count data
names(resdata.F2)[1] <- "Airradians_TranscriptID"
resdata.F2.annot     <- merge(Airr_Cvirg_annotation,resdata.F2, by = 'Airradians_TranscriptID')
resdata.F2.annot     <- resdata.F2.annot[order(resdata.F2.annot$padj), ]  # Order by adjusted p-value
# write out annotated DESeq2 DEGs
write.csv(resdata.F2.annot, "../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_DESeq2results_F2s.csv") # write
# What are the Protein names of these DEGs?
# first gather gene IDs for the DEGs (note: this is also used for the pheatmap in the transformed Exp heatmap)
numDEGs_padj_F2 # 4 - number of DEGs (from above) - use as integer in call below
topgenes.IDs_F2 <- head(rownames(DEGresults.ordered_F2),numDEGs_padj_F2) # call gene IDs for DEGs: pdj < 0.05 FDR < 0.05 
length(topgenes.IDs_F2) == numDEGs_padj_F2 # must be TRUE
# DEGs Protein IDs - lets take a look shall we! 
DEGs_annotated_F2s <- Airr_Cvirg_annotation %>% filter(Airradians_TranscriptID %in% topgenes.IDs_F2)
# nrow(DEGs_annotated_F2s) # 169 - all are present! 


```

## Plot the DEG statistics

```{r histogram}
# histogram of FDR
png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_FDR_hist.png", 1000, 1000, pointsize=20)
hist(DEGresults_F1$padj, breaks=20, col="grey") # view histogram
abline(h=c( (nrow(DEGresults_F1)*0.05), 
            ((table(DEGresults_F1$padj < 0.1)[2]) + (nrow(DEGresults_F1)*0.1)),
            ((table(DEGresults_F1$padj < 0.05)[2]) + (nrow(DEGresults_F1)*0.05)) ),
                  col=c("blue", "red", "red"), lty=c(1,2,1), lwd=c(1, 3, 1)) # add line at 
dev.off()

png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_FDR_hist.png", 1000, 1000, pointsize=20)
hist(DEGresults_F2$padj, breaks=20, col="grey") # view histogram
abline(h=c( (nrow(DEGresults_F2)*0.05), 
            ((table(DEGresults_F2$padj < 0.1)[2]) + (nrow(DEGresults_F2)*0.1)),
            ((table(DEGresults_F2$padj < 0.05)[2]) + (nrow(DEGresults_F2)*0.05)) ),
                  col=c("blue", "red", "red"), lty=c(1,2,1), lwd=c(1, 3, 1)) # add line at 
dev.off()

?EnhancedVolcano
# volcano plot 
# png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_DEGs-VolcanoPlot.png", 1000, 1000, pointsize=20)
pdf("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_DEGs-VolcanoPlot.pdf", width = 7, height = 5)
EnhancedVolcano(DEGresults_F1,
                #lab = rownames(DEGresults_F2),
                lab = NA, # no labels
                #labSize = 4, # remove gene labels
                x = 'log2FoldChange',
                y = 'padj',
                title = 'F1s: pCO2 Treatment (Low v High)',
                subtitle = "DESeq2 - Differential expression",
                FCcutoff = 0.5,
                pCutoff = 0.05,
                 ylim = c(0,5),
                pointSize = 4.0,
                labSize = 3,
                colAlpha = 1,
                legendPosition = 'right',
                legendLabSize = 12,
                legendIconSize = 2,
                widthConnectors = 0.75)
dev.off()


# png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_DEGs-VolcanoPlot.png", 1000, 1000, pointsize=20)
pdf("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_DEGs-VolcanoPlot.pdf", width = 7, height = 5)
EnhancedVolcano(DEGresults_F2,
                #lab = rownames(DEGresults_F2),
                lab = NA, # no labels
                #labSize = 4, # remove gene labels
                x = 'log2FoldChange',
                y = 'padj',
                title = 'F2s: pCO2 Treatment (Low v High)',
                subtitle = "DESeq2 - Differential expression",
                FCcutoff = 0.5,
                 ylim = c(0,5),
                pCutoff = 0.05,
                pointSize = 4.0,
                colAlpha = 1,
                legendPosition = 'right',
                legendLabSize = 12,
                legendIconSize = 4.0,
                widthConnectors = 0.75)
dev.off()

# Plot dispersion 

png("../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_dispersions.png", 1000, 1000, pointsize=20)
plotDispEsts(dds.run_F1, main="dispersions")
dev.off()

png("../../Output/Transcriptomics/DESeq2/F2_juveniles/F2_dispersions.png", 1000, 1000, pointsize=20)
plotDispEsts(dds.run_F2, main="dispersions")
dev.off()


```

## Figures for F1 and F2 data 
```{r, Figs}

PCA_F1_vst <- ggplot(pcaData_vstExp_F1, 
                     aes(x = PC1, 
                         y = PC2, 
                         color = pCO2, 
                         label=name)) +
                geom_point(size =4) +
                #scale_fill_manual(c('grey50', 'white')) +
                theme_classic() +
                stat_ellipse() +
                ylim(-20,20) +
                xlim(-35,35) +
                theme(legend.position = 'none',axis.text = element_text(size = 12)) +
                ggtitle("F1 PCA: vst expression data") +
                xlab(paste0("PC1: ", percentVar_vstExp_F1[1], "% variance")) + 
                ylab(paste0("PC2: ", percentVar_vstExp_F1[2], "% variance")) +
                coord_fixed()
PCA_F2_vst <- ggplot(pcaData_vstExp_F2, 
                     aes(x = PC1, 
                         y = PC2, 
                         color = pCO2, 
                         label=name)) +
                geom_point(size =4) +
                theme_classic() +
                stat_ellipse() +
                ylim(-20,20) +
                xlim(-35,35) +
                theme(legend.position = 'none',axis.text = element_text(size = 12)) +
                ggtitle("F2 PCA: vst expression data") +
                xlab(paste0("PC1: ", percentVar_vstExp_F2[1], "% variance")) + 
                ylab(paste0("PC2: ", percentVar_vstExp_F2[2], "% variance")) +
                coord_fixed()

F1_Volcano <- EnhancedVolcano(DEGresults_F1,
                #lab = rownames(DEGresults_F2),
                lab = NA, # no labels
                #labSize = 4, # remove gene labels
                x = 'log2FoldChange',
                y = 'padj',
                # title = 'F1s: pCO2 Treatment (Low v High)',
                # subtitle = "DESeq2 - Differential expression",
                titleLabSize = NA,
                FCcutoff = 0.5,
                pCutoff = 0.05,
                pointSize = 2,
                axisLabSize = 10,
                labSize = 3,
                colAlpha = 1,
                legendPosition = "none",
                # legendLabSize = 12,
                # legendIconSize = 2,
                widthConnectors = 0.75)
F2_Volcano <- EnhancedVolcano(DEGresults_F2,
                #lab = rownames(DEGresults_F2),
                lab = NA, # no labels
                #labSize = 4, # remove gene labels
                x = 'log2FoldChange',
                y = 'padj',
                # title = 'F2s: pCO2 Treatment (Low v High)',
                # subtitle = "DESeq2 - Differential expression",
                # title = NA,
                titleLabSize = NA,
                FCcutoff = 0.5,
                pCutoff = 0.05,
                pointSize = 2,
                axisLabSize = 10,
                labSize = 3,
                colAlpha = 1,
                legendPosition = "none",
                # legendLabSize = 12,
                widthConnectors = 0.75)
# ?EnhancedVolcano
ggarrange(PCA_F1_vst, PCA_F2_vst, 
          F1_Volcano, F2_Volcano,
          nrow=2, ncol=2)

pdf("../../Output/Transcriptomics/DESeq2/PCA_F1_F2_vst.pdf", width = 14, height = 5)
ggarrange(PCA_F1_vst, PCA_F2_vst, 
          nrow=1, ncol=2)
dev.off()
```

## plot heatmap

```{r heatmap for transformed data}

# Plot pheatmap map rlog
# setup the save pheatmap function
save_pheatmap <- function(x, filename, width=1000, height=960) { # template for saving pheatmap outputs
  stopifnot(!missing(x))
  stopifnot(!missing(filename))
  png(filename,width = width, height=height)
  grid::grid.newpage()
  grid::grid.draw(x$gtable)
  dev.off()
}
# colors for the heatmap
# colorblind palette
colorBlindBlack8  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                         "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
pie(rep(1, 8), col = colorBlindBlack8) # view the pie chart for colorblindness
ann_colors = list(
    pCO2 = c(Low="#56B4E9", High="#E69F00"))
df_annot.col         <- as.data.frame(colData(dds.run_F1)[c("pCO2")])


# rlogExp
rlogExp_F1 <- rlogTransformation(dds.run_F1)
# use topgenes.IDs from the chunk above - this calls only the pdj > 0.05 from the output results of 'dds.run'
topgenes_rlog.counts_F1      <- assay(rlogExp_F1)[topgenes.IDs_F1,] 
topgenes_rlog.corrected_F1   <- topgenes_rlog.counts_F1 - rowMeans(topgenes_rlog.counts_F1) # subtract from the row mean to get +/- 0 to normalize and ease the aesthetic
df_annot.col_F1         <- as.data.frame(colData(dds.run_F1)[c("pCO2")])
rlog.heatmap <- pheatmap(topgenes_rlog.corrected_F1, 
                            annotation_col=df_annot.col_F1, 
                            main = "Ambient versus Moderate (169 total DEGs)",
                            cutree_cols = 2,
                            cutree_rows = 2,
                            annotation_legend = TRUE,
                            annotation_colors = ann_colors,
                            show_rownames = TRUE, # Boolean for gene names
                            labels_col=df_annot.col_F1$pCO2, 
                            angle_col = 0,
                            fontsize = 8,
                            legend = TRUE)
save_pheatmap(rlog.heatmap, filename = "../../Output/Transcriptomics/DESeq2/F1_juveniles/F1_rlog_heatmap.png") #Save pheatmap



# vstExp
# use topgenes.IDs from the chunk above - this calls only the pdj > 0.05 from the output results of 'dds.run'
vstExp_F1 <- vst(dds.run_F1)
topgenes_vst.counts_F1      <- assay(vstExp_F1)[topgenes.IDs_F1,] 
topgenes_vst.corrected_F1   <- topgenes_vst.counts_F1 - rowMeans(topgenes_vst.counts_F1) # subtract from the row mean to get +/- 0 to normalize and ease the aesthetic
vst.heatmap_F1 <- pheatmap(topgenes_vst.corrected_F1, 
                            annotation_col=df_annot.col_F1, 
                            main = "Ambient versus Moderate (169 total DEGs)",
                            cutree_cols = 3,
                            cutree_rows = 2,
                            annotation_legend = TRUE,
                            annotation_colors = ann_colors,
                            show_rownames = TRUE, # Boolean for gene names
                            labels_col=df_annot.col_F1$pCO2, 
                            angle_col = 0,
                            fontsize = 8,
                            legend = TRUE)
save_pheatmap(vst.heatmap_F1, filename = "../../Output/Transcriptomics/DESeq2/F1_juveniles/vst_heatmap.png") #Save pheatmap

```


# plot all the DEGs
```{r plot the rlogExp}

# ========================================================== 
#  F1s  
# ==========================================================
rlogExp_F1_df        <- as.data.frame(assay(rlogExp_F1)) %>% 
                           tibble::rownames_to_column("Gene.ID")
rlogExp_F1_DEGs      <- rlogExp_F1_df %>% 
                          dplyr::filter(Gene.ID %in% topgenes.IDs_F1)
rlogExp_F1_DEGs_melt <- reshape2::melt(rlogExp_F1_DEGs, id.vars='Gene.ID') %>% 
                        dplyr::rename(Sample.Name = variable, # to merge with 'Exp.metadata'
                                      rlogExp = value) # the data to get mean SE values 
DEGs_annotated_F1    <- Airr_Cvirg_annotation %>% 
                          dplyr::filter(Airradians_TranscriptID %in% topgenes.IDs_F1) %>% 
                          dplyr::select(Airradians_TranscriptID,blastxEval_CvirgProteinID) %>% 
                          dplyr::rename(Gene.ID = Airradians_TranscriptID,
                                      Protein.ID = blastxEval_CvirgProteinID)

rlogExp_F1_DEGs_annotated <- merge(DEGs_annotated_F1, rlogExp_F1_DEGs_melt, by = "Gene.ID")
rlogExp_F1_DEGs_MASTER    <- merge(rlogExp_F1_DEGs_annotated,Exp.metadata, by = "Sample.Name")
# library(stringr)
rlogExp_F1_DEGs_MEAN.SE   <- rlogExp_F1_DEGs_MASTER %>% 
                              dplyr:::group_by(Gene.ID, Protein.ID,pCO2) %>% 
                              dplyr::summarise(mean.rlogExp    = mean(rlogExp),
                                               sd.rlogExp     = sd(rlogExp),
                                               n = n(),
                                               sderror.rlogExp = sd.rlogExp/(sqrt(n))) %>% 
                              dplyr::select(-n) %>% 
                              dplyr::mutate(Protein_contig = paste(substr(Protein.ID,1,30),
                                                                   str_split(Gene.ID, "\\.", simplify=T)[,3],
                                                                   sep="_"))
pd <- position_dodge(0.3)
for(i in 1:length(topgenes.IDs_F1)) {
  
  geneID_loop  <- topgenes.IDs_F1[i]
  
  df_loop      <- rlogExp_F1_DEGs_MEAN.SE %>% 
                  dplyr::filter(Gene.ID %in% geneID_loop) %>% 
                  dplyr::mutate(Protein_contig = str_remove_all(Protein_contig,"/"))
  
  plot_loop    <- df_loop %>% 
                    ggplot(aes(x=pCO2, 
                               y=mean.rlogExp, 
                               fill=pCO2)) +  # , colour=supp, group=supp))
                    theme_classic() +
                    geom_errorbar(aes(ymin=mean.rlogExp-sderror.rlogExp, 
                                      ymax=mean.rlogExp+sderror.rlogExp), 
                                  colour="black", 
                                  width=.1,
                                  position=pd) +
                    geom_point(size = 4, 
                               shape=21,
                               position=pd) +            
                    xlab("pCO2 treatment") +
                    ylab("") +                 # note the mean was first by sample ID THEN by treatment
                    scale_fill_manual(values=c("white",
                                               "grey50")) +
                    ggtitle(df_loop[1,7]) +
                    theme(axis.text.x = element_text(size = 20),
                          axis.text.y = element_text(size = 20),
                          axis.ticks.length=unit(.25, "cm")) +
                    theme(legend.position = "none")
  
if(df_loop[1,4]>df_loop[2,4]) { # Upregulated, high pCO2 == high expression
  pdf(paste("../../Output/Transcriptomics/DESeq2/F1_juveniles/Plots_MeanSE/Upregulated_DEGs/",df_loop[1,7],".pdf", sep = ''), width=5, height=5)
  print(plot_loop)
  dev.off() 
  } else {
  pdf(paste("../../Output/Transcriptomics/DESeq2/F1_juveniles/Plots_MeanSE/Downregulated_DEGs/",df_loop[1,7],".pdf", sep = ''), width=5, height=5)
  print(plot_loop)
  dev.off()  
  }
}




# ========================================================== 
#  F2s  
# ==========================================================
rlogExp_F2_df        <- as.data.frame(assay(rlogExp_F2)) %>% 
                           tibble::rownames_to_column("Gene.ID")
rlogExp_F2_DEGs      <- rlogExp_F2_df %>% 
                          dplyr::filter(Gene.ID %in% topgenes.IDs_F2)
rlogExp_F2_DEGs_melt <- reshape2::melt(rlogExp_F2_DEGs, id.vars='Gene.ID') %>% 
                        dplyr::rename(Sample.Name = variable, # to merge with 'Exp.metadata'
                                      rlogExp = value) # the data to get mean SE values 
DEGs_annotated_F2    <- Airr_Cvirg_annotation %>% 
                          dplyr::filter(Airradians_TranscriptID %in% topgenes.IDs_F2) %>% 
                          dplyr::select(Airradians_TranscriptID,blastxEval_CvirgProteinID) %>% 
                          dplyr::rename(Gene.ID = Airradians_TranscriptID,
                                      Protein.ID = blastxEval_CvirgProteinID)

rlogExp_F2_DEGs_annotated <- merge(DEGs_annotated_F2, rlogExp_F2_DEGs_melt, by = "Gene.ID")
rlogExp_F2_DEGs_MASTER    <- merge(rlogExp_F2_DEGs_annotated,Exp.metadata, by = "Sample.Name")
# library(stringr)
rlogExp_F2_DEGs_MEAN.SE   <- rlogExp_F2_DEGs_MASTER %>% 
                              dplyr:::group_by(Gene.ID, Protein.ID,pCO2) %>% 
                              dplyr::summarise(mean.rlogExp    = mean(rlogExp),
                                               sd.rlogExp     = sd(rlogExp),
                                               n = n(),
                                               sderror.rlogExp = sd.rlogExp/(sqrt(n))) %>% 
                              dplyr::select(-n) %>% 
                              dplyr::mutate(Protein_contig = paste(substr(Protein.ID,1,30),
                                                                   str_split(Gene.ID, "\\.", simplify=T)[,3],
                                                                   sep="_"))
pd <- position_dodge(0.3)
for(i in 1:length(topgenes.IDs_F2)) {
  
  geneID_loop  <- topgenes.IDs_F2[i]
  
  df_loop      <- rlogExp_F2_DEGs_MEAN.SE %>% 
                  dplyr::filter(Gene.ID %in% geneID_loop) %>% 
                  dplyr::mutate(Protein_contig = str_remove_all(Protein_contig,"/"))
  
  plot_loop    <- df_loop %>% 
                    ggplot(aes(x=pCO2, 
                               y=mean.rlogExp, 
                               fill=pCO2)) +  # , colour=supp, group=supp))
                    theme_classic() +
                    geom_errorbar(aes(ymin=mean.rlogExp-sderror.rlogExp, 
                                      ymax=mean.rlogExp+sderror.rlogExp), 
                                  colour="black", 
                                  width=.1,
                                  position=pd) +
                    geom_point(size = 4, 
                               shape=21,
                               position=pd) +            
                    xlab("pCO2 treatment") +
                    ylab("") +                 # note the mean was first by sample ID THEN by treatment
                    scale_fill_manual(values=c("white",
                                               "grey50")) +
                    ggtitle(df_loop[1,7]) +
                    theme(axis.text.x = element_text(size = 20),
                          axis.text.y = element_text(size = 20),
                          axis.ticks.length=unit(.25, "cm")) +
                    theme(legend.position = "none")
  
if(df_loop[1,4]>df_loop[2,4]) { # Upregulated, high pCO2 == high expression
  pdf(paste("../../Output/Transcriptomics/DESeq2/F2_juveniles/Plots_MeanSE/Upregulated_DEGs/",df_loop[1,7],".pdf", sep = ''), width=5, height=5)
  print(plot_loop)
  dev.off() 
  } else {
  pdf(paste("../../Output/Transcriptomics/DESeq2/F2_juveniles/Plots_MeanSE/Downregulated_DEGs/",df_loop[1,7],".pdf", sep = ''), width=5, height=5)
  print(plot_loop)
  dev.off()  
  }
}
```

