---
title: "GO_Analysis_DESeq2_10cpm"
author: "Samuel Gurr"
date: "September, 6, 2023"
output: html_document
---

## Setup: 

```{r setup, include=TRUE}

knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis")

```


NOTE: after runinng this once... you can load the liibraries (below) and skip to 'the 'Find GOslim terms' to load the .csv files for plotting
Load libraries
```{r load_libraries, include = TRUE}
# load libraries - notes show the install command needed to install (pre installed)
library(goseq)
library(dplyr)
library(forcats)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(grDevices)
library(reshape2)
library(Rmisc)
library(ggpubr)
library(tibble)
library(hrbrthemes)
library(gridExtra)
library(tidyr)
library(zoo)
library(ComplexHeatmap)
library(circlize)
library(GSEABase)
library(data.table)
library(stringr)
```

#### Set path

```{r set the path out, include = TRUE}
path_out = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Transcriptomics/DESeq2'
```

LOAD DATA:
Annotation and DE data (from DESeq2 Rmd script)
```{r Load_annot_and_DE_files, include = TRUE}
# Annotation file - acheived with diamond against the Cvirginica genome - Airradians genome is unannotated!
Airr_Cvirg_annotation <- read.csv(file="Data/Transcriptomics/seq_id_AirrCvirg_MERGED_master.csv",
                                  sep = ',', 
                                  header = T) %>% 
                        dplyr::select(c('Airradians_TranscriptID',
                                 "blastxEval_CvirgTranscriptID",
                                 "blastxEval_CvirgProteinID",
                                 "blastxEval_CvirgGeneID",
                                 "blastxEval_CvirgGOterms",
                                 "meanLength"))

# DE files - all genes and filtered raw counts
DE_F1s <-read.csv("Output/Transcriptomics/DESeq2/F1_juveniles/F1_DESeq2results_F1s.csv", head = T) # write
DE_F2s <- read.csv("Output/Transcriptomics/DESeq2/F2_juveniles/F2_DESeq2results_F2s.csv", head = T) # write


# filtered counts tables 3CPM - format matrix after upload [from Count_Matrix_Stats.Filter.R] 
filtered_counts_all                 <- read.csv(file="Output/Transcriptomics/Filtered_counts_matrix/filtered_3cpm50perc.csv", sep=',', header=TRUE)  
colnames(filtered_counts_all)[1]    <- "gene.ID"# rename Pgen gene ID column
exp_data                            <- read.csv(file="Data/Transcriptomics/exp.metadata.csv", sep=',', header=TRUE)

counts_F1                           <- filtered_counts_all %>% 
                                          dplyr::select(
                                            gene.ID,# select gene ID of course
                                          (exp_data %>% dplyr::filter(Date %in% 20211027))$SampleName_readmatrix) # select only sample IDs from F1s

counts_F2                           <- filtered_counts_all %>% 
                                          dplyr::select(
                                            gene.ID,# select gene ID of course
                                            (exp_data %>% 
                                               dplyr::filter(!SampleName_readmatrix %in% "Ai37") %>% # remove sample 37 - not successfully sequenced
                                               dplyr::filter(Date %in% 20220228))$SampleName_readmatrix) # select only sample IDs from F1s

# GOslim
slim <- getOBOCollection("http://current.geneontology.org/ontology/subsets/goslim_generic.obo") #get GO database - # call goslim_generic.obo terms as 'slim'

```

```{r }

# create a referecne from the Geoduck annotation file to merge with the DE sumamry lists 
ref           <- Airr_Cvirg_annotation[,c(1,5)]
colnames(ref) <- c("Airradians_TranscriptID", "gene.annotation") # the Airradians transcript IDs (e.g. evm.model.Contig0.1) and the gO terms from diamond/blast with Cvirg genome

# F1s - call padj < 0.05 and assign boolean to logfold change direction
DE_F1s_dir <- DE_F1s %>% 
                    dplyr::select('Airradians_TranscriptID','log2FoldChange','padj') %>% 
                    dplyr::filter(padj < 0.05) %>% 
                    dplyr::mutate(dir =
                      case_when(log2FoldChange > 0 ~ "up",
                                log2FoldChange < 0 ~ "down")) %>% 
                    dplyr::mutate(up = 
                        case_when(dir == "up" ~ TRUE, .default = FALSE),
                                  down = 
                        case_when(dir == "down" ~ TRUE, .default = FALSE)) %>% 
                    dplyr::select(-c(padj, dir)) %>% mutate(Effect = "Generation_1")

# F2s - call padj < 0.05 and assign boolean to logfold change direction
DE_F2s_dir <- DE_F2s %>% 
                    dplyr::select('Airradians_TranscriptID','log2FoldChange','padj') %>% 
                    dplyr::filter(padj < 0.05) %>% 
                    dplyr::mutate(dir =
                      case_when(log2FoldChange > 0 ~ "up",
                                log2FoldChange < 0 ~ "down")) %>% 
                    dplyr::mutate(up = 
                        case_when(dir == "up" ~ TRUE, .default = FALSE),
                                  down = 
                        case_when(dir == "down" ~ TRUE, .default = FALSE)) %>% 
                    dplyr::select(-c(padj, dir)) %>% mutate(Effect = "Generation_2")

# rbind to merge the DE for Gen 1 and 2
DE_Master <- rbind(DE_F1s_dir, DE_F2s_dir)

# merge in the annotation 
DE_Master_with_annotation <- merge(DE_Master, ref, by="Airradians_TranscriptID", all = T) %>% dplyr::filter(!log2FoldChange %in% NA)

# sanity check - row numbers should be equal 
nrow(DE_Master) == nrow(DE_Master_with_annotation) # TRUE, must be TRUE or we have problems!

# write csv
write.csv(DE_Master_with_annotation, file = "Output/Transcriptomics/DESeq2/DE_All_Annotation.csv", row.names = FALSE)
```
Prep Differential Expression data (from DESeq2) by Date and direction of DE 
```{r}
# Objective here is to call the DE genes (up and down) 
# Gen 1  ------------------------------------------- #
dim(DE_F1s_dir) # 150 DEGs
DE_F1s_dir.UPREG  <- DE_F1s_dir %>% dplyr::filter(up %in% TRUE)         # UPREG call - 91
DE_F1s_dir.DWNREG <- DE_F1s_dir %>% dplyr::filter(down %in% TRUE)       # DWNREG call - 59
# Gen 2  ------------------------------------------- #
dim(DE_F2s_dir) # 4 DEGs
DE_F2s_dir.UPREG  <- DE_F2s_dir %>% dplyr::filter(up %in% TRUE)         # UPREG call - 2
DE_F2s_dir.DWNREG <- DE_F2s_dir %>% dplyr::filter(down %in% TRUE)       # DWNREG call - 2
```

goseq
Prepare dataframe(s) and vectors for goseq 
(1) Format 'GO.term' for goseq from the P.generosa annotation .fna file 'Geoduck_annotation'
```{r GO.terms_data}
# call the GO terms
AirrCgig_GOterms                <- as.data.frame(Airr_Cvirg_annotation) %>% dplyr::select(c('Airradians_TranscriptID','blastxEval_CvirgGOterms'))
colnames(AirrCgig_GOterms)[1:2] <- c('transcript.ID', 'GO.terms') # call gene name and the GO terms - (Uniprot ID 'V5')
splitted                        <- strsplit(as.character(AirrCgig_GOterms$GO.terms), ";") #slit into multiple GO ids by delimiter'; ' remember the space after ; is needed here! without this you will only call the first listed GO term for each gene!
GO.terms                        <- data.frame(v1 = rep.int(AirrCgig_GOterms$transcript.ID, sapply(splitted, length)), 
                                              v2 = unlist(splitted)) #list all genes with each of their GO terms in a single row
```


(2) Unique Genes - vector based on all unique mapped reads  - Remember this is based on the genes for EACH sampling day becasue DEeq2 was run separately (i.e. days 0, 7, 14, and 21)
(3) Gene length 
Set ID and gene length vectors, and make a binary matrix indicating which genes are differentially expressed. These are used as input to nullp, which for calculates a Probability Weighting Function for each set of DEGs.
```{r Unique_genes}
# Prepare dataframe(s) and vectors for goseq 

# Format 'GO.term' for goseq from the P.generosa annotation .fna file 'Geoduck_annotation'
IDvector.F1 <- as.vector(unique(DE_F1s_dir$Airradians_TranscriptID))   # call unique genes (those filtered and used in DESEq2) on day0 - 'IDvector'
IDvector.F2 <- as.vector(unique(DE_F2s_dir$Airradians_TranscriptID))  # call unique genes (those filtered and used in DESEq2) on day7 - 'IDvector'
GO_unique.genes.all <- as.vector(unique(Airr_Cvirg_annotation$Airradians_TranscriptID)) # call all unique genes for GO analysis (goseq)

# Gene length 
GO_gene.length           <- unique(Airr_Cvirg_annotation %>% dplyr::select(c("Airradians_TranscriptID","meanLength")))
names(GO_gene.length)[1] <- "gene.ID" # cange the column name to merge with the gene counts on each day to call ID and length vectors UNIQUE to the experiment day

# merge length with counts data
length_vector   <- GO_gene.length$meanLength
GeneLength.F1   <- merge(GO_gene.length, counts_F1, by = "gene.ID")   # merge day0 counts with 'GO_gene.length' 
GeneLength.F2   <- merge(GO_gene.length, counts_F2, by = "gene.ID")  # merge day7 counts with 'GO_gene.length' 

# call length values for goseq - confirms that the IDvector and length_vector are the same!!!
length_vector.F1 <- GeneLength.F1$meanLength    # length vector for all unique reads addressed in DESeq2 F1s
sum(sapply(length_vector.F1,length)) == dim(counts_F1)[1] #should be TRUE
length_vector.F2 <- GeneLength.F2$meanLength    # length vector for all unique reads address in DESeq2 F2s
sum(sapply(length_vector.F2,length)) == dim(counts_F2)[1] #should be TRUE


```

(4) Call DE datasets (from DESeq2) - merge to the genes list 'GO_unique.genes.all' to create a binary vector 0 = not DE'd; 1 = DE'd
```{r Binary_DEGs - must run the prep steps above}

# F1s

DE_F1s_UPREG_boolean    <-as.integer(GO_unique.genes.all%in%(DE_F1s_dir.UPREG$Airradians_TranscriptID)) # Day 0 - Primary - Upregulated DEGs
names(DE_F1s_UPREG_boolean)=GO_unique.genes.all
sum(sapply(DE_F1s_UPREG_boolean,length)) # 18874
sum(DE_F1s_UPREG_boolean == 1) # should be 91 but is 83 -    missing due to no blast alignment to the Cvig genome

DE_F1s_DWNREG_boolean    <-as.integer(GO_unique.genes.all%in%(DE_F1s_dir.DWNREG$Airradians_TranscriptID)) # Day 0 - Primary - Upregulated DEGs
names(DE_F1s_DWNREG_boolean)=GO_unique.genes.all
sum(sapply(DE_F1s_DWNREG_boolean,length)) # 18874
sum(DE_F1s_DWNREG_boolean == 1) # should be 59 but is 37 -    missing due to no blast alignment to the Cvig genome


# F2s

DE_F2s_UPREG_boolean    <-as.integer(GO_unique.genes.all%in%(DE_F2s_dir.UPREG$Airradians_TranscriptID)) # Day 0 - Primary - Upregulated DEGs
names(DE_F2s_UPREG_boolean)=GO_unique.genes.all
sum(sapply(DE_F2s_UPREG_boolean,length)) # 18874
sum(DE_F2s_UPREG_boolean == 1) # should be 2

DE_F2s_DWNREG_boolean    <-as.integer(GO_unique.genes.all%in%(DE_F2s_dir.DWNREG$Airradians_TranscriptID)) # Day 0 - Primary - Upregulated DEGs
names(DE_F2s_DWNREG_boolean)=GO_unique.genes.all
sum(sapply(DE_F2s_DWNREG_boolean,length)) # 18874
sum(DE_F2s_DWNREG_boolean == 1) # should be 2 but is 1


```

Let's review what we have for goseq
```{r NOTE_checklist}
# Review what we have for goseq....

# (1) Go terms ---------------- #
#  head(GO.terms)

# (2) ID vector --------------- #
# head(IDvector.F1)
# head(IDvector.F2)

# (3) Length vector ----------- #
# head(length_vector.F1)
# head(length_vector.F2)

# (4) Binary DEG vectors ------ # 
# head(DE_F1s_UPREG_boolean)   
# head(DE_F1s_DWNREG_boolean)  
# head(DE_F2s_UPREG_boolean)    
# head(DE_F2s_DWNREG_boolean) 


```

It's goseq time!!!
Calculate Probability Weighting Function
```{r pwf}
#Calculate Probability Weighting Function (using 'nullp')

# F1s ------------------------------------------ #

DEG.pwf_F1_up    <-nullp(DE_F1s_UPREG_boolean,  id=GO_unique.genes.all, bias.data=length_vector) # weight vector by length of gene
DEG.pwf_F1_down  <-nullp(DE_F1s_DWNREG_boolean, id=GO_unique.genes.all, bias.data=length_vector) # weight vector by length of gene

# F2s ------------------------------------------ #

DEG.pwf_F2_up    <-nullp(DE_F2s_UPREG_boolean,  id=GO_unique.genes.all, bias.data=length_vector) # weight vector by length of gene
DEG.pwf_F2_down  <-nullp(DE_F2s_DWNREG_boolean, id=GO_unique.genes.all, bias.data=length_vector) # weight vector by length of gene


```

Run goseq
```{r goseq}

# F1s ------------------------------------------ #
GO_F1.UP     <-goseq(DEG.pwf_F1_up,   GO_unique.genes.all, gene2cat=GO.terms, test.cats=c("GO:CC", "GO:BP", "GO:MF"), method="Wallenius", use_genes_without_cat=TRUE)
GO_F1.DOWN   <-goseq(DEG.pwf_F1_down, GO_unique.genes.all, gene2cat=GO.terms, test.cats=c("GO:CC", "GO:BP", "GO:MF"), method="Wallenius", use_genes_without_cat=TRUE)
# F2s ------------------------------------------ #
GO_F2.UP     <-goseq(DEG.pwf_F2_up,   GO_unique.genes.all, gene2cat=GO.terms, test.cats=c("GO:CC", "GO:BP", "GO:MF"), method="Wallenius", use_genes_without_cat=TRUE)
GO_F2.DOWN   <-goseq(DEG.pwf_F2_down, GO_unique.genes.all, gene2cat=GO.terms, test.cats=c("GO:CC", "GO:BP", "GO:MF"), method="Wallenius", use_genes_without_cat=TRUE)

```

Find only enriched GO terms that are statistically significant at cutoff
```{r}


# F1S------------------------------------------------------- #

# UPREGULATED GENES - those with higher expression from ambient (control) stress priming
F1.UP.05<-GO_F1.UP$category[GO_F1.UP$over_represented_pvalue<.05]
F1.UP.05<-data.frame(F1.UP.05)
colnames(F1.UP.05) <- c("category")
F1.UP.05 <- merge(F1.UP.05, GO_F1.UP, by="category")
F1.UP.05 <- F1.UP.05[order(F1.UP.05$ontology, F1.UP.05$over_represented_pvalue, -F1.UP.05$numDEInCat),]
F1.UP.05$term <- as.factor(F1.UP.05$term)
F1.UP.05_filtered <- F1.UP.05 %>% filter(!(numDEInCat<2 & ontology == "BP"), !(numDEInCat<2 & ontology == "MF"))
nrow(filter(F1.UP.05_filtered, ontology=="BP")) #number sig BP terms == 8
nrow(filter(F1.UP.05_filtered, ontology=="MF")) #number sig MF terms == 7
nrow(F1.UP.05_filtered) # == 23
#DOWNREGULATED GENES  - those with higher expression from moderate stress priming
F1.DOWN.05<-GO_F1.DOWN$category[GO_F1.DOWN$over_represented_pvalue<.05]
F1.DOWN.05<-data.frame(F1.DOWN.05)
colnames(F1.DOWN.05) <- c("category")
F1.DOWN.05 <- merge(F1.DOWN.05, GO_F1.DOWN, by="category")
F1.DOWN.05 <- F1.DOWN.05[order(F1.DOWN.05$ontology, F1.DOWN.05$over_represented_pvalue, -F1.DOWN.05$numDEInCat),]
F1.DOWN.05$term <- as.factor(F1.DOWN.05$term)
F1.DOWN.05_filtered <- F1.DOWN.05 %>% filter(!(numDEInCat<2 & ontology == "BP"), !(numDEInCat<2 & ontology == "MF"))
nrow(filter(F1.DOWN.05_filtered, ontology=="BP")) #number sig BP terms == 2
nrow(filter(F1.DOWN.05_filtered, ontology=="MF")) #number sig MF terms == 1
nrow(F1.DOWN.05_filtered) # == 4

# F2S------------------------------------------------------- #

# UPREGULATED GENES - those with higher expression from ambient (control) stress priming
F2.UP.05<-GO_F2.UP$category[GO_F2.UP$over_represented_pvalue<.05]
F2.UP.05<-data.frame(F2.UP.05)
colnames(F2.UP.05) <- c("category")
F2.UP.05 <- merge(F2.UP.05, GO_F2.UP, by="category")
F2.UP.05 <- F2.UP.05[order(F2.UP.05$ontology, F2.UP.05$over_represented_pvalue, -F2.UP.05$numDEInCat),]
F2.UP.05$term <- as.factor(F2.UP.05$term)
F2.UP.05_filtered <- F2.UP.05 %>% filter(!(numDEInCat<2 & ontology == "BP"), !(numDEInCat<2 & ontology == "MF"))
nrow(filter(F2.UP.05_filtered, ontology=="BP")) #number sig BP terms == 2
nrow(filter(F2.UP.05_filtered, ontology=="MF")) #number sig MF terms == 1
nrow(F2.UP.05_filtered) # == 5
#DOWNREGULATED GENES  - those with higher expression from moderate stress priming
F2.DOWN.05<-GO_F2.DOWN$category[GO_F2.DOWN$over_represented_pvalue<.05]
F2.DOWN.05<-data.frame(F2.DOWN.05)
colnames(F2.DOWN.05) <- c("category")
F2.DOWN.05 <- merge(F2.DOWN.05, GO_F2.DOWN, by="category")
F2.DOWN.05 <- F2.DOWN.05[order(F2.DOWN.05$ontology, F2.DOWN.05$over_represented_pvalue, -F2.DOWN.05$numDEInCat),]
F2.DOWN.05$term <- as.factor(F2.DOWN.05$term)
F2.DOWN.05_filtered <- F2.DOWN.05 %>% filter(!(numDEInCat<2 & ontology == "BP"), !(numDEInCat<2 & ontology == "MF"))
nrow(filter(F2.DOWN.05_filtered, ontology=="BP")) #number sig BP terms == 0
nrow(filter(F2.DOWN.05_filtered, ontology=="MF")) #number sig MF terms == 1
nrow(F2.DOWN.05_filtered) # == 1
```

Save significant terms
```{r, warning=FALSE}

##### NOTE #####
# Save both the filtered and unfiltered data sets! (two output files for each pairwise DE analysis)
# The data sets without the filter (number of genes for GO calls) were compiled into a cumulative data file 'compileGO_Master.R' in the Scripts folder 
# Review the output from this script - this spreadsheet contains ALL unfiltered data!!!


write.csv(F1.UP.05, file    = "Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_F1_Upregulated_unfiltered.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F1.DOWN.05, file  = "Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_F1_Downregulated_unfiltered.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F1.UP.05_filtered, file    = "Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_0.05_F1_Upregulated.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F1.DOWN.05_filtered, file  = "Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_0.05_F1_Downregulated.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT

write.csv(F2.UP.05, file    = "Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_F2_Upregulated_unfiltered.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F2.DOWN.05, file  = "Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_F2_Downregulated_unfiltered.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F2.UP.05_filtered, file    = "Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_0.05_F2_Upregulated.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT
write.csv(F2.DOWN.05_filtered, file  = "Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_0.05_F2_Downregulated.csv", row.names = FALSE) # unfiltered of GO terms <= 2 numDEinCAT

```

Save GO_Results_Master files
```{r - Save GO_Results_Master files}

F1.UP.05_filtered   <- read.csv("Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_0.05_F1_Upregulated.csv", h=T) %>% 
  dplyr::mutate(Effect = 'Generation_1', Dir = 'up')  # unfiltered of GO terms <= 2 numDEinCAT

F1.DOWN.05_filtered <- read.csv("Output/Transcriptomics/DESeq2/F1_juveniles/GOseq/GO_0.05_F1_Downregulated.csv", h=T)  %>% 
  dplyr::mutate(Effect = 'Generation_1', Dir = 'down')# unfiltered of GO terms <= 2 numDEinCAT

F2.UP.05_filtered   <- read.csv("Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_0.05_F2_Upregulated.csv", h=T)  %>% 
  dplyr::mutate(Effect = 'Generation_2', Dir = 'up')# unfiltered of GO terms <= 2 numDEinCAT

F2.DOWN.05_filtered <- read.csv("Output/Transcriptomics/DESeq2/F2_juveniles/GOseq/GO_0.05_F2_Downregulated.csv", h=T)  %>% 
  dplyr::mutate(Effect = 'Generation_2', Dir = 'down')# unfiltered of GO terms <= 2 numDEinCAT

# Master ALL WGCNA significant modules with treatment
Master_goseq_results      <- rbind(F1.UP.05_filtered, F1.DOWN.05_filtered,
                                   F2.UP.05_filtered, F2.DOWN.05_filtered)

loopvars <- as.data.frame(c('Generation_1:up', 'Generation_1:down',
                     'Generation_2:up', 'Generation_2:down'))


DE_Master_with_annotation <- DE_Master_with_annotation %>% 
  dplyr::mutate(Dir = case_when(up == 'TRUE' ~ 'up', up == 'FALSE' ~ 'down'))

#  for the for loop...
df_total             <- data.frame() # start dataframe 
GO.table             <- data.frame(matrix(nrow = 0, ncol = 11)) # create dataframe to save cumunalitively during for loop
colnames(GO.table)   <- c('Effect', 'Dir',  'GO_term' , 'GO_ID', 'ontology', 'pvalue',  'Gene_count', 'Gene_ratio', 'Transcript_ID', 'geneSymbol', 'Protein_name') # names for comuns in the for loop


# un the loop
for (i in 1:nrow(loopvars)) {
  
  gen <- gsub(':.*','',loopvars[2,1])
  dir <- gsub('.*:','',loopvars[2,1])
  
  Ref.GO.terms       <- DE_Master_with_annotation %>%  
                          dplyr::filter(Dir %in% dir & Effect %in% gen) %>% 
                          dplyr::mutate(gene.annotation = strsplit(gene.annotation, ";")) %>%  
                          unnest(gene.annotation) %>% 
                          dplyr::rename(GO_ID = gene.annotation)
   
  GO.results         <- Master_goseq_results %>%  
                          dplyr::filter(!ontology %in% 'CC') %>% 
                          dplyr::select(!'under_represented_pvalue') %>% 
                          dplyr::rename(Gene_count = numDEInCat, GO_term = term) %>% 
                          dplyr::mutate(Gene_ratio = Gene_count/numInCat) %>% 
                          dplyr::select(-'numInCat') %>% 
                          dplyr::filter(Dir %in% dir & Effect %in% gen) %>% 
                          dplyr::rename(GO_ID = category, pvalue = over_represented_pvalue)

  # Master <- rbind(GO.table, (as.data.frame(merge(GO.results, Ref.GO.terms, by = c("GO_ID", 'Effect', 'Dir')))[,c(3,2,6,1,7,4,5,8,9,12,11)]) )
  Master <- rbind(GO.table, (as.data.frame(merge(GO.results, Ref.GO.terms, by = c("GO_ID", 'Effect', 'Dir')))))
  df       <- data.frame(Master) # name dataframe for this single row
  df_total <- rbind(df_total,df) #bind to a cumulative list dataframe
  print(nrow(df_total)) # print to monitor progress      
  
} 



# write.csv(Day2_larvae_master, file = "Output/WGCNA/day2_larvae/GO_analysis/RR_cutoff/Day2_GO_Results_Master.csv", row.names = FALSE)
# write.csv(Day18_spat_master, file = "Output/WGCNA/day18_spat/GO_analysis/RR_cutoff/Day18_GO_Results_Master.csv", row.names = FALSE)
```








GOslim analysis - data reduction from the many GO terms to more broad function/processes
Read in files if previous steps not run.
```{r}
# PRIMARY EFFECT GO DATA SETS
d0.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day0/GO.05.Day0_PrimEffect_Upregulated.csv")
d0.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day0/GO.05.Day0_PrimEffect_Downregulated.csv")

d7.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/GO.05.Day7_PrimEffect_Upregulated.csv")
d7.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/GO.05.Day7_PrimEffect_Downregulated.csv")

d14.UP.05   <- read.csv("../Output/GO/DESeq2_goseq/Day14/GO.05.Day14_PrimEffect_Upregulated.csv")
d14.DOWN.05 <- read.csv("../Output/GO/DESeq2_goseq/Day14/GO.05.Day14_PrimEffect_Downregulated.csv")

d21.UP.05   <- read.csv("../Output/GO/DESeq2_goseq/Day21/GO.05.Day21_PrimEffect_Upregulated.csv")
d21.DOWN.05 <- read.csv("../Output/GO/DESeq2_goseq/Day21/GO.05.Day21_PrimEffect_Downregulated.csv")

Constant.UP.05   <- read.csv("../Output/GO/DESeq2_goseq/GO.05.ConstantDEGs_PrimEffect_Upregulated.csv")
Constant.DOWN.05 <- read.csv("../Output/GO/DESeq2_goseq/GO.05.ConstantDEGs_PrimEffect_Downregulated.csv")

d0.UP.05$dir    <- "Up"
d7.UP.05$dir    <- "Up"
d14.UP.05$dir   <- "Up"
d21.UP.05$dir   <- "Up"

d0.DOWN.05$dir  <- "Down"
d7.DOWN.05$dir  <- "Down"
d14.DOWN.05$dir <- "Down"
d21.DOWN.05$dir <- "Down"

d0.UP.05$Day    <- "Day0"
d7.UP.05$Day    <- "Day7"
d14.UP.05$Day   <- "Day14"
d21.UP.05$Day   <- "Day21"

d0.DOWN.05$Day  <- "Day0"
d7.DOWN.05$Day  <- "Day7"
d14.DOWN.05$Day <- "Day14"
d21.DOWN.05$Day <- "Day21"

Master_goseq_results      <- rbind(d0.UP.05, d7.UP.05, d14.UP.05,d21.UP.05,
                              d0.DOWN.05, d7.DOWN.05, d14.DOWN.05, d21.DOWN.05) # Master GOseq OF ALL PRIMARY EFFECTS
Master_goseq_results <- Master_goseq_results %>%  dplyr::filter(!ontology %in% 'CC') # Master GOseq OF ALL PRIMARY EFFECTS

DE_d0.primary <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day0/DE_Day0_Primary.csv", sep=',', header=TRUE)
colnames(DE_d0.primary)[2] <- "gene.ID" # rename Pgen gene ID column
DE_d0.primary$Day <- "Day0"

DE_d7.primary <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day7/DE_Day7_Primary.csv", sep=',', header=TRUE) 
colnames(DE_d7.primary)[2] <- "gene.ID"# rename Pgen gene ID column
DE_d7.primary$Day <- "Day7"

DE_d14.primary <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day14/DE_Day14_Primary.csv", sep=',', header=TRUE) 
colnames(DE_d14.primary)[2] <- "gene.ID"# rename Pgen gene ID column
DE_d14.primary$Day <- "Day14"

DE_d21.primary <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day21/DE_Day21_Primary.csv", sep=',', header=TRUE) 
colnames(DE_d21.primary)[2] <- "gene.ID"# rename Pgen gene ID column
DE_d21.primary$Day <- "Day21"

Master_DESeq2_results      <- rbind(DE_d0.primary[,c('gene.ID','up','down','Day')], DE_d7.primary[,c('gene.ID','up','down','Day')], 
                                    DE_d14.primary[,c('gene.ID','up','down','Day')],DE_d21.primary[,c('gene.ID','up','down','Day')]) # Master DESeq2 


# sECOND EFFECT ON DAY 7
d7.Second.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GO.05.Day7_SecondEffect_AvM_Upregulated.csv")
d7.Second.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GO.05.Day7_SecondEffect_AvM_Downregulated.csv")

d7.MAvAM.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GO.05.Day7_GroupEffect_MAvAM_Upregulated.csv")
d7.MAvAM.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GO.05.Day7_GroupEffect_MAvAM_Downregulated.csv")

d7.Second.UP.05$dir    <- "Up"
d7.Second.DOWN.05$dir  <- "Down"
d7.MAvAM.UP.05$dir     <- "Up"
d7.MAvAM.DOWN.05$dir   <- "Down"

d7.Second.UP.05$effect    <- "secondAvM"
d7.Second.DOWN.05$effect  <- "secondAvM"
d7.MAvAM.UP.05$effect     <- "MAvAM"
d7.MAvAM.DOWN.05$effect   <- "MAvAM"
View(Master_DESeq2_results_SECOND)
Master_goseq_results_SECOND  <- rbind(d7.Second.UP.05, d7.Second.DOWN.05, 
                              d7.MAvAM.UP.05, d7.MAvAM.DOWN.05) # Master GOseq OF ALL PRIMARY EFFECTS
Master_goseq_results_SECOND <- Master_goseq_results_SECOND %>%  dplyr::filter(!ontology %in% 'CC') # Master GOseq OF ALL PRIMARY EFFECTS

DE_d7.second <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day7/DE_Day7_Second.csv", sep=',', header=TRUE) 
colnames(DE_d7.second)[2] <- "gene.ID"# rename Pgen gene ID column
DE_d7.second$effect <- "secondAvM"

DE_d7.MAvAM <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/Day7/DE_Day7_MA_AM.csv", sep=',', header=TRUE) 
colnames(DE_d7.MAvAM)[2] <- "gene.ID"# rename Pgen gene ID column
DE_d7.MAvAM$effect <- "MAvAM"

Master_DESeq2_results_SECOND  <- rbind(DE_d7.second[,c('gene.ID','up','down','effect')], DE_d7.MAvAM[,c('gene.ID','up','down','effect')]) #



# Build a master list of all genes and GO terms 'Pgen_GOterms2'
Geoduck_annotation <- read.delim2(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Seq_details/Panopea-generosa-genes-annotations.txt", header=F) # Load themaster Pgenerosa gene list 
Pgen_GOterms <- Geoduck_annotation %>% dplyr::select(c('V1','V8')) # select only two columns - those with the gene IDs and those with the GO terms
Pgen_GOterms2 <- strsplit(Pgen_GOterms$V8, split = "; ") # create a string splitting by delimiter '; ' - view the data to see that this separates each GO term entry in the string
Pgen_GOterms2 <- data.frame(gene.ID = rep(Pgen_GOterms$V1, sapply(Pgen_GOterms2, length)), Go.terms = unlist(Pgen_GOterms2)) # create new dataframe 'Pgen_GOterms2' listing genes for each GO term (MUCH longer!)
Pgen_GOterms2 <- na.omit(Pgen_GOterms2) # ommit the NAs  - genes without GO annotation


Pgen_condenced <- Geoduck_annotation[,c(1,7)] # load just the PGEN ID and the putative gene terms
Pgen_condenced$Gene_term    <- sub(" \\(EC.*", "", Pgen_condenced$V7)  # str_extract(annot.condenced$V7, "[^(]+")
Pgen_reference <- na.omit(Pgen_condenced[c(1,3)])
names(Pgen_reference)  <- c('PgenIDs', 'Gene_terms')



######################################################################################################################################################
###################################################################################################################################################### #
#
#
# PRIMARY EFFECT  GOSLIM ANALYSIS LOOP
#
#
###################################################################################################################################################### #
######################################################################################################################################################
# call all the module colors and days to loop GOslim analysis 
GOslimLoop_vars <- unique(Master_goseq_results[c(8,9)]) 
GOslimLoop_vars <- GOslimLoop_vars %>%dplyr::filter(!Day =='Day0')

# FOR LOOP FOR GOSLIM ANALYSIS AND CSV OUTPUTS 
for (i in 1:nrow(GOslimLoop_vars)) {
  # call the target dataset
  goseq_res         <- Master_goseq_results %>%  dplyr::filter(dir %in% GOslimLoop_vars[i,1], Day %in% GOslimLoop_vars[i,2])
  if (GOslimLoop_vars[i,1] == 'Up') {DESeq2_res <- Master_DESeq2_results %>%  dplyr::filter(up == 'TRUE') 
  } else {DESeq2_res <- Master_DESeq2_results %>%  dplyr::filter(up == 'FALSE') }
  DESeq2_res_2       <- DESeq2_res  %>%  dplyr::filter(Day %in% GOslimLoop_vars[i,2])
  gene_names         <- DESeq2_res_2$gene.ID # all gene IDs in the particular WGCNA module 
  # Biological Function - run GOslim
  goseq_res_BP        <- goseq_res %>%  filter(ontology=="BP") # BP - all GO terms upregulated
  BP_GOcollection     <- GOCollection(goseq_res_BP$category)
  GOslims_BP          <- data.frame(goSlim(BP_GOcollection, slim, "BP")) #Find common parent terms to slim down our list
  GOslims_BP$category <- row.names(GOslims_BP) #save rownames as category
  
  # Molecular Function - run GOslim
  goseq_res_MF        <- goseq_res %>%  filter(ontology=="MF") # BP - all GO terms upregulated
  MF_GOcollection     <- GOCollection(goseq_res_MF$category)
  GOslims_MF          <- data.frame(goSlim(MF_GOcollection, slim, "MF")) #Find common parent terms to slim down our list
  GOslims_MF$category <- row.names(GOslims_MF) #save rownames as category
  
  # ====================================================================================
  # Get mapped terms - add to the GOslims datatable 
  # from Sam White's Biostars [post](https://support.bioconductor.org/p/128407/#128409).
  # ====================================================================================
  # Write function mappedIds to get the query terms that mapped to the slim categories 
  # ...in other words, add a column to your slim dataframe with all the GO terms from goseq
  mappedIds <-  function(df, collection, OFFSPRING) {  #the command to run requires a dataframe of slim terms, like slims_MF above, your list of query terms, and the offspring from the GOCollection by goSlim
    map <- as.list(OFFSPRING[rownames(df)]) # Subset GOcollection offspring by the rownames of your dataframe
    mapped <- lapply(map, intersect, ids(collection)) #Find the terms that intersect between the subset made above of your query terms and the GOids from the GO collection
    df[["go_terms"]] <- vapply(unname(mapped), paste, collapse = ";", character(1L)) #Add column "go_terms" with matching terms 
    df #show resulting dataframe
  }
   
  BPslim_Mapped <- mappedIds(GOslims_BP, BP_GOcollection, GOBPOFFSPRING)
  MFslim_Mapped <- mappedIds(GOslims_MF, MF_GOcollection, GOMFOFFSPRING)
  
  
  # BIOLOGICAL PROCESS
  BPslim             <- filter(BPslim_Mapped, Term!="biological_process") #filter out empty slims and term "biological process" and slims with < 2 GO terms (omitted the Count>=2)
  BPsplitted         <- strsplit(as.character(BPslim$go_terms), ";") #split into multiple GO ids
  BPslim$BPsplitted  <- BPsplitted
  for (n in 1:nrow(BPslim)) {
    table       <- data.frame(GOlist = unlist(BPslim[n,6])) # call the BPsplitted column of characters and create a small table to filter
    table       <- unique(table)
    
    Pgen_module  <- Pgen_GOterms2 %>% dplyr::filter(gene.ID %in% gene_names) # d7_Mod.Brown$X calls the gene names in the origin Module membership dataframe at the start of this script
    Pgen_loop    <- Pgen_module %>% dplyr::filter(Go.terms %in% table$GOlist) # filter Gene IDs with the GO term
    Pgen_geneIDs <- Pgen_loop[-2] # ommit the GO.terms to call unique gene calls 
    Pgen_geneIDs <- unique(Pgen_geneIDs) # call unique Gene calls (unique genes that had the GO term within each of the GOslim bins)
   
    BPslim$Gene.Count[n] <- nrow(Pgen_geneIDs)  # count of unique GeneIDs in each GOslim bin
    BPslim$Gene.IDs[[n]] <- vapply((Pgen_geneIDs$gene.ID), paste, collapse = ";", character(1L))
    } # end n in 1:nrow
  
  BPslim_A <- data.frame(Term = rep.int(BPslim$Term, sapply(BPsplitted, length)), go_term = unlist(BPsplitted)) #list all
  BPslim_B <- merge(BPslim_A, BPslim, by="Term") #Add back counts, term, and category info
  BPslim_C <- unique(setDT(BPslim_B)[order(go_term, -Gene.Count)], by = "category") #remove duplicate offspring terms, keeping only those in the larger umbrella term (Count number)
  BPslim_final <- BPslim_C[,c(1,5,3,2,6,8:9)]
  colnames(BPslim_final) <- c("slim_term", "slim_cat", "GO_count", "GO_terms", "GO_list", "Gene_count", "Gene_IDs")
  BPslim_final[["Gene_IDs"]] <- vapply(unname(BPslim_final$Gene_IDs), paste, collapse = ";", character(1L)) # convert from a list to simply a charaacter string with ; delimiter
  #BPslim_final <- data.frame(slim_term=BPslim_C$Term, slim_cat=BPslim_C$category, category=BPslim_C$go_term, Gene.Count=BPslim_C$Gene.Count, GO.Count=BPslim_C$Count, Gene.IDs=BPslim_C$Gene.IDs) #rename columns) #rename columns
  BPslim_final$module_day <- paste(GOslimLoop_vars[i,2], GOslimLoop_vars[i,1], sep = '_')
  
  
        if (nrow(goseq_res_BP) >0) {
        BPslim_GOterm_summary       <- BPslim_final[,c(1,2,5,7)]
        s <- strsplit(BPslim_GOterm_summary$GO_list, split = ";")
        BPslim_GOterm_summary_2     <- data.frame(slim_term = rep(BPslim_GOterm_summary$slim_term, sapply(s, length)),
                                                  Gene_IDs  = rep(BPslim_GOterm_summary$Gene_IDs, sapply(s, length)),
                                                   GO_terms = unlist(s))
        colnames(goseq_res_BP)[1]   <- 'GO_terms'
        BPslim_GOterm_summary_final <- merge(goseq_res_BP, BPslim_GOterm_summary_2, by = 'GO_terms')
        
        
        s_2 <- strsplit(BPslim_GOterm_summary_final$Gene_IDs, split = ";")
        BPslim_GOterm_gene_annotation <- data.frame(slim_term      = rep(BPslim_GOterm_summary_final$slim_term, sapply(s_2, length)),
                                                    over_represented_pvalue = rep(BPslim_GOterm_summary_final$over_represented_pvalue, sapply(s_2, length)),
                                                    GO_terms       = rep(BPslim_GOterm_summary_final$GO_terms, sapply(s_2, length)),
                                                    term           = rep(BPslim_GOterm_summary_final$term, sapply(s_2, length)),
                                                    ontology       = rep(BPslim_GOterm_summary_final$ontology, sapply(s_2, length)),
                                                    Day            = rep(BPslim_GOterm_summary_final$Day, sapply(s_2, length)),
                                                    dir            = rep(BPslim_GOterm_summary_final$dir, sapply(s_2, length)),
                                                    PgenIDs        = unlist(s_2))
        BP_master_gene_reference <- merge(BPslim_GOterm_gene_annotation, Pgen_reference, by = "PgenIDs")
        
        } else (c(BPslim_GOterm_summary_final = NULL, BP_master_gene_reference = NULL))
  
  
  # MOLECULAR FUNCTION
  MFslim             <- filter(MFslim_Mapped, Term!="molecular_function") #filter out empty slims and term "biological process" (omitted the Count>=2)
  MFsplitted         <- strsplit(as.character(MFslim$go_terms), ";") #split into multiple GO ids
  MFslim$MFsplitted  <- MFsplitted
  for (m in 1:nrow(MFslim)) {
    table       <- data.frame(GOlist = unlist(MFslim[m,6])) # call the MFsplitted column of characters and create a small table to filter
    table       <- unique(table)
    
    Pgen_module  <- Pgen_GOterms2 %>% dplyr::filter(gene.ID %in% gene_names) # d7_Mod.Brown$X calls the gene names in the origin Module membership dataframe at the start of this script
    Pgen_loop    <- Pgen_module %>% dplyr::filter(Go.terms %in% table$GOlist) # filter Gene IDs with the GO term
    Pgen_geneIDs <- Pgen_loop[-2] # ommit the GO.terms to call unique gene calls 
    Pgen_geneIDs <- unique(Pgen_geneIDs) # call unique Gene calls (unique genes that had the GO term within each of the GOslim bins)
    
    MFslim$Gene.Count[m] <- nrow(Pgen_geneIDs)  # count of unique GeneIDs in each GOslim bin
    MFslim$Gene.IDs[[m]] <- vapply((Pgen_geneIDs$gene.ID), paste, collapse = ";", character(1L))
    } # end m in 1:nrow
  
    MFslim_A <- data.frame(Term = rep.int(MFslim$Term, sapply(MFsplitted, length)), go_term = unlist(MFsplitted)) #list all
    MFslim_B <- merge(MFslim_A, MFslim, by="Term") #Add back counts, term, and category info
    MFslim_C <- unique(setDT(MFslim_B)[order(go_term, -Gene.Count)], by = "category") #remove duplicate offspring terms, keeping only those in the larger umbrella term (Count number)
    MFslim_final <- MFslim_C[,c(1,5,3,2,6,8:9)]
    colnames(MFslim_final) <- c("slim_term", "slim_cat", "GO_count", "GO_terms", "GO_list", "Gene_count", "Gene_IDs")
    MFslim_final[["Gene_IDs"]] <- vapply(unname(MFslim_final$Gene_IDs), paste, collapse = ";", character(1L)) # convert from a list to simply a charaacter string with ; delimiter
    # MFslim_final <- data.frame(slim_term=MFslim_C$Term, slim_cat=MFslim_C$category, category=MFslim_C$go_term, Gene.Count=MFslim_C$Gene.Count, GO.Count=MFslim_C$Count) #rename columns) #rename columns
    MFslim_final$module_day <- paste(GOslimLoop_vars[i,2], GOslimLoop_vars[i,1], sep = '_')
    
    
    
            if (nrow(goseq_res_MF) >0) {
        MFslim_GOterm_summary       <- MFslim_final[,c(1,2,5,7)]
        s <- strsplit(MFslim_GOterm_summary$GO_list, split = ";")
        MFslim_GOterm_summary_2     <- data.frame(slim_term = rep(MFslim_GOterm_summary$slim_term, sapply(s, length)),
                                                  Gene_IDs  = rep(MFslim_GOterm_summary$Gene_IDs, sapply(s, length)),
                                                   GO_terms = unlist(s))
        colnames(goseq_res_MF)[1]   <- 'GO_terms'
        MFslim_GOterm_summary_final <- merge(goseq_res_MF, MFslim_GOterm_summary_2, by = 'GO_terms')
        
        
        s_2 <- strsplit(MFslim_GOterm_summary_final$Gene_IDs, split = ";")
        MFslim_GOterm_gene_annotation <- data.frame(slim_term      = rep(MFslim_GOterm_summary_final$slim_term, sapply(s_2, length)),
                                                    over_represented_pvalue = rep(MFslim_GOterm_summary_final$over_represented_pvalue, sapply(s_2, length)),
                                                    GO_terms       = rep(MFslim_GOterm_summary_final$GO_terms, sapply(s_2, length)),
                                                    term           = rep(MFslim_GOterm_summary_final$term, sapply(s_2, length)),
                                                    ontology       = rep(MFslim_GOterm_summary_final$ontology, sapply(s_2, length)),
                                                    Day            = rep(MFslim_GOterm_summary_final$Day, sapply(s_2, length)),
                                                    dir            = rep(MFslim_GOterm_summary_final$dir, sapply(s_2, length)),
                                                    PgenIDs        = unlist(s_2))
        MF_master_gene_reference <- merge(MFslim_GOterm_gene_annotation, Pgen_reference, by = "PgenIDs")
        
        } else (c(MFslim_GOterm_summary_final = NULL, MF_master_gene_reference = NULL))
    
    
    
    
    # save GOslim final datasets for BP and MF of each  module in their respective folder(s) by Day
    write.csv(MFslim_final, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOslim_MolFunction_",GOslimLoop_vars[i,1], "regulated.csv", sep ='')) # save csv file              
    write.csv(BPslim_final, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOslim_BiolProc_",GOslimLoop_vars[i,1], "regulated.csv", sep ='')) # save csv file       

    write.csv(MFslim_GOterm_summary_final, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOterms_and_GOslim_MolFunction_",GOslimLoop_vars[i,1], "regulated.csv", sep ='')) # save csv file
    write.csv(BPslim_GOterm_summary_final, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOterms_and_GOslim_BiolProc_",GOslimLoop_vars[i,1], "regulated.csv", sep ='')) # save csv file
    
    write.csv(MF_master_gene_reference, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOterms_and_GOslim_MolFunction_",GOslimLoop_vars[i,1], "regulated_GENE_REFERENCE.csv", sep ='')) # save csv
    write.csv(BP_master_gene_reference, file = paste("../Output/GO/DESeq2_goseq/", GOslimLoop_vars[i,2], "/GOterms_and_GOslim_BiolProc_",GOslimLoop_vars[i,1], "regulated_GENE_REFERENCE.csv", sep ='')) # save csv       
    
    print(paste(GOslimLoop_vars[i,2], GOslimLoop_vars[i,1], "done", sep = ' '))
}
    
    
    
    
    
    
    
    
    
    
    
    
    
    

    
    
    
    
    

######################################################################################################################################################
###################################################################################################################################################### #
#
#
# SECOND RREATMENT EFFECT  GOSLIM ANALYSIS LOOP (AMBIETN VS. MODERATE AND THE FULL INTERACTION AM V. MA)
#
#
###################################################################################################################################################### #
######################################################################################################################################################
# call all the module colors and days to loop GOslim analysis 
GOslimLoop_vars_SECOND<- unique(Master_goseq_results_SECOND[c(8,9)]) 
fix(GOslimLoop_vars_SECOND2)
GOslimLoop_vars_SECOND_OM <- GOslimLoop_vars_SECOND[-1,]
# FOR LOOP FOR GOSLIM ANALYSIS AND CSV OUTPUTS 
for (i in 1:nrow(GOslimLoop_vars_SECOND_OM)) {
  # call the target dataset
  goseq_res         <- Master_goseq_results_SECOND %>%  dplyr::filter(dir %in% GOslimLoop_vars_SECOND_OM[i,1], effect %in% GOslimLoop_vars_SECOND_OM[i,2])
  if (GOslimLoop_vars_SECOND_OM[i,1] == 'Up') {DESeq2_res <- Master_DESeq2_results_SECOND %>%  dplyr::filter(up == 'TRUE') 
  } else {DESeq2_res <- Master_DESeq2_results_SECOND %>%  dplyr::filter(up == 'FALSE') }
  DESeq2_res_2       <- DESeq2_res  %>%  dplyr::filter(effect %in% GOslimLoop_vars_SECOND_OM[i,2])
  gene_names         <- DESeq2_res_2$gene.ID # all gene IDs in the particular WGCNA module 
  # Biological Function - run GOslim
  goseq_res_BP        <- goseq_res %>%  filter(ontology=="BP") # BP - all GO terms upregulated
  BP_GOcollection     <- GOCollection(goseq_res_BP$category)
  GOslims_BP          <- data.frame(goSlim(BP_GOcollection, slim, "BP")) #Find common parent terms to slim down our list
  GOslims_BP$category <- row.names(GOslims_BP) #save rownames as category
  
  # Molecular Function - run GOslim
  goseq_res_MF        <- goseq_res %>%  filter(ontology=="MF") # BP - all GO terms upregulated
  MF_GOcollection     <- GOCollection(goseq_res_MF$category)
  GOslims_MF          <- data.frame(goSlim(MF_GOcollection, slim, "MF")) #Find common parent terms to slim down our list
  GOslims_MF$category <- row.names(GOslims_MF) #save rownames as category
  
  # ====================================================================================
  # Get mapped terms - add to the GOslims datatable 
  # from Sam White's Biostars [post](https://support.bioconductor.org/p/128407/#128409).
  # ====================================================================================
  # Write function mappedIds to get the query terms that mapped to the slim categories 
  # ...in other words, add a column to your slim dataframe with all the GO terms from goseq
  mappedIds <-  function(df, collection, OFFSPRING) {  #the command to run requires a dataframe of slim terms, like slims_MF above, your list of query terms, and the offspring from the GOCollection by goSlim
    map <- as.list(OFFSPRING[rownames(df)]) # Subset GOcollection offspring by the rownames of your dataframe
    mapped <- lapply(map, intersect, ids(collection)) #Find the terms that intersect between the subset made above of your query terms and the GOids from the GO collection
    df[["go_terms"]] <- vapply(unname(mapped), paste, collapse = ";", character(1L)) #Add column "go_terms" with matching terms 
    df #show resulting dataframe
  }
   
  BPslim_Mapped <- mappedIds(GOslims_BP, BP_GOcollection, GOBPOFFSPRING)
  MFslim_Mapped <- mappedIds(GOslims_MF, MF_GOcollection, GOMFOFFSPRING)
  
  
  # BIOLOGICAL PROCESS
  BPslim             <- filter(BPslim_Mapped, Term!="biological_process") #filter out empty slims and term "biological process" and slims with < 2 GO terms (omitted the Count>=2)
  BPsplitted         <- strsplit(as.character(BPslim$go_terms), ";") #split into multiple GO ids
  BPslim$BPsplitted  <- BPsplitted
  for (n in 1:nrow(BPslim)) {
    table       <- data.frame(GOlist = unlist(BPslim[n,6])) # call the BPsplitted column of characters and create a small table to filter
    table       <- unique(table)
    
    Pgen_module  <- Pgen_GOterms2 %>% dplyr::filter(gene.ID %in% gene_names) # d7_Mod.Brown$X calls the gene names in the origin Module membership dataframe at the start of this script
    Pgen_loop    <- Pgen_module %>% dplyr::filter(Go.terms %in% table$GOlist) # filter Gene IDs with the GO term
    Pgen_geneIDs <- Pgen_loop[-2] # ommit the GO.terms to call unique gene calls 
    Pgen_geneIDs <- unique(Pgen_geneIDs) # call unique Gene calls (unique genes that had the GO term within each of the GOslim bins)
   
    BPslim$Gene.Count[n] <- nrow(Pgen_geneIDs)  # count of unique GeneIDs in each GOslim bin
    BPslim$Gene.IDs[[n]] <- vapply((Pgen_geneIDs$gene.ID), paste, collapse = ";", character(1L))
    } # end n in 1:nrow
  
  BPslim_A <- data.frame(Term = rep.int(BPslim$Term, sapply(BPsplitted, length)), go_term = unlist(BPsplitted)) #list all
  BPslim_B <- merge(BPslim_A, BPslim, by="Term") #Add back counts, term, and category info
  BPslim_C <- unique(setDT(BPslim_B)[order(go_term, -Gene.Count)], by = "category") #remove duplicate offspring terms, keeping only those in the larger umbrella term (Count number)
  BPslim_final <- BPslim_C[,c(1,5,3,2,6,8:9)]
  colnames(BPslim_final) <- c("slim_term", "slim_cat", "GO_count", "GO_terms", "GO_list", "Gene_count", "Gene_IDs")
  BPslim_final[["Gene_IDs"]] <- vapply(unname(BPslim_final$Gene_IDs), paste, collapse = ";", character(1L)) # convert from a list to simply a charaacter string with ; delimiter
  #BPslim_final <- data.frame(slim_term=BPslim_C$Term, slim_cat=BPslim_C$category, category=BPslim_C$go_term, Gene.Count=BPslim_C$Gene.Count, GO.Count=BPslim_C$Count, Gene.IDs=BPslim_C$Gene.IDs) #rename columns) #rename columns
  BPslim_final$effect_dir <- paste(GOslimLoop_vars_SECOND_OM[i,2], GOslimLoop_vars_SECOND_OM[i,1], sep = '_')
  
  
        if (nrow(goseq_res_BP) >1) {
        BPslim_GOterm_summary       <- BPslim_final[,c(1,2,5,7)]
        s <- strsplit(BPslim_GOterm_summary$GO_list, split = ";")
        BPslim_GOterm_summary_2     <- data.frame(slim_term = rep(BPslim_GOterm_summary$slim_term, sapply(s, length)),
                                                  Gene_IDs  = rep(BPslim_GOterm_summary$Gene_IDs, sapply(s, length)),
                                                   GO_terms = unlist(s))
        colnames(goseq_res_BP)[1]   <- 'GO_terms'
        BPslim_GOterm_summary_final <- merge(goseq_res_BP, BPslim_GOterm_summary_2, by = 'GO_terms')
        
        
        s_2 <- strsplit(BPslim_GOterm_summary_final$Gene_IDs, split = ";")
        BPslim_GOterm_gene_annotation <- data.frame(slim_term      = rep(BPslim_GOterm_summary_final$slim_term, sapply(s_2, length)),
                                                    over_represented_pvalue = rep(BPslim_GOterm_summary_final$over_represented_pvalue, sapply(s_2, length)),
                                                    GO_terms       = rep(BPslim_GOterm_summary_final$GO_terms, sapply(s_2, length)),
                                                    term           = rep(BPslim_GOterm_summary_final$term, sapply(s_2, length)),
                                                    ontology       = rep(BPslim_GOterm_summary_final$ontology, sapply(s_2, length)),
                                                    effect            = rep(BPslim_GOterm_summary_final$effect, sapply(s_2, length)),
                                                    dir            = rep(BPslim_GOterm_summary_final$dir, sapply(s_2, length)),
                                                    PgenIDs        = unlist(s_2))
        BP_master_gene_reference <- merge(BPslim_GOterm_gene_annotation, Pgen_reference, by = "PgenIDs")
        
    # save GOslim final datasets for BP and MF of each  module in their respective folder(s) by Day
    write.csv(BPslim_final, file = paste("../Output/GO/DESeq2_goseq/Day7/GOslim_BiolProc_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1], "regulated.csv", sep ='')) 
    write.csv(BPslim_GOterm_summary_final, file = paste("../Output/GO/DESeq2_goseq/Day7/GOterms_and_GOslim_BiolProc_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1], "regulated.csv", sep ='')) 
    write.csv(BP_master_gene_reference, file = paste("../Output/GO/DESeq2_goseq/Day7/GOterms_and_GOslim_BiolProc_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1],  "regulated_GENE_REFERENCE.csv", sep ='')) 
    
    
        } else (c(BPslim_GOterm_summary_final = NULL, BP_master_gene_reference = NULL))
  
  
  # MOLECULAR FUNCTION
  MFslim             <- filter(MFslim_Mapped, Term!="molecular_function") #filter out empty slims and term "biological process" (omitted the Count>=2)
  MFsplitted         <- strsplit(as.character(MFslim$go_terms), ";") #split into multiple GO ids
  MFslim$MFsplitted  <- MFsplitted
  for (m in 1:nrow(MFslim)) {
    table       <- data.frame(GOlist = unlist(MFslim[m,6])) # call the MFsplitted column of characters and create a small table to filter
    table       <- unique(table)
    
    Pgen_module  <- Pgen_GOterms2 %>% dplyr::filter(gene.ID %in% gene_names) # d7_Mod.Brown$X calls the gene names in the origin Module membership dataframe at the start of this script
    Pgen_loop    <- Pgen_module %>% dplyr::filter(Go.terms %in% table$GOlist) # filter Gene IDs with the GO term
    Pgen_geneIDs <- Pgen_loop[-2] # ommit the GO.terms to call unique gene calls 
    Pgen_geneIDs <- unique(Pgen_geneIDs) # call unique Gene calls (unique genes that had the GO term within each of the GOslim bins)
    
    MFslim$Gene.Count[m] <- nrow(Pgen_geneIDs)  # count of unique GeneIDs in each GOslim bin
    MFslim$Gene.IDs[[m]] <- vapply((Pgen_geneIDs$gene.ID), paste, collapse = ";", character(1L))
    } # end m in 1:nrow
  
    MFslim_A <- data.frame(Term = rep.int(MFslim$Term, sapply(MFsplitted, length)), go_term = unlist(MFsplitted)) #list all
    MFslim_B <- merge(MFslim_A, MFslim, by="Term") #Add back counts, term, and category info
    MFslim_C <- unique(setDT(MFslim_B)[order(go_term, -Gene.Count)], by = "category") #remove duplicate offspring terms, keeping only those in the larger umbrella term (Count number)
    MFslim_final <- MFslim_C[,c(1,5,3,2,6,8:9)]
    colnames(MFslim_final) <- c("slim_term", "slim_cat", "GO_count", "GO_terms", "GO_list", "Gene_count", "Gene_IDs")
    MFslim_final[["Gene_IDs"]] <- vapply(unname(MFslim_final$Gene_IDs), paste, collapse = ";", character(1L)) # convert from a list to simply a charaacter string with ; delimiter
    # MFslim_final <- data.frame(slim_term=MFslim_C$Term, slim_cat=MFslim_C$category, category=MFslim_C$go_term, Gene.Count=MFslim_C$Gene.Count, GO.Count=MFslim_C$Count) #rename columns) #rename columns
    MFslim_final$effect_dir <- paste(GOslimLoop_vars_SECOND_OM[i,2], GOslimLoop_vars_SECOND_OM[i,1], sep = '_')
    
    
    
            if (nrow(goseq_res_MF) >1) {
        MFslim_GOterm_summary       <- MFslim_final[,c(1,2,5,7)]
        s <- strsplit(MFslim_GOterm_summary$GO_list, split = ";")
        MFslim_GOterm_summary_2     <- data.frame(slim_term = rep(MFslim_GOterm_summary$slim_term, sapply(s, length)),
                                                  Gene_IDs  = rep(MFslim_GOterm_summary$Gene_IDs, sapply(s, length)),
                                                   GO_terms = unlist(s))
        colnames(goseq_res_MF)[1]   <- 'GO_terms'
        MFslim_GOterm_summary_final <- merge(goseq_res_MF, MFslim_GOterm_summary_2, by = 'GO_terms')
        
        
        s_2 <- strsplit(MFslim_GOterm_summary_final$Gene_IDs, split = ";")
        MFslim_GOterm_gene_annotation <- data.frame(slim_term      = rep(MFslim_GOterm_summary_final$slim_term, sapply(s_2, length)),
                                                    over_represented_pvalue = rep(MFslim_GOterm_summary_final$over_represented_pvalue, sapply(s_2, length)),
                                                    GO_terms       = rep(MFslim_GOterm_summary_final$GO_terms, sapply(s_2, length)),
                                                    term           = rep(MFslim_GOterm_summary_final$term, sapply(s_2, length)),
                                                    ontology       = rep(MFslim_GOterm_summary_final$ontology, sapply(s_2, length)),
                                                    effect         = rep(MFslim_GOterm_summary_final$effect, sapply(s_2, length)),
                                                    dir            = rep(MFslim_GOterm_summary_final$dir, sapply(s_2, length)),
                                                    PgenIDs        = unlist(s_2))
        MF_master_gene_reference <- merge(MFslim_GOterm_gene_annotation, Pgen_reference, by = "PgenIDs")
        
            # save GOslim final datasets for BP and MF of each  module in their respective folder(s) by Day
     write.csv(MFslim_final, file = paste("../Output/GO/DESeq2_goseq/Day7/GOslim_MolFunction_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1], "regulated.csv", sep ='')) 
     write.csv(MFslim_GOterm_summary_final, file = paste("../Output/GO/DESeq2_goseq/Day7/GOterms_and_GOslim_MolFunction_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1],  "regulated.csv", sep ='')) 
     write.csv(MF_master_gene_reference, file = paste("../Output/GO/DESeq2_goseq/Day7/GOterms_and_GOslim_MolFunction_",GOslimLoop_vars_SECOND_OM[i,2], "_", GOslimLoop_vars_SECOND_OM[i,1],  "regulated_GENE_REFERENCE.csv", sep ='')) 
        
        } else (c(MFslim_GOterm_summary_final = NULL, MF_master_gene_reference = NULL))
    
    print(paste(GOslimLoop_vars_SECOND_OM[i,2], GOslimLoop_vars_SECOND_OM[i,1], "done", sep = ' '))
}

```



PLOTTING  GOslim --log1- pvalue plots 
PRIMARY  EFFECT
```{r}
# read in the outputs from the previous... (note- we did not run goslim fror Day0 DEGs because there were very very few)

D7_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day7/primary_effect/GOterms_and_GOslim_BiolProc_Upregulated.csv")
D7_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day7/primary_effect/GOterms_and_GOslim_BiolProc_Downregulated.csv")
D7_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day7/primary_effect/GOterms_and_GOslim_MolFunction_Upregulated.csv")
D7_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day7/primary_effect/GOterms_and_GOslim_MolFunction_Downregulated.csv")

D14_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOterms_and_GOslim_BiolProc_Upregulated.csv")
D14_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOterms_and_GOslim_BiolProc_Downregulated.csv")
D14_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOterms_and_GOslim_MolFunction_Upregulated.csv")
D14_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOterms_and_GOslim_MolFunction_Downregulated.csv")

D21_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOterms_and_GOslim_BiolProc_Upregulated.csv")
D21_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOterms_and_GOslim_BiolProc_Downregulated.csv")
D21_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOterms_and_GOslim_MolFunction_Upregulated.csv")
D21_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOterms_and_GOslim_MolFunction_Downregulated.csv")



#MASTER FOR PLOTTING 
# biological process upregulated 
BP_UP_Master <- rbind(D7_Goslim_UP_BP, D14_Goslim_UP_BP, D21_Goslim_UP_BP)
BP_UP_Master$day_dir <- paste(BP_UP_Master$Day, BP_UP_Master$dir, sep ='_')
BP_UP_Master$day_dir <- factor(BP_UP_Master$day_dir , levels = c("Day7_Up", "Day14_Up", "Day21_Up"))
# biological process donwregualted 
BP_DOWN_Master <- rbind(D7_Goslim_DOWN_BP, D14_Goslim_DOWN_BP, D21_Goslim_DOWN_BP)
BP_DOWN_Master$day_dir <- paste(BP_DOWN_Master$Day, BP_DOWN_Master$dir, sep ='_')
BP_DOWN_Master$day_dir <- factor(BP_DOWN_Master$day_dir , levels = c("Day7_Down", "Day14_Down", "Day21_Down"))

# molecular function upregulated 
MF_UP_Master <- rbind(D7_Goslim_UP_MF, D14_Goslim_UP_MF, D21_Goslim_UP_MF)
MF_UP_Master$day_dir <- paste(MF_UP_Master$Day, MF_UP_Master$dir, sep ='_')
MF_UP_Master$day_dir <- factor(MF_UP_Master$day_dir , levels = c("Day7_Up", "Day14_Up", "Day21_Up"))
# molecular function donwregualted 
MF_DOWN_Master <- rbind(D7_Goslim_DOWN_MF, D14_Goslim_DOWN_MF, D21_Goslim_DOWN_MF)
MF_DOWN_Master$day_dir <- paste(MF_DOWN_Master$Day, MF_DOWN_Master$dir, sep ='_')
MF_DOWN_Master$day_dir <- factor(MF_DOWN_Master$day_dir , levels = c("Day7_Down", "Day14_Down", "Day21_Down"))


############################################################################################################## 3
#  Biological Process Upregulated 
BP_UP_Plot <-ggplot(data = BP_UP_Master, aes(x = day_dir, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Biological Process: Primary Effect upregulated genes (higher by ambient history)') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Biol_Process_Upregulated_DEGs_PrimEffect.pdf", sep =''), width=15, height=35)
print(BP_UP_Plot)
dev.off()

############################################################################################################## 3
#  Molecular Function Upregulated 
MF_UP_Plot <-ggplot(data = MF_UP_Master, aes(x = day_dir, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(MF_UP_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(MF_UP_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Molecular Function: Primary Effect upregulated genes (higher by ambient history)') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Mol_Function_Upregulated_DEGs_PrimEffect.pdf", sep =''), width=25, height=15)
print(MF_UP_Plot)
dev.off()








############################################################################################################## 3
#  Biological Process Downregulated 
BP_DOWN_Plot <-ggplot(data = BP_DOWN_Master, aes(x = day_dir, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(BP_DOWN_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(BP_DOWN_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Biological Process: Primary Effect Downregulated genes (higher by ambient history)') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Biol_Process_Downregulated_DEGs_PrimEffect.pdf", sep =''), width=15, height=35)
print(BP_DOWN_Plot)
dev.off()

############################################################################################################## 3
#  Molecular Function Downregulated 
MF_DOWN_Plot <-ggplot(data = MF_DOWN_Master, aes(x = day_dir, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(MF_DOWN_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(MF_DOWN_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Molecular Function: Primary Effect Downregulated genes (higher by Moderate stress history)') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Mol_Function_Downregulated_DEGs_PrimEffect.pdf", sep =''), width=20, height=4)
print(MF_DOWN_Plot)
dev.off()

```


PLOTTING  GOslim --log1- pvalue plots 
SECOND EFFECT AND GROUP EFFECT PLOTS (DAY 7)
```{r}
# read in the outputs from the previous... (note- we did not run goslim fror Day0 DEGs because there were very very few)
# DAY 7 - SECOND TREATMENT EFFECT AMBIENT > MODERATE
# D7_Goslim_secondAvM_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day7/secondAvM/GOterms_and_GOslim_BiolProc_secondAvM_Upregulated.csv") #no upregualted terms! 
D7_Goslim_secondAvM_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GOterms_and_GOslim_BiolProc_secondAvM_Downregulated.csv")
# D7_Goslim_secondAvM_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day7/secondAvM/GOterms_and_GOslim_MolFunction_secondAvM_Upregulated.csv") #no upregualted terms! 
D7_Goslim_secondAvM_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GOterms_and_GOslim_MolFunction_secondAvM_Downregulated.csv")


# DAY 7 - GROUP TREATMENT EFFECT MA > AM
D7_Goslim_MAvAM_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GOterms_and_GOslim_BiolProc_MAvAM_Upregulated.csv") 
D7_Goslim_MAvAM_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GOterms_and_GOslim_BiolProc_MAvAM_Downregulated.csv")
# D7_Goslim_MAvAM_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GOterms_and_GOslim_MolFunction_MAvAM_Upregulated.csv") # no upregualted molecular function terms!
D7_Goslim_MAvAM_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GOterms_and_GOslim_MolFunction_MAvAM_Downregulated.csv")


############################################################################################################## 
# DAY 7 - MA  versus AM - Full model effect 
#  Biological Process Upregulated 
BP_UP_Plot_MAvAM <-ggplot(data = D7_Goslim_MAvAM_UP_BP, aes(x = effect, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Biological Process: Day 7 Full model effect MA versus AM') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/Biol_Process_Upregulated_DEGs_MAvAM.pdf", sep =''), width=15, height=15)
print(BP_UP_Plot_MAvAM)
dev.off()

#  Biological Process Upregulated 
BP_DOWN_Plot_MAvAM <-ggplot(data = D7_Goslim_MAvAM_DOWN_BP, aes(x = effect, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(BP_UP_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Biological Process: Day 7 Full model effect MA versus AM') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/Biol_Process_Downregulated_DEGs_MAvAM.pdf", sep =''), width=15, height=10)
print(BP_DOWN_Plot_MAvAM)
dev.off()


############################################################################################################## 3
#  Molecular Function Upregulated 
MF_DOWN_Plot_MAvAM <-ggplot(data = D7_Goslim_MAvAM_DOWN_MF, aes(x = effect, y = forcats::fct_rev(term))) + 
  geom_tile(aes(fill= -log10(over_represented_pvalue), width = 1)) + 
  scale_fill_gradient(low = "grey95", high = "black",limits=c(0, (ceiling(max(-log10(MF_UP_Master$over_represented_pvalue))))), breaks=seq(0, (ceiling(max(-log10(MF_UP_Master$over_represented_pvalue)))),by=2))  +
  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                     strip.text.x = element_text(size = 8, face = "bold"),
                     axis.title.x = element_blank(),
                     axis.title.y = element_text(size=8),
                     axis.text = element_text(size = 8), legend.position = "right",
                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
  ggtitle('Molecular Function: Day 7 Full model effect MA versus AM') +
  # facet_wrap(~ (substr(slim_term, 1,30)))
  facet_wrap((substr(slim_term, 1,30)) ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/Mol_Function_Downregulated_DEGs_MAvAM.pdf", sep =''), width=15, height=10)
print(MF_DOWN_Plot_MAvAM)
dev.off()




```




PLOTTING  GOslim - gene count plots 
```{r}
# read in the outputs from the previous... (note- we did not run goslim fror Day0 DEGs because there were very very few)

D7_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day7/GOslim_BiolProc_Upregulated.csv")
D7_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day7/GOslim_BiolProc_Downregulated.csv")

D7_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day7/GOslim_MolFunction_Upregulated.csv")
D7_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day7/GOslim_MolFunction_Downregulated.csv")


D14_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOslim_BiolProc_Upregulated.csv")
D14_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOslim_BiolProc_Downregulated.csv")

D14_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOslim_MolFunction_Upregulated.csv")
D14_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day14/GOslim_MolFunction_Downregulated.csv")



D21_Goslim_UP_BP    <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOslim_BiolProc_Upregulated.csv")
D21_Goslim_DOWN_BP  <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOslim_BiolProc_Downregulated.csv")

D21_Goslim_UP_MF    <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOslim_MolFunction_Upregulated.csv")
D21_Goslim_DOWN_MF  <- read.csv("../Output/GO/DESeq2_goseq/Day21/GOslim_MolFunction_Downregulated.csv")



#MASTER FOR PLOTTING 
# biological process upregulated 
BP_UP_Master <- rbind(D7_Goslim_UP_BP, D14_Goslim_UP_BP, D21_Goslim_UP_BP)
BP_UP_Master$module_day <- factor(BP_UP_Master$module_day , levels = c("Day7_Up", "Day14_Up", "Day21_Up"))
# biological process donwregualted 
BP_DOWN_Master <- rbind(D7_Goslim_DOWN_BP, D14_Goslim_DOWN_BP, D21_Goslim_DOWN_BP)
BP_DOWN_Master$module_day <- factor(BP_DOWN_Master$module_day , levels = c("Day7_Down", "Day14_Down", "Day21_Down"))


MF_UP_Master <- rbind(D7_Goslim_UP_MF, D14_Goslim_UP_MF, D21_Goslim_UP_MF)
MF_UP_Master$module_day <- factor(MF_UP_Master$module_day , levels = c("Day7_Up", "Day14_Up", "Day21_Up"))
# biological process donwregualted 
MF_DOWN_Master <- rbind(D7_Goslim_DOWN_MF, D14_Goslim_DOWN_MF, D21_Goslim_DOWN_MF)
MF_DOWN_Master$module_day <- factor(MF_DOWN_Master$module_day , levels = c("Day7_Down", "Day14_Down", "Day21_Down"))


# plots
BP_UP_Plot <- BP_UP_Master %>% dplyr::filter(Gene_count >= 5) %>%  
              ggplot(aes(x = "BP_Upreg", y = forcats::fct_rev(slim_term))) + 
                geom_tile(aes(fill=Gene_count, width = 1)) + 
                scale_fill_gradient(low = "grey95", high = "grey10",limits=c(0, 20), breaks=seq(0,20,by=5)) +
                facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                   strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                   strip.text.x = element_text(size = 8, face = "bold"),
                                   axis.title.x = element_blank(),
                                   axis.title.y = element_text(size=8),
                                   axis.text = element_text(size = 8), legend.position = "right",
                                   plot.margin = unit(c(0,1,0,0.25), "cm"))+
                ggtitle('GOslim Biological Process: Upregulated DEGs Primary Effect All')

BP_DOWN_Plot <- BP_DOWN_Master %>% dplyr::filter(Gene_count >= 5) %>%  
                ggplot(aes(x = "BP_Downreg", y = forcats::fct_rev(slim_term))) + 
                  geom_tile(aes(fill=Gene_count, width = 1)) + 
                  scale_fill_gradient(low = "grey95", high = "grey10",limits=c(0, 20), breaks=seq(0,20,by=5)) +
                  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                     strip.text.x = element_text(size = 8, face = "bold"),
                                     axis.title.x = element_blank(),
                                     axis.title.y = element_text(size=8),
                                     axis.text = element_text(size = 8), legend.position = "right",
                                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
                  ggtitle('GOslim Biological Process: Downregulated DEGs Primary Effect All')





MF_UP_Plot <-MF_UP_Master %>% dplyr::filter(Gene_count >= 2) %>% 
             ggplot(aes(x = "MF_Upreg", y = forcats::fct_rev(slim_term))) + 
                geom_tile(aes(fill=Gene_count, width = 1)) + 
                scale_fill_gradient(low = "grey95", high = "grey10",limits=c(0, 20), breaks=seq(0,20,by=5)) +
                facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                   strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                   strip.text.x = element_text(size = 8, face = "bold"),
                                   axis.title.x = element_blank(),
                                   axis.title.y = element_text(size=8),
                                   axis.text = element_text(size = 8), legend.position = "right",
                                   plot.margin = unit(c(0,1,0,0.25), "cm"))+
                ggtitle('GOslim Mol Function: Upregulated DEGs Primary Effect All')

MF_DOWN_Plot <-MF_DOWN_Master %>% dplyr::filter(Gene_count >= 2) %>% 
                 ggplot(aes(x = "MF_Downreg", y = forcats::fct_rev(slim_term))) + 
                  geom_tile(aes(fill=Gene_count, width = 1)) + 
                  scale_fill_gradient(low = "grey95", high = "grey10",limits=c(0, 20), breaks=seq(0,20,by=5)) +
                  facet_grid(~module_day, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                     strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                     strip.text.x = element_text(size = 8, face = "bold"),
                                     axis.title.x = element_blank(),
                                     axis.title.y = element_text(size=8),
                                     axis.text = element_text(size = 8), legend.position = "right",
                                     plot.margin = unit(c(0,1,0,0.25), "cm"))+
                  ggtitle('GOslim Mol Function: Downregulated DEGs Primary Effect All')




# SAVE PLOTS  ------------------------------------------------------------------------------------------------- #
pdf(paste("../Output/GO/DESeq2_goseq/GOslim_PrimEff_BiolProcess.pdf", sep =''), width=20, height=8)
print(ggarrange(BP_UP_Plot, BP_DOWN_Plot,         
                plotlist = NULL,
                ncol = 2,
                nrow = 1,
                labels = NULL))
dev.off() 


pdf(paste("../Output/GO/DESeq2_goseq/GOslim_PrimEff_MolFunction.pdf", sep =''), width=20, height=8)
print(ggarrange(MF_UP_Plot, MF_DOWN_Plot,         
                plotlist = NULL,
                ncol = 2,
                nrow = 1,
                labels = NULL))
dev.off() 

```







prep
```{r prep data}
# add ontology column  ---------------------------------------------------------------------------------------- #
All.UP_BPslim_final$Ontolgy <- "BP_Upregulated_all"
All.UP_MFslim_final$Ontolgy <- "MF_Upregulated_all"

All.DOWN_BPslim_final$Ontolgy <- "BP_Downregulated_all"
All.DOWN_MFslim_final$Ontolgy <- "MF_Downregulated_all"

# BIND DATA TO FACET THE PLOTS BY UP AND DOWN REG   ---------------------------------------------------------- #
# bp
BP_All <- rbind(All.UP_BPslim_final, All.DOWN_BPslim_final) # merge the data by binding rows 
BP_All$Ont <- "BP" # create a new common clumn to call in the plot 
BP_All$Ontolgy <- factor(BP_All$Ontolgy, levels = c("BP_Upregulated_all", "BP_Downregulated_all"))# reorder the facotr level for the facet wrap plot 
BP_All_filtered <- BP_All %>%  dplyr::filter(Gene.Count > 1) # ommit all with gene counts >1
# mf
MF_All <- rbind(All.UP_MFslim_final, All.DOWN_MFslim_final) # merge the data by binding rows 
MF_All$Ont <- "MF" # create a new common clumn to call in the plot 
MF_All$Ontolgy <- factor(MF_All$Ontolgy, levels = c("MF_Upregulated_all", "MF_Downregulated_all")) # reorder the facotr level for the facet wrap plot 
MF_All_filtered <- MF_All %>%  dplyr::filter(Gene.Count > 1) # ommit all with gene counts >1
```

Stacked bar plots -  Gene Counts within GOslim term (NOTE: there are likely duplicates (or more) BETWEEN the GOslim bins - however EACH bin contains UNIQUE genes)
```{r barplots - ALL DEGs PrimEffect} 
# create color palette  --------------------------------------------------------------------------------------- #
library(RColorBrewer)
cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7") # color blind pallette
OrangeRed <- brewer.pal(2, "OrRd") 
GreenBlue <- brewer.pal(2, "GnBu") 


# PLOTTING --------------------------------------------------------------------------------------------------- #
BP_Plot_PrimEffect_All <- ggplot(data = BP_All_filtered, aes(x = Ont, y = Gene.Count, fill=forcats::fct_reorder(slim_term,Gene.Count,.desc = TRUE))) + # BP plot
                               geom_bar(color = "white",size=1.5,stat="identity") + # call bar and create lines between each slim term
                               scale_fill_manual(values =  rev( colorRampPalette(OrangeRed)( (nrow(BP_All)) ) ) )+ # fill with pallette accomodating the max nmber of slim terms
                               geom_text(aes(label = forcats::fct_reorder(slim_term,Gene.Count,.desc = TRUE)), colour = "black", position="stack", size = 7, vjust = 1.25) + # add labels
                               theme_classic() + # classic theme
                               ylim(0, 300) + 
                               theme(legend.position = "none",text = element_text(size=25)) +
                               facet_wrap(~Ontolgy) # facet by the upregulated and downregulated datasets

MF_Plot_PrimEffect_All <- ggplot(data = MF_All_filtered, aes(x = Ont, y = Gene.Count, fill=forcats::fct_reorder(slim_term,Gene.Count,.desc = TRUE))) + # MF plot
                               geom_bar(color = "white",size=1.5,stat="identity") + # call bar and create lines between each slim term
                               scale_fill_manual(values =  rev( colorRampPalette(GreenBlue)( (nrow(MF_All)) ) ) )+ # fill with pallette accomodating the max nmber of slim terms
                               geom_text(aes(label = forcats::fct_reorder(slim_term,Gene.Count,.desc = TRUE)), colour = "black", position="stack", size = 7, vjust = 1.25) + # add labels
                               theme_classic() + # classic theme
                               ylim(0, 100) +
                               theme(legend.position = "none",text = element_text(size=25)) +
                               facet_wrap(~Ontolgy) # facet by the upregulated and downregulated datasets

# SAVE PLOTS  ------------------------------------------------------------------------------------------------- #
pdf(paste("../Output/GO/DESeq2_goseq/GOslim_All_PrimEff_BP.pdf", sep =''), width=15, height=20)
print(ggarrange(BP_Plot_PrimEffect_All,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()     

pdf(paste("../Output/GO/DESeq2_goseq/GOslim_All_PrimEff_MF.pdf", sep =''), width=15, height=20)
print(ggarrange(MF_Plot_PrimEffect_All,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()     

```

Geomtile Heatmaps
```{r geom_tile heatmaps- ALL DEGs PrimEffect}

# plots
BP_Plot_PrimEffect_All <-ggplot(data = BP_All_filtered, aes(x = Ont, y = slim_term)) + 
                          geom_tile(aes(fill=Gene.Count, width = 1)) + 
                          scale_fill_gradient(low = "thistle1", high = "steelblue4") +
                          facet_grid(~Ontolgy, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                          theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                             panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                             strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                             strip.text.x = element_text(size = 8, face = "bold"),
                                             axis.title.x = element_blank(),
                                             axis.title.y = element_text(size=8),
                                             axis.text = element_text(size = 8), legend.position = "right",
                                             plot.margin = unit(c(0,1,0,0.25), "cm"))+
                          ggtitle('GOslim Biological Process: DESeq2 DEGs PrimEffect')

# plot MF
MF_Plot_PrimEffect_All <-ggplot(data = MF_All_filtered, aes(x = Ont, y = slim_term)) + 
                          geom_tile(aes(fill=Gene.Count, width = 1)) + 
                          scale_fill_gradient(low = "azure2", high = "springgreen4") +
                          facet_grid(~Ontolgy, labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                          theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                             panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                                             strip.text.y = element_text(angle=0, size = 8, face = "bold"),
                                             strip.text.x = element_text(size = 8, face = "bold"),
                                             axis.title.x = element_blank(),
                                             axis.title.y = element_text(size=8),
                                             axis.text = element_text(size = 8), legend.position = "right",
                                             plot.margin = unit(c(0,1,0,0.25), "cm"))+
                          ggtitle('GOslim Molecular Function: DESeq2 DEGs PrimEffect')

pdf(paste("../Output/GO/DESeq2_goseq/GOslim_All_PrimEff_Heatmap.pdf", sep =''), width=20, height=8)
print(ggarrange(BP_Plot_PrimEffect_All, MF_Plot_PrimEffect_All,         
                plotlist = NULL,
                ncol = 2,
                nrow = 1,
                labels = NULL))
dev.off() 
```


Follow-up from the stacked blots above...
What are the genesin the GOslimss of interest
Extract genes in GOslim bins of interest and plots their LFC results (DESeq2)
```{r} 
# prep data for the for loop plotting...
# add column 'DE.direction'
All.DOWN_MFslim$DE.direction  <- "downregulated"
All.DOWN_BPslim$DE.direction  <- "downregulated"
All.UP_MFslim$DE.direction    <- "upregulated"
All.UP_BPslim$DE.direction    <- "upregulated"

# add column 'Experiment.note'
All.DOWN_MFslim$Experiment.note  <- "All_Days_PrimaryEfffect"
All.DOWN_BPslim$Experiment.note  <- "All_Days_PrimaryEfffect"
All.UP_MFslim$Experiment.note    <- "All_Days_PrimaryEfffect"
All.UP_BPslim$Experiment.note    <- "All_Days_PrimaryEfffect"

# ommit rownames
rownames(All.DOWN_MFslim)<-NULL
rownames(All.DOWN_BPslim)<-NULL
rownames(All.UP_MFslim)  <-NULL
rownames(All.UP_BPslim)  <-NULL

# merge data frames to build a master GOslim
Master_GOslim <- rbind(All.DOWN_MFslim[,c(10,7,9,8,3,4,5)], All.DOWN_BPslim[,c(10,7,9,8,3,4,5)], All.UP_MFslim[,c(10,7,9,8,3,4,5)], All.UP_BPslim[,c(10,7,9,8,3,4,5)]) # merge for a master table with rbind

# load DESeq2 results 
All_DEGs_Primary.Ambieant_v_Moderate<-read.csv("C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/DESeq2/10cpm/DE_PrimaryTreatment.All.csv")
All_DEGs_Primary.Ambieant_v_Moderate <- All_DEGs_Primary.Ambieant_v_Moderate[2:(ncol(All_DEGs_Primary.Ambieant_v_Moderate))] # ommit the first column - DESEq2 results data 
names(All_DEGs_Primary.Ambieant_v_Moderate)[1] <- 'Gene.ID' # rename the column 

Pgen_annot <- Geoduck_annotation[,c(1,7)]# call only the gene ID and gene names in the annotation csv
names(Pgen_annot) <- c('Gene.ID', 'Gene.name') # rename the columns 
Pgen_annot$Gene.name <- str_extract(Pgen_annot$Gene.name, "[^(]+") # call all gene names before the delimiter ( when the EC code is included)

# loop through the gene IDsin each GOslim bin, DESeq2 results heatmap facetted by sampling day in for loop
for (i in 1:nrow(Master_GOslim)) {
  
  genes <- data.frame(geneids = unlist(Master_GOslim[i,4]))
  
  if (Master_GOslim[i,3] == "downregulated") {
  
    DEG_data <- All_DEGs_Primary.Ambieant_v_Moderate %>% dplyr::filter(down %in% TRUE)  # filter only downregualted genes
    DEG_data_loop <- DEG_data %>% dplyr::filter(Gene.ID %in% genes$geneids)
    DEG_data_merge <- merge(Pgen_annot, DEG_data_loop, by ="Gene.ID")
    
    DEG_data_merge$Day_Trmt <- str_extract(DEG_data_merge$Day_Trmt, "[^_]+")
    
    Plot <- DEG_data_merge %>% #mutate(Day_Trmt = fct_relevel(Day_Trmt,  "Day7", "Day14", "Day21")) %>% 
              ggplot(aes(x = "NA", y = Gene.name)) + 
                geom_tile(aes(fill=log2FoldChange, width = 1)) + 
                scale_fill_gradient(low = "orangered3", high = "orange1") +
                facet_grid(~Day_Trmt, scales = "free_y", labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                strip.text.y = element_text(angle=0, size = 11, face = "bold"),
                strip.text.x = element_text(size = 12, face = "bold"),
                axis.title.x = element_blank(),
                axis.title.y = element_text(size=15),
                axis.text = element_text(size = 12), legend.position = "right",
                plot.margin = unit(c(0,1,0,0.25), "cm"))+
                ggtitle(Master_GOslim[i,5])
    pdf(paste("../Output/GO/DESeq2_goseq/All_PrimEff_GOslim/Downregulated/",Master_GOslim[i,5],".pdf", sep =''), width=18, height=10)
    print(Plot)
    dev.off()
  
    } else {
        DEG_data <- All_DEGs_Primary.Ambieant_v_Moderate %>% dplyr::filter(up %in% TRUE)  # filter only downregualted genes
        DEG_data_loop <- DEG_data %>% dplyr::filter(Gene.ID %in% genes$geneids)
        DEG_data_merge <- merge(Pgen_annot, DEG_data_loop, by ="Gene.ID")
        
        DEG_data_merge$Day_Trmt <- str_extract(DEG_data_merge$Day_Trmt, "[^_]+")
        
        Plot <- DEG_data_merge %>% #mutate(Day_Trmt = fct_relevel(Day_Trmt,  "Day7", "Day14", "Day21")) %>% 
                  ggplot(aes(x = "NA", y = Gene.name)) + 
                    geom_tile(aes(fill=log2FoldChange, width = 1)) + 
                    scale_fill_gradient(low = "palegreen1", high = "green4") +
                    facet_grid( ~Day_Trmt, scales = "free_y", labeller = label_wrap_gen(width = 10, multi_line = TRUE))+
                    theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                    strip.text.y = element_text(angle=0, size = 11, face = "bold"),
                    strip.text.x = element_text(size = 12, face = "bold"),
                    axis.title.x = element_blank(),
                    axis.title.y = element_text(size=15),
                    axis.text = element_text(size = 12), legend.position = "right",
                    plot.margin = unit(c(0,1,0,0.25), "cm"))+
                    ggtitle(Master_GOslim[i,5])
        pdf(paste("../Output/GO/DESeq2_goseq/All_PrimEff_GOslim/Upregulated/",Master_GOslim[i,5],".pdf", sep =''), width=18, height=10)
        print(Plot)
        dev.off()
  } # end of if else statement

} # end of for loop


```




Geom_Segment Plotting: -log1- p alue all primary efffect down regualted and upregulated genes (figure 2B)
# SECOND EFFECT (A v M main effect AND full group effect MA versus AM)
```{r All Upreg and Downreg GO terms in response to priming}

# Build a master list of all genes and GO terms 'Pgen_GOterms2'
Geoduck_annotation <- read.delim2(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Seq_details/Panopea-generosa-genes-annotations.txt", header=F) # Load themaster Pgenerosa gene list 
Pgen_GOterms <- Geoduck_annotation %>% dplyr::select(c('V1','V8')) # select only two columns - those with the gene IDs and those with the GO terms
Pgen_GOterms2 <- strsplit(Pgen_GOterms$V8, split = "; ") # create a string splitting by delimiter '; ' - view the data to see that this separates each GO term entry in the string
Pgen_GOterms2 <- data.frame(gene.ID = rep(Pgen_GOterms$V1, sapply(Pgen_GOterms2, length)), Go.terms = unlist(Pgen_GOterms2)) # create new dataframe 'Pgen_GOterms2' listing genes for each GO term (MUCH longer!)
Pgen_GOterms2 <- na.omit(Pgen_GOterms2) # ommit the NAs  - genes without GO annotation

d7.UP.second_AvM.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GO.05.Day7_SecondEffect_AvM_Upregulated.csv")
d7.UP.second_AvM.05$Dir = "Upregulated"
d7.DOWN.second_AvM.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/second_effect_AvM/GO.05.Day7_SecondEffect_AvM_Downregulated.csv")
d7.DOWN.second_AvM.05$Dir = "Downregulated"

d7.UP.MAvAM.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GO.05.Day7_GroupEffect_MAvAM_Upregulated.csv")
d7.UP.MAvAM.05$Dir = "Upregulated"
d7.DOWN.MAvAM.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/group_effect_MAvAM/GO.05.Day7_GroupEffect_MAvAM_Downregulated.csv")
d7.DOWN.MAvAM.05$Dir = "Downregulated"

# Master ALL DESeq2 significant modules with treatment
Second_goseq_results      <- rbind(d7.UP.second_AvM.05, d7.DOWN.second_AvM.05)
MAvAM_goseq_results      <- rbind(d7.UP.MAvAM.05, d7.DOWN.MAvAM.05)



# PLOTS 
# Second Treatment effect Ambient > Moderate 
AvM_BiolProcess <- Second_goseq_results %>%  dplyr::filter(ontology %in% ('BP')) %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Biological Process: Day 7 Second Treatment Ambient v Moderate") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Dir ~., scales="free_y", ncol= 1, strip.position="right")


AvM_MolFunction <- Second_goseq_results %>%  dplyr::filter(ontology %in% ('MF')) %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Molecular Function: Day 7 Second Treatment Ambient v Moderate") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Dir ~., scales="free_y", ncol= 1, strip.position="right")

pdf(paste("../Output/GO/DESeq2_goseq/Day7_SecondEffect_AvM_plots/GOplot_DESeq2_Day7_AvM_BP.pdf", sep =''), width=10, height=12)
print(ggarrange(AvM_BiolProcess,         
                plotlist = NULL,
                ncol = 1,
                nrow = 2,
            labels = NULL))
dev.off()   

pdf(paste("../Output/GO/DESeq2_goseq/Day7_SecondEffect_AvM_plots/GOplot_DESeq2_Day7_AvM_MF.pdf", sep =''), width=25, height=8)
print(ggarrange(AvM_MolFunction,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()   


# Second Treatment effect Ambient > Moderate 
MVvAM_BiolProcess <- MAvAM_goseq_results %>%  dplyr::filter(ontology %in% ('BP')) %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Biological Process: Day 7 Full Model MA v AM") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Dir ~., scales="free_y", ncol= 1, strip.position="right")


MVvAM_MolFunction <- MAvAM_goseq_results %>%  dplyr::filter(ontology %in% ('MF')) %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Molecular Function: Day 7 Full Model MA v AM") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Dir ~., scales="free_y", ncol= 1, strip.position="right")


pdf(paste("../Output/GO/DESeq2_goseq/Day7_FullModEffect_MAvAM_plots/GOplot_DESeq2_Day7_MAvAM_BP.pdf", sep =''), width=10, height=12)
print(ggarrange(MVvAM_BiolProcess,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()   

pdf(paste("../Output/GO/DESeq2_goseq/Day7_FullModEffect_MAvAM_plots/GOplot_DESeq2_Day7_MAvAM_MF.pdf", sep =''), width=10, height=8)
print(ggarrange(MVvAM_MolFunction,         
                plotlist = NULL,
                ncol = 1,
                nrow = 2,
            labels = NULL))
dev.off()      


```

Geom_Segment Plotting: -log1- p alue all primary efffect down regualted and upregulated genes (figure 2B)
# PRIMARY Effect
```{r All Upreg and Downreg GO terms in response to priming}

# Build a master list of all genes and GO terms 'Pgen_GOterms2'
Geoduck_annotation <- read.delim2(file="C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Seq_details/Panopea-generosa-genes-annotations.txt", header=F) # Load themaster Pgenerosa gene list 
Pgen_GOterms <- Geoduck_annotation %>% dplyr::select(c('V1','V8')) # select only two columns - those with the gene IDs and those with the GO terms
Pgen_GOterms2 <- strsplit(Pgen_GOterms$V8, split = "; ") # create a string splitting by delimiter '; ' - view the data to see that this separates each GO term entry in the string
Pgen_GOterms2 <- data.frame(gene.ID = rep(Pgen_GOterms$V1, sapply(Pgen_GOterms2, length)), Go.terms = unlist(Pgen_GOterms2)) # create new dataframe 'Pgen_GOterms2' listing genes for each GO term (MUCH longer!)
Pgen_GOterms2 <- na.omit(Pgen_GOterms2) # ommit the NAs  - genes without GO annotation



d0.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day0/GO.05.Day0_PrimEffect_Upregulated.csv")
d0.UP.05$Day = "Day0"
d0.UP.05$Dir = "Upregulated"
d0.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day0/GO.05.Day0_PrimEffect_Downregulated.csv")
d0.DOWN.05$Day = "Day0"
d0.DOWN.05$Dir = "Downregulated"

d7.UP.05    <- read.csv("../Output/GO/DESeq2_goseq/Day7/GO.05.Day7_PrimEffect_Upregulated.csv")
d7.UP.05$Day = "Day7"
d7.UP.05$Dir = "Upregulated"
d7.DOWN.05  <- read.csv("../Output/GO/DESeq2_goseq/Day7/GO.05.Day7_PrimEffect_Downregulated.csv")
d7.DOWN.05$Day = "Day7"
d7.DOWN.05$Dir = "Downregulated"

d14.UP.05   <- read.csv("../Output/GO/DESeq2_goseq/Day14/GO.05.Day14_PrimEffect_Upregulated.csv")
d14.UP.05$Day = "Day14"
d14.UP.05$Dir = "Upregulated"
d14.DOWN.05 <- read.csv("../Output/GO/DESeq2_goseq/Day14/GO.05.Day14_PrimEffect_Downregulated.csv")
d14.DOWN.05$Day = "Day14"
d14.DOWN.05$Dir = "Downregulated"

d21.UP.05   <- read.csv("../Output/GO/DESeq2_goseq/Day21/GO.05.Day21_PrimEffect_Upregulated.csv")
d21.UP.05$Day = "Day21"
d21.UP.05$Dir = "Upregulated"
d21.DOWN.05 <- read.csv("../Output/GO/DESeq2_goseq/Day21/GO.05.Day21_PrimEffect_Downregulated.csv")
d21.DOWN.05$Day = "Day21"
d21.DOWN.05$Dir = "Downregulated"

# Master ALL DESeq2 significant modules with treatment
Master_goseq_results      <- rbind(d0.UP.05, d0.DOWN.05, 
                              d7.UP.05, d7.DOWN.05,
                              d14.UP.05, d14.DOWN.05, 
                              d21.UP.05, d21.DOWN.05)
# View(Master_goseq_results)


# call enriched GO terms and plot 
#  UPREGULATED GENES! 
# day 0 UPREGULATED
GO_d0.UP.05.a<-d0.UP.05$category[d0.UP.05$over_represented_pvalue<.05] # change twice here
GO_d0.UP.05<-data.frame(GO_d0.UP.05.a)
colnames(GO_d0.UP.05) <- c("category")
GO_d0.UP.05 <- merge(GO_d0.UP.05, d0.UP.05, by="category") # change here
GO_d0.UP.05 <- GO_d0.UP.05[order(-GO_d0.UP.05$numDEInCat),]
GO_d0.UP.05$term <- as.factor(GO_d0.UP.05$term)

d0_UP_MF <- GO_d0.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd0_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d0_UP'))
d0_UP_BP <- GO_d0.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd0_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d0_UP'))

# day 7 UPREGULATED
GO_d7.UP.05.a<-d7.UP.05$category[d7.UP.05$over_represented_pvalue<.05] # change twice here
GO_d7.UP.05<-data.frame(GO_d7.UP.05.a)
colnames(GO_d7.UP.05) <- c("category")
GO_d7.UP.05 <- merge(GO_d7.UP.05, d7.UP.05, by="category") # change here
GO_d7.UP.05 <- GO_d7.UP.05[order(-GO_d7.UP.05$numDEInCat),]
GO_d7.UP.05$term <- as.factor(GO_d7.UP.05$term)

d7_UP_MF <- GO_d7.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd7_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d7_UP'))
d7_UP_BP <- GO_d7.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd7_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d7_UP'))

# day 14 UPREGULATED
GO_d14.UP.05.a<-d14.UP.05$category[d14.UP.05$over_represented_pvalue<.05] # change twice here
GO_d14.UP.05<-data.frame(GO_d14.UP.05.a)
colnames(GO_d14.UP.05) <- c("category")
GO_d14.UP.05 <- merge(GO_d14.UP.05, d14.UP.05, by="category") # change here
GO_d14.UP.05 <- GO_d14.UP.05[order(-GO_d14.UP.05$numDEInCat),]
GO_d14.UP.05$term <- as.factor(GO_d14.UP.05$term)

d14_UP_MF <- GO_d14.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd14_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d14_UP'))
d14_UP_BP <- GO_d14.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd14_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d14_UP'))

# day 21 UPREGULATED
GO_d21.UP.05.a<-d21.UP.05$category[d21.UP.05$over_represented_pvalue<.05] # change twice here
GO_d21.UP.05<-data.frame(GO_d21.UP.05.a)
colnames(GO_d21.UP.05) <- c("category")
GO_d21.UP.05 <- merge(GO_d21.UP.05, d21.UP.05, by="category") # change here
GO_d21.UP.05 <- GO_d21.UP.05[order(-GO_d21.UP.05$numDEInCat),]
GO_d21.UP.05$term <- as.factor(GO_d21.UP.05$term)

d21_UP_MF <- GO_d21.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd21_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d21_UP'))
d21_UP_BP <- GO_d21.UP.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd21_UP', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d21_UP'))


#======================================================================= #
# bind the rows of MF and BP in the clustered modules (those twith primary treatment effect in same pattern/directionality)
MF_UP <- rbind(d0_UP_MF, d7_UP_MF, d14_UP_MF, d21_UP_MF) 
BP_UP <- rbind(d0_UP_BP, d7_UP_BP, d14_UP_BP, d21_UP_BP)


MF_UP$term <- gsub(",.*$", "", MF_UP$term)
MF_UP$Day = factor(MF_UP$Day, levels = c("Day0", "Day7", "Day14", "Day21"))
MF_UP_plot <- MF_UP  %>%  mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Molecular Function: Upregulated DEGs Primary Effect (higher by ambient history)") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Day ~., scales="free_y", ncol= 1, strip.position="right")
                  #facet_wrap(~ Day,nrow = 1)

BP_UP$term <- gsub(",.*$", "", BP_UP$term)
BP_UP$Day = factor(BP_UP$Day, levels = c("Day0", "Day7", "Day14", "Day21"))
BP_UP_plot <- BP_UP  %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Biological Process: Upregulated DEGs Primary Effect (higher by ambient history)") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Day ~., scales="free_y", ncol= 1, strip.position="right")



# Downregulated plots 
# day 0 DOWNREGULATED
GO_d0.DOWN.05.a<-d0.DOWN.05$category[d0.DOWN.05$over_represented_pvalue<.05] # change twice here
GO_d0.DOWN.05<-data.frame(GO_d0.DOWN.05.a)
colnames(GO_d0.DOWN.05) <- c("category")
GO_d0.DOWN.05 <- merge(GO_d0.DOWN.05, d0.DOWN.05, by="category") # change here
GO_d0.DOWN.05 <- GO_d0.DOWN.05[order(-GO_d0.DOWN.05$numDEInCat),]
GO_d0.DOWN.05$term <- as.factor(GO_d0.DOWN.05$term)

d0_DOWN_MF <- GO_d0.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd0_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d0_DOWN'))
d0_DOWN_BP <- GO_d0.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd0_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d0_DOWN'))

# day 7 DOWNREGULATED
GO_d7.DOWN.05.a<-d7.DOWN.05$category[d7.DOWN.05$over_represented_pvalue<.05] # change twice here
GO_d7.DOWN.05<-data.frame(GO_d7.DOWN.05.a)
colnames(GO_d7.DOWN.05) <- c("category")
GO_d7.DOWN.05 <- merge(GO_d7.DOWN.05, d7.DOWN.05, by="category") # change here
GO_d7.DOWN.05 <- GO_d7.DOWN.05[order(-GO_d7.DOWN.05$numDEInCat),]
GO_d7.DOWN.05$term <- as.factor(GO_d7.DOWN.05$term)

d7_DOWN_MF <- GO_d7.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd7_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d7_DOWN'))
d7_DOWN_BP <- GO_d7.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd7_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d7_DOWN'))

# day 14 DOWNREGULATED
GO_d14.DOWN.05.a<-d14.DOWN.05$category[d14.DOWN.05$over_represented_pvalue<.05] # change twice here
GO_d14.DOWN.05<-data.frame(GO_d14.DOWN.05.a)
colnames(GO_d14.DOWN.05) <- c("category")
GO_d14.DOWN.05 <- merge(GO_d14.DOWN.05, d14.DOWN.05, by="category") # change here
GO_d14.DOWN.05 <- GO_d14.DOWN.05[order(-GO_d14.DOWN.05$numDEInCat),]
GO_d14.DOWN.05$term <- as.factor(GO_d14.DOWN.05$term)

d14_DOWN_MF <- GO_d14.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd14_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d14_DOWN'))
d14_DOWN_BP <- GO_d14.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd14_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d14_DOWN'))

# day 21 DOWNREGULATED
GO_d21.DOWN.05.a<-d21.DOWN.05$category[d21.DOWN.05$over_represented_pvalue<.05] # change twice here
GO_d21.DOWN.05<-data.frame(GO_d21.DOWN.05.a)
colnames(GO_d21.DOWN.05) <- c("category")
GO_d21.DOWN.05 <- merge(GO_d21.DOWN.05, d21.DOWN.05, by="category") # change here
GO_d21.DOWN.05 <- GO_d21.DOWN.05[order(-GO_d21.DOWN.05$numDEInCat),]
GO_d21.DOWN.05$term <- as.factor(GO_d21.DOWN.05$term)

d21_DOWN_MF <- GO_d21.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd21_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('MF_d21_DOWN'))
d21_DOWN_BP <- GO_d21.DOWN.05 %>% 
  drop_na(ontology) %>% 
  mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) ),
         ontology = paste(ontology, 'd21_DOWN', sep = "_")) %>%
  dplyr::filter(ontology %in% ('BP_d21_DOWN'))


#======================================================================= #
# bind the rows of MF and BP in the clustered modules (those twith primary treatment effect in same pattern/directionality)
MF_DOWN <- rbind(d0_DOWN_MF, d7_DOWN_MF, d14_DOWN_MF, d21_DOWN_MF) 
BP_DOWN <- rbind(d0_DOWN_BP, d7_DOWN_BP, d14_DOWN_BP, d21_DOWN_BP)


MF_DOWN$term <- gsub(",.*$", "", MF_DOWN$term)
MF_DOWN$Day = factor(MF_DOWN$Day, levels = c("Day0", "Day7", "Day14", "Day21"))
MF_DOWN_plot <- MF_DOWN  %>% mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Molecular Function: Downregulated DEGs Primary Effect (higher by Moderate history)") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Day ~., scales="free_y", ncol= 1, strip.position="right")

BP_DOWN$term <- gsub(",.*$", "", BP_DOWN$term)
BP_DOWN$Day = factor(BP_DOWN$Day, levels = c("Day0", "Day7", "Day14", "Day21"))
BP_DOWN_plot <- BP_DOWN    %>%  mutate(term = fct_reorder(term, -log10(over_represented_pvalue))) %>%
                  #mutate(term = fct_reorder(term, Day)) %>%
                  ggplot(aes(x=term, y=-log10(over_represented_pvalue))) +
                  geom_segment( aes(x=term ,xend=term, y=1, yend=-log10(over_represented_pvalue)), color="grey95", size = 3) +
                  geom_point(size=3, shape = 15, colour = "grey70") +
                  coord_flip() +
                  theme(
                    panel.grid.minor.y = element_blank(),
                    panel.grid.major.y = element_blank(),
                    legend.position="bottom"
                  ) +
                  xlab("") +
                  ylab("") +
                  ggtitle("Biological Process: Downregulated DEGs Primary Effect (higher by Moderate history)") +
                  #geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
                  theme_bw() + #Set background color 
                  theme(panel.border = element_blank(), # Set border
                        panel.grid.major = element_blank(), #Set major gridlines
                        panel.grid.minor = element_blank(), #Set minor gridlines
                        axis.line = element_line(colour = "black"), #Set axes color
                        plot.background=element_blank()) + #Set the plot background #set title attributes
                  #geom_hline(yintercept=0.25, linetype="dashed",  color = "black", size=2) +
                  facet_wrap(Day ~., scales="free_y", ncol= 1, strip.position="right")

# MOLECULAR FUNCTION GRAPHS OUTPUT 

pdf(paste("../Output/GO/DESeq2_goseq/GOplot_DESeq2_PrimEffect_Upregulated_MF.pdf", sep =''), width=10, height=12)
print(ggarrange(MF_UP_plot,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()      


pdf(paste("../Output/GO/DESeq2_goseq/GOplot_DESeq2_PrimEffect_Downregulated_MF.pdf", sep =''), width=10, height=12)
print(ggarrange(MF_DOWN_plot,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()      


# BIOLOFICAL PROCESS GRAPHS OUTPUT

pdf(paste("../Output/GO/DESeq2_goseq/GOplot_DESeq2_PrimEffect_Upregulated_BP.pdf", sep =''), width=10, height=18)
print(ggarrange(BP_UP_plot,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()      


pdf(paste("../Output/GO/DESeq2_goseq/GOplot_DESeq2_PrimEffect_Downregulated_BP.pdf", sep =''), width=10, height=18)
print(ggarrange(BP_DOWN_plot,         
                plotlist = NULL,
                ncol = 1,
                nrow = 1,
            labels = NULL))
dev.off()      


```

Plotting: Day 0
```{r plots_Day0.Primary}
#How many enriched GO terms do we have
# class(GO_d14.all)
# head(GO_d14.all)
# tail(GO.wall)
# nrow(GO.wall)

# UPREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
UP_enriched.GO.05.a<-GO_d0.UP$category[GO_d0.UP$over_represented_pvalue<.05] # change twice here
UP_enriched.GO.05<-data.frame(UP_enriched.GO.05.a)
colnames(UP_enriched.GO.05) <- c("category")
UP_enriched.GO.05 <- merge(UP_enriched.GO.05, GO_d0.UP, by="category") # change here
UP_enriched.GO.05 <- UP_enriched.GO.05[order(-UP_enriched.GO.05$numDEInCat),]
UP_enriched.GO.05$term <- as.factor(UP_enriched.GO.05$term)
head(UP_enriched.GO.05)

UP_MF <- subset(UP_enriched.GO.05, ontology=="MF")
UP_MF <- UP_MF[order(-UP_MF$numDEInCat),]
UP_CC <- subset(UP_enriched.GO.05, ontology=="CC")
UP_CC <- UP_CC[order(-UP_CC$numDEInCat),]
UP_BP <- subset(UP_enriched.GO.05, ontology=="BP")
UP_BP <- UP_BP[order(-UP_BP$numDEInCat),]

# Molecular Processes
MFplot_UP <- UP_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_UP <- UP_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_UP <- UP_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# DOWNREGULATED DEGs ------------------------------------------------------------------------------- # 
#Find only enriched GO terms that are statistically significant at cutoff 
DOWN_enriched.GO.05.a<-GO_d0.DOWN$category[GO_d0.DOWN$over_represented_pvalue<.05]
DOWN_enriched.GO.05<-data.frame(DOWN_enriched.GO.05.a)
colnames(DOWN_enriched.GO.05) <- c("category")
DOWN_enriched.GO.05 <- merge(DOWN_enriched.GO.05, GO_d0.DOWN, by="category")
DOWN_enriched.GO.05 <- DOWN_enriched.GO.05[order(-DOWN_enriched.GO.05$numDEInCat),]
DOWN_enriched.GO.05$term <- as.factor(DOWN_enriched.GO.05$term)
head(DOWN_enriched.GO.05)

DOWN_MF <- subset(DOWN_enriched.GO.05, ontology=="MF")
DOWN_MF <- DOWN_MF[order(-DOWN_MF$numDEInCat),]
DOWN_CC <- subset(DOWN_enriched.GO.05, ontology=="CC")
DOWN_CC <- DOWN_CC[order(-DOWN_CC$numDEInCat),]
DOWN_BP <- subset(DOWN_enriched.GO.05, ontology=="BP")
DOWN_BP <- DOWN_BP[order(-DOWN_BP$numDEInCat),]

# Molecular Processes
MFplot_DOWN <- DOWN_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_DOWN <- DOWN_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_DOWN <- DOWN_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# GOplot <- grid.arrange(MFplot, CCplot, BPplot, ncol=3, clip="off")
# ggsave("GOplot.pdf", GOplot, width = 21, height = 21, units = c("in"))

# Merge plots!
num_up   <- dim(DE_d0.primary.UPREG)[1] # call num upregulated genes
num_down <-dim(DE_d0.primary.DWNREG)[1] # call num downregulated genes

GOplot.merge_UP <- UP_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 0 Upregulated DEGs") +
  geom_label(aes(x = 0.5, y = 0.5, label = paste(num_up, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_UP

GOplot.merge_DOWN <- DOWN_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 0 Downregulated DEGs") +
  geom_label(aes(x = 0.5, y = 1.5, label = paste(num_down, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_DOWN

GO.plot_d0.Primary<-grid.arrange(GOplot.merge_UP, GOplot.merge_DOWN, nrow=2, clip="off")
ggsave("../Output/GO/goseq/Day0/GOplot_d0.Primary.pdf", GO.plot_d0.Primary, width = 21, height = 21, units = c("in"))
getwd()
```

Plotting: Day 7
```{r plots_Day7.Primary}
#How many enriched GO terms do we have
# class(GO_d14.all)
# head(GO_d14.all)
# tail(GO.wall)
# nrow(GO.wall)

# UPREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
UP_enriched.GO.05.a<-GO_d7.UP$category[GO_d7.UP$over_represented_pvalue<.05]
UP_enriched.GO.05<-data.frame(UP_enriched.GO.05.a)
colnames(UP_enriched.GO.05) <- c("category")
UP_enriched.GO.05 <- merge(UP_enriched.GO.05, GO_d7.UP, by="category")
UP_enriched.GO.05 <- UP_enriched.GO.05[order(-UP_enriched.GO.05$numDEInCat),]
UP_enriched.GO.05$term <- as.factor(UP_enriched.GO.05$term)
head(UP_enriched.GO.05)

UP_MF <- subset(UP_enriched.GO.05, ontology=="MF")
UP_MF <- UP_MF[order(-UP_MF$numDEInCat),]
UP_CC <- subset(UP_enriched.GO.05, ontology=="CC")
UP_CC <- UP_CC[order(-UP_CC$numDEInCat),]
UP_BP <- subset(UP_enriched.GO.05, ontology=="BP")
UP_BP <- UP_BP[order(-UP_BP$numDEInCat),]

# Molecular Processes
MFplot_UP <- UP_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_UP <- UP_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_UP <- UP_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# DOWNREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
DOWN_enriched.GO.05.a<-GO_d7.DOWN$category[GO_d7.DOWN$over_represented_pvalue<.05]
DOWN_enriched.GO.05<-data.frame(DOWN_enriched.GO.05.a)
colnames(DOWN_enriched.GO.05) <- c("category")
DOWN_enriched.GO.05 <- merge(DOWN_enriched.GO.05, GO_d7.DOWN, by="category")
DOWN_enriched.GO.05 <- DOWN_enriched.GO.05[order(-DOWN_enriched.GO.05$numDEInCat),]
DOWN_enriched.GO.05$term <- as.factor(DOWN_enriched.GO.05$term)
head(DOWN_enriched.GO.05)

DOWN_MF <- subset(DOWN_enriched.GO.05, ontology=="MF")
DOWN_MF <- DOWN_MF[order(-DOWN_MF$numDEInCat),]
DOWN_CC <- subset(DOWN_enriched.GO.05, ontology=="CC")
DOWN_CC <- DOWN_CC[order(-DOWN_CC$numDEInCat),]
DOWN_BP <- subset(DOWN_enriched.GO.05, ontology=="BP")
DOWN_BP <- DOWN_BP[order(-DOWN_BP$numDEInCat),]

# Molecular Processes
MFplot_DOWN <- DOWN_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_DOWN <- DOWN_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_DOWN <- DOWN_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# GOplot <- grid.arrange(MFplot, CCplot, BPplot, ncol=3, clip="off")
# ggsave("GOplot.pdf", GOplot, width = 21, height = 21, units = c("in"))

# Merge plots!
num_up   <- dim(DE_d7.primary.UPREG)[1] # call num upregulated genes
num_down <-dim(DE_d7.primary.DWNREG)[1] # call num downregulated genes

GOplot.merge_UP <- UP_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 7 Upregulated DEGs") +
  geom_label(aes(x = 2, y = 2, label = paste(num_up, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_UP

GOplot.merge_DOWN <- DOWN_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 7 Downregulated DEGs") +
  geom_label(aes(x = 2, y = 2, label = paste(num_down, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_DOWN

GO.plot_d7.Primary<-grid.arrange(GOplot.merge_UP, GOplot.merge_DOWN, nrow=2, clip="off")
ggsave("../Output/GO/goseq/Day7/GOplot_d7.Primary.pdf", GO.plot_d7.Primary, width = 21, height = 21, units = c("in"))
```

Plotting: Day 14
```{r plots_Day14.Primary}
#How many enriched GO terms do we have
# class(GO_d14.all)
# head(GO_d14.all)
# tail(GO.wall)
# nrow(GO.wall)

# UPREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
UP_enriched.GO.05.a<-GO_d14.UP$category[GO_d14.UP$over_represented_pvalue<.05]
UP_enriched.GO.05<-data.frame(UP_enriched.GO.05.a)
colnames(UP_enriched.GO.05) <- c("category")
UP_enriched.GO.05 <- merge(UP_enriched.GO.05, GO_d14.UP, by="category")
UP_enriched.GO.05 <- UP_enriched.GO.05[order(-UP_enriched.GO.05$numDEInCat),]
UP_enriched.GO.05$term <- as.factor(UP_enriched.GO.05$term)
head(UP_enriched.GO.05)

UP_MF <- subset(UP_enriched.GO.05, ontology=="MF")
UP_MF <- UP_MF[order(-UP_MF$numDEInCat),]
UP_CC <- subset(UP_enriched.GO.05, ontology=="CC")
UP_CC <- UP_CC[order(-UP_CC$numDEInCat),]
UP_BP <- subset(UP_enriched.GO.05, ontology=="BP")
UP_BP <- UP_BP[order(-UP_BP$numDEInCat),]

# Molecular Processes
MFplot_UP <- UP_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_UP <- UP_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_UP <- UP_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# DOWNREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
DOWN_enriched.GO.05.a<-GO_d14.DOWN$category[GO_d14.DOWN$over_represented_pvalue<.05]
DOWN_enriched.GO.05<-data.frame(DOWN_enriched.GO.05.a)
colnames(DOWN_enriched.GO.05) <- c("category")
DOWN_enriched.GO.05 <- merge(DOWN_enriched.GO.05, GO_d14.DOWN, by="category")
DOWN_enriched.GO.05 <- DOWN_enriched.GO.05[order(-DOWN_enriched.GO.05$numDEInCat),]
DOWN_enriched.GO.05$term <- as.factor(DOWN_enriched.GO.05$term)
head(DOWN_enriched.GO.05)

DOWN_MF <- subset(DOWN_enriched.GO.05, ontology=="MF")
DOWN_MF <- DOWN_MF[order(-DOWN_MF$numDEInCat),]
DOWN_CC <- subset(DOWN_enriched.GO.05, ontology=="CC")
DOWN_CC <- DOWN_CC[order(-DOWN_CC$numDEInCat),]
DOWN_BP <- subset(DOWN_enriched.GO.05, ontology=="BP")
DOWN_BP <- DOWN_BP[order(-DOWN_BP$numDEInCat),]

# Molecular Processes
MFplot_DOWN <- DOWN_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_DOWN <- DOWN_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_DOWN <- DOWN_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# GOplot <- grid.arrange(MFplot, CCplot, BPplot, ncol=3, clip="off")
# ggsave("GOplot.pdf", GOplot, width = 21, height = 21, units = c("in"))

# Merge plots!
num_up   <- dim(DE_d14.primary.UPREG)[1] # call num upregulated genes
num_down <-dim(DE_d14.primary.DWNREG)[1] # call num downregulated genes

GOplot.merge_UP <- UP_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 14 Upregulated DEGs") +
  geom_label(aes(x = 2, y = 20, label = paste(num_up, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_UP

GOplot.merge_DOWN <- DOWN_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 14 Downregulated DEGs") +
  geom_label(aes(x = 2, y = 6, label = paste(num_down, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_DOWN

GO.plot_d14.Primary<- grid.arrange(GOplot.merge_UP, GOplot.merge_DOWN, nrow=2, clip="off")
ggsave("../Output/GO/goseq/Day14/GOplot_d14.Primary.pdf", GO.plot_d14.Primary, width = 21, height = 21, units = c("in"))
```

Plotting: Day 21
```{r plots_Day21.Primary}
#How many enriched GO terms do we have
# class(GO_d14.all)
# head(GO_d14.all)
# tail(GO.wall)
# nrow(GO.wall)

# UPREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
UP_enriched.GO.05.a<-GO_d21.UP$category[GO_d21.UP$over_represented_pvalue<.05]
UP_enriched.GO.05<-data.frame(UP_enriched.GO.05.a)
colnames(UP_enriched.GO.05) <- c("category")
UP_enriched.GO.05 <- merge(UP_enriched.GO.05, GO_d21.UP, by="category")
UP_enriched.GO.05 <- UP_enriched.GO.05[order(-UP_enriched.GO.05$numDEInCat),]
UP_enriched.GO.05$term <- as.factor(UP_enriched.GO.05$term)
head(UP_enriched.GO.05)

UP_MF <- subset(UP_enriched.GO.05, ontology=="MF")
UP_MF <- UP_MF[order(-UP_MF$numDEInCat),]
UP_CC <- subset(UP_enriched.GO.05, ontology=="CC")
UP_CC <- UP_CC[order(-UP_CC$numDEInCat),]
UP_BP <- subset(UP_enriched.GO.05, ontology=="BP")
UP_BP <- UP_BP[order(-UP_BP$numDEInCat),]

# Molecular Processes
MFplot_UP <- UP_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_UP <- UP_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_UP <- UP_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# DOWNREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
DOWN_enriched.GO.05.a<-GO_d21.DOWN$category[GO_d21.DOWN$over_represented_pvalue<.05]
DOWN_enriched.GO.05<-data.frame(DOWN_enriched.GO.05.a)
colnames(DOWN_enriched.GO.05) <- c("category")
DOWN_enriched.GO.05 <- merge(DOWN_enriched.GO.05, GO_d21.DOWN, by="category")
DOWN_enriched.GO.05 <- DOWN_enriched.GO.05[order(-DOWN_enriched.GO.05$numDEInCat),]
DOWN_enriched.GO.05$term <- as.factor(DOWN_enriched.GO.05$term)
head(DOWN_enriched.GO.05)

DOWN_MF <- subset(DOWN_enriched.GO.05, ontology=="MF")
DOWN_MF <- DOWN_MF[order(-DOWN_MF$numDEInCat),]
DOWN_CC <- subset(DOWN_enriched.GO.05, ontology=="CC")
DOWN_CC <- DOWN_CC[order(-DOWN_CC$numDEInCat),]
DOWN_BP <- subset(DOWN_enriched.GO.05, ontology=="BP")
DOWN_BP <- DOWN_BP[order(-DOWN_BP$numDEInCat),]

# Molecular Processes
MFplot_DOWN <- DOWN_MF %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Molecular Function") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

#Cellular Processes
CCplot_DOWN <- DOWN_CC %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("Cellular Component") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# Biological Processes 
BPplot_DOWN <- DOWN_BP %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, color="#69b3a2") +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none") +
  xlab("") +
  ylab("") +
  ggtitle("Biological Process") + #add a main title
  theme(plot.title = element_text(face = 'bold', 
                                  size = 12, 
                                  hjust = 0)) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank())#Set the plot background

# GOplot <- grid.arrange(MFplot, CCplot, BPplot, ncol=3, clip="off")
# ggsave("GOplot.pdf", GOplot, width = 21, height = 21, units = c("in"))

# Merge plots!
num_up   <- dim(DE_d21.primary.UPREG)[1] # call num upregulated genes
num_down <-dim(DE_d21.primary.DWNREG)[1] # call num downregulated genes

GOplot.merge_UP <- UP_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 21 Upregulated DEGs") +
  geom_label(aes(x = 2, y = 7, label = paste(num_up, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_UP

GOplot.merge_DOWN <- DOWN_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Day 21 Downregulated DEGs") +
  geom_label(aes(x = 2, y = 3, label = paste(num_down, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_DOWN

GO.plot_d21.Primary<-grid.arrange(GOplot.merge_UP, GOplot.merge_DOWN, nrow=2, clip="off")
ggsave("../Output/GO/goseq/Day21/GOplot_d21.Primary.pdf", GO.plot_d21.Primary, width = 21, height = 21, units = c("in"))
```

Plotting: Constant DEGs Days 7 14 21 affected by Primary treatment history
```{r Constant_All}
#How many enriched GO terms do we have
# class(GO_d14.all)
# head(GO_d14.all)
# tail(GO.wall)
# nrow(GO.wall)

# UPREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
UP_enriched.GO.05.a<-GO_Constant.UP$category[GO_Constant.UP$over_represented_pvalue<.05]
UP_enriched.GO.05<-data.frame(UP_enriched.GO.05.a)
colnames(UP_enriched.GO.05) <- c("category")
UP_enriched.GO.05 <- merge(UP_enriched.GO.05, GO_Constant.UP, by="category")
UP_enriched.GO.05 <- UP_enriched.GO.05[order(-UP_enriched.GO.05$numDEInCat),]
UP_enriched.GO.05$term <- as.factor(UP_enriched.GO.05$term)
head(UP_enriched.GO.05)

UP_MF <- subset(UP_enriched.GO.05, ontology=="MF")
UP_MF <- UP_MF[order(-UP_MF$numDEInCat),]
UP_CC <- subset(UP_enriched.GO.05, ontology=="CC")
UP_CC <- UP_CC[order(-UP_CC$numDEInCat),]
UP_BP <- subset(UP_enriched.GO.05, ontology=="BP")
UP_BP <- UP_BP[order(-UP_BP$numDEInCat),]

# Molecular Processes
head(UP_MF)

MFplot_UP <- UP_MF %>%
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#00BFC4') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Mol Fxn: Constant DEGs UPREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 

#Cellular Processes
CCplot_UP <- UP_CC %>% 
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#7CAE00') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Cell Comp: Constant DEGs UPREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 

# Biological Processes 
BPplot_UP <- UP_BP %>%
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#69b3a2') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Biol Proc: Constant DEGs UPREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 


# DOWNREGULATED DEGs ------------------------------------------------------------------------------- #
#Find only enriched GO terms that are statistically significant at cutoff 
DOWN_enriched.GO.05.a<-GO_Constant.DOWN$category[GO_Constant.DOWN$over_represented_pvalue<.05]
DOWN_enriched.GO.05<-data.frame(DOWN_enriched.GO.05.a)
colnames(DOWN_enriched.GO.05) <- c("category")
DOWN_enriched.GO.05 <- merge(DOWN_enriched.GO.05, GO_Constant.DOWN, by="category")
DOWN_enriched.GO.05 <- DOWN_enriched.GO.05[order(-DOWN_enriched.GO.05$numDEInCat),]
DOWN_enriched.GO.05$term <- as.factor(DOWN_enriched.GO.05$term)
head(DOWN_enriched.GO.05)

DOWN_MF <- subset(DOWN_enriched.GO.05, ontology=="MF")
DOWN_MF <- DOWN_MF[order(-DOWN_MF$numDEInCat),]
DOWN_CC <- subset(DOWN_enriched.GO.05, ontology=="CC")
DOWN_CC <- DOWN_CC[order(-DOWN_CC$numDEInCat),]
DOWN_BP <- subset(DOWN_enriched.GO.05, ontology=="BP")
DOWN_BP <- DOWN_BP[order(-DOWN_BP$numDEInCat),]

# Molecular Function
MFplot_DOWN <- DOWN_MF %>%
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#00BFC4') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Mol Fxn: Constant DEGs DOWNREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 

#Cellular Processes
CCplot_DOWN <- DOWN_CC %>% 
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#7CAE00') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Cell Comp: Constant DEGs DOWNREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 

# Biological Processes 
BPplot_DOWN <- DOWN_BP %>%
              mutate(term = fct_reorder(term, (-log10(over_represented_pvalue)) )) %>%
              ggplot(aes(ontology, term, fill= ontology, alpha = over_represented_pvalue)) + 
              geom_tile(fill = '#69b3a2') +
              scale_alpha_continuous(range = c(1, 0.3)) +
              theme_classic2() + 
              ggtitle("GO Biol Proc: Constant DEGs DOWNREGULATED") +
              xlab("") +
              ylab('') +
              theme(legend.position="none") 


# GOplot <- grid.arrange(MFplot, CCplot, BPplot, ncol=3, clip="off")
# ggsave("GOplot.pdf", GOplot, width = 21, height = 21, units = c("in"))

# Merge plots!
num_up   <- dim(Contant_upreg)[1] # call num upregulated genes
num_down <-dim(Contant_dwnreg)[1] # call num downregulated genes

GOplot.merge_UP <- UP_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Constant Upregulated DEGs") +
  geom_label(aes(x = 1, y = 3, label = paste(num_up, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_UP

GOplot.merge_DOWN <- DOWN_enriched.GO.05 %>% drop_na(ontology) %>% mutate(term = fct_reorder(term, numDEInCat)) %>%
  mutate(term = fct_reorder(term, ontology)) %>%
  ggplot( aes(x=term, y=numDEInCat) ) +
  geom_segment( aes(x=term ,xend=term, y=0, yend=numDEInCat), color="grey") +
  geom_point(size=3, aes(colour = ontology)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="bottom"
  ) +
  xlab("") +
  ylab("") +
  ggtitle("GO: Constant Downregulated DEGs") +
  geom_label(aes(x = 1, y = 3, label = paste(num_down, "DEGs"))) +
  theme_bw() + #Set background color 
  theme(panel.border = element_blank(), # Set border
        panel.grid.major = element_blank(), #Set major gridlines
        panel.grid.minor = element_blank(), #Set minor gridlines
        axis.line = element_line(colour = "black"), #Set axes color
        plot.background=element_blank()) #Set the plot background #set title attributes
# GOplot.merge_DOWN

GO.plot_Constant<-grid.arrange(GOplot.merge_UP, GOplot.merge_DOWN, nrow=2, clip="off")
ggsave("C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Output/GO/GOplot_Constant.Primary.pdf", GO.plot_Constant, width = 21, height = 21, units = c("in"))
```















### GO_MWU - not using this for the paper but did a bit of work here... Can review it for future data
Create all files for the GO_MWU.R script
output two-column csv of just the gene.id and log2fc 
```{r GO_MWU files - Primary_Treatment}
DE_d0.P <- data.frame(DE_d0.primary[,c(2,4)])
write.csv(DE_d0.P,"C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Data/GO/GO_MWU/d0.P.DE_GO.terms.csv",row.names=FALSE,quote=FALSE)

DE_d7.P <- data.frame(DE_d7.primary[,c(2,4)])
write.csv(DE_d7.P,"C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Data/GO/GO_MWU/d7.P.DE_GO.terms.csv",row.names=FALSE,quote=FALSE)

DE_d14.P <- data.frame(DE_d14.primary[,c(2,4)])
write.csv(DE_d14.P,"C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Data/GO/GO_MWU/d14.P.DE_GO.terms.csv",row.names=FALSE,quote=FALSE)

DE_d21.P <- data.frame(DE_d21.primary[,c(2,4)])
write.csv(DE_d21.P,"C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Data/GO/GO_MWU/d21.P.DE_GO.terms.csv",row.names=FALSE,quote=FALSE)

```

### Genewalk

link to tutorial: https://churchman.med.harvard.edu/genewalk/#tutorial
Citation (bioRxiv preprint): Ietswaart, R., Gyori, B. M., Bachman, J. A., Sorger, P. K., & Churchman, L. S. (2019). GeneWalk identifies relevant gene functions for a biological context using network representation learning. bioRxiv, 755579.
About: Genewalk is curently designed to perform function network analysis of DEGs with human and mouse identifiers

```{r prep genewalk files}
Geoduck.gene_HGNC.list <- Geoduck_annotation %>% dplyr::select(c("V1","V6")) # call the geoduck gene ID and the HGNC in the annotation file
colnames(Geoduck.gene_HGNC.list) <- c("gene.ID", "HGNC_symbol") # rename columns
# note that the HGNC column contains the HNC code with the model taxa as 'HUMAN, MOUSE, CHICK, etc.'
Geoduck.gene_HGNC.list$HGNC<- sapply(strsplit((Geoduck.gene_HGNC.list$HGNC), "_"), '[', 1) # this splits the HGNC by the delimiter "_" and calls just the HGNC code - note the model taxa is now absent from the dataframe! 


# change the col name of the gene.ID  in the DE datasets

# DAY 0 ------------------------------------------- #

# UPREGULATED

GW.d0.primary.UPREG <- merge((DE_d0.primary.UPREG[order(DE_d0.primary.UPREG$log2FoldChange, decreasing = TRUE),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d0.upreg.percHGNC <- ((dim(na.omit(GW.d0.primary.UPREG))[1]) / (dim(DE_d0.primary.UPREG)[1]) )*100 # percent of DEGs with HGNC ID

# DOWNREGULATED
GW.d0.primary.DWNREG <- merge((DE_d0.primary.DWNREG[order(DE_d0.primary.DWNREG$log2FoldChange),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d0.downreg.percHGNC <- ((dim(na.omit(GW.d0.primary.DWNREG))[1]) / (dim(DE_d0.primary.DWNREG)[1]) )*100 # percent of DEGs with HGNC ID

# DAY 7 ------------------------------------------- #

# UPREGULATED
GW.d7.primary.UPREG <- merge((DE_d7.primary.UPREG[order(DE_d7.primary.UPREG$log2FoldChange, decreasing = TRUE),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d7.upreg.percHGNC <- ((dim(na.omit(GW.d7.primary.UPREG))[1]) / (dim(DE_d7.primary.UPREG)[1]) )*100 # percent of DEGs with HGNC ID

# DOWNREGULATED
GW.d7.primary.DWNREG <- merge((DE_d7.primary.DWNREG[order(DE_d7.primary.DWNREG$log2FoldChange),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d7.downreg.percHGNC <- ((dim(na.omit(GW.d7.primary.DWNREG))[1]) / (dim(DE_d7.primary.DWNREG)[1]) )*100 # percent of DEGs with HGNC ID

# DAY 14 ------------------------------------------- #

# UPREGULATED
GW.d14.primary.UPREG <- merge((DE_d14.primary.UPREG[order(DE_d14.primary.UPREG$log2FoldChange, decreasing = TRUE),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d14.upreg.percHGNC <- ((dim(na.omit(GW.d14.primary.UPREG))[1]) / (dim(DE_d14.primary.UPREG)[1]) )*100 # percent of DEGs with HGNC ID

# DOWNREGULATED
GW.d14.primary.DWNREG <- merge((DE_d14.primary.DWNREG[order(DE_d14.primary.DWNREG$log2FoldChange),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC") # sort to order by greatest logfold change and merge with HGNC list
d14.downreg.percHGNC <- ((dim(na.omit(GW.d14.primary.DWNREG))[1]) / (dim(DE_d14.primary.DWNREG)[1]) )*100 # percent of DEGs with HGNC ID

# DAY 21 ------------------------------------------- #

# UPREGULATED
GW.d21.primary.UPREG <- merge((DE_d21.primary.UPREG[order(DE_d21.primary.UPREG$log2FoldChange, decreasing = TRUE),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d21.upreg.percHGNC <- ((dim(na.omit(GW.d21.primary.UPREG))[1]) / (dim(DE_d21.primary.UPREG)[1]) )*100 # percent of DEGs with HGNC ID

# DOWNREGULATED
GW.d21.primary.DWNREG <- merge((DE_d21.primary.DWNREG[order(DE_d21.primary.DWNREG$log2FoldChange),]), Geoduck.gene_HGNC.list, by = "gene.ID") %>% dplyr::select("HGNC")
d21.downreg.percHGNC <- ((dim(na.omit(GW.d21.primary.DWNREG))[1]) / (dim(DE_d21.primary.DWNREG)[1]) )*100 # percent of DEGs with HGNC ID


### OUTPUT Genewalk tables as csv wihtout header
GW.d0.primary.UPREG.om   <- na.omit(GW.d0.primary.UPREG)
GW.d0.primary.DWNREG.om  <- na.omit(GW.d0.primary.DWNREG)

GW.d7.primary.UPREG.om   <- na.omit(GW.d7.primary.UPREG)
GW.d7.primary.DWNREG.om  <- na.omit(GW.d7.primary.DWNREG) 

GW.d14.primary.UPREG.om  <- na.omit(GW.d14.primary.UPREG)
GW.d14.primary.DWNREG.om <- na.omit(GW.d14.primary.DWNREG)

GW.d21.primary.UPREG.om  <- na.omit(GW.d21.primary.UPREG)
GW.d21.primary.DWNREG.om <- na.omit(GW.d21.primary.DWNREG)

path_genewalk='C:/Users/samjg/Documents/Github_repositories/Pgenerosa_TagSeq_Metabolomics/TagSeq/Analysis/Data/GO/Genewalk_files/' # call path
# output files 
write.table(GW.d0.primary.UPREG.om,paste(path_genewalk,"Day0_upreg.csv", sep =''),sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)
write.table(GW.d0.primary.DWNREG.om, paste(path_genewalk,"Day0_downreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)

write.table(GW.d7.primary.UPREG.om,paste(path_genewalk,"Day7_upreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)
write.table(GW.d7.primary.DWNREG.om,paste(path_genewalk,"Day7_downreg.csv", sep =''), sep=",", col.names=FALSE, row.names=FALSE, quote=FALSE)

write.table(GW.d14.primary.UPREG.om,paste(path_genewalk,"Day14_upreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)
write.table(GW.d14.primary.DWNREG.om,paste(path_genewalk,"Day14_downreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)

write.table(GW.d21.primary.UPREG.om,paste(path_genewalk,"Day21_upreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)
write.table(GW.d21.primary.DWNREG.om,paste(path_genewalk,"Day21_downreg.csv", sep =''), sep=",", col.names=FALSE,row.names=FALSE, quote=FALSE)
```

```{r Genewalk_knitr_table}
GW_summarytable <- data.frame(matrix(nrow = 4, ncol = 8)) # create a new data table
colnames(GW_summarytable)<-c('Day', 'Treatment', 'DEGs_upreg', 'numHGNC_upreg', 'percHGNC_upreg', 'DEGs_dwnreg', 'numHGNC_dwnreg', 'percHGNC_dwnreg') 
GW_summarytable$Day <- c("0","7","14","21")
GW_summarytable$Treatment <- "Ambient_v_Moderate"
GW_summarytable$DEGs_upreg <- c((dim(DE_d0.primary.UPREG)[1]), (dim(DE_d7.primary.UPREG)[1]), (dim(DE_d14.primary.UPREG)[1]), (dim(DE_d21.primary.UPREG)[1]))
GW_summarytable$numHGNC_upreg <- c((dim(na.omit(GW.d0.primary.UPREG))[1]),(dim(na.omit(GW.d7.primary.UPREG))[1]),(dim(na.omit(GW.d14.primary.UPREG))[1]),(dim(na.omit(GW.d21.primary.UPREG))[1]))
GW_summarytable$percHGNC_upreg <- c(d0.upreg.percHGNC,d7.upreg.percHGNC,d14.upreg.percHGNC,d21.upreg.percHGNC)
GW_summarytable$DEGs_dwnreg <- c((dim(DE_d0.primary.DWNREG)[1]), (dim(DE_d7.primary.DWNREG)[1]), (dim(DE_d14.primary.DWNREG)[1]), (dim(DE_d21.primary.DWNREG)[1]))
GW_summarytable$numHGNC_dwnreg<- c((dim(na.omit(GW.d0.primary.DWNREG))[1]),(dim(na.omit(GW.d7.primary.DWNREG))[1]),(dim(na.omit(GW.d14.primary.DWNREG))[1]),(dim(na.omit(GW.d21.primary.DWNREG))[1]))
GW_summarytable$percHGNC_dwnreg <- c(d0.downreg.percHGNC,d7.downreg.percHGNC,d14.downreg.percHGNC,d21.downreg.percHGNC)

knitr::kable(GW_summarytable, caption = "Summary table of Genewalk files - total DEGs and mapping abund HGNC IDs")
# Write csv
write.csv(GW_summarytable,paste(path_genewalk,"Summary_HGNC_hits.csv"))
```

