---
title: "RespirationRates_biovolume_estimation"
author: "Samuel Gurr"
date: "2022-11-29"
output: html_document
---

```{r setup, include=FALSE}

# LOAD PACKAGES - yay! :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(Rmisc)
library(devtools)
library(ggpubr)
library(SciViews)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # personal computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# biovolume data taken for adult Argopecten irradians in Gurr et al. 2021
Gurr2021_biovol  <- read.csv(file="Data/Physiology/Length/Reference_Gurr_etal_2021.csv", header=T) # 123 bay scallop (Ai) samples with biovolume 
# size reference for resp rate data  - actual biovolume only on few timepoints 
Reference_resp_size   <- read.csv(file="Data/Physiology/Respiration/Reference_resp_size.csv", header=T)
# resp rate data 
RR_master <- read.csv(file="Output/Respiration/Calculated_Resp_Master.csv", header=T) %>% 
              filter(!Food %in% 'unfed') %>% # omit low food trial data 
              filter(!Date %in% '8/30/2022') %>% # an F2 measurement
              dplyr::mutate(resp_umol_L_hr_mg_WDW = 
                              resp_umol_L_hr/as.numeric(whole_Dry_weight)) %>%  # call whole dry weight corrected MO2
              dplyr::mutate(resp_umol_L_hr_mmLength = 
                              resp_umol_L_hr/ (1000/Length_um))  %>% # call length corrected MO2
  # unique(RR_master$Date) # "10/26/2021" "2/2/2022"   "3/1/2022"   "8/30/2022"  "9/14/2021"  "9/22/2022"  "9/30/2021"
              dplyr::mutate(Age = case_when(Date == '9/14/2021'  ~ 50,
                                            Date == '9/30/2021'  ~ 66,
                                            Date == '10/26/2021'  ~ 92, 
                                            Date == '2/2/2022' ~ 191,
                                            Date == '3/1/2022'  ~ 218,
                                            Date == '9/22/2022'  ~ 423,
                                            Date == '10/26/2022' ~ 457)) %>% 
              dplyr::mutate(Age = as.factor(Age)) %>% 
              dplyr::arrange(Age)
      
```

## Examine biovolume

**objective**

* we *do not* have biovolume for all samples 
measured for RR, however we need this information to 
subtract displacement of vol from the RR chambers 

What do we have in our respiration dataset? 

* length for all samples, *can we estimate biovol with this info?*

* a few biovolume meaurements, as the weight of the alive scallop (g) in seawater
  * note: measurements did not involve waiting for sw to fill the internal cavity of the scallop

## Pre-existing data (Gurr et al. 2021)

In this study, the biovolume was measured in 122 adult bay scallops 47.95623 +/- 3.637415 (SD)
alongside individual length, width, thickness, and wet weight. 

In the following chunks... I will examine the following: 

### (1) Actual vs. Calculated biovolume - pre-existing data

* use Gurr et al. 2021 data to estimate a calculated alternative for biovolume via 2* Volume of a spherical cap, EQ:  (1/6)πh(3a2 + h2) 
  
  * these data contain all parameters necessary to input into the equation

* determine whether this calculation provides an accurate estimate of biovolume in this size range

### (2) Estimate size relationships

* assuming allometry, what are the size ratios of length to width to thickness, all necessary inputs to the spherical cap EQ but not measured in our target respirometry data 


### (3) Actual vs. Calculated biovolume - our data

* in contrast to (1), this step will examine the reliability of the vol of a spherical cap and the size relationships to back calculate biovolume for our data 

* note: our data in this repository *only* has the length measured, therefore we need to estimate shell thickness for input in the equation (from 2)



# (1) Actual vs. Calculated biovolume - pre-existing data
```{r, actual vs estimated 1}
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# With data from Gurr et al. 2021..
# explore the relationships between length, biovolume, thickness, width
# the interesting aspect of this data is we have all size measurements 

# note: biovolume was measured in Gurr et al. 2021 by the weight (g) of volume displaced in seawater and accounted for salinity
# (1) vessel filled to target volume (2) animal place in, allowed to open valves/clap (3) displaced water above the target vol pipetted and weighed

Gurr2021_biovol.calc <- Gurr2021_biovol %>% 
  dplyr::filter(species %in% 'Ai') %>%  # call argopecten data (also has oyster data C. virginica)
  dplyr::mutate(h = as.numeric(thickness_mm / 2)) %>% # divide by 2 fo the calculation of a single cap
  dplyr::mutate(length.width.mean = ((length_mm+width_mm)/2)) %>% 
  dplyr::mutate(a = as.numeric(length.width.mean/2)) %>% # av of the length and width (slightly different) and get radius
  dplyr::mutate(Cap_vol_L = ((1/6)*3.14*h)*(3*(a^2) + h^2)) %>% # volume of a spherical cap (1/6)πh(3a2 + h2)
  dplyr::mutate(Biovol_estimate_mL3 = (Cap_vol_L*2)/1000)


Biov_true_vs_calculated <- Gurr2021_biovol.calc %>%
   dplyr::filter(Timepoint %in% 'pre-deployment') %>%  # no biovolume measurements taken at post deployment
   ggplot(aes(x=pre_biovolume_mL, y=Biovol_estimate_mL3)) + # , color = as.factor(site))
   geom_point() +
   xlab("biovolume_KNOWN") + 
   ylab("boivolume_CalcVCAP") +
   geom_smooth(method='lm', formula= y~x) +
   theme_bw()
Biov_true_vs_calculated

# looks to be very accurate at least for the size range of these animals from Gurr et al. 2021

```



# (2) Estimate size relationships
```{r, estimate size relationships}
# since we only have shell length, what is the average relationship of length to width and thickness to generate volume?
Gurr2021_size.relationships <- Gurr2021_biovol %>% 
  dplyr::filter(species %in% 'Ai') %>% 
  dplyr::select(c('pre_biovolume_mL', 'length_mm', 'width_mm', 'thickness_mm')) %>% 
  dplyr::mutate(length.biov = (length_mm/pre_biovolume_mL)) %>% 
  dplyr::mutate(length.width = (length_mm/width_mm)) %>% 
  dplyr::mutate(length.thick = (length_mm/thickness_mm)) %>% 
  dplyr::mutate(length.cubed = (length_mm^3)) %>% 
  dplyr::mutate(lengthcubed.biov = (length.cubed/pre_biovolume_mL))
  
  
Length.Width <- Gurr2021_size.relationships[!is.na(Gurr2021_size.relationships$length.width),] %>%
    dplyr::filter(!thickness_mm > 50) %>% 
    summarySE(measurevar="length.width")  # mean = 0.9387522	stdev = 0.02717396	- consistent relationship


length_width <- Gurr2021_size.relationships %>%
  dplyr::filter(!thickness_mm > 50) %>% 
   ggplot(aes(x=length_mm, y=width_mm)) + # , color = as.factor(site))
   geom_point() +
   xlab("length (mm)") + 
   ylab("width (mm)") +
   ggtitle("Length / 0.94 (+/- 0.2 SD) = Width") +
   geom_smooth(method='lm', formula= y~x) +
   theme_bw()


Length.Thickness <- Gurr2021_size.relationships[!is.na(Gurr2021_size.relationships$length.thick),] %>%
  dplyr::filter(!thickness_mm > 50) %>% 
  summarySE(measurevar="length.thick")  # mean = 2.487012	stdev = 0.2249636	- highly variable relationship

length_thickness <- Gurr2021_size.relationships %>%
  dplyr::filter(!thickness_mm > 50) %>% 
   ggplot(aes(x=length_mm, y=thickness_mm)) + # , color = as.factor(site))
   geom_point() +
   xlab("length (mm)") + 
   ggtitle("Length / 2.5(+/- 0.2 SD) = Shell thickness") +
   ylab("shell thickness (mm)") +
  
   geom_smooth(method='lm', formula= y~x) +
   theme_bw()

ggarrange(length_width, length_thickness)




Length.biovol <- Gurr2021_size.relationships[!is.na(Gurr2021_size.relationships$length.biov),] %>% summarySE(measurevar="length.biov")  # mean = 2.55471	stdev = 0.4976332	

Lengthcubed.Biovol <- Gurr2021_size.relationships[!is.na(Gurr2021_size.relationships$lengthcubed.biov),] %>%
    dplyr::filter(!thickness_mm > 50) %>% 
    summarySE(measurevar="lengthcubed.biov")  # mean = 5815.944		stdev = 927.8011	

927.8011/5815.944 # 0.1595272 %

```


# (3) Actual vs. Calculated biovolume - our data

Volume of a spherical cap (1/6)πh(3a2 + h2) == Vcap

* h = height 

  * for a scallop is 1/2*shell thickness
  
  * calc shell thickness as length / 2.5
  
* a = radius from the cap bottom 

  * for scallop shell is 1/2*length from hinge
  
* R = radius from the center of the sphere - not applicable for the known measurements of the scallop

* Vcap*2 = estaimted biovolume of a live scallop, accounting for both valves

```{r, actual vs. Calculated biovolume 2}


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Now to test with the current data in this study..


# volume of a spherical cap (1/3)πh2(3R - h) or (1/6)πh(3a2 + h2)
# h = height (for a scallop is 1/2*shell thickness)
# a = radius from the cap bottom (for scallop shell is 1/2*length from hinge)
# R = radius from the center of the sphere - not applicable for the known measurments of the scallop
Reference_resp_sizeOM <- Reference_resp_size[!is.na(Reference_resp_size$Biovolume_g_in_sw),] %>% 
  dplyr::filter(!Biovolume_g_in_sw %in% '<add here>') %>% 
  dplyr::mutate(Length_mm = as.numeric(Length_um/1000)) %>% 
  dplyr::select(c('Date','pH','Length_mm','Biovolume_g_in_sw')) %>% 
  dplyr::mutate(Thickness_mm_estimate = Length_mm / 2.5) %>% # from data taken in Gurr et al. 2021 (adult A.irradians)
  dplyr::mutate(h = as.numeric(Thickness_mm_estimate / 2)) %>% # divide by 2 fo the calculation of a single cap
  dplyr::mutate(a = as.numeric((Length_mm/0.97)/2)) %>% # note the length is 0.94 of the width in adult scallops (Gurr et al. 2021 data)
  dplyr::mutate(Cap_vol_L = ((1/6)*3.14*h)*(3*(a^2) + h^2)) %>% 
  dplyr::mutate(Biovol_estimate_mL3 = (Cap_vol_L*2)/1000)

# colnames(Reference_resp_sizeOM)
Biov_actual_Vcap <- Reference_resp_sizeOM %>%
   ggplot(aes(x=as.numeric(Biovol_estimate_mL3), y=as.numeric(Biovolume_g_in_sw))) + # color = as.factor(pH))) + 
   geom_point() + 
   ylab("biovolume_KNOWN") + 
   xlab("boivolume_CalcVCAP") +
   ggtitle("Biovolume actual vs. Vcap estimated") +
   geom_smooth(method='lm', formula= y~x) +
   ggpmisc::stat_poly_eq(parse=T, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x.npc = "left") +
   theme_bw()
# Biov_actual_Vcap


Biov_length3_regression <- Reference_resp_sizeOM %>%
   dplyr::mutate(length_cubed = (Length_mm^3)) %>% 
   ggplot(aes(x=as.numeric(length_cubed), y=as.numeric(Biovolume_g_in_sw))) + # color = as.factor(pH))) + 
   geom_point() + 
   xlab("length^3") + 
   ylab("biovolume_KNOWN") +
   ggtitle("Biovolume actual vs. length^3") +
   geom_smooth(method='lm', formula= y~x) +
   ggpmisc::stat_poly_eq(parse=T, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x.npc = "left") +
   theme_bw()
# Biov_length3_regression

ggarrange(Biov_actual_Vcap, Biov_length3_regression)


# (-0.00429)+(0.000198*50000)
Reference_resp_sizeOM %>%
   dplyr::mutate(length_cubed = (Length_mm^3)) %>% 
   dplyr::mutate(Biovol_length3 = (-0.00429)+(0.000198*length_cubed)) %>% 
   ggplot(aes(x=as.numeric(Biovol_length3), y=as.numeric(Biovolume_g_in_sw))) + # color = as.factor(pH))) + 
   geom_point() + 
   xlab("biovolume_calc") + 
   ylab("biovolume_KNOWN") +
   ggtitle("Biovolume actual vs. EQ_fromlength^3") +
   geom_smooth(method='lm', formula= y~x) +
   ggpmisc::stat_poly_eq(parse=T, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x.npc = "left") +
   theme_bw()

```

# EQ for length cubed to biovolume == (-0.00429)+(0.000198*x); x == length_mm^3