---
title: "Respiration workflow example"
author: "Samuel Gurr"
date: "2023-02-28"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=TRUE,message = FALSE, warning = FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(devtools) # devtools::install_github # use devtools to instlal github link
library(LoLinR) # install_github('colin-olito/LoLinR') # install LoLinR from github
library(dplyr)
library(lubridate)
library(rMR) 
library(ggplot2)
library(stringr)

# SET WORKING DIRECTORY AND OUTPUT PATH :::::::::::::::::::::::::::::::::::::::::::::::
knitr::opts_knit$set(root.dir = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis')
path.p    <- "Data/Physiology/Respiration" #the location of all your respirometry files 
```

# STEP 1: OUTPUT A RAW PLOT FOR ALL DATA 

## A. call the directroy names to loop through files (though we will NOT loop in this excersize 

```{r, echo = TRUE,message = FALSE, warning = FALSE}

folder.names           <- basename(list.files(path = path.p, pattern = "202", recursive = FALSE)) #list all csv file names in the folder and subfolders - all data in directories by YYYMMDD - data recorded in year 2021-2023 
folder.names.table     <- data.frame(folder.names) # you see we have many data directories! each with resp data as .csv or .txt depending on resens or loligo data 


```

* lets focus on ONLY row 15: 20230223 - contains F2 adults measured with LoLigo (.txt files) 

```{r, echo = TRUE,message = FALSE, warning = FALSE}

folder.names.table    <- folder.names.table[15,] # 20230223 - we will call this directroy for this workflow example 

```


##  B. call the file names in the directory 20230223


```{r, echo = TRUE,message = FALSE, warning = FALSE}


file.names.table      <- data.frame(txt.files = # call a data frame with a list of all text files wihtin the folder.names.table (only 20230223)
                                      (basename(
                                        list.files(
                                          path = paste(path.p,'/',folder.names.table ,sep=''), # "Data/Physiology/Respiration/20230223"
                                          pattern = "txt$", recursive = TRUE))))  %>%  # list all text files - run here up and see this also contains the txt files WIHTOUT the 'raw' in the title - we DO NOT want these!
                         dplyr::filter(grepl('raw', txt.files))  # only call the txt files with 'raw' in the title

file.names.table
# take a look at the file  - we have three .txt files in 20230223 directroy 
# txt.files
# 1 run_1_raw.txt
# 2 run_2_raw.txt
# 3 run_3_raw.txt
```

##  C. Loop through each  file and plot! 


* before getting started let's first lets open a single file to understand how the loop works! 


```{r, echo = TRUE,message = FALSE, warning = FALSE}


folder.names.table # our existing directroy 20230223 where the three runs in txt format are stored 
file.names.table[1,1] # this calls the first row of the first columns in file.names.table as "run_1_raw.txt" - remember this is the exact name of the file! 
# lets paste these parameters into our file name to call 'run_1_raw.txt'
Resp.Data  <- read.delim2(file = 
                            paste(path.p,'/',folder.names.table, '/', file.names.table[1,1], sep=''), # call out path by stringing together known directories and filename
                          header = TRUE, # yes there is aheader here that we want to retain (column names!)
                          skip = 37,  # the raw loligo data has undesired metadata in the first 37 rows! thus we will skip this in order have the correct headers and data called downstream
                          fileEncoding= "windows-1252") #reads in the data files correctly in their raw format 
# head(Resp.Data)
```


* now lets do this in a looped fashion (commented throughout!)

  - note: if you want to run this line by line do the following: 
  
  (1) do not run the 'for' line at the start - use Cntrl+Enter ro tun line by line
  
  (2) change file.name to call [1,1], [2,1] OR [3,1] for the individual three files in 20230223 folder 
  


```{r, echo = TRUE,message = FALSE, warning = FALSE}


for(m in 1:nrow(file.names.table)) { # the following is ONLY structured for LiLigo data in txt format! 
    
      file.name <- file.names.table[m,1] # CHANGE HERE TO file.names.table[1,1] IF YOU WNAT TO RUN LINE BY LINE!!!
  
      # read the file name one by one - runs the WHOLE loop with the first then the second and so on
      Resp.Data  <- read.delim2(file = 
                                  paste(path.p,'/',folder.names.table, '/', file.name, sep=''), 
                                header = TRUE, 
                                skip = 37, 
                                fileEncoding= "windows-1252") #reads in the data files one  by one first by 'm' as row 1 in file.names.table[m,1], second by 'm' as second row and so on!

  
      
     # Data data 
     # reformat the raw date and call the seconds and minutes timestamp! 
     # raw format is "2/23/2023/11:52:07 AM" containing a lot of info but we need to parse and concvert for it to be meaningful 
      
      Resp.Data$date      <- paste((sub("2023.*", "", Resp.Data$Date..Time..DD.MM.YYYY.HH.MM.SS.)), '2023', sep='') #  date - use 'sub' to call everything before 2023, add back 2023 using paste
      
      Resp.Data$time_Sec  <- period_to_seconds(hms(substr((strptime(sub(".*2023/", "", Resp.Data$Date..Time..DD.MM.YYYY.HH.MM.SS.), "%I:%M:%S %p")) , 12,19))) # time - use 'sub' to call target time of the raw date time after 'year/' + strptime' convert to 24 hr clock + 'period_to_seconds' converts the hms to seconds  

  
      
      
  
     # assign the remaining parameters
      Resp.Data$seconds   <- (Resp.Data$time_Sec - Resp.Data$time_Sec[1])    # seconds as a time series where the first tow is now 0 and each substracted from that initial value 
      
      Resp.Data$minutes   <- (Resp.Data$time_Sec - Resp.Data$time_Sec[1])/60 # convert to minutes 
      
      temperature_C       <- as.numeric(Resp.Data$CH1.temp...C.[1]) # call the temperature data - the dsaem for each channel - this here from CH1 
      
      barromP_kPa         <- as.numeric(Resp.Data$Barometric.pressure..hPa.[1]) / 10 # call the barometric pressure data - this was input manually before we started - we need this data to convert from air saturation to mg/L O2
      
      salinity.pp.thou    <- as.numeric(Resp.Data$Salinity....[1]) # call the salinity - again this was input manually at the start of the experiment 
      
      Resp.Data           <- Resp.Data %>% # use 'dplyr' 
        #dplyr::filter(!Phase %in% 'Flush') %>% # remove the initial rows labeled flush 
        dplyr::select(c(date, seconds, minutes, contains(".O2...air.sat")))  # all target oxygen conuptiondata is labelled .O2...air.sat - call all these data (8 channels in the loligo system!) 

      colnames(Resp.Data)[c(4:(ncol(Resp.Data)))] <- substr( ( colnames(Resp.Data)[c(4:(ncol(Resp.Data)))] ), 1,3) # clean these column names to make things easier - firs all columns 4 and therafter.. sorted their column name as the first 3 characters (i.e. CH1, CH2, etc.) 
      
  
      
      # We have data every second - this is computationally intensive and redundant 
      # truncate the data to every 15 sceonds 
      Resp.Data_15sec = Resp.Data[seq(1, nrow(Resp.Data), 15), ]
  
      
      # lets plot! 
      
      
      date.plot  <- folder.names.table # the directroy timestamp as 20230223
      
      run.plot   <- gsub("_raw.*","", file.name) # the looped run! 
      
      plot_title <- paste(date.plot, run.plot, sep = '_') # the title merging these two parameters as date_runn.umber
      
      
      
      
      PLOT <- Resp.Data_15sec %>% # plote pipeline 
        
        
        # before we plot we need to convert the data from air saturation to mg/L O2! 
        dplyr::select(-c('date', 'seconds')) %>%  # select out the data we do not need- the date and seconds columns (we ONLY want columns contianing data and the minutes timestamp)
        reshape2::melt(id.vars = "minutes",variable.name = "channel", value.name = "air.sat") %>% # melt the data from wide foramnt (channels as columns each with data) to long (one column with data, addition column to designate channel IDs)
        dplyr::filter(!air.sat  %in% 'NaN') %>% # omit NAs in this data 
        dplyr::mutate(mg.L.min =   (DO.unit.convert(as.numeric(air.sat),  # use teh presens package DO.unit.convert to convert air saturation to mg/L, inputs several of the constants we called earlier!
                                                    DO.units.in = "pct", DO.units.out ="mg/L", 
                                                    bar.units.in = "kPa", bar.press = barromP_kPa, bar.units.out = "kpa",
                                                    temp.C = temperature_C, 
                                                    salinity.units = "pp.thou", salinity = salinity.pp.thou))) %>% 
        
        
        
        ggplot(aes(x = minutes , y = mg.L.min)) + # plot simple regression
        geom_smooth(method = "loess", se=FALSE, color="black", formula = mg.L.min ~ minutes) + # call a loess curve 
        theme_classic() +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+ 
        labs(y = expression(RAW_mg~L^{-1}~O[2]%.%min^{-1})) + # name y axis
        xlab("minutes") + # name the x axis 
        geom_point() + 
        ggtitle(plot_title) + # insert the title we called earlier based on the loop file name and date directroy 
        facet_wrap(~channel) # wrap by channel ID column - creates separte plots for each channel 
      
      print(PLOT) # view! 
      
      
      # D. output the plot in RAnalysis\Output\Respiration\workflow_example\plots_raw
      pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/workflow_example/plots_raw/",folder.names.table,"_", sub("_raw.*","",file.name),"_regression.pdf"), width=10, height=12)
      print(PLOT)
      dev.off()

}
```

* view the output plots, in this case we see that truncating at < 40 minutes fits all data on 20220223 runs 

* note that this willnot always be the case, on specific dates we may need to truncate differently depending on the run


## Run LoLinR to obtain raw rates and plot diagnositcs 

```{r, echo = TRUE,message = FALSE, warning = FALSE}

# Call the cumulative dataframe that we will write to in the for loop below
df_total             <- data.frame() # start dataframe 
resp.table           <- data.frame(matrix(nrow = 1, ncol = 7)) # create dataframe to add cumulatively during for loop
colnames(resp.table) <- c('Date', 'Channel', 'Lpc', 'Leq' , 'Lz', 'alpha','Filename') # names for columns in the for loop

# Loligo parametrs 
a <- 0.4 # alpha 0.4 by the authors default suggestions - review Olito et al. and their github page for details

# Run the loop!
for(m in 1:nrow(file.names.table)) { # the following is ONLY structured for LiLigo data in txt format! 
    
    # (1) start will the same steps in the previous loop we ran for plotting  (of coutse this time without the plotting)
    # call the file 'm' and read it 
      file.name <- file.names.table[m,1] 
      Resp.Data  <- read.delim2(file = 
                                  paste(path.p,'/',folder.names.table, '/', file.name, sep=''), 
                                header = TRUE, 
                                skip = 37, 
                                fileEncoding= "windows-1252") 
    # format the date and call variables needed to convert units of air saturation to mg O2
      Resp.Data$date      <- paste((sub("2023.*", "", Resp.Data$Date..Time..DD.MM.YYYY.HH.MM.SS.)), '2023', sep='')
      Resp.Data$time_Sec  <- period_to_seconds(hms(
        substr((strptime(sub(".*2023/", "", Resp.Data$Date..Time..DD.MM.YYYY.HH.MM.SS.), "%I:%M:%S %p")) , 12,19))) 
      Resp.Data$seconds   <- (Resp.Data$time_Sec - Resp.Data$time_Sec[1]) 
      Resp.Data$minutes   <- (Resp.Data$time_Sec - Resp.Data$time_Sec[1])/60 
      temperature_C       <- as.numeric(Resp.Data$CH1.temp...C.[1]) 
      barromP_kPa         <- as.numeric(Resp.Data$Barometric.pressure..hPa.[1]) / 10 
      salinity.pp.thou    <- as.numeric(Resp.Data$Salinity....[1]) 
    # select the columns we need for our table 
      Resp.Data           <- Resp.Data %>% 
        dplyr::select(c(date, seconds, minutes, contains(".O2...air.sat"))) 
      colnames(Resp.Data)[c(4:(ncol(Resp.Data)))] <- substr( ( colnames(Resp.Data)[c(4:(ncol(Resp.Data)))] ), 1,3) 
    # Call data every 15 seconds (else computationally intensive with LoLinr in next loop)
      Resp.Data_15sec = Resp.Data[seq(1, nrow(Resp.Data), 15), ] %>% 
                            dplyr::filter(minutes < 40) # IMPORTANT! we want  < 40 minutes in this record 

      
              # NEW!!!! the inside for loop for each column 'j' in filename 'm'
              # remember, we called  columns date, seconds, minutes first, thus O2 rate data starts at column 4
              for(j in 4:(ncol(Resp.Data_15sec))){ # for each sensor column 'j' (..starting at column 4) 
                Resp_loop <- (Resp.Data_15sec[,c(3,j)]) %>% 
                            dplyr::filter(!str_detect(((Resp.Data_15sec[,c(3,j)])[,2]),"NaN")) %>%  # omit the NAs
                            dplyr::mutate(minutes = as.numeric(minutes)) #  %>% # convert minutes to numeric
                # convert units using liligo package 
                Resp_loop$mgL     <- DO.unit.convert(as.numeric(Resp_loop[,2]),  #n R package from loligo rMR t convert
                                                     DO.units.in = "pct", DO.units.out ="mg/L", 
                                                     bar.units.in = "kPa", bar.press = barromP_kPa, bar.units.out = "kpa",
                                                     temp.C = temperature_C, 
                                                     salinity.units = "pp.thou", salinity = salinity.pp.thou)
    
                     # now run data!
                     if (nrow(Resp_loop) < 1) { # if column 'j' is NA write NA in the cumulative sheet...
                        resp.table$Date                <- Resp.Data_15sec[1,1]
                        resp.table$Channel             <- colnames(Resp_loop)[2] 
                        resp.table[3:ncol(resp.table)] <- 'NA'
                        df       <- data.frame(resp.table) # name dataframe for this single row
                        df_total <- rbind(df_total,df) #bind to a cumulative list dataframe
                        print(df_total) # print to monitor progress
                        
                        } else { # else run LoLinR for x=mins and y=mg/l O2
                            model <- rankLocReg(
                            xall    = as.numeric(Resp_loop[, 1]), 
                            yall    = as.numeric(Resp_loop[, 3]), # call x as the minute timeseries and y as the mg L-1 O2 
                            alpha   = a,  
                            method  = "pc", 
                            verbose = TRUE) 
                        
                            sum.table <- summary(model)
                            
                            resp.table$Date       <- Resp.Data_15sec[1,1]
                            resp.table$Channel    <- colnames(Resp_loop)[2] 
                            resp.table$Lpc        <- sum.table$Lcompare[3,6] # Lpc slope - call the column 'b1'
                            resp.table$Leq        <- sum.table$Lcompare[2,6] # Leq slope - call the column 'b1'
                            resp.table$Lz         <- sum.table$Lcompare[1,6] # Lz slope  - call the column 'b1'
                            resp.table$alpha      <- a
                            resp.table$Filename   <- file.names.table[m,1]
                            
                            df       <- data.frame(resp.table) # name dataframe for this single row
                            df_total <- rbind(df_total,df) #bind to a cumulative list dataframe
                            print(df_total) # print to monitor progress
                            }  # end of  else statement to run LoLinR
            
                           # save plots every inside loop and name by date_run_vialposition
                           pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/workflow_example/plots_alpha0.4_increm15sec/20230223_", sub("_raw.*","",file.names.table[m,1]),"_",colnames(Resp_loop)[2],"_regression.pdf")) # call the pdf to output with loop
                            plot(model) # print the diagnostic plot
                            dev.off() # save it
                            
       } # inside for loop for 'j' O2 columns in each 'm' file 
} # outside for loop for 'm' filenames 

```


```{r, echo = TRUE,message = FALSE, warning = FALSE}

write.table(df_total,"C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/workflow_example/RR_LoLin_raw.csv", sep=",",row.names=FALSE)  # write out


```