---
title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(devtools)
library(ggpubr)
library(hrbrthemes)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

 setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # personal computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
resp.data              <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4_15sectrunc1hour.csv", header=T) %>% 
                          dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
start.end_resp.data    <- read.csv(file="Output/Respiration/Cumulative_resp_start_end.csv", header=T, sep = "") %>% 
                          dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the start and end simplified resp data

resp.ref               <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% 
                           dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt')

lengths                <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T)

lengths_spat           <- read.csv(file="Data/Respiration/Lengths_larvae_spat_resp.csv", header=T)


```


### Merge master resp data frame with lengths

```{r merge resp with length data and treatment IDs, echo=FALSE}

# lengths_spat contains early development resp runs
# as multiple individuals per well (in some cases!) 
# whereas 'lengths' is for juvenile-adult stage scallops each as one length for each resp value 
# thus, we need to summarise as a mean for the 'lengths_spat' file before merging with the other file
head(lengths) # here are the juveniles and adults - a single length individual for each resp channel
head(lengths_spat) # take a look at it here, you see muliple entries for a single well for the larvae/spat resp runs
lengths_spat_MEAN <- as.data.frame(lengths_spat %>% 
                      dplyr::group_by(Date,Run,Plate,Channel) %>% 
                      dplyr::summarise(Length_um = mean(Length))) # group and summarise as a mean
lenghts_master <- rbind.fill(lengths, lengths_spat_MEAN) # use rbind.fill to merge including NAs for missing columns

# check the data - ensure all data was run
nrow(resp.data) == nrow(start.end_resp.data) # MUST be TRUE
resp_all_raw <- merge(resp.data, start.end_resp.data)

# merge the exp_metadata with the resp.data
resp.ref_length_merged                 <- merge(resp.ref, lenghts_master) # all TRUE allows us to keep the blanks
nrow(resp.ref_length_merged)
nrow(lenghts_master)
resp.data_merged                       <- merge(resp.data, resp.ref_length_merged) %>% # out master file moving forward....
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                                            dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                                            dplyr::arrange(Date_formatted,Run, Channel, .by_group = TRUE)
kable(head(resp.data_merged))
View(resp.data_merged)
```

#### Visual diagnostic plots to correct poor data (3 data points to change..)

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

- found three calls that inaccurately represent the rates of oxygen consumption 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

```{r IMPORTANT correct poor data, echo=TRUE, message = FALSE, warning = FALSE}
resp.data_merged[47,c(1:6)]  # 	C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq call better regression than Lp5resp.data_merged[124,c(1:6)] 
resp.data_merged[90,c(1:6)]  #   C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[84,c(1:6)]  # 	C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487  - ommit this
resp.data_merged[135,c(1:6)]   # 	2/2/2022	CH1	run_1_raw.txt  -0.03291728	-0.02714124	-0.0271412; data change Lpc to -0.0209
resp.data_merged[148,c(1:6)]   # 	2/2/2022	CH2	run_3_raw.txt	-0.004996976	-0.007234043	-0.007234043; data change Lpc to -0.0124

# change according to diagnostics of plots and in Lolin script 
resp.data_merged[47,4] <- resp.data_merged[47,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq call better regression than Lpc
resp.data_merged[90,4] <- resp.data_merged[90,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq call better regression than Lpc
resp.data_merged[84,4] <- -0.0296 # 20210930_Plate_1_Run_2_C1_regression - plot shows noise after the 20 minutes mark, we reran this at the end of the LoLin script, insert here!
resp.data_merged[135,4] <- -0.0209
resp.data_merged[148,4] <- -0.0124


# double check if correct
resp.data_merged[47,c(1:6)] # -0.0608251
resp.data_merged[90,c(1:6)] # -0.07603444
resp.data_merged[84,c(1:6)] # -0.0296
resp.data_merged[135,c(1:6)]  # -0.0209
resp.data_merged[148,c(1:6)]  # -0.0124
```

#### Calculate blank rates, view means by day pH_treatment and instrument

* note: respiration rates were recorded using both SDR dish (24 channel) and Loligo 8-channel sensors - different blanks for each

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- data.frame(merge(resp.ref, resp_all_raw, by = c('Date', 'Channel', 'Filename')) %>% 
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  #dplyr::filter(Lpc <0) %>% 
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" ) %>% # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  dplyr::select(c('Date', 'Run', 'Channel','Filename','pH','Lpc', 'Leq', 'Lz', 'Rate_mgO2_hour', 'filetype')) %>% 
                  dplyr::arrange(Date,pH, .by_group = TRUE)) 
# kable((blanks_all_raw)[,c(1:3,6,8,12:14)])


# mean blanks for the LoLinR output ('Lpc')
blanks_meansLoLin <- blanks_all_raw %>% 
                       dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Runs
                       dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
                       dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                                        #   = sd(abs(Lpc)),
                                        # BLANK.mean_Leq = mean(abs(Leq)), 
                                        # BLANK.mean_Lz  = mean(abs(Lz)),
                                        n = n()) %>% 
                        dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                        dplyr::arrange(Date_formatted, Run, pH)
# kable(blanks_meansLoLin) # View - notice some of the date/runs combos do not have BOTH treatmentents represented!
dups_LoLin        <- blanks_meansLoLin[c(1, 16,19,20,23,26),] %>% # call the rows that do not have BOTH pH 7.5 and 8.0 represented (due to positive rates, bad data, etc)         
                        dplyr::mutate(pH = ifelse(pH == 8.0, 7.5,  ifelse(pH == 7.5, 8.0, NA))) # do a little conditional call to call the opposite treatment in this dataframe..
blanks_meansLoLin <- rbind(blanks_meansLoLin, dups_LoLin) %>%  dplyr::arrange(Date_formatted, Run, pH)


# mean blanks for the start - to - end values ('Rate_mgO2_hour')
blanks_meansStartEnd <- blanks_all_raw %>% 
                         dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Runs
                         dplyr::filter(!Rate_mgO2_hour <0) %>% # ommit blank calls that d/n represent oxygen consumption
                         dplyr::summarise(BLANK.start.end_mean  = mean(Rate_mgO2_hour),
                                          # BLANK.start.end_sd  = sd(Rate_mgO2_hour),
                                          n = n()) %>% 
                          dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                          dplyr::arrange(Date_formatted, Run, pH)
# kable(blanks_meansStartEnd) # View - notice some of the date/runs combos do not have BOTH treatmentents represented!
dups_StartEnd          <- blanks_meansStartEnd[c(1, 16,19,28),] %>% # call the rows that do not have BOTH pH 7.5 and 8.0 represented (due to positive rates, bad data, etc)    
                          dplyr::mutate(pH = ifelse(pH == 8.0, 7.5,  ifelse(pH == 7.5, 8.0, NA))) # do a little conditional call to call the opposite treatment dataframe..
blanks_meansStartEnd   <- rbind(blanks_meansStartEnd, dups_StartEnd) %>%  dplyr::arrange(Date_formatted, Run, pH)




blanks_means <- merge(blanks_meansLoLin, blanks_meansStartEnd) %>% dplyr::arrange(Date_formatted, Run, pH)

kable(blanks_means) # View the inserted duplicates for the other treatment on same run/date

```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH", "Run", "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::filter(!Lpc > 0) %>% # remove values with positive O2 - should be none here, double check by removing the '!' and run partial pipeline (found 9/14/2021	pH 8	LoLigo_data	CH1)
  dplyr::mutate(resp_blankStand = (abs(Lpc)) - BLANK.mean_Lpc)  %>%  # Lpc =  Lolin calculated resp (used for SMR actual rates), raw value is negative, take the absolute value and subtract from the mean blank Lpc (already abs value)
  dplyr::mutate(start.end_resp_blankStand = Rate_mgO2_hour - BLANK.start.end_mean) # just start and end (simplified rate in mg O2 per hour) for O:N comparisons
# 
# Resp.Master_2 <- merge(resp.data_merged, blanks_means_0202, by=c("Date", "Run","filetype")) %>% 
#   dplyr::filter(Date %in% '2/2/2022') %>% 
#   dplyr::filter(!Lpc > 0) %>%  # remove values with positive O2 - should be none here, double check by removing the '!' and run partial pipeline
#   dplyr::mutate(resp_blankStand = (abs(Lpc)) - BLANK.mean_Lpc)  %>%  # Lpc =  Lolin calculated resp (used for SMR actual rates), raw value is negative, take the absolute value and subtract from the mean blank Lpc (already abs value)
#   dplyr::mutate(start.end_resp_blankStand = Rate_mgO2_hour - BLANK.start.end_mean) # just start and end (simplified rate in mg O2 per hour) for O:N comparisons
# 
# Resp.Master <- rbind(Resp.Master_1, Resp.Master_2)


plot(Resp.Master$start.end_resp_blankStand, Resp.Master$resp_blankStand)



```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
* 'Fed_unfed'
* 'pCO2'

```{r master resp file, echo=FALSE}

Resp.Master_OM <- Resp.Master[!is.na(Resp.Master$Length_um),] %>% dplyr::filter(!resp_blankStand < 0) %>% # ommit respiration values that are positive  
  dplyr::mutate(volume = case_when(filetype == "LoLigo_data" & Date == '9/14/2021' ~ 2.2, # small vessels for loligo system - 22 ml vessels
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH1' ~ 68.55323, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH2' ~ 68.85583, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021')                       & Channel == 'CH3' ~ 68.87473, # larger custom vessels measured individually... 
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH4' ~ 68.95481, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH5' ~ 68.57288, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH6' ~ 68.01878, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH7' ~ 68.54551, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('10/26/2021','2/2/2022','3/1/2022') & Channel == 'CH8' ~ 68.53297, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH3' ~ 68.87473, # larger custom vessels measured individually... # note ch3 used vessel #9 on and after 2/2/2022 
                                   filetype == "SDR_data" ~ 1.7)) %>% # 24-well plate - 1700ul 
  
  # true rates calculated using LoLinRscript
  dplyr::mutate(resp_mg_L_hr   = ( (abs(resp_blankStand)) *  # currently as just mg O2 per minute
                                      (volume/1000) * # correct Liters - mg per L per min
                                       60) )  %>% # convert rate per minutes to rate per hour
  dplyr::mutate(resp_umol_L_hr = (resp_mg_L_hr*1000) / 32) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                                
  
  # simplified start end rates used to compare O:N ratios
  dplyr::mutate(start.end_resp_mg_L_hr   = (start.end_resp_blankStand*(volume/1000)))  %>% # convert rate per minutes to rate per hour
  dplyr::mutate(start.end_resp_umol_L_hr = (((start.end_resp_mg_L_hr) * (1000)) / 32) ) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                          
  
  
  dplyr::mutate(Age = case_when(Date == '9/14/2021' ~ 50, Date == '9/30/2021' ~ 66, Date == '10/26/2021' ~ 92, Date == '2/2/2022' ~ 190, Date == '3/1/2022' ~ 217)) %>% 
  dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == 'F' ~ "High food", is.na(Fed_Unfed) ~ "High food", Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm"))

# diagnostics..
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_blankStand < 0) # call negatives
print(Resp.outliers) # 25  samples have negative values when correcting for the blank, meaning the blank rate was GREATER than the sample resp value

```


### Relationship between Whole dry weight  v. Shell length 

```{r DW v shell length plot,  echo=TRUE, message = FALSE, warning = FALSE}

Resp.Master_OM %>% ggplot(aes(x = Length_um, y = Dry_Tissue_weight)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("Scallop_TissueDW_mg") +
                                xlab("Length_um") +
                                geom_point() 


Resp.Master_OM %>% ggplot(aes(x = whole_Dry_weight, y = Dry_Tissue_weight)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("Scallop_TissueDW_mg") +
                                xlab("whole_Dry_weight") +
                                geom_point() 

Resp.Master_OM %>% ggplot(aes(x = Dry_Tissue_weight, y = resp_umol_L_hr)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("resp_umol_L_hr") +
                                xlab("Dry_Tissue_weight") +
                                geom_point() 

```


### Standardize rates as...

##### (1) shell length: umol L-1 O2 mm shell length hour-1
##### (2) whole dry weight: umol L-1 O2 g whole dry weight hour-1 

```{r Calculate Resp Rates & WRTIE CSV, echo=TRUE, message = FALSE, warning = FALSE}
# Resp.Master_OM <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),]

# (1) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# NORMALIZED for Shell length
Resp.Master_OM$resp_µmol_L_mm_Length_hr <- (Resp.Master_OM$resp_umol_L_hr / # multiple by 1000 to convert mmol/ O2 to umol/L O2
              (Resp.Master_OM$Length_um/1000)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1

Resp.Master_OM$start.end_resp_umol_mm_Length_hr <- (Resp.Master_OM$start.end_resp_umol_L_hr/ # multiple by 1000 to convert mmol/ O2 to umol/L O2
              (Resp.Master_OM$Length_um/1000)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1

# (2) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# NORMALIZED for Tissue Dry weight (TDW)
Resp.Master_OM$resp_µmol_L_mg_TDW_hr <- (Resp.Master_OM$resp_umol_L_hr / # multiple by 1000 to convert mmol/ O2 to umol/L O2
              (Resp.Master_OM$Dry_Tissue_weight*1000)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1

Resp.Master_OM$start.end_resp_µmol_L_mg_TDW_hr <- (Resp.Master_OM$start.end_resp_umol_L_hr / # multiple by 1000 to convert mmol/ O2 to umol/L O2
              (Resp.Master_OM$Dry_Tissue_weight*1000)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1

#write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
write.csv(Resp.Master_OM, "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")


View(Resp.Master_OM)
```


### Try allometric coefficient (b) of TDW and resp data

* note: not all phys dates contain tissue dry weight (TDW) due to siz and fragility of the cell for accurate dissections

```{r allometric coefficient calc, echo=TRUE, message = FALSE, warning = FALSE}

# ABOUT:
# Pilditch and Grant (1999) Effect of temperature fluctuations and food supply on the growth and metabolism of juvenile sea scallops
# Measured metabolic rates  standardized to tissue dry weight (TDW) (note: this is a standard in the field but we do not have this measurement for our animals...)
# due to the range of sizes (1.13 - 2.29 g DW) the authoirs accout for the variation by scaling to a standard scallop with a 1 g dry tissue weight by the equation:
# R_s = (TWD_s / TWD_obs)^b * R_obs
# R_s = standard rate
# R_obs = observed rate 
# TWD_s = standardized dry tissue weight (they used 1 g here)
# TWD_obs = the observed dry tissue weight


# b = the coefficient estimated empirically by fitting the allometric equation below
# [ln(VO2])] = ln(a) + b*(ln(TDW))
# Allometric coefficient for shell length and respiration rate 
require(SciViews)
ln_VO2 <- as.numeric(ln( (Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),]$resp_umol_L_hr)  )) # assign resp value
ln_TDW  <- as.numeric(ln( (Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),]$Dry_Tissue_weight)  )) # assign length value 
model  <- lm(ln_VO2~ln_TDW) # run model for r quared value
summary(model)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/Shell_length_resp_allometric_coefficient.pdf"))
plot((Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),]$Dry_Tissue_weight),(Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),]$resp_umol_L_hr)) 
abline(model)
legend("topleft",legend=paste("R2 is", (format(summary(model)$r.squared,digits=3)), sep = " ")) 
dev.off()

# b (allometric coefficient) == 0.812

# Using this allometric coefficient....
# R_s    = (SL_s / SL_obs)^b * R_obs
# R_s    = (TWD_s / TWD_obs)^b * R_obs
# R_s    = resp_µmol_L_SL.StzedRate
# R_obs  = resp_umol_L_hr
# SL_s   = 3000 um (shown in plot above)
# SL_obs = Length_um/1000 = mm shell length observed
# b      = 0.812 (calculated above from r^squared in the regression model)

SL_s <- 3 # mm shell size near to the mean for both the low food and high food scallops 
SL_obs <- (Resp.Master_OM$Length_um/1000) # in mm
b = summary(model)$r.squared

Resp.Master_OM$resp_µmol_L_SL.StzedRate <- ((SL_s / SL_obs)^b)*Resp.Master_OM$resp_umol_L_hr
View(Resp.Master_OM)
```


### Plot the RAW rates by the size metrics 

####  (1) Shell length vs. Raw respiration rate (umol O2 L- hr-1)...
``` {r Shell length vs. raw respiration rate, echo=TRUE, message = FALSE, warning = FALSE}

# by Length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_Length_resp_all <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                        ggplot(aes(x = Length_um, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                          labs(title = "Raw Resp v. Shell length (μm)", y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Shell length") +
                          theme(legend.position="none") +
                          geom_point()

P_Length_resp_facet <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                        ggplot(aes(x = Length_um, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                           theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+ 
                          labs(y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Shell length (μm)") +
                          geom_point() + 
                          facet_wrap(~Age*Food, scales = "free")

P_Length_resp_boxplot <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                            ggplot( aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_umol_L_hr , fill = pCO2)) +
                            theme(panel.grid=element_blank()) +
                            geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                            scale_fill_manual(values=c("white","grey50")) +
                            geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                            theme_classic()+ 
                            facet_wrap(~Age, scales = "free")

# print in markdown file 
ggarrange(P_Length_resp_all, P_Length_resp_facet, P_Length_resp_boxplot,nrow = 3)
# Export to pdf
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Shell_length_resp_raw.pdf"), width = 10, height = 6)
ggarrange(P_Length_resp_all, P_Length_resp_facet, P_Length_resp_boxplot,nrow = 3)
dev.off()

```
####  (2) TDW vs. Raw respiration rate (umol O2 L- hr-1)...
``` {r TDW vs. raw respiration rate, echo=TRUE, message = FALSE, warning = FALSE}

# by Length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_TDW_resp_all <- Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                        ggplot(aes(x = Dry_Tissue_weight, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                          labs(title = "Raw Resp v. Tissue dry weight (g)", y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Tissue dry weight (g)") +
                          theme(legend.position="none") +
                          geom_point()

P_TDW_resp_facet <- Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                        ggplot(aes(x = Dry_Tissue_weight, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                           theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+ 
                          labs(y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Tissue dry weight (g)") +
                          geom_point() + 
                          facet_wrap(~Age*pH, scales = "free")

P_TDW_resp_normed <- Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                    ggplot( aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mg_TDW_hr , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic()+ 
                    facet_wrap(~Age, scales = "free")

# print in markdown file 
ggarrange(P_TDW_resp_all, P_TDW_resp_facet,P_TDW_resp_normed,nrow = 3)
# Export to pdf
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Shell_length_resp_raw.pdf"), width = 10, height = 6)
ggarrange(P_Length_resp_all, P_Length_resp_facet,ncol = 2)
dev.off()

```

### (1,2, and 3) Assemble Standrdized rate (allometric coeff) and corrected rates for shell length and dry tissue weight...
```{r Line plot , echo=TRUE, message = FALSE, warning = FALSE}

# Length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Length_um
SumTab_Len      <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),] %>%  
            summarySE(measurevar="Length_um", groupvars=c("Age", "pCO2", "Fed_Unfed"))
SumTab_Len$pCO2 <- factor(SumTab_Len$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Length_time    <- ggplot(data=SumTab_Len, aes(x=Age, y=Length_um, color=pCO2)) +
                    geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
                    geom_point()+ 
                    scale_color_manual(values=c("forestgreen","darkorange2"))+
                    geom_errorbar(aes(ymin=Length_um-se, ymax=Length_um+se), width=.2,
                                  position=position_dodge(.1))+
                    theme_bw() +  
                    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                    scale_x_continuous(name ="Age (d)") +
                    labs(title =  "Shell length over time..", 
                         y = "Shell length (μm)") +
                    scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
                    theme(legend.position="none") +
                    # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
                    facet_wrap(~pCO2)



# resp_µmol_L_mm_Length_hr
RespSumTab_Len      <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_µmol_L_mm_Length_hr),] %>%  
                        summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("Age", "pCO2", "Fed_Unfed"))
RespSumTab_Len$pCO2 <- factor(RespSumTab_Len$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Resp_LengthStand    <- ggplot(data=RespSumTab_Len, aes(x=Age, y=resp_µmol_L_mm_Length_hr, color=pCO2)) +
                        geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
                        geom_point()+ 
                        scale_color_manual(values=c("forestgreen","darkorange2"))+
                        geom_errorbar(aes(ymin=resp_µmol_L_mm_Length_hr-se, ymax=resp_µmol_L_mm_Length_hr+se), width=.2,
                                      position=position_dodge(.1))+
                        theme_bw() +  
                        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                        scale_x_continuous(name ="Age (d)") +
                        labs(title = "Resp corrected by shell length", 
                             y = expression(μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1})) +
                        scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
                        theme(legend.position="none") +
                        # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
                        facet_wrap(~pCO2)


# Print assembled plot from previous chunks....  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# both shell length and whole dry weight used for standardizing respiration rate - view the diagnostic pots for this here (good visual!)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/All_Respiration_normalized_summary.pdf"), width = 10, height = 12)
ggarrange(P_SLStzd_resp_all, Resp_SLStand, NA,
          P_Length_resp_all ,Length_time, Resp_LengthStand,
          P_WholeDW_resp_all, WholeDW_time, Resp_DryWgtStand, ncol = 3, nrow = 3, heights=c(1,1))
dev.off()


ggarrange(Resp_SLStand,
          Resp_LengthStand,
          Resp_DryWgtStand, ncol = 1,nrow = 3) %>% 
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Standardized_resp_rates.pdf")


```




### Skip to here to load the resp master file (if already completed above chunks!!)



```{r load master resp file, echo=FALSE}
# Resp.Master_OM    <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # personel computer 
Resp.Master_OM    <- read.csv(file="C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # work computer
```



# Analysis 



### 9/14/2021 F1 juvenile scallops

**About**
- two pCO2 treatments 
- **before** we culled and started the food limitation trials


##### number of replicates for analysis...

```{r 9/14 replicates and mean resp, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master_OM %>% 
              dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
              dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication


Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pH")) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))


```

### 9/14/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/14 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# plot the replicates (visual diagnostics of random factor)
Resp914_Length_reps<- ggboxplot(Resp_0914, x = "pH", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_Length_reps


# one way anova 
LMmod_914_SL <- lm(resp_µmol_L_mm_Length_hr ~ pCO2, data=Resp_0914)
summary(aov(LMmod_914_SL))
# Df  Sum Sq   Mean Sq F value Pr(>F)
# pCO2         1 1.6e-05 1.601e-05   0.135  0.718
# Residuals   16 1.9e-03 1.187e-04
shapiro.test(residuals(LMmod_914_SL)) #  0.592
leveneTest(LMmod_914_SL) # 0.4815

# Linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0914_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2, random=~1|Chamber_tank, data=Resp_0914)
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  10   |  30.69  | 0.0002476 |
# |    **pCO2**     |   1   |   6   | 0.07053 |  0.7995   |
pander(anova(LMEmod_0914_SL), style='rmarkdown') # anova table of lmer
kable(as.data.frame(anova(LMEmod_0914_SL))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0914_SL) # print the model diagnostics 
dev.off()

# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0914_SL)[[1]])[2], (anova(LMEmod_0914_SL)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_0914_SL)[[3]])[2] # call f
pval <- (anova(LMEmod_0914_SL)[[4]])[2] # call p value

# plot
Resp914_Length <- ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 20210914 (shell length stand.)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                     stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
                     annotate("text", x=2, y=0.000005, size = 4, label = "shapiro wilk = 0.3347") +
                     annotate("text", x=2, y=0.0000075, size = 4, label = "levene's = ???") +
                     annotate("text", x=2, y=0.0000115, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
Resp914_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp914_Length,Resp914_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_respiration_length.pdf")

```


#### b factor standardized (scaled for shell length)

```{r 9/14 b factor standardized , echo=TRUE, message = FALSE, warning = FALSE}

# b factor standardized  (bfactor) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# plot the replicates (visual diagnostics of random factor)
Resp914_bfactor_reps<- ggboxplot(Resp_0914, x = "pH", y = "resp_µmol_L_SL.StzedRate", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_bfactor_reps

# Linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0914_bfactor<-lme(resp_µmol_L_SL.StzedRate ~ pCO2, random=~1|Chamber_tank, data=Resp_0914)
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  16   |  68.08  | 3.707e-07 |
# |    **pCO2**     |   1   |   6   | 0.4731  |  0.5173   |
pander(anova(LMEmod_0914_bfactor), style='rmarkdown') # anova table of lmer
kable(as.data.frame(anova(LMEmod_0914_bfactor))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_SLStzed_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_SLStzed_LME_Diagnostics.pdf"))
check_model(LMEmod_0914_bfactor) # print the model diagnostics 
dev.off()

# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0914_bfactor)[[1]])[2], (anova(LMEmod_0914_bfactor)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_0914_bfactor)[[3]])[2] # call f
pval <- (anova(LMEmod_0914_bfactor)[[4]])[2] # call p value

# plot
Resp914_bfactor <- ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_SL.StzedRate , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 20210914 (b factor stand.)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                     stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
                     annotate("text", x=2, y=0.000005, size = 4, label = "shapiro wilk = 0.3347") +
                     annotate("text", x=2, y=0.0000075, size = 4, label = "levene's = ???") +
                     annotate("text", x=2, y=0.0000115, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
Resp914_bfactor # print this figure...


# Export the figures to pdf
ggarrange(Resp914_bfactor,Resp914_bfactor_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210914_figs_tables/20210914_respiration_SLStzd.standardized.pdf")

```


#### Whole dry weight standardized

```{r 9/14 Whole dry weight standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Whole animal Dry weight standardized (DW) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
Resp914_WholeDW_reps<- ggboxplot(Resp_0914, x = "pH", y = "resp_µmol_L_mg_TDW_hr", color = "Replicate",
                          add = c("mean_se", "dotplot"),
                          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_WholeDW_reps

require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0914_DW<-lme(resp_µmol_L_g_hr ~ pCO2, random=~1|Replicate, data=Resp_0914[!is.na(Resp_0914$resp_µmol_L_g_hr),])
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  16   |  31.58  | 3.836e-05 |
# |    **pCO2**     |   1   |  16   | 0.1122  |   0.742   |
pander(anova(LMEmod_0914_DW), style='rmarkdown')



# linear model without the random effect 
LMmod_0914_DW <- aov(lm(resp_µmol_L_g_hr~pCO2,data=Resp_0914[!is.na(Resp_0914$resp_µmol_L_g_hr),]))
# |    &nbsp;     | Df |  Sum Sq  | Mean Sq  | F value | Pr(>F) |
# |:-------------:|:--:|:--------:|:--------:|:-------:|:------:|
# |   **pCO2**    | 1  | 0.000286 | 0.000286 | 0.1125  | 0.741  |
# | **Residuals** | 19 | 0.04829  | 0.002541 |   NA    |   NA   |
pander(summary(LMmod_0914_DW), style='rmarkdown') # 0.741  
  
  
check_model(LMmod_0914_DW) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_0914_DW)) #  normal - 0.002138
leveneTest(LMmod_0914_DW) # good - 0.9079

DF   <- paste( (summary(LMmod_0914_DW)[[1]][["Df"]])[1], (summary(LMmod_0914_DW)[[1]][["Df"]])[2], sep = '/')
Fval <- (summary(LMmod_0914_DW)[[1]][["F value"]])[1]
pval <- (summary(LMmod_0914_DW)[[1]][["Pr(>F)"]])[1]

Resp914_WholeDW <- ggplot(Resp_0914[!is.na(Resp_0914$resp_µmol_L_g_hr),], aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_g_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              # scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
              theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
              stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
              labs(title = "F1 Scallops: respiration rates on 20210914 (whole dry weight stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%g^{-1}~DW%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))
Resp914_WholeDW


# Export to pdf
ggarrange(Resp914_WholeDW,Resp914_WholeDW_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration_DW.standardized.pdf")

```


# 9/30/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/30 replicates, echo=FALSE}

Resp_0930 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

Resp_0930 %>% dplyr::group_by(pH, Food, Replicate) %>% dplyr::summarise(n()) # tank replication

Resp_0930 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=("pH")) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


## 9/30/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/30 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}


# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Resp930_Length_reps <- ggboxplot(Resp_0930, x = "pHxFood", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
          add = c("mean_se", "dotplot"),
          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_Length_reps


# two way anova 
LMmod_930_SL <- lm(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, data=Resp_0930)
summary(aov(LMmod_930_SL))
#             Df   Sum Sq   Mean Sq F value Pr(>F)  
# pCO2         1 0.000768 0.0007679   4.395 0.0408 *
# Food         1 0.000869 0.0008688   4.973 0.0300 *
# pCO2:Food    1 0.000084 0.0000840   0.481 0.4910  
# Residuals   53 0.009259 0.0001747  
shapiro.test(residuals(LMmod_930_SL)) #  0.02539
leveneTest(LMmod_930_SL) # 0.2124

# Linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0930_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, random=~1|random_fact, data=Resp_0930) 
# |     &nbsp;      | numDF | denDF | F-value | p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:--------:|
# | **(Intercept)** |   1   |  41   |  101.6  | 1.17e-12 |
# |    **pCO2**     |   1   |  12   |  3.448  | 0.08805  |
# |    **Food**     |   1   |  12   |  3.994  | 0.06883  |
# |  **pCO2:Food**  |   1   |  12   | 0.2928  |  0.5983  |
pander(anova(LMEmod_0930_SL), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_0930_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0930_SL) 
dev.off()


# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0930_SL)[[1]])[3], (anova(LMEmod_0930_SL)[[2]])[3], sep = '/') # call DF
Fval <- (anova(LMEmod_0930_SL)[[3]])[3] # call f
pval <- (anova(LMEmod_0930_SL)[[4]])[3] # call p value

# plot
Resp930_Length <- ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              #scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
              theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20210930 (shell length stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
               stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
               facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food')))
Resp930_Length

# Export to pdf
ggarrange(Resp930_Length,Resp930_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_Figures.pdf")

```


# density plot - Day 64

```{r, Day 92 density respiration plot }
library(dplyr)
library(tidyr)
Resp_0930$pHxFood <- as.factor(Resp_0930$pHxFood)

df_mean <- Resp_0930 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_0930, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_0930$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_64DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_0930, aes(x = resp_µmol_L_mm_Length_hr, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.22) +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 64 DPF)", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_64DPF

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_64DPF # print the model diagnostics 
dev.off()

```

#### b factor standardized (scaled for shell length)

```{r 9/30 b factor standardized , echo=TRUE, message = FALSE, warning = FALSE}

# b factor standardized  (bfactor) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# plot the replicates (visual diagnostics of random factor)
Resp930_bfactor_reps<- ggboxplot(Resp_0930, x = "pHxFood", y = "resp_µmol_L_SL.StzedRate", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_bfactor_reps

# Linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0930_bfactor<-lme(resp_µmol_L_SL.StzedRate ~ pCO2 * Food, random=~1|random_fact, data=Resp_0930) 
# |     &nbsp;      | numDF | denDF | F-value | p-value |
# |:---------------:|:-----:|:-----:|:-------:|:-------:|
# | **(Intercept)** |   1   |  57   |  518.1  |    0    |
# |    **pCO2**     |   1   |  12   |  3.433  | 0.08863 | '
# |    **Food**     |   1   |  12   |  6.419  | 0.02625 | **
# |  **pCO2:Food**  |   1   |  12   | 0.04438 | 0.8367  |
pander(anova(LMEmod_0930_bfactor), style='rmarkdown') # anova table of lmer
kable(as.data.frame(anova(LMEmod_0930_bfactor))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_SLStzed_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_SLStzed_LME_Diagnostics.pdf"))
check_model(LMEmod_0930_bfactor) # print the model diagnostics 
dev.off()

# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0930_bfactor)[[1]])[2], (anova(LMEmod_0930_bfactor)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_0930_bfactor)[[3]])[2] # call f
pval <- (anova(LMEmod_0930_bfactor)[[4]])[2] # call p value

# plot
Resp930_bfactor <- ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_SL.StzedRate , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              #scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
              theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20210930 (b fact stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
               stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
               facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food')))
Resp930_bfactor # print this figure...


# Export the figures to pdf
ggarrange(Resp930_bfactor,Resp930_bfactor_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_respiration_SLStzd.standardized.pdf")

```

#### Whole dry weight standardized

```{r 9/30 Whole dry weight standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Whole animal Dry weight standardized (DW) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Resp_0930$pHxFood   <- paste(Resp_0930$pH, Resp_0930$Food, sep = "_")
Resp930_WholeDW_reps <- ggboxplot(Resp_0930, x = "pHxFood", y = "resp_µmol_L_mg_TDW_hr", color = "Replicate",
          add = c("mean_se", "dotplot"),
          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_WholeDW_reps

require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_0930_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, random=~1|Chamber_tank, data=Resp_0930)
# |     &nbsp;      | numDF | denDF | F-value  | p-value |
# |:---------------:|:-----:|:-----:|:--------:|:-------:|
# | **(Intercept)** |   1   |  63   |  515.6   |    0    |
# |    **pCO2**     |   1   |   6   |  3.792   | 0.09943 |
# |    **Food**     |   1   |  63   |  4.029   | 0.04901 |
# |  **pCO2:Food**  |   1   |  63   | 0.009658 |  0.922  |
pander(anova(LMEmod_0930_SL), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_0930_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0930_SL) 
dev.off()


# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0930_SL)[[1]])[3], (anova(LMEmod_0930_SL)[[2]])[3], sep = '/') # call DF
Fval <- (anova(LMEmod_0930_SL)[[3]])[3] # call f
pval <- (anova(LMEmod_0930_SL)[[4]])[3] # call p value

# plot
Resp930_WholeDW <-  ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_g_hr , fill = pCO2)) +
                      theme(panel.grid=element_blank()) +
                      geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                      scale_fill_manual(values=c("white","grey50")) +
                      geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                      theme_classic() +
                      scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                      #scale_y_continuous(expand = c(0, 0), limits = c(0, 200)) +
                      theme(axis.text=element_text(size=8),
                                  axis.title=element_text(size=8,face="bold")) +
                      labs(title = "F1 Scallops: respiration rates on 20210930 (whole dry weight stand.)", 
                           y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%g^{-1}~DW%.% hr^{-1}~")"),
                           x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
                       stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
                        facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # +
Resp930_WholeDW


# Export to pdf
ggarrange(Resp930_WholeDW,Resp930_WholeDW_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_respiration_DW.standardized.pdf")

```


# 10/26/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 10/26 replicates, echo=FALSE}

Resp_1026 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::filter(Food %in% 'fed') %>% 
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

Resp_1026 %>% dplyr::group_by(pH, Food, Replicate) %>% dplyr::summarise(n()) # tank replication

Resp_1026 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=(c("Food","pH"))) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


### 10/26/2021 Linear mixed-effects models, diagnostics, and plots


#### Length standardized

```{r 10/26 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Res1026_Length_reps <- ggboxplot(Resp_1026, x = "pHxFood", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
                          add = c("mean_se", "dotplot"),
                          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Res1026_Length_reps

# two way anova 
LMmod_1026_SL <- lm(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, data=Resp_1026)
summary(aov(LMmod_1026_SL))
#             Df   Sum Sq  Mean Sq F value   Pr(>F)    
# pCO2         1 0.000000 0.000000   0.000    0.993    
# Food         1 0.010103 0.010103  42.524 7.87e-07 ***
# pCO2:Food    1 0.000010 0.000010   0.042    0.840    
# Residuals   25 0.005939 0.000238    
shapiro.test(residuals(LMmod_1026_SL)) #  0.7057
leveneTest(LMmod_1026_SL) # 0.009394 **


# linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_1026_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, random=~1|random_fact, data=Resp_1026)
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  13   |  72.67  | 1.108e-06 |
# |    **pCO2**     |   1   |  12   | 0.2179  |   0.649   |
# |    **Food**     |   1   |  12   |  30.57  | 0.0001301 |
# |  **pCO2:Food**  |   1   |  12   | 0.1083  |  0.7478   |
pander(anova(LMEmod_1026_SL), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_1026_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_1026_SL) 
dev.off()
# tukey posthoc for lmer model
require('lsmeans')
lsmeans(LMEmod_1026_SL, pairwise~pCO2 * Food, adjust="tukey") # Compute least-squares means
# $contrasts
#  contrast                         estimate       SE df t.ratio p.value
#  500 µatm fed - 800 µatm fed     -5.74e-05 8.93e-06 12  -6.430  0.0002
#  500 µatm fed - 500 µatm unfed    9.03e-05 9.41e-06 12   9.589  <.0001
#  500 µatm fed - 800 µatm unfed    9.08e-05 9.41e-06 12   9.640  <.0001
#  800 µatm fed - 500 µatm unfed    1.48e-04 8.93e-06 12  16.538  <.0001
#  800 µatm fed - 800 µatm unfed    1.48e-04 8.93e-06 12  16.592  <.0001
 # 500 µatm unfed - 800 µatm unfed  4.82e-07 9.41e-06 12   0.051  0.9999


# plot
Resp1026_Length <- ggplot(Resp_1026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              # scale_y_continuous(expand = c(0, 0), limits = c(0, 250)) +
              theme(axis.text=element_text(size=8),
                    axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20211026 (shell length stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%m^{-1}~shell~length%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
              facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # +
Resp1026_Length


# Export to pdf
ggarrange(Resp1026_Length, Res1026_Length_reps,nrow = 2) %>% 
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_Figures.pdf")

```


# density plot - Day 92

```{r, Day 92 density respiration plot }
library(dplyr)
library(tidyr)
Resp_1026$pHxFood <- as.factor(Resp_1026$pHxFood)
Resp_1026$resp_µmol_L_mm_Length_hr.noSCI     <- format(as.numeric(Resp_1026$resp_µmol_L_mm_Length_hr), scientific = FALSE, digits = 3)
Resp_1026$resp_µmol_L_mm_Length_hr.NUM       <- as.numeric(sprintf("%s", Resp_1026$resp_µmol_L_mm_Length_hr.noSCI))

df_mean <- Resp_1026 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr.NUM)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_1026, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr.NUM)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_1026$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_92DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_1026, aes(x = resp_µmol_L_mm_Length_hr.NUM, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 92 DPF)", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%m^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_92DPF

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_92DPF # print the model diagnostics 
dev.off()

```

#### b factor standardized (scaled for shell length)

```{r 9/30 b factor standardized , echo=TRUE, message = FALSE, warning = FALSE}

# b factor standardized  (bfactor) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# plot the replicates (visual diagnostics of random factor)
Resp1026_bfactor_reps<- ggboxplot(Resp_1026, x = "pHxFood", y = "resp_µmol_L_SL.StzedRate", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp1026_bfactor_reps

# Linear mixed-effects model
require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_1026_bfactor<-lme(resp_µmol_L_SL.StzedRate ~ pCO2 * Food, random=~1|random_fact, data=Resp_1026) 
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  18   |  706.4  | 6.661e-16 |
# |    **pCO2**     |   1   |  12   |  26.71  | 0.0002339 |
# |    **Food**     |   1   |  12   |   363   | 2.458e-10 |
# |  **pCO2:Food**  |   1   |  12   |  14.75  |  0.00235  | ###
pander(anova(LMEmod_1026_bfactor), style='rmarkdown') # anova table of lmer
kable(as.data.frame(anova(LMEmod_1026_bfactor))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp.SLStzed_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_SLStzed_LME_Diagnostics.pdf"))
check_model(LMEmod_1026_bfactor) # print the model diagnostics 
dev.off()
# tukey posthoc for lmer model
require('lsmeans')
lsmeans(LMEmod_1026_bfactor, pairwise~pCO2 * Food, adjust="tukey") # Compute least-squares means
# $contrasts
#  contrast                         estimate       SE df t.ratio p.value
#  500 µatm fed - 800 µatm fed     -1.91e-04 3.41e-05 12  -5.619  0.0006
#  500 µatm fed - 500 µatm unfed    3.71e-04 3.59e-05 12  10.326  <.0001
#  500 µatm fed - 800 µatm unfed    3.70e-04 3.59e-05 12  10.289  <.0001
#  800 µatm fed - 500 µatm unfed    5.62e-04 3.41e-05 12  16.503  <.0001
#  800 µatm fed - 800 µatm unfed    5.61e-04 3.41e-05 12  16.465  <.0001
#  500 µatm unfed - 800 µatm unfed -1.32e-06 3.59e-05 12  -0.037  1.0000


# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_1026_bfactor)[[1]])[2], (anova(LMEmod_1026_bfactor)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_1026_bfactor)[[3]])[2] # call f
pval <- (anova(LMEmod_1026_bfactor)[[4]])[2] # call p value

# plot
Resp1026_bfactor <- ggplot(Resp_1026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_SL.StzedRate , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              #scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
              theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20211026 (b fact stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
               stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
               facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food')))
Resp1026_bfactor # print this figure...


# Export the figures to pdf
ggarrange(Resp1026_bfactor,Resp1026_bfactor_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA /RAnalysis/Output/Respiration/20211026_figs_tables/20211026_respiration_SLStzd.standardized.pdf")

```


#### Whole dry weight standardized


```{r 10/26 Whole dry weight standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Whole animal Dry weight standardized (DW) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Res1026_WholeDW_reps <- ggboxplot(Resp_1026, x = "pH", y = "resp_µmol_L_mg_TDW_hr", color = "Replicate",
                          add = c("mean_se", "dotplot"),
                          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Res1026_WholeDW_reps


require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_1026_DW<-lme(resp_µmol_L_mg_TDW_hr ~ pCO2, random=~1|Replicate, data=Resp_1026)
# |     &nbsp;      | numDF | denDF | F-value | p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:--------:|
# | **(Intercept)** |   1   |   6   |  18.75  | 0.004928 |
# |    **pCO2**     |   1   |   6   |  2.914  |  0.1387  |
pander(anova(LMEmod_1026_DW), style='rmarkdown')



# linear model without the random effect 
LMmod_1026_DW <- aov(lm(resp_µmol_L_mg_TDW_hr~pCO2,data=Resp_1026))
# |    &nbsp;     | Df |  Sum Sq  | Mean Sq  | F value | Pr(>F) |
# |:-------------:|:--:|:--------:|:--------:|:-------:|:------:|
# |   **pCO2**    | 1  | 0.001184 | 0.001184 |  1.178  | 0.306  |
# | **Residuals** | 9  | 0.009049 | 0.001005 |   NA    |   NA   |
pander(summary(LMmod_1026_DW), style='rmarkdown')
check_model(LMmod_1026_DW) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_1026_DW)) #  normal - 0.3929
leveneTest(LMmod_1026_DW) # 0.139


Res1026_WholeDW <- ggplot(Resp_1026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mg_TDW_hr , fill = pCO2)) +
                            theme(panel.grid=element_blank()) +
                            geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                            scale_fill_manual(values=c("white","grey50")) +
                            geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                            theme_classic() +
                            scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                            # scale_y_continuous(expand = c(0, 0), limits = c(0, 150)) +
                            theme(axis.text=element_text(size=8),
                                  axis.title=element_text(size=8,face="bold")) +
                            labs(title = "F1 Scallops: respiration rates on 20211026 (whole dry weight stand.)", 
                                 y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%g^{-1}~DW%.% hr^{-1}~")"),
                                 x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))
Res1026_WholeDW

# Export to pdf
ggarrange(Res1026_WholeDW, Res1026_WholeDW_reps,nrow = 2) %>% 
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_respiration_DW.standardized.pdf")

```









# 2/2/2022 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 2/2 replicates, echo=FALSE}

Resp_0202 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '2/2/2022')  %>% # call only 10/14
  dplyr::select(-Center) 

Resp_0202 %>% dplyr::group_by(pH) %>% dplyr::summarise(n()) # tank replication

Resp_0202 %>% summarySE(measurevar="resp_µmol_L_mg_TDW_hr", groupvars=(c("pH"))) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


### 2/02/2022 Linear mixed-effects models, diagnostics, and plots


#### Length standardized

```{r 10/26 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Res0202_TDW_reps <- ggboxplot(Resp_0202, x = "pH", y = "resp_µmol_L_mg_TDW_hr", color = "Replicate",
                          add = c("mean_se", "dotplot"),
                          palette = c("#00AFBB", "#E7B800", "brown", "grey", "purple", "blue", "black", "orange"))
Res0202_TDW_reps

require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMmod_0202_SL<-aov(lm(resp_µmol_L_mg_TDW_hr ~ pCO2, data=Resp_0202))
summary(LMmod_0202_SL)
# |    &nbsp;     | Df |  Sum Sq  | Mean Sq  | F value  | Pr(>F) |
# |:-------------:|:--:|:--------:|:--------:|:--------:|:------:|
# |   **pCO2**    | 1  | 1.56e-05 | 1.56e-05 | 0.006697 | 0.9358 |
# | **Residuals** | 16 | 0.03728  | 0.00233  |    NA    |   NA   |
pander(anova(LMmod_0202_SL), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_0222_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20210222_figs_tables/20210222_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20210222_figs_tables/20210222_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0222_SL) 
dev.off()


# plot
Resp0202_TDW <- ggplot(Resp_0202, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mg_TDW_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              # scale_y_continuous(expand = c(0, 0), limits = c(0, 250)) +
              theme(axis.text=element_text(size=8),
                    axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20210202 (Tissue dry weight stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%m^{-1}~shell~length%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))
Resp0202_TDW


# Export to pdf
# ggarrange(Resp0222_Length, Resp0202_TDW,nrow = 2) %>% 
#   ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/AAirradians_multigen_OA/RAnalysis/Output/Respiration/20210222_figs_tables/20210222_resp_Figures.pdf")

```

