---
title: "RespirationRates_calc_F1s"
author: "Samuel Gurr"
date: "11/29/2022"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(devtools)
library(ggpubr)
library(hrbrthemes)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # personal computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
resp.data           <- read.csv(file="Output/Respiration/RR_LoLin_raw.csv", header=T) %>% 
                          dplyr::filter(!Date %in% "9/14/2021" | 
                                          !Filename %in% 'Run_1_raw.txt') %>%  # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
                          dplyr::filter(!(Date %in% "10/26/2022" & 
                                            Filename %in% 'run_1_raw.txt' & Channel %in% 'CH2')) # omit bad data point



start.end_resp.data <- read.csv(file="Output/Respiration/RR_start_end_raw.csv", header=T, sep = "") #%>% 
                          #dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the start and end simplified resp data

resp.ref            <- read.csv(file="Data/Physiology/Respiration/Reference_resp_ID.csv", header=T) %>% 
                           dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') 


# data to correct for length, dry weight, etc. 
lengths_juv_adults  <- read.csv(file="Data/Physiology/Respiration/Reference_resp_size.csv", header=T)

lengths_spat        <- read.csv(file="Data/Physiology/Respiration/Reference_resp_size_LARVAE.csv", header=T) %>% 
                          dplyr::mutate(Length_um = Length * 1000) %>% # current length in mm
                          dplyr::select(!Length)
# View(resp.data)

```


### Merge master resp data frame with lengths

```{r merge resp with length data and treatment IDs, echo=FALSE}

# lengths_spat contains early development resp runs
# as multiple individuals per well (in some cases!) 
# whereas 'lengths' is for juvenile-adult stage scallops each as one length for each resp value 
# thus, we need to summarise as a mean for the 'lengths_spat' file before merging with the other file
head(lengths_juv_adults) # here are the juveniles and adults - a single length individual for each resp channel
head(lengths_spat) # take a look at it here, you see muliple entries for a single well for the larvae/spat resp runs
lengths_spat_MEAN <- as.data.frame(lengths_spat %>% 
                      dplyr::group_by(Date,Run,Plate,Channel, Chamber_tank,Number,pH) %>% 
                      dplyr::summarise(Length_um = mean(Length_um))) %>% # group and summarise as a mean
                      dplyr::select(!Channel)
lenghts_master <- rbind.fill(lengths_juv_adults, lengths_spat_MEAN) # use rbind.fill to merge including NAs for missing columns

# check the data - ensure all data was run
if(nrow(resp.data) == nrow(start.end_resp.data)){ # MUST be TRUE
resp_all_raw <- merge(resp.data, start.end_resp.data)
} else{resp_all_raw <- resp.data}

# merge the exp_metadata with the resp.data
resp.ref_length_merged                 <- merge(resp.ref, 
                                                lenghts_master) # all TRUE allows us to keep the blanks

resp.data_merged                       <- merge(resp.data, resp.ref_length_merged) %>% 
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", 
                                                                                   "SDR_data", 
                                                                                   "LoLigo_data"))) %>% 
                                            dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                                            dplyr::arrange(Date_formatted,Run, Channel, .by_group = TRUE)
kable(head(resp.data_merged))
unique(resp.data_merged$Date)
# View(resp.data_merged)
```

#### Visual diagnostic plots to correct poor data (3 data points to change..)

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

- found three calls that inaccurately represent the rates of oxygen consumption 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

```{r IMPORTANT correct poor data, echo=TRUE, message = FALSE, warning = FALSE}

# NOTE: the F2s have a late start in resp value in 2/23/2023 run 2 channel 6 - scllop did not open until late in trial and ended same time as others - we discussed omission

resp.data_merged[47,c(1:6)]  # 	C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq call better regression than Lp5resp.data_merged[124,c(1:6)] 
resp.data_merged[90,c(1:6)]  #  C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[84,c(1:6)]  # 	C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487  - ommit this
resp.data_merged[135,c(1:6)] # 	2/2/2022	CH1	run_1_raw.txt  -0.03291728	-0.02714124	-0.0271412; data change Lpc to -0.0209
resp.data_merged[148,c(1:6)] # 	2/2/2022	CH2	run_3_raw.txt	-0.004996976	-0.007234043	-0.007234043; data change Lpc to -0.0124
resp.data_merged[257,c(1:6)] #  10/26/2022	CH3	run_2_raw.txt	0.04303898	-0.0047484	-0.0047484; data change Lpc to -0.1063
resp.data_merged[258,c(1:6)] #  10/26/2022	CH4	run_2_raw.txt	-0.003937913	-0.003744103	-0.003744103; data change Lpc to -0.0900
resp.data_merged[261,c(1:6)] #  10/26/2022	CH7	run_2_raw.txt	-0.002582753	-0.004017686	-0.004017686; data change Lpc to -0.1012

# change according to diagnostics of plots and in Lolin script 
resp.data_merged[47,4] <- resp.data_merged[47,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq call better regression than Lpc
resp.data_merged[90,4] <- resp.data_merged[90,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq call better regression than Lpc
resp.data_merged[84,4] <- -0.0296 # 20210930_Plate_1_Run_2_C1_regression - plot shows noise after the 20 minutes mark, we reran this at the end of the LoLin script, insert here!
resp.data_merged[135,4] <- -0.0209
resp.data_merged[148,4] <- -0.0124
resp.data_merged[257,4] <- -0.1063
resp.data_merged[258,4] <- -0.0900
resp.data_merged[261,4] <- -0.1012

# double check if correct
resp.data_merged[47,c(1:6)] # -0.0608251
resp.data_merged[90,c(1:6)] # -0.07603444
resp.data_merged[84,c(1:6)] # -0.0296
resp.data_merged[135,c(1:6)]  # -0.0209
resp.data_merged[148,c(1:6)]  # -0.0124
resp.data_merged[257,c(1:6)]  # -0.1063
resp.data_merged[258,c(1:6)]  # -0.09
resp.data_merged[261,c(1:6)]  # -0.1012
```

#### Calculate blank rates, view means by day pH_treatment and instrument

* note: respiration rates were recorded using both SDR dish (24 channel) and Loligo 8-channel sensors - different blanks for each

```{r call blanks, echo=FALSE}



blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- data.frame(merge(resp.data, resp.ref)) %>% # data.frame((merge(resp_all_raw, resp.ref)) %>%
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  #dplyr::filter(Lpc <0) %>% 
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date ==  '9/30/2021'   | !pH == "7.5" | !Channel == "B2" | !Run == "1" | !Plate == "1" ) %>% # abnormal high rate for a blank - omission approximates the mean blank for the other treatment (bad data)
                  dplyr::filter(!Date == '8/30/2022' | !Lpc < -0.02) %>% # omit the few outlier blanks shiting rates higher than those with spat or larvae
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" ) %>% # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  dplyr::select(c('Date', 'Run', 'Channel','Filename','pH','Lpc', 'Leq', 'Lz','filetype')) %>% # add 'Rate_mgO2_hour'hen the start and end is completed
                  dplyr::arrange(Date,pH, .by_group = TRUE)




# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# mean blanks for the LoLinR output ('Lpc') ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

blanks_all_raw %>% 
  select(Lpc) %>% 
  dplyr::mutate(Lpc_filt = case_when(Lpc > 0 & Lpc < 0.005 ~ 0,TRUE ~ Lpc))# fed F1 foodxOA

blanks_meansLoLin <- blanks_all_raw %>% 
                       dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Run
                       #dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
                       dplyr::mutate(Lpc_filt = case_when(Lpc > 0 & Lpc < 0.005 ~ 0,TRUE ~ Lpc)) %>% #  when LPC is positive but veery close to zero - assign as zero
                       dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                                        #   = sd(abs(Lpc)),
                                        # BLANK.mean_Leq = mean(abs(Leq)), 
                                        # BLANK.mean_Lz  = mean(abs(Lz)),
                                        n = n()) %>% 
                        dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                        dplyr::arrange(Date_formatted, Run, pH)
# kable(blanks_meansLoLin) # View - notice some of the date/runs do not have BOTH treatments represented!
dups_LoLin        <- blanks_meansLoLin[(17),] %>% #one rows that does have each treatment  represented (due to positive rates, bad data, etc)         
                        dplyr::mutate(pH = ifelse(pH == 8.0, 7.5,  ifelse(pH == 7.5, 8.0, NA))) # do a little conditional call to call the opposite treatment in this dataframe..
blanks_meansLoLin <- rbind(blanks_meansLoLin, dups_LoLin) %>%  dplyr::arrange(Date_formatted, Run, pH) # bind together




# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# mean blanks for the start - to - end values ('Rate_mgO2_hour') :::::::::::::::::::::::::::::::::::::::::




# blanks_meansStartEnd <- blanks_all_raw %>% 
#                          dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Runs
#                          dplyr::filter(!Rate_mgO2_hour < 0) %>% # ommit blank calls that d/n represent oxygen consumption
#                          dplyr::summarise(BLANK.start.end_mean  = mean(Rate_mgO2_hour),
#                                           # BLANK.start.end_sd  = sd(Rate_mgO2_hour),
#                                           n = n()) %>% 
#                           dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
#                           dplyr::arrange(Date_formatted, Run, pH)
# # kable(blanks_meansStartEnd) # View - notice some of the date/runs combos do not have BOTH treatmentents represented!
# dups_StartEnd          <- blanks_meansStartEnd[c(1, 16,19,28),] %>% # call the rows that do not have BOTH pH 7.5 and 8.0 represented (due to positive rates, bad data, etc)    
#                           dplyr::mutate(pH = ifelse(pH == 8.0, 7.5,  ifelse(pH == 7.5, 8.0, NA))) # do a little conditional call to call the opposite treatment dataframe..
# blanks_meansStartEnd   <- rbind(blanks_meansStartEnd, dups_StartEnd) %>%  dplyr::arrange(Date_formatted, Run, pH)
# 




# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# merge blanks Lolin rates and blanks for start-end rates ::::::::::::::::::::::::::::::::::::::::::::::::

#... first and foremost! do not do this if rate calculations differ in row size 
# (not all data ran for Lolin and star end resp)


if(nrow(resp.data) == nrow(start.end_resp.data)){ # if they are the same length (all data ran for both analysis)
blanks_means <- merge(blanks_meansLoLin, blanks_meansStartEnd) %>% dplyr::arrange(Date_formatted, Run, pH) # merge blanks
} else{blanks_means <- blanks_meansLoLin} # else we focus only on the blanks for the LoLin rate (what we will use) 



# lets take a look at our mean blank values! :::::::::::::::::::::::::::::::::::::::::::::::::::::


kable(blanks_means) # View the inserted duplicates for the other treatment on same run/date

# NOTe: 10/26/22 has wide differences between blank rates
```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH", "Run", "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::filter(!Lpc > 0) %>% # remove values with positive O2 - should be none here, double check by removing the '!' and run partial pipeline (found 9/14/2021	pH 8	LoLigo_data	CH1)
  dplyr::mutate(resp_blankStand = (abs(Lpc)) - BLANK.mean_Lpc) # %>%  # Lpc =  Lolin calculated resp (used for SMR actual rates), raw value is negative, take the absolute value and subtract from the mean blank Lpc (already abs value)
 # dplyr::mutate(start.end_resp_blankStand = Rate_mgO2_hour - BLANK.start.end_mean) # just start and end (simplified rate in mg O2 per hour) for O:N comparisons

#plot(Resp.Master$start.end_resp_blankStand, Resp.Master$resp_blankStand)

```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
* 'Fed_unfed'
* 'pCO2'

```{r master resp file, echo=FALSE}
# View(Resp.Master[!is.na(Resp.Master$Length_um),])
Resp.Master_OM <- Resp.Master[!is.na(Resp.Master$Length_um),] %>% 
  dplyr::filter(!resp_blankStand < 0) %>% # ommit respiration values that are positive  
  dplyr::mutate(volume = 
                  
            case_when(
              
                      # F1 DATA HERE :::::::::::
              
                      filetype == "LoLigo_data" & Date %in% c('9/14/2021','9/30/2021') ~ 2.2,# fed F1 foodxOA
                      
                      filetype == "SDR_data" & Date %in% c('9/30/2021','10/26/2021')~ 1.7, # small unfed F1s foodxOA 
                      
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH1' ~ 23.1, # F1 data
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH2' ~ 23.05, 
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH4' ~ 22.55,
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH5' ~ 23.18,
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH6' ~ 23.24,
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH7' ~ 22.63, 
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH8' ~ 22.95,
                      # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH3' ~ 23.31,
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH1' ~ 68.55323, # F1 data
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH2' ~ 68.85583, 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH4' ~ 68.95481,
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH5' ~ 68.57288,
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH6' ~ 68.01878,
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH7' ~ 68.54551, 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH8' ~ 68.53297,
                      filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH3' ~ 68.87473,

                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH1' ~ 68.55323, # F1 data
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH2' ~ 68.85583, 
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH4' ~ 68.95481,
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH5' ~ 68.57288,
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH6' ~ 68.01878,
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH7' ~ 68.54551, 
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH8' ~ 68.53297,
                      filetype == "LoLigo_data" & Date %in% c('2/2/2022','3/1/2022') & Channel == 'CH3' ~ 68.87473,
                      
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH1' ~ 196.6, # F1 data
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH2' ~ 200.6, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH3' ~ 201.4, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH4' ~ 200, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH5' ~ 199.2, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH6' ~ 200.4, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH7' ~ 201.3, 
                      filetype == "LoLigo_data" & Date %in% c('9/22/2022') & Channel == 'CH8' ~ 201.7, 
                      
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH1' ~ (236.70+18), # F1 data
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH2' ~ (239.88+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH3' ~ (228.63+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH4' ~ (234.35+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH5' ~ (224.31+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH6' ~ (229.07+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH7' ~ (223.11+18), 
                      filetype == "LoLigo_data" & Date %in% c('10/26/2022') & Channel == 'CH8' ~ (225.59+18), 
                
                      # F2 DATA HERE :::::::::::
                      
                      filetype == "SDR_data" & Date %in% c('8/30/2022') ~ 0.08, # F2 data 
                      filetype == "SDR_data" & Date %in% c('9/22/2022') ~ 1.7,  # F2 data
                      
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH1' ~ 23.1, # F2 data
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH2' ~ 23.05,
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH3' ~ 23.31,
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH4' ~ 22.55,
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH5' ~ 23.18,
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH6' ~ 23.24,
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH7' ~ 22.63, 
                      filetype == "LoLigo_data" & Date %in% c('11/16/2022') & Channel == 'CH8' ~ 22.95, 
  
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH1' ~ 68.55323, # F1 data
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH2' ~ 68.85583, 
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH4' ~ 68.95481,
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH5' ~ 68.57288,
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH6' ~ 68.01878,
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH7' ~ 68.54551, 
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH8' ~ 68.53297,
                      filetype == "LoLigo_data" & Date %in% c('1/31/2023') & Channel == 'CH3' ~ 68.87473,                      
                      
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH1' ~ 198.2, # F2 data
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH2' ~ 212.5,
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH3' ~ 209.8,
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH4' ~ 211.8,
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH5' ~ 212.6,
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH6' ~ 212.8,
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH7' ~ 213.5, 
                      filetype == "LoLigo_data" & Date %in% c('2/23/2023') & Channel == 'CH8' ~ 212)) %>% # F2 data
  # BIOVOLUME 
  # note that biovolume was not measured for 9/14/2021, 9/30/2021, 10/26/21 (unfed only!), 9/22/22 (F2s only, SDR data)
 
   # (1) Vcap biovolume  - note we Aare NOT moving forward with this, however the regressions are great so I am keeping it for future reference (Sam)
  # Calculate biovolume using the volume of spherical cap and length measurements of scallops (leveraged data from Gurr et al. 2021 to test)
  dplyr::mutate(Length_mm = Length_um/1000) %>% 
  dplyr::mutate(Thickness_mm_estimate = Length_mm / 2.5) %>% # 2.5 ratio estimated in Biovolume_estimate.Rmd
  dplyr::mutate(h = as.numeric(Thickness_mm_estimate / 2)) %>% # divide by 2 fo the calculation of a single cap
  dplyr::mutate(a = as.numeric((Length_mm/0.97)/2)) %>% # 0.94 ratio estimated in Biovolume_estimate.Rmd
  dplyr::mutate(Cap_vol_L = ((1/6)*3.14*h)*(3*(a^2) + h^2)) %>% # Volume of a spherical cap (1/6)πh(3a2 + h2) == Vcap
  dplyr::mutate(Biovol_estimate_VCap = (Cap_vol_L*2)/1000)  %>% 

  # (2) Length^3
  # from length^3 to biovolume == (-0.00429)+(0.000198*x); x == length_mm^3 - this regression was run in biovolume testing script 
  dplyr::mutate(Biovol_length3 = (0.000198*(Length_mm^3)))  %>%  # calc biovolume based on length^3;  in Seember 2022 we decided to go with the length3 method for extrapolating biovolume for animals that do not have biovolume measurments 
  
  
  # CALCULATE THE ACTUAL VOLUME (accounting for measured and calculated biovolumes)
  
  # (1) 'calculated_volume' employing length^3 biovolume estimate to correct for volume displaces
  dplyr::mutate(calculated_volume = (volume - Biovol_length3)) %>%  # calculated biovolume based on length^3
  
  # (2) 'measured_volume' employing ONLY the measured values - resulting in many NAs for data where we did not measure it
  dplyr::mutate(measured_volume = (volume - Biovolume_g_in_sw)) %>%  # calculated biovolume based on length^3
  
  # NOTE: 'calcANDactual_volume' here is the continingency statement used to obtain a SINGLE resp value using (1) measured biovol when applicable (2) measured biovoume when measured is unavailable
  # as of 1/5/2023 - team decided they want TWO resp data files (1) only with measured biovolumes - including many NAs (2) only calculated - no NAs, used calculated value
  # dplyr::mutate(calcANDactual_volume = ifelse(is.na(Biovolume_g_in_sw), (volume - Biovol_length3), # NA, calculate actual volume using the calculated biovolume using the length^3 regression EQ
  #                                      #NOTE THE SMALL ANIMALS HAVE NEGATIVE BIOVOLUME USING TH ELENGTH 3 EQUATION, BUT POSITIVE USING VCAP
  #                               ifelse(Biovolume_g_in_sw > 0, (volume - Biovolume_g_in_sw), # if a value is present for biovolume, simply use it!
  #                                      NA))) %>%  # if the measured volume is below 0, poutput an NA, this should NEVER be the case (unless a typo!)
  
  
  
  # ESTIMATE MG HR RESP RATE in TWO ways

  # (1) using ONLY measured biovolume as 'Biovolume_g_in_sw' (resulting in many NAs!!!!)
  dplyr::mutate(resp_mg_hr   = ( (abs(resp_blankStand)) *  # currently as just mg O2 per minute - DOUBLE CHECK
                                      #(volume/1000) * # correct Liters - mg per L per min
                                      (measured_volume/1000) * # correct Liters - mg per L per min
                                       60) )  %>% # convert rate per minutes to rate per hour
  dplyr::mutate(resp_umol_hr = (resp_mg_hr*1000) / 32) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                                

  # (1) using ONLY calculated biovolumes to correct - should have no NAs
  dplyr::mutate(resp_mg_hr_biovolcalc   = ( (abs(resp_blankStand)) *  # currently as just mg O2 per minute - DOUBLE CHECK
                                      #(volume/1000) * # correct Liters - mg per L per min
                                      (calculated_volume/1000) * # correct Liters - mg per L per min
                                       60) )  %>% # convert rate per minutes to rate per hour
  dplyr::mutate(resp_umol_hr_biovolcalc = (resp_mg_hr_biovolcalc*1000) / 32) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                                

  # simplified start end rates used to compare O:N ratios 
  # dplyr::mutate(start.end_resp_mg_L_hr   = (start.end_resp_blankStand*(volume/1000)))  %>% # convert rate per minutes to rate per hour
  # dplyr::mutate(start.end_resp_umol_L_hr = (((start.end_resp_mg_L_hr) * (1000)) / 32) ) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                          
  
  
  dplyr::mutate(Age = # currently only set up for F1s
                  case_when(Date == '9/14/2021' ~ 50, 
                            Date == '9/30/2021' ~ 66, 
                            Date == '10/26/2021' ~ 92, 
                            Date == '2/2/2022' ~ 190, 
                            Date == '3/1/2022' ~ 217,
                            Date == '9/22/2022' & filetype == "LoLigo_data" ~ 423, # F2s also measured this day as SDR data 
                            Date == '10/26/2022' ~ 460)) %>% 
    
  dplyr::mutate(Fed_Unfed = 
                  case_when(Fed_Unfed == 'F' ~ "High food", 
                            is.na(Fed_Unfed) ~ "High food", 
                            Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = 
                  case_when(pH == 8.0 ~ "500 uatm", 
                            pH == 7.5 ~ "800 uatm",
                            pH == 7.0 ~ "1200 uatm"))

# diagnostics..
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_blankStand < 0) # call negatives
# print(Resp.outliers) # 21 samples have negative values when correcting for the blank, meaning the blank rate was GREATER than the sample resp value


```


### Relationship between Whole dry weight  v. Shell length 

```{r DW v shell length plot,  echo=TRUE, message = FALSE, warning = FALSE}

Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                                dplyr::mutate(Dry_Tissue_weight = as.numeric(Dry_Tissue_weight)) %>% 
                                ggplot(aes(x = Length_um, y = Dry_Tissue_weight)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("Scallop_TissueDW_mg") +
                                xlab("Length_um") +
                                geom_point() 


Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                                dplyr::mutate(Dry_Tissue_weight = as.numeric(Dry_Tissue_weight)) %>% 
                                dplyr::mutate(whole_Dry_weight = as.numeric(whole_Dry_weight)) %>% 
                                ggplot(aes(x = whole_Dry_weight, y = Dry_Tissue_weight)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("Scallop_TissueDW_mg") +
                                xlab("whole_Dry_weight") +
                                geom_point() 

Resp.Master_OM[!is.na(Resp.Master_OM$Dry_Tissue_weight),] %>% 
                                dplyr::mutate(Dry_Tissue_weight = as.numeric(Dry_Tissue_weight)) %>% 
                                ggplot(aes(x = Dry_Tissue_weight, y = resp_umol_hr)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("resp_umol_L_hr") +
                                xlab("Dry_Tissue_weight") +
                                geom_point() 

Resp.Master_OM %>% ggplot(aes(x = Length_um, y = resp_umol_hr)) +
                                geom_smooth(method = "loess") +
                                theme_classic() +
                                ylab("resp_umol_L_hr") +
                                xlab("Length_um") +
                                geom_point() 
```


### Standardize rates as...

##### (1) shell length: umol L-1 O2 mm shell length hour-1
##### (2) whole dry weight: umol L-1 O2 g whole dry weight hour-1 

```{r Calculate Resp Rates & WRTIE CSV, echo=TRUE, message = FALSE, warning = FALSE}

#write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_calc_raw.csv")


View(Resp.Master_OM)
```

