---
title: "Seawater Chemistry"
author: "Samuel Gurr"
date: "8/7/2024"
output: html_document
---

### SET UP
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
# SET WORKING DIRECTORY 
# knitr::opts_knit$set(root.dir = "C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB-Airradians_multigen_OA/larvae") # Katie's
#knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # Sam's
knitr::opts_knit$set(root.dir = "C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/RAnalysis/") # Sam's work


```





```{r load data}
# install.packages('gcookbook')
# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(reshape2)
library(knitr)
library(kableExtra)
library(car)
library(gcookbook)
library(ggpubr)
# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# F1 
F1_chem_larvae     <- read.csv(file="Data/SeawaterChemistry/F1/F1_water_chemistry_raw_larvae.csv", header=TRUE) # load the chem data
F1_chem_spat.adult <- read.csv(file="Data/SeawaterChemistry/F1/F1_water_chemistry_raw.csv", header=TRUE) # load the chem data


# F2
F2_chem_pre        <- read.csv(file="Data/SeawaterChemistry/F2/F2_water_chemistry_pre_overwinter_raw.csv", header=TRUE) # load the chem data
F2_chem_post       <- read.csv(file="Data/SeawaterChemistry/F2/F2_water_chemistry_post_overwinter_raw.csv", header=TRUE) # load the chem data
# note the pthe pre post is abitrary - GEneveive left off on the cumulative doc at mid January 
# what this readlly representes is wehent DIC broke down, the second as -post; is when the DIC broke down 
# therefore she reports the TA pH TA DC and the DIC pH at the headers of all columns 

```


# MASTER FILE MERGE (rbind) datasets within generation

```{r F1 edit master file}
ncol(F1_chem_larvae) == ncol(F1_chem_spat.adult) # TRUE - same spreadsheet
colnames(F1_chem_larvae) == colnames(F1_chem_spat.adult) # TRUE - also the same

F1_carbchem <- rbind(F1_chem_larvae, F1_chem_spat.adult) %>% 
                dplyr::select(Date, Treatment, Replicate, Type,
                              Temperature_bucket_C, Salinity, DO_mg_l, 
                              TCO2_mmol_kgSW, TA_mmol_kgSW,
                              pH_out, pCO2_out_matm, Wca_out, War_out_DIC_pH) %>% 
                dplyr::rename(WCa_out = Wca_out,
                              WAr_out = War_out_DIC_pH)

# NOTe: full carbonate chemistry was taken non-continuosly, call all rows that contain full carb

F1_carbchem                <- F1_carbchem[!(is.na(F1_carbchem$WAr_out)),] 
F1_carbchem.flagged.DIC.TA <- subset(F1_carbchem, (TCO2_mmol_kgSW > TA_mmol_kgSW)) # 13 rows flagged for DIC<TA
carbchem.flagged.odd       <- subset(F1_carbchem, WAr_out > 400) # 8 w/ high aragonite, next highest is 2.05

write.csv(carbchem.flagged.odd), "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1s/flagged_data.csv")

F1_carbchem.final <- subset(F1_carbchem, !(TCO2_mmol_kgSW > TA_mmol_kgSW)) %>% # DIC>TA omit
                        dplyr::filter(WAr_out < 3) %>% # omit these odd aragonite points
                        dplyr::mutate(pCO2_treatment = 
                                        case_when(Treatment == 8 ~ 'Low',
                                                  Treatment == 7.5 ~ 'Moderate',
                                                  Treatment == 7 ~ 'Severe'),
                                              Generation = 'F1') %>% 
                        dplyr::filter(!(pCO2_treatment %in% 'Severe'),!(Type %in% 'Larvae') ) %>% 
                        dplyr::select(-c(TCO2_mmol_kgSW,TA_mmol_kgSW, Type))

write.csv(F1_carbchem.final, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1s/master/CarbChem_master.csv")

```

## F2 master file 
* total 64 sampling dates over the course of the experiment from spat to adult stage - we dont need all of it though!
```{r F2 edit master file}
names(F2_chem_pre)
F2_chem_pre.OM <- F2_chem_pre %>% dplyr::mutate(Treatment = 
                                                  case_when(Replicate.color %in% 'green/purple' ~ 7.0,
                                          TRUE ~ Treatment)
                                               ) %>% 
                                  tidyr::drop_na(Wca_out) %>% 
                                  dplyr::select(Date, Treatment, Replicate,
                                      Temperature_bucket_C, Salinity, DO_mg_l,
                                      pH_out, pCO2_out_matm, Wca_out, War_out_DIC_pH) %>% 
                                  dplyr::rename(WCa_out = Wca_out,
                                                WAr_out = War_out_DIC_pH)
                              
F2_chem_pre.REP.SUMM <- F2_chem_pre.OM %>% dplyr::select(c(Date, Treatment)) %>% 
                       dplyr::group_by_all() %>% 
                       dplyr::summarise(n=n())

length(unique(F2_chem_pre.REP.SUMM$Date)) # 31 dates when measured over this period! 


F2_chem_post.OM <- F2_chem_post %>% 
                                   tidyr::drop_na(Temperature_spec_C)

F2_chem_post.REP.SUMM <- F2_chem_post.OM %>% dplyr::select(c(Date, Treatment)) %>% 
                       dplyr::group_by_all() %>% 
                       dplyr::summarise(n=n())

length(unique(F2_chem_post.REP.SUMM$Date)) # 33 dates when measured over this period! 


#  call the core datasets
F2_chem_post.core.columns   <- F2_chem_post[,c(1,3:4,6:8)]

F2_chem_post.DIC_pH.columns <- F2_chem_post[ ,grepl( ("DIC_pH"), names(F2_chem_post) ) ]
names(F2_chem_post.DIC_pH.columns) = gsub(pattern = "_DIC_pH.*", replacement = "", x = names(F2_chem_post.DIC_pH.columns))
F2_chem_post.DIC_pH         <- cbind(F2_chem_post.core.columns, F2_chem_post.DIC_pH.columns)


F2_chem_post.TA_pH.columns        <- F2_chem_post[ ,grepl( ("TA_pH"), names(F2_chem_post) ) ]
names(F2_chem_post.TA_pH.columns) = gsub(pattern = "_TA_pH.*", replacement = "", x = names(F2_chem_post.TA_pH.columns))
F2_chem_post.TA_pH                <- cbind(F2_chem_post.core.columns, F2_chem_post.TA_pH.columns)

# Use full_join to merge the DIC_pH with the TA_pH dataframe 
# this method below ensures ALL cased when we have DIC_pH are prioritizes
# cases when DIC was broken (NAs for DIC_pH carb chem) are filled with TA_pH calculated data
# this is wat we discussed with Shannon - use TA-PH when DIC was broken, otherwise DIC_pH whenever able 
F2_chem_post_final <- dplyr::full_join(F2_chem_post.DIC_pH, F2_chem_post.TA_pH, 
                                by = c("Date", "Treatment", "Replicate",
                                       "Temperature_bucket_C", "Salinity", "DO_mg_l"), suffix = c("", ".y")) %>%
                        mutate(across( names(F2_chem_post.TA_pH.columns), 
                                      ~ coalesce(., cur_data()[[ paste0(cur_column(), ".y") ]]))) %>%
                        select(-ends_with(".y")) %>% 
                        na.omit() %>% 
                        dplyr::select(Date, Treatment, Replicate,
                                      Temperature_bucket_C, Salinity, DO_mg_l,
                                      pH_out, pCO2_out_.matm., WCa_out, WAr_out) %>% 
                        dplyr::rename(pCO2_out_matm = pCO2_out_.matm.)

# sanity check, are the names the same?                        
names(F2_chem_post_final) == names(F2_chem_pre.OM)

# If true, we can rbind the datasets!

F2_carbchem.final <- rbind(F2_chem_pre.OM, F2_chem_post_final) %>% 
                                dplyr::mutate(pCO2_treatment = 
                                        case_when(Treatment == 8 ~ 'Low',
                                                  Treatment == 7.5 ~ 'Moderate',
                                                  Treatment == 7 ~ 'Severe'),
                                              Generation = 'F2')
```


### Flag odd values 

* Note: to do this stewise, move forward with this chunk using F1_carbchem.final and F1_carbchem.final
look at the plots generated fromthe Smooth Ribbon, these points are daily means within treatment (mean of all replicates measured)
In some cased there are glaring outliers, far from the 95% CI trend and bland with the other treatment

* Below I have completed these sanity check and repeately (and excrutiatingly) diagnosed those that present odd patterns, 
I have flagged these and output the data. 

* Generated are data omitted of these flagged values as "...OM" and these are now used to generate Smooth Ribbon files in 
downsream chunks. 

* that is all.



```{r long master files}
names(F1_carbchem.final) == names(F1_carbchem.final) # must be TRUE meaning the columnnames are exactly the same and we can merge successfully 

# Beofre we merge, execuate cuts that we mentioned above inthe bullets before the chunk, read them please! 
# If you proceed wtith 'F1_carbchem.final' and do not filterthere are several outliers, below I remedy them 

# F1 data shows ouliers that are simply omitted by the calcite sat state < 1.7 in the low treatment 
F1_carbchem.final.OM <- F1_carbchem.final %>% dplyr::filter(!(pCO2_treatment %in% 'Low' & 
                                                                WCa_out < 1.7))
 
# F2 data have outliers that are also easily filtered out by calcite saturation state < 2.0 in the low treatment 
F2_carbchem.final.OM <- F2_carbchem.final %>% dplyr::filter(!(pCO2_treatment %in% 'Low' & 
                                                                WCa_out < 2.0))

# run the same code with '!' to callthese datapoint ONLY and output them as 'flagged'
F1_carbchem.flagged <- F1_carbchem.final %>% dplyr::filter((pCO2_treatment %in% 'Low' & 
                                                                WCa_out < 1.7))

F2_carbchem.flagged <- F2_carbchem.final %>% dplyr::filter((pCO2_treatment %in% 'Low' & 
                                                                WCa_out < 2.0))

 # now proceed with 'F1_carbchem.final.OM'
# ALL
# change to long format to properly facet
carbchem.MASTER_long <- rbind(F1_carbchem.final.OM, F2_carbchem.final.OM) %>% 
                          dplyr::select(!c(Treatment)) %>% 
                          dplyr::filter(Replicate %in% c('A','B','C','D','E','F','G','H')) %>% 
                          melt(id.vars=c('Date', 'Replicate', 'Generation', 'pCO2_treatment')) %>% 
                          na.omit() %>% 
                          dplyr::mutate(Date = 
                                          as.POSIXct(Date, format = "%m/%d/%Y"),
                                        Month = months(Date),
                                        Year  = lubridate::year(Date)) 

carbchem.MASTER_long$value <- as.numeric(carbchem.MASTER_long$value) # make numeric

# MEANS PER SAMPLING DAY (reducing replicates within treatment to one mean) 
# aquire means by group for mean SE plotting by Date and treamtent
carbchem.MEANS.by.day <- carbchem.MASTER_long %>% # calc means and standard error
                           dplyr::group_by(Date, pCO2_treatment, Generation, variable) %>% 
                           dplyr::summarise(mean = mean(value),
                                            sd   = sd(value),
                                            se   = sd/(sqrt(n())), 
                                            n = n())

# MONTHLY MEANS (taking the daily means within above and reduce to monthly) 
carbchem.MEANS.monthy.by.rep <-  carbchem.MASTER_long %>% # calc means and standard error
                                   dplyr::group_by(Month, Year, Replicate, pCO2_treatment, variable) %>% 
                                   dplyr::summarise(
                                            mean.month.rep = mean(value),
                                            sd.month.rep   = sd(value),
                                            se.month.rep   = sd.month.rep/(sqrt(n())) ) %>% 
                                   dplyr::mutate(
                                     Month = as.integer(factor(Month, levels = month.name)),
                                     Month_Year = (paste0(Month,'/',Year)),
                                     Date = lubridate::my(Month_Year))
 
carbchem.MEANS.monthy       <- carbchem.MEANS.monthy.by.rep %>% 
                                   dplyr::group_by(Date, Month_Year, pCO2_treatment, variable) %>% 
                                   dplyr::summarise(
                                            mean.month.all = mean(mean.month.rep),
                                            sd.month.all   = sd(mean.month.rep),
                                            se.month.all   = sd.month.all/(sqrt(n())) )


```



```{r plot}


# plot em!
colnames(carbchem.MASTER) # target select

pd <- position_dodge(0.1) # adjust the jitter for the different treatments   


Larvae <- carbchem.MASTER_MEANS %>% 
  dplyr::filter(Type %in% 'Larvae') %>% 
  dplyr::filter(variable %in% (c('Temperature_bucket_C',
                                 'Salinity',
                                 'DO_mg_l',
                                 'pH',
                                 'pH_out',
                                 'TCO2_mmol_kgSW',
                                 'TA_mmol_kgSW',
                                 'War_out_DIC_pH',
                                 'Wca_out'))) %>% 
  ggplot(aes(x=Date, y=mean, shape=Type, colour=factor(pCO2_treatment))) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  scale_colour_manual(values = c("Low" = "forestgreen",
                                 "Moderate"="orange")) +
                                 # "Severe" = "purple")) +
  theme_classic() +
  geom_point(position=pd, size=2) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 5)) +
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 300000)) +
  facet_wrap(~variable, scales = "free")



pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1s/plots/F1_larvae.pdf", width=12, height=8)
print(Larvae)
graphics.off()



Juvenile <- carbchem.MASTER_MEANS %>% 
  dplyr::filter(Type %in% 'Juveniles') %>% 
  dplyr::filter(variable %in% (c('Temperature_bucket_C',
                                 'Salinity',
                                 'DO_mg_l',
                                 'pH',
                                 'pH_out',
                                 'TCO2_mmol_kgSW',
                                 'TA_mmol_kgSW',
                                 'War_out_DIC_pH',
                                 'Wca_out'))) %>% 
  ggplot(aes(x=Date, y=mean, shape=Type, colour=factor(pCO2_treatment))) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  scale_colour_manual(values = c("Low" = "forestgreen",
                                 "Moderate"="orange")) +
                                 # "Severe" = "purple")) +
  theme_classic() +
  geom_point(position=pd, size=2) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 5)) +
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 300000)) +
  facet_wrap(~variable, scales = "free")
print(Juvenile)

pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1s/plots/F1_juveniles.pdf", width=12, height=8)
print(Juvenile)
graphics.off()


Adult <- carbchem.MASTER_MEANS %>% 
  dplyr::filter(Type %in% 'Adults') %>% 
  dplyr::filter(pCO2_treatment %in% c("Low", "Moderate")) %>% 
  dplyr::filter(variable %in% (c('Temperature_bucket_C',
                                 'Salinity',
                                 'DO_mg_l',
                                 'pH',
                                 'pH_out',
                                 'TCO2_mmol_kgSW',
                                 'TA_mmol_kgSW',
                                 'War_out_DIC_pH',
                                 'Wca_out'))) %>% 
  ggplot(aes(x=Date, y=mean, shape=Type, colour=factor(pCO2_treatment))) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  scale_colour_manual(values = c("Low" = "forestgreen",
                                 "Moderate"="orange")) +
  theme_classic() +
  geom_point(position=pd, size=2) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 5)) +
  scale_x_date(date_labels="%b-%d",date_breaks  ="3 month")+
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 300000)) +
  facet_wrap(~variable, scales = "free")
print(Adult)

pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1s/plots/F1_adults.pdf", width=12, height=8)
print(Adult)
graphics.off()




Ph_out_all <- as.data.frame(
  carbchem.MEANS.monthy %>% 
                na.omit() %>% 
                # dplyr::filter(!Type %in% 'Larvae') %>carbchem.MASTER_MEANS.MONTLY% 
                dplyr::filter(pCO2_treatment %in% c("Low", "Moderate")) %>% 
                dplyr::filter(variable %in% c(
                                               'Temperature_bucket_C',
                                               'Salinity',
                                               # 'DO_mg_l',
                                               # 'pH',
                                               'pH_out',
                                               # 'TCO2_mmol_kgSW',
                                               # 'TA_mmol_kgSW',
                                               'War_out_DIC_pH',
                                               'Wca_out'
                                               ))
                                          )

ggplot(data= Ph_out_all, 
         aes(x=Date, 
             y=mean.month.all)) +
             # shape=Type, 
            # colour=factor(pCO2_treatment)))  +
  # stat_summary(geom = "line", fun.y = mean) +
  # stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.3)
  geom_ribbon(aes(ymin = (mean.month.all - sd.month.all ), 
                  ymax = (mean.month.all + sd.month.all ),
                  fill=factor(pCO2_treatment)), alpha = 0.2) +
  geom_line(aes(y = mean.month.all - sd.month.all,
                colour=factor(pCO2_treatment)), 
            linetype = "solid") +
  geom_line(aes(y = mean.month.all + sd.month.all,
                colour=factor(pCO2_treatment)), 
            linetype = "solid") +
  #geom_line()  +
  scale_fill_manual(values=c("forestgreen", "orange"), name="fill") +
  scale_colour_manual(values = c("Low" = "forestgreen",
                                 "Moderate"="orange")) +
  theme_classic() +
  # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), colour="black", width=.1, position=pd) +
  # geom_line(position=pd) +
  # scale_colour_manual(values = c("Low" = "forestgreen",
  #                                "Moderate"="orange")) +
  # theme_classic() +
  # geom_point(position=pd, size=2) +
  # theme(axis.text.x = element_text(angle = 45, hjust=1, size = 5)) +
  # scale_x_date(date_labels="%b-%d",date_breaks  ="3 month")+
  # #scale_y_continuous(expand = c(0, 0), limits = c(0, 300000)) +
  facet_wrap(~variable, scales = "free")



```


```{r SmoothRibbon function with gam}
# how do we get smooth geom ribbon figures
# in summary run gam and use a fine scale for x axis 
# https://stackoverflow.com/questions/61029929/smoothing-geom-ribbon
# A principled way to achieve what you want is to fit a GAM model to your data using the gam() function in mgcv and then apply the predict() function to that model over a finer grid of values for your predictor variable. The grid can cover the span defined by the range of observed values for your predictor variable.
# load R packages
library(ggplot2)
library(mgcv)


SmoothRibbon <- function(datafilename, col_name) {

data <- as.data.frame(
  # carbchem.MEANS.by.day %>% 
                datafilename %>% 
                na.omit() %>% 
                # dplyr::filter(!Type %in% 'Larvae') %>carbchem.MASTER_MEANS.MONTLY% 
                dplyr::filter(pCO2_treatment %in% c("Low", "Moderate")) %>% 
                dplyr::filter(variable %in% (
                                               # 'Temperature_bucket_C',
                                               # 'Salinity',
                                               # 'DO_mg_l',
                                               # 'pH',
                                               # 'pH_out'
                                               col_name
                                               # 'TCO2_mmol_kgSW'
                                               # 'TA_mmol_kgSW',
                                               # 'pCO2_out_matm'
                                               #'War_out_DIC_pH'
                                               # 'Wca_out'
                                               ))
                                          ) %>% 
                 mutate(Date_asnum = dense_rank(Date))


# calc the num days because the Date_asnumin ascending order dot not 
# represent the elapsed time properly as an x axis
data$NumDays  <- as.numeric(
                            difftime(as.Date(data$Date),
                            as.Date(data$Date[1]),
                            units="days")
                            )

data.low      <- data %>% dplyr::filter(pCO2_treatment %in% 'Low')
data.moderate <- data %>% dplyr::filter(pCO2_treatment %in% 'Moderate')
data.all.ordered  <- rbind(data.low, data.moderate)


# fit GAM model
m.low      <- gam(mean ~ s(NumDays), data = data.low) 
m.moderate <- gam(mean ~ s(NumDays), data = data.moderate) 

# define finer grid of predictor values
xnew.low      <- seq(min(data.low$NumDays), 
                     max(data.low$NumDays), by = 0.1) 
xnew.moderate <- seq(min(data.moderate$NumDays), 
                     max(data.moderate$NumDays), by = 0.1) 

# apply predict() function to the fitted GAM model
# using the finer grid of x values
p.low      <- predict(m.low, newdata = data.frame(NumDays = xnew.low), se = TRUE) 
p.moderate <- predict(m.moderate, newdata = data.frame(NumDays = xnew.moderate), se = TRUE) 

# plot the estimated mean values of y (fit) at given x values
# over the finer grid of x values;
# superimpose approximate 95% confidence band for the true 
# mean values of y at given x values in the finer grid
g.low <- data.frame(NumDays = xnew.low, 
            fit = p.low$fit,
            lwr = p.low$fit - 1.96*p.low$se.fit, # 1.96 * SE = 95% CI
            upr = p.low$fit + 1.96*p.low$se.fit  # 1.96 * SE = 95% CI
            ) %>% 
         dplyr::mutate(pCO2_treatment = "Low")

g.moderate <- data.frame(NumDays = xnew.moderate, 
            fit = p.moderate$fit,
            lwr = p.moderate$fit - 1.96*p.moderate$se.fit, 
            upr = p.moderate$fit + 1.96*p.moderate$se.fit) %>% 
         dplyr::mutate(pCO2_treatment = "Moderate")

# r bind the data sets
# use the first date of data and add the elapsed numberic time, not that 1 = seconds, we 
# convert to days by mutliplying by 86400 (seconds in a day)
g.master <- rbind(g.low, g.moderate) %>% 
                  dplyr::mutate(Date = data$Date[1] + NumDays*86400)

theme_set(theme_classic())

p <- ggplot(data = g.master, aes(Date, fit)) + 
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill=factor(pCO2_treatment)), alpha = 0.2) + 
  geom_line(aes(y = lwr,
                colour=factor(pCO2_treatment)),
            linetype = "solid") +
  geom_line(aes(y = upr,
                colour=factor(pCO2_treatment)),
            linetype = "solid") +
  geom_point(data = data.all.ordered, 
             aes(Date, mean,
                 colour=factor(pCO2_treatment)), 
             shape = 3, size =1) +
  ylab(col_name) +
  theme(legend.position="none") +
  scale_fill_manual(values=c("forestgreen", "orange"), name="fill") +
  scale_colour_manual(values=c("forestgreen", "orange"), name="fill") 

print(p)
}

```

* USe SMooth Ribbon to make some narly plots!
```{r Nice plots!}
library(ggpubr)
carbchem.MEANS.by.day.F1 <- carbchem.MEANS.by.day %>% filter(Generation %in% 'F1') 
carbchem.MEANS.by.day.F2 <- carbchem.MEANS.by.day %>% filter(Generation %in% 'F2')

# pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1/plots/F1_Chem_95CI.pdf", width=8, height=11)
pdf("C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F1/plots/F1_Chem_95CI.pdf", width=8, height=11)
    ggarrange(
          SmoothRibbon(carbchem.MEANS.by.day.F1, "Temperature_bucket_C"),
          SmoothRibbon(carbchem.MEANS.by.day.F1, "Salinity"),
          SmoothRibbon(carbchem.MEANS.by.day.F1, "pCO2_out_matm"),
          SmoothRibbon(carbchem.MEANS.by.day.F1, "pH_out"),
          SmoothRibbon(carbchem.MEANS.by.day.F1, "WAr_out"),
          SmoothRibbon(carbchem.MEANS.by.day.F1, "WCa_out"),
          nrow = 3,
          ncol = 2
    )
graphics.off()




# pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F2/plots/F2_Chem_95CI.pdf", width=8, height=11)
pdf("C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/RAnalysis/Output/SeawaterChemistry/F2/plots/F2_Chem_95CI.pdf", width=8, height=11)
    ggarrange(
          SmoothRibbon(carbchem.MEANS.by.day.F2, "Temperature_bucket_C"),
          SmoothRibbon(carbchem.MEANS.by.day.F2, "Salinity"),
          SmoothRibbon(carbchem.MEANS.by.day.F2, "pCO2_out_matm"),
          SmoothRibbon(carbchem.MEANS.by.day.F2, "pH_out"),
          SmoothRibbon(carbchem.MEANS.by.day.F2, "WAr_out"),
          SmoothRibbon(carbchem.MEANS.by.day.F2, "WCa_out"),
          nrow = 3,
          ncol = 2
    )
graphics.off()

```



# TABLE (all data)

```{r use dplyr to build chemistry table, include=FALSE}
carbchem.MASTER_MEANS <- carbchem.MASTER_long %>% # calc means and standard error
   na.omit() %>% 
   dplyr::group_by(Date, Type, pCO2_treatment, variable) %>% 
   dplyr::summarise(mean = mean(value),
                    sd   = sd(value),
                    se   = sd/(sqrt(n())) )

chem_meanDate <- carbchem.MASTER_MEANS %>% 
     na.omit() %>% 
   dplyr::group_by(pCO2_treatment, variable) %>% 
   dplyr::summarise(mean2 = mean(mean),
                    sd   = sd(mean),
                    se   = sd/(sqrt(n())) ,
                    n = n())

carbchem.MASTER_wideMEANS <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="mean2")
carbchem.MASTER_wideStErr <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="se")
carbchem.MASTER_wideN     <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="n")

# final table

colnames(carbchem.MASTER_wideMEANS)
FINAL_TABLE                <- data.frame(matrix(nrow = nrow(carbchem.MASTER_wideMEANS), ncol = 1))

FINAL_TABLE$pCO2_Treatment <- carbchem.MASTER_wideMEANS$pCO2_treatment

FINAL_TABLE$Salinity       <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$Salinity, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$Salinity, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$Salinity,
                                     ")",
                                     sep = "")

FINAL_TABLE$pCO2           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH,
                                     ")",
                                     sep = "")

FINAL_TABLE$Temperature    <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$Temperature_bucket_C, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$Temperature_bucket_C, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$Temperature_bucket_C,
                                     ")",
                                     sep = "")

FINAL_TABLE$pH             <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$pH_out, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$pH_out, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$pH_out,
                                     ")",
                                     sep = "")

FINAL_TABLE$HCO3           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$HCO3_out_mmol_kgSW, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$HCO3_out_mmol_kgSW, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$HCO3_out_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$CO3           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$CO3_out_mmol_kgSW, digits=3)),
                                             "±",
                                     (signif(carbchem.MASTER_wideStErr$CO3_out_mmol_kgSW, digits=3)), sep="  ")),
                                     " (",
                                     carbchem.MASTER_wideN$CO3_out_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$TA             <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$TA_mmol_kgSW, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$TA_mmol_kgSW, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$TA_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$Aragonite.Sat  <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$War_out_DIC_pH, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$War_out_DIC_pH, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$War_out_DIC_pH,
                                     ")",
                                     sep = "")

FINAL_TABLE                <- FINAL_TABLE[,-1] # view table
```


## knitR to print the table 
```{r lable output, echo=TRUE}
FINAL_TABLE %>%
  kbl(caption = "Table 1. Seawater chemistry") %>%
  kable_classic(full_width = T, html_font = "Cambria")
```


#### save data
```{r save tables, echo=TRUE}
# save output table
# write.table(chem_meanDate,"C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Water_Chem/Chem.Table_sep.csv",sep=",", row.names=FALSE)  # write table to 
# write.table(FINAL_TABLE,"C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Water_Chem/Chem.Table.csv",sep=",", row.names=FALSE)  # write table to 

```










# TABLE (all data)

```{r use dplyr to build chemistry table, include=FALSE}

# change to long format to properly facet
carbchem.MASTER_long <- carbchem.MASTER %>% 
  dplyr::select(!c(Treatment,Replicate)) %>% 
  melt(id.vars=c('Date', 'Type', 'pCO2_treatment'))

carbchem.MASTER_long$value <- as.numeric(carbchem.MASTER_long$value) # make numeric

carbchem.MASTER_MEANS <- carbchem.MASTER_long %>% # calc means and standard error
   na.omit() %>% 
   dplyr::group_by(Date, Type, pCO2_treatment, variable) %>% 
   dplyr::summarise(mean = mean(value),
                    sd   = sd(value),
                    se   = sd/(sqrt(n())) )

chem_meanDate <- carbchem.MASTER_MEANS %>% 
     na.omit() %>% 
   dplyr::group_by(pCO2_treatment, variable) %>% 
   dplyr::summarise(mean2 = mean(mean),
                    sd   = sd(mean),
                    se   = sd/(sqrt(n())) ,
                    n = n())

carbchem.MASTER_wideMEANS <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="mean2")
carbchem.MASTER_wideStErr <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="se")
carbchem.MASTER_wideN     <- dcast(chem_meanDate, pCO2_treatment ~ variable, value.var="n")

# final table

colnames(carbchem.MASTER_wideMEANS)
FINAL_TABLE                <- data.frame(matrix(nrow = nrow(carbchem.MASTER_wideMEANS), ncol = 1))

FINAL_TABLE$pCO2_Treatment <- carbchem.MASTER_wideMEANS$pCO2_treatment

FINAL_TABLE$Salinity       <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$Salinity, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$Salinity, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$Salinity,
                                     ")",
                                     sep = "")

FINAL_TABLE$pCO2           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$xCO2_out._dry_at._1_atm_.ppm_.DIC_pH,
                                     ")",
                                     sep = "")

FINAL_TABLE$Temperature    <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$Temperature_bucket_C, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$Temperature_bucket_C, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$Temperature_bucket_C,
                                     ")",
                                     sep = "")

FINAL_TABLE$pH             <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$pH_out, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$pH_out, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$pH_out,
                                     ")",
                                     sep = "")

FINAL_TABLE$HCO3           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$HCO3_out_mmol_kgSW, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$HCO3_out_mmol_kgSW, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$HCO3_out_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$CO3           <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$CO3_out_mmol_kgSW, digits=3)),
                                             "±",
                                     (signif(carbchem.MASTER_wideStErr$CO3_out_mmol_kgSW, digits=3)), sep="  ")),
                                     " (",
                                     carbchem.MASTER_wideN$CO3_out_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$TA             <- paste( (paste( (signif(carbchem.MASTER_wideMEANS$TA_mmol_kgSW, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$TA_mmol_kgSW, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$TA_mmol_kgSW,
                                     ")",
                                     sep = "")

FINAL_TABLE$Aragonite.Sat  <-  paste( (paste( (signif(carbchem.MASTER_wideMEANS$War_out_DIC_pH, digits=3)),
                                     (signif(carbchem.MASTER_wideStErr$War_out_DIC_pH, digits=3)), sep=" ± ")),
                                     " (",
                                     carbchem.MASTER_wideN$War_out_DIC_pH,
                                     ")",
                                     sep = "")

FINAL_TABLE                <- FINAL_TABLE[,-1] # view table
```


## knitR to print the table 
```{r lable output, echo=TRUE}
FINAL_TABLE %>%
  kbl(caption = "Table 1. Seawater chemistry") %>%
  kable_classic(full_width = T, html_font = "Cambria")
```


#### save data (food x OA manuscript)
```{r save tables, echo=TRUE}
# save output table
# write.table(chem_meanDate,"C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Water_Chem/Chem.Table_sep.csv",sep=",", row.names=FALSE)  # write table to 
# write.table(FINAL_TABLE,"C:/Users/samjg/Documents/Github_repositories/Cvirginica_multistressor/RAnalysis/Output/Water_Chem/Chem.Table.csv",sep=",", row.names=FALSE)  # write table to 

```
