---
title: "F1_Scope_for_growth"
author: "Samuel Gurr"
date: "2023-03-18"
output: html_document
---

# F1s: scope for growth

-   **objective**: to merge all data for F1s in which standard metabolic rates (resp), excretion rates, and biodeposition were completed **on the same individual(s)!**

    -   Create 'F1_Master' file: merge together respiration, excretion and biodepsotion data by a unique identifier for the individual

        -   i.e. date \* pH_treatment \* replicate tank \* dry tissue weight (mg)

        -   Note! master file data are limited by the biodeposition runs - there's pleeenty of data for respiration and excretion in which biodeposition *was not* completed

        -   these 'master' data use allometric scaling (b factor and mean correction) via **tissue dry weight** since *all* individuals used for biodeposition were large enough to separate tissue from shell for drying

            -   important to state because the cumulative respiration and excretion data (both including individuals with and without biodeposition runs) is corrected via **shell length** applicable to all life stages, like those too small/fragile to obtatin accurate estimation of dry tissue

    -   Calculate scope for growth

    -   Plot data

    -   Run statistics

    -   (*Optional*) Adjust plots to emphasize significant effect(s)

### load packages and set directory for this markdown file

```{r setup}

library(devtools) # devtools::install_github # use devtools to instlal github link
library(LoLinR) # install_github('colin-olito/LoLinR') # install LoLinR from github
library(dplyr)
library(lubridate)
library(rMR) 
library(dplyr)
library(stringr)
library(rlang)
library(ggplot2)
library(ggfortify)
library(DESeq2)
library(devtools)
library(ggbiplot)
library(VennDiagram)# venn diagrams
library(eulerr) #venn diagrams -  check out the R shiny app (http://eulerr.co/) 

# set wd
knitr::opts_knit$set(root.dir = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis')
# getwd()

```

# (1) Create 'F1 Master' file

## Load biodeposition, respiration, and excretion data

```{r}

Biodeposition    <- read.csv("Output/Biodeposition/Biodeposition_master_F1.csv", header = T)

RespirationRates <- read.csv(file="Output/Respiration/F1_RR_calc_master.csv", header=T)

ExcretionRates   <- read.csv(file="Output/ExcretionRates/F1/F1_ExcretionRates_master.csv", header=T) 
```

## Add minor adjustments to these files to assist merging

-   importantly, we adjust the excretion data for b factor normalization below, other datasets are already prepped with this correction
-   Note: : biodep does not have the columns to merge by including the Run, Vhamber_Tank, Replicate, etc. However... we can merge by the equal length and tissue dry weight in the RR dataset below! first we need to reformat a few things here
-   b factor TDW from use of all data in both F1 and F1
-   TDW correction to 1 g TDW (as opposed to a mean or median within the dataset)
    -   biodeposition.R and RR_calc scripts contain this correction, excretion corrects in the chunk below

```{r}
unique(Biodeposition$Date)
# biodep
Biodeposition_adj    <- Biodeposition %>% 
                          dplyr::select(-c(X, tank_ID.y)) %>% 
                          dplyr::rename(tank_ID = tank_ID.x) %>% 
                          dplyr::mutate(Date = format(strptime(Date, format = "%Y%m%d"), "%m/%d/%Y")) %>% # format to mm/dd/yyy as RR dataset
                          dplyr::mutate(Replicate = gsub("[^a-zA-Z]", "", tank_ID)) %>% # new replicate column - reflects RR dataset 
                          dplyr::rename(Dry_Tissue_weight = animal_dry_weight_g) %>% # change name to match RR
                          dplyr::rename(Length_mm = animal_length_mm) %>% # change name to match RR
                          dplyr::rename(pH = treatment) %>% # rename to match 
                          dplyr::select(-c(tank_ID, animal_number, initial_filter_weight_mg, dry_filter_weight_mg,ash_filter_weight_mg, inclubation_time_hours)) %>% 
                          dplyr::mutate(Date = case_when(Date == "03/02/2022" ~ '3/2/2022',
                                                         Date == "09/23/2022" ~ '9/23/2022',
                                                         Date == "10/27/2022" ~ '10/27/2022')) %>% 
                          dplyr::select(-Length_mm) # lenngth is the exact same as the resp and Excretion data except diff sig figs and some missing
nrow(Biodeposition_adj) # nrow 43

# RR
unique(RespirationRates$Date)
RespirationRates_adj <- RespirationRates %>% 
                          dplyr::filter(Date %in% c('3/1/2022','9/22/2022', '10/26/2022')) %>% # , '3/27/2023'
                          dplyr::mutate(Date = case_when(Date == "3/1/2022" ~ '3/2/2022',
                                                         Date == "9/22/2022" ~ '9/23/2022',
                                                         Date == "10/26/2022" ~ '10/27/2022')) %>%                           
                          dplyr::mutate(Replicate = gsub("[^a-zA-Z]", "", Chamber_tank)) %>% # new replicate column - reflects RR dataset 
                          dplyr::select(c(Date, 
                                          Age,  
                                          pH, 
                                          pCO2,
                                          Replicate,
                                          Length_mm, 
                                          Dry_Tissue_weight,
                                          resp_umol_hr_bFactorNormTDW.1g)) %>% 
                          dplyr::rename(RR_resp_umol_hr_bfactorTDW = 
                                          resp_umol_hr_bFactorNormTDW.1g) 
RespirationRates_adj$Dry_Tissue_weight <- as.numeric(RespirationRates_adj$Dry_Tissue_weight)                     
nrow(RespirationRates_adj) # 45

# ER
# note - we will bfctor and mean corret for TDW)
bTDW    <- 1.07 # FR_bfactor script using ALL F1 and F1 data!
unique(ExcretionRates$Date)
ExcretionRates_adj  <- ExcretionRates  %>% 
                          dplyr::filter(Date %in% c(20220301, 20220922, 20221026)) %>% 
                          dplyr::mutate(Date = format(strptime(Date, format = "%Y%m%d"), "%m/%d/%Y")) %>% # format to mm/dd/yyy as RR dataset
                          dplyr::mutate(Date = case_when(Date == '03/01/2022' ~ '3/2/2022',
                                                         Date == '09/22/2022' ~ '9/23/2022',
                                                         Date == '10/26/2022' ~ '10/27/2022')) %>% 
                          dplyr::mutate(ExcretionRate_mg_hr = ExcretionRate_ug_mL_hr/1000) %>% 
                          dplyr::rename(ExcretionRate_umol_hr = ExcretionRate_umol_mL_hr) %>% 
  
                          dplyr::mutate(ExcretionRate_mg_hr_bFactorNormTDW = 
                                          (ExcretionRate_mg_hr)*((1/Dry_Tissue_weight)^bTDW)) %>% # TDW b factor - mg
                          
                          dplyr::mutate(ExcretionRate_umol_hr_bFactorNormTDW = 
                                          (ExcretionRate_umol_hr)*((1/Dry_Tissue_weight)^bTDW)) %>% # TDW b factor - umol
                          dplyr::mutate(Length_mm = as.numeric(Length_um / 1000)) %>% # Length_mm matched biodep and RR 
                          dplyr::select(c(Date, 
                                          pH, 
                                          Replicate, 
                                          Chamber_tank,
                                          Length_um,
                                          Dry_Tissue_weight,
                                          ExcretionRate_mg_hr_bFactorNormTDW,
                                          ExcretionRate_umol_hr_bFactorNormTDW))
# sanity check before we merge
nrow(ExcretionRates_adj)          == (nrow(RespirationRates_adj)  + nrow(Biodeposition_adj)) / 2 # FLASE becuase there were 2 outliers removed for biodep
unique(ExcretionRates_adj$Date)   == unique(RespirationRates_adj$Date) # should be TRUE
unique(RespirationRates_adj$Date) ==  unique(Biodeposition_adj$Date)  # should be TRUE
```

### Unique identifier

-   Date \* pH \* dry tissue weight

```{r}

Biodeposition_adj$uniqueID <- paste(Biodeposition_adj$Date,
                                 Biodeposition_adj$pH,
                                 Biodeposition_adj$Dry_Tissue_weight, 
                                 sep = '_')

RespirationRates_adj$uniqueID <- paste(RespirationRates_adj$Date,
                             RespirationRates_adj$pH,
                             RespirationRates_adj$Dry_Tissue_weight, 
                             sep = '_')

ExcretionRates_adj$uniqueID <- paste(ExcretionRates_adj$Date,
                             ExcretionRates_adj$pH,
                             ExcretionRates_adj$Dry_Tissue_weight, 
                             sep = '_')
```

### Test the unique identifier before merging

```{r}
# subset the ER data removing all instances that contain the same unique identifier 
# returns nothing == we are good to merge!

# btwn RR and ER
nrow(subset(ExcretionRates_adj, 
       !(uniqueID %in% RespirationRates_adj$uniqueID))) # no discrepancies btwn files (yay!)

# now btwn RR and biodep
nrow(subset(RespirationRates_adj, 
            !(uniqueID %in% Biodeposition_adj$uniqueID))) # 2 discrepancies, these are the removed outliers from biodep
```

### Let's merge this thang!

```{r}

# merge RR and ER - check the number of rows == 42
RR_ER_merge <- merge(RespirationRates_adj,ExcretionRates_adj) %>% dplyr::select(!pCO2)
# ommitted pCO2 because biodep has the correct micro symbol and is merged below 
nrow(RR_ER_merge) # 53 

# merge this data with the biodep - adjust the columns to be our master file!
F1_Masterfile <- merge(RR_ER_merge, Biodeposition_adj, 
                    by = c('Date','uniqueID','Dry_Tissue_weight', 'Replicate', 'pH')) %>% 
                  dplyr::select(c(Date, 
                                  Age,
                                  pCO2,
                                  pH,
                                  Replicate,
                                  Chamber_tank,
                                  Length_mm,
                                  Dry_Tissue_weight,
                                  RR_resp_umol_hr_bfactorTDW,
                                  ExcretionRate_umol_hr_bFactorNormTDW,
                                  IER_correct,
                                  IRR_correct,
                                  OER_correct,
                                  ORR_correct,
                                  CR_correct,
                                  FR_correct,
                                  RR_correct,
                                  p,
                                  f,
                                  i,
                                  SE,
                                  AR,
                                  AE))
nrow(F1_Masterfile) # 48 rows
# View(F1_Masterfile)


```

### Write the file to output folder

```{r}

write.csv(F1_Masterfile, "Output/F1_RR_ER_Biodep_master.csv")
```

# Scope for growth calc

* Pousee et al. 
The bioenergetics status of a bivalve can be assessed by calculating the “scope for growth” (SFG, [15,16]). 
This estimator is based upon mathematical expressions that incorporate feeding functions such as clearance rate 
(CR, the volume of water totally filtered per time unit) and assimilation efficiency (AE, the fraction of organic matter consumed that is assimilated), 
and food availability to calculate the energy intake. Energy expenditures are estimated through respiration (RR) and excretion rates (ER) that are used 
to determine the catabolized energy. The subtraction of this catabolized energy from the energy intake is the SFG. 

(RR + ER) = energy expenditures
(RR + ER) = energy expenditures




RR was converted to oxygen-catabolized energy (R) using 14.0 J mg-1 O2, 
ER converted to U using 24.83 J mg-1 NH4-N [45]. 
The absorbed energy (A, J h-1) calculated as A = CR*AE*Δfood, with CR (L h-1) and AE (no unit) obtained from the biodeposition method and 
Δfood the energetic content of the food (J mg-1) obtained from Δfood = (0.632+0.086 (%C))×4.184, where %C was the organic matter of the seston
caloric value of dried phytoplankton = (0.632+0.086 *(%C)) where %C is the % of organic carbon 



## SFG or P = A - (R + U)

-   Widdows and Johnson 1988 " Physiological energetics of *Mytilus edulis*: Scope for Growth
-   **P** = production - estimated from the difference between the energy absorbed from the food and energy expenditure via respiration and excretion - referred to as Scope for Growth (SGF)
-   **A** = C x absorption efficiency
    -   C = Clearnace rate (l g-1 h-1) x POM (mg L-1) x 23 J mg-1 ash free dry weight
-   **R** = VO2 (ml O2 g-1 hr-1) x 20.33 J ml-1 O2
-   **U** = mg NH4 g-1 hr-1 x 19.4 J mg-1 NH4




```{r}
unique(Biodep_blanks$Date)
Biodep_blanks <- read.csv("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Biodeposition/Biodeposition_input_blank.csv", h=T, sep =",") %>% 
                            dplyr::filter(Type%in% 'blank') %>%  # blanks from the biodep rig, not the inpu, we stopped using input value to correct
                            dplyr::filter(Date %in% c(20220302, 20220923, 20221027)) %>% 
                            dplyr::mutate(Date = case_when(Date == 20220302 ~ '3/2/2022',
                                                           Date == 20220923 ~ '9/23/2022',
                                                           Date == 20221027 ~ '10/27/2022')) %>% 
                            dplyr::select(c(Date,treatment,Perc_ORG_1)) %>% 
                            dplyr::rename(pH = treatment)
unique(Biodep_blanks$Date)# "3/2/2022"   "9/23/2022"  "10/27/2022"


nrow(F1_Masterfile) == nrow(merge(Biodep_blanks,F1_Masterfile, by = c("Date", "pH"))) # TRUE = YAY!

F1_Masterfile_2.0 <- merge(Biodep_blanks,F1_Masterfile, by = c("Date", "pH")) %>% 
  dplyr::mutate(
                # RR
                RR_resp_mgO2_hr_bfactorTDW = ((RR_resp_umol_hr_bfactorTDW/1000)*32),# convert umol to mg O2
                RR_Joules_hr               = RR_resp_mgO2_hr_bfactorTDW*14, # convert to joules
                # ER
                ExcretionRate_mgNH4_bFactorNormTDW = ((ExcretionRate_umol_hr_bFactorNormTDW/1000)*18.04), # convert umol to mg NH4
                ER_Joules_hr                       = ExcretionRate_mgNH4_bFactorNormTDW*24.83, # convert o Joules
                # caloric value of dried phytoplankton
                Food_Joules_mg = (0.632+0.086 *(Perc_ORG_1))*4.184, # caloric value of dried phytoplaknton following Pousee et al. -referenced paper below for calculation
                #Platt T, Irwin B. Caloric content of phytoplankton. Limnology and Oceanography. 1973;18(2):306–10
                # A
                A_Joules_hr = (CR_correct*AE)*Food_Joules_mg,
                # FINALLY SCOPE FOR GROWTH YALL
                SFG = A_Joules_hr - (RR_Joules_hr + ER_Joules_hr)
  )
                


# following the Widdows and Johnson 1988 aper described above..
# Note- RR is in L O2 so we will multiply 20.33*1000 to account for 20.33 Joules per ml-1 O2 
F1_Masterfile$RR_Energy_Widdows.1988     <- (20.33*F1_Masterfile$RR_resp_umol_hr_bfactorTDW)
F1_Masterfile$RR_Excretion_Widdows.1988  <- (19.4*F1_Masterfile$ExcretionRate_umol_hr_bFactorNormTDW)

F1_Masterfile$SfG_Widdows.1988           <- (  
                        (F1_Masterfile$AR * (F1_Masterfile$CR_correct*23)) - 
                        (F1_Masterfile$RR_Energy_Widdows.1988 + F1_Masterfile$RR_Excretion_Widdows.1988)
                        )

```

```{r, analysis and plots}

# stats
library(car)
unique(F1_Masterfile_2.0$Date)

F1_Masterfile_3_2_2022 <- F1_Masterfile_2.0 %>% dplyr::filter(Date %in% '3/2/2022')
SGFmod_322 <- aov(lm(SFG ~ pCO2 , data =F1_Masterfile_3_2_2022 ))
shapiro.test(resid(SGFmod_322)) # 0.2245
leveneTest(SGFmod_322)# 0.7378
summary(SGFmod_322)
#             Df Sum Sq Mean Sq F value Pr(>F)
# pCO2         1    266   265.7   1.236  0.279
# Residuals   21   4514   215.0 


F1_Masterfile_9_23_22<- F1_Masterfile_2.0 %>% dplyr::filter(Date %in% '9/23/2022')
SGFmod_923 <- aov(lm(SFG ~ pCO2 , data =F1_Masterfile_9_23_22 ))
shapiro.test(resid(SGFmod_923)) # 0.8132
leveneTest(SGFmod_923)# 0.8839
summary(SGFmod_923)
#             Df Sum Sq Mean Sq F value Pr(>F)
# pCO2         1    491   490.7   0.656  0.435
# Residuals   11   8225   747.7



F1_Masterfile_10_27_22 <- F1_Masterfile_2.0 %>% dplyr::filter(Date %in% '10/27/2022')
SGFmod_1027 <- aov(lm(SFG ~ pCO2 , data =F1_Masterfile_10_27_22 ))
shapiro.test(resid(SGFmod_1027)) # 0.009596
leveneTest(SGFmod_1027)# 0.9256 **
SGFmod_1027_KW <- kruskal.test(SFG ~ pCO2, data =F1_Masterfile_10_27_22)
# Kruskal-Wallis chi-squared = 0.92308, df = 1, p-value = 0.3367


F1_Masterfile_2.0$pCO2 <- factor(F1_Masterfile_2.0$pCO2, levels= c('500 μatm','800 μatm','1200 μatm'))
SFG_Pousse_F1          <- ggplot(data=F1_Masterfile_2.0, aes(x=pCO2, y=SFG, colour=pCO2)) +
                        scale_colour_manual(values=c("forestgreen","orange", "purple"))+
                        theme_classic() +  
                        geom_boxplot(fill="white", 
                                     outlier.colour=NA, 
                                     position=position_dodge(width=0.9)) +
                        geom_point(position=position_jitterdodge()) +
                        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                        theme(axis.text.x=element_blank(),axis.title.x=element_blank()) +
                        labs(title="F1 Bay Scallops: Scope for Growth ", x ="Month", y = "Scope for Growth") + 
                        facet_wrap(~Date)

pdf("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/F1_SFG.pdf")
print(SFG_Pousse_F1)
dev.off()
```
