---
title: "F1_size_surival"
author: "Samuel Gurr"
date: "3/13/2024"
output:
  pdf_document:
    latex_engine: xelatex
---

Last updates: March 3, 2024


## Load libraries

```{r setup, include= FALSE, echo = FALSE}

# LOAD LIBRARIES 
library(ggplot2)
library(tidyr)
library(dplyr)
library(rcompanion)
library(FSA)
library(car)
library(forcats)
library(kableExtra) # nice Rmd tables
library(emmeans)
library(ggpubr)
library(survival)
library(Rmisc)
library(coxme)
library(survminer)
library(ggsurvfit) # survfit2
library(gtsummary) # tbl_survfit
library(survminer) # ggforect hazard ratio plot
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis")

```

## load data - F1 survival for the grow out 
* Note: this entials when the animals were transferred from the static system upstairs 
to the basement under flow throgh conditions, reestablishing a baseline starting density on 8/18/2021 (23 DPF)
```{r load data}
F1_survival <- read.csv(file= "Data/Physiology/Survival/F1/cumulative_raw/F1_survival_raw_growout.csv", header = TRUE)
unique(F1_survival$Date)
unique(F1_survival$Age)
```

# SUVIVAL: Visualize and Stats


## Visual

### Table Summary
* N per treamment per day and the mean +- survival
```{r F1 summary table means}

summ_F1 <- F1_survival %>%  na.omit() %>% summarySE(measurevar="Survival", groupvars=c("Age", "Treatment"))
summ_F1 %>% kbl() %>% kable_classic(full_width = F, html_font = "Cambria")
unique(summ_F1$Age) == unique(F1_survival$Age) # should all be true, the na omit above is essential for replicates w/o value later on..
```

### Plot it
```{r F1 plot raw counts}
F1_PlotMeanSE <-  ggplot(summ_F1, aes(x=Age, y=Survival, color=Treatment)) + geom_line()+
                          geom_point()+ 
                           geom_errorbar(aes(ymin=Survival-se, 
                                             ymax=Survival+se), width=.2,
                                        position=position_dodge(.1)) +
                          scale_color_manual(values=c("green4", "darkorange1"))+
                          theme_classic() + 
                          labs(x="Age (days)", y="Percent Survival")+ #scale_y_continuous(breaks=seq(0,100,20))+ 
                          ggtitle("F1 grow out survival (Mean +- SE)") + 
                          theme(legend.position="none",
                                panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                panel.background = element_blank(), 
                                axis.line = element_line(colour = "black"))
 
F1_PlotMeanSE

pdf("Output/Survival/F1/F1_Survival_meanSE.pdf", width=8, height=3)
print(F1_PlotMeanSE)
dev.off()

```

## Survival - binary data calc
```{r assemble binary survival object}

# count data with the replicate resolution 

surv_F1 <- F1_survival %>% 
              dplyr::mutate(Count = 
                              as.numeric(gsub(",","",Count))) %>% # remove the commas from these numbers- id as character if not removed!
              dplyr::rename(Count_alive = Count) %>% # rename to avoid confusion
              dplyr::mutate(Count_total = case_when(Survival == 0 ~ 0,
                                               Survival >0 ~
                                                 (1/as.numeric(Survival))*
                                                 as.numeric(Count_alive)),# proportion is that of alive
                           Count_dead = Count_total - Count_alive)


binary_surv_df     <- data.frame()

surv_F1 <- surv_F1[!is.na(surv_F1$Survival),]
for (i in 1:nrow(surv_F1)) {
   count_alive <- round(surv_F1[i,]$Count_alive) # divide all counts by 1000, round to nearest
   count_dead  <- round(surv_F1[i,]$Count_dead)  # divide all counts by 1000, round to nearest
   
   loopDF           <- data.frame(matrix(0,ncol = 4, nrow = (count_alive + count_dead))) 
   colnames(loopDF) <- (c('Treatment','Replicate','Age','Count_dead'))
   loopDF           <- loopDF %>% 
                            dplyr::mutate(
                            Treatment = surv_F1[i,]$Treatment,
                            Replicate   = surv_F1[i,]$Rep,  
                            Age         = surv_F1[i,]$Age,
                            Count_dead  = surv_F1[i,]$Count_dead
                          ) 
  loopDF[c(1:count_dead),4] = 1 # 1 for dead 
  loopDF[c((count_dead + 1):nrow(loopDF)),4] = 0 # 0 for alive

  loopDF           <- data.frame(loopDF) # name dataframe for this single row
  binary_surv_df <- rbind(binary_surv_df,loopDF) #bind to a cumulative list dataframe
  
}


# mean suriv object - synthesizing the count data within time nad treamtnet (means by replicate!)


surv_F1_MEANS <- surv_F1 %>% 
              dplyr::select(-c(Date, Rep, Survival)) %>% 
              dplyr::group_by(Treatment, Age) %>% 
              dplyr::summarise(mean_Count_alive = mean(Count_alive), 
                               mean_Count_dead = mean(Count_dead))
# call datafarme binary for plotting
binary_surv_df_MEANS <- data.frame() # start dataframe 

# run it 
for (i in 1:nrow(surv_F1_MEANS)) {
   count_alive <- round(surv_F1_MEANS[i,]$mean_Count_alive) # divide all counts by 1000, round to nearest
   count_dead  <- round(surv_F1_MEANS[i,]$mean_Count_dead)  # divide all counts by 1000, round to nearest
   
   loopDF           <- data.frame(matrix(0,ncol = 3, nrow = (count_alive + count_dead))) 
   colnames(loopDF) <- (c('Treatment','Age','Count_dead'))
   loopDF           <- loopDF %>% 
                            dplyr::mutate(
                            Treatment = surv_F1_MEANS[i,]$Treatment,
                            Age         = surv_F1_MEANS[i,]$Age
                          ) 
  loopDF[c(1:count_dead),3] = 1 # 1 for dead 
  loopDF[c((count_dead + 1):nrow(loopDF)),3] = 0 # 0 for alive

  loopDF             <- data.frame(loopDF) # name dataframe for this single row
  binary_surv_df_MEANS <- rbind(binary_surv_df_MEANS,loopDF) #bind to a cumulative list dataframe
  
}
# View(binary_surv_F1_MEANS)
```


```{r}
# To address tank as a random factor it MUST be numeric, change this here
unique(binary_surv_df$Replicate) # "A" "B" "C" "D" "E" NA
binary_surv_df <- binary_surv_df %>% 
                    dplyr::mutate(Replicate = case_when(Replicate== 'A'~1,
                                                       Replicate== 'B'~2,
                                                       Replicate== 'C'~3,
                                                       Replicate== 'D'~4,
                                                       Replicate== 'E'~4,
                                                       Replicate== 'F'~5,
                                                       Replicate== 'G'~6,
                                                       Replicate== 'H'~7),
                                  TankID   = as.numeric(
                                                        as.factor(
                                                          paste0(
                                                              Replicate, Treatment)
                                                          )
                                                        )
                                  ) %>% 
                        na.omit()
unique(binary_surv_df$Replicate)  # 1 2 3 4 5 6 7

# convert to numeric to be sure
binary_surv_df$Replicate <- as.numeric(binary_surv_df$Replicate)



# For meaningful comparison to F2, truncate binary_surv_df to 217 dpf (F2 ended at 219 dpf)

binary_surv_df_217dpf <- binary_surv_df %>% filter(Age <= 217)
unique(binary_surv_df_217dpf$Age) # 23  51  64  92 129 147 182 217
```
# Create surv objects 
  * binary_surv_df - all data with replicate as random factor
  * binary_surv_df_MEANS - no replicate, this is the mean 0s and 1s 
```{r create surv object}

binary_surv_df$Age <- as.numeric(binary_surv_df$Age)
surv_obj.all <- survfit2(Surv(Age, Count_dead) ~ Treatment+(1|Replicate), data = binary_surv_df)
#                                            n events median 0.95LCL 0.95UCL
# Treatment=Low, 1 | Replicate=TRUE      23867   2995    303     303     318
# Treatment=Moderate, 1 | Replicate=TRUE 24079   3907    273     273     273

binary_surv_df_MEANS$Age <- as.numeric(binary_surv_df_MEANS$Age)
surv_obj.means <- survfit2(Surv(Age, Count_dead) ~ Treatment, data = binary_surv_df_MEANS)

#                       n events median 0.95LCL 0.95UCL
# Treatment=Low      5686    651    318     303     346
# Treatment=Moderate 5739    862    303     273     303







# For meaningful comparison to F2, truncate binary_surv_df to 217 dpf (F2 ended at 219 dpf)

binary_surv_df_217dpf$Age <- as.numeric(binary_surv_df_217dpf$Age)
surv_obj_217dpf.all       <- survfit2(Surv(Age, Count_dead) ~ Treatment+(1|Replicate), 
                                      data = binary_surv_df_217dpf)
#                                            n events median 0.95LCL 0.95UCL
# Treatment=Low, 1 | Replicate=TRUE      22840   3268    217     217     217
# Treatment=Moderate, 1 | Replicate=TRUE 24192   5307    182     182     182

binary_surv_df_217dpf$Age <- as.numeric(binary_surv_df_217dpf$Age)
surv_obj_217dpf.means     <- survfit2(Surv(Age, Count_dead) ~ Treatment, 
                                  data = binary_surv_df_217dpf)
#                        n events median 0.95LCL 0.95UCL
# Treatment=Low      22840   3268    217     217     217
# Treatment=Moderate 24192   5307    182     182     182

```


# Plot the surv object

```{r plot the surv object}

# plot the surv data 
# NOTE: this is NOT ideal for the plot becasue it does not take into about the 
# replicate tanks, think about your data, a bunch of 0s and 1s for count dead v alive with 
# rep included, (and unaddress in this figure) this is increasing the 0s and 1s represented! 
surv_F1_all  <- Surv(time = as.numeric(binary_surv_df$Age), 
                     event = as.numeric(binary_surv_df$Count_dead), type = "right")

F1_Survplot.all <- ggsurvplot(surv_obj.all, 
                           risk.table = F, 
                           pval = F, 
                           conf.int = TRUE,
                           pval.method=TRUE,
                           legend.labs=c("500 μatm","800 μatm"),
                           palette = alpha(c("forestgreen","darkorange2"), c(1,1)), 
                           ggtheme = theme_survminer(),
                           font.tickslab = c(10),
                           break.x.by = 100 ,xlab = "Age (dpf)", 
                           legend.title = "pCO2 treatment"
                          )


# plot the MEAN surv data 
# NOTE: this is more appropriate for teh figure, we have only one set of 0s and 1s for each treament and each day 
# as opposed to mutliple sets per replicate tank that will go unaccounted for in the figure (above) 
# this results in a higher variability in our data - perhaps due to less occurances of datapoints? Still a better representation 


F1_Survplot_MEANS <- ggsurvplot(surv_obj.means, 
                           risk.table = F, 
                           pval = F, 
                           conf.int = TRUE,
                           pval.method=TRUE,
                           legend.labs=c("500 μatm","800 μatm"),
                           palette = alpha(c("forestgreen","darkorange2"), c(1,1)), 
                           ggtheme = theme_survminer(),
                           font.tickslab = c(10),
                           break.x.by = 100 ,xlab = "Age (dpf)", 
                           legend.title = "pCO2 treatment"
                          )

# output plot 
pdf(paste0("Output/Survival/F1/F1_Survival_plot.pdf"),width=8, height=3)
print(F1_Survplot_MEANS)
dev.off()

```


```{r Plot surv_obj}

F1_KaplanMeier.all <- surv_obj.all %>% 
                      ggsurvfit(linetype_aes = TRUE, linewidth = 1) +
                        scale_color_manual(values = c("forestgreen","orange")) +
                        scale_fill_manual(values = c("forestgreen","orange")) +
                        labs(
                          x = "Days",
                          y = "Overall survival probability"
                        ) + 
                        add_confidence_interval() +
                        # add_risktable() +
                        # add_risktable_strata_symbol() + # (symbol = "\U25CF", size = 10
                        # scale_ggsurvfit(x_scales = list(breaks = 0:1)) #+
                        add_pvalue(location  = "annotation", x = 8.5)
F1_KaplanMeier.all


F1_KaplanMeier.means <- surv_obj.means %>% 
                        ggsurvfit(linetype_aes = TRUE, linewidth = 1) +
                          scale_color_manual(values = c("forestgreen","orange")) +
                          scale_fill_manual(values = c("forestgreen","orange")) +
                          labs(
                            x = "Days",
                            y = "Overall survival probability"
                          ) + 
                          add_confidence_interval() +
                          # add_risktable() +
                          # add_risktable_strata_symbol() + # (symbol = "\U25CF", size = 10
                          # scale_ggsurvfit(x_scales = list(breaks = 0:1)) #+
                          add_pvalue(location  = "annotation", x = 8.5)
F1_KaplanMeier.means

# output plot 
pdf(paste0("Output/Survival/F1/F1_Survival_ggsurvfit.pdf"),width=8, height=4)
print(F1_KaplanMeier.means)
dev.off()














# For meaningful comparison to F2, truncate binary_surv_df to 217 dpf (F2 ended at 219 dpf)


F1_KaplanMeier_217dpf.all <- surv_obj_217dpf.all %>% 
                      ggsurvfit(linetype_aes = TRUE, linewidth = 1) +
                        scale_color_manual(values = c("forestgreen","orange")) +
                        scale_fill_manual(values = c("forestgreen","orange")) +
                        labs(
                          x = "Days",
                          y = "Overall survival probability"
                        ) + 
                        add_confidence_interval() +
                        # add_risktable() +
                        # add_risktable_strata_symbol() + # (symbol = "\U25CF", size = 10
                        # scale_ggsurvfit(x_scales = list(breaks = 0:1)) #+
                        add_pvalue(location  = "annotation", x = 8.5)
F1_KaplanMeier_217dpf.all


F1_KaplanMeier_217dpf.means <- surv_obj_217dpf.means %>% 
                        ggsurvfit(linetype_aes = TRUE, linewidth = 1) +
                          scale_color_manual(values = c("forestgreen","orange")) +
                          scale_fill_manual(values = c("forestgreen","orange")) +
                          labs(
                            x = "Days",
                            y = "Overall survival probability"
                          ) + 
                          add_confidence_interval() +
                          # add_risktable() +
                          # add_risktable_strata_symbol() + # (symbol = "\U25CF", size = 10
                          # scale_ggsurvfit(x_scales = list(breaks = 0:1)) #+
                          add_pvalue(location  = "annotation", x = 8.5)
F1_KaplanMeier_217dpf.means

# output plot 
pdf(paste0("Output/Survival/F1/F1_Survival_217dpf_ggsurvfit.pdf"),width=8, height=4)
print(F1_KaplanMeier_217dpf.means)
dev.off()
```

## Estimating x-time survival
* per 100 days post fertilization
```{r}

F1_100d_surv_prob <- surv_obj.all %>% 
                          tbl_survfit(
                            times = 100,
                            label_header = "**survival to 100 days post-fertilization (95% CI)**")
F1_100d_surv_prob$table_body$stat_1[2]
F1_100d_surv_prob$table_body$stat_1[3]


# for loop every 50 days between 100 - 450 days post fertilization to a summary table!
x <- seq.int(100,450, by = 50) # call the integer
summarytable <- data.frame() # summary table 
for (i in 1:length(x)) { # for loop
  survtable <- surv_obj.means %>% tbl_survfit(times = x[i])
  survtable$table_body$stat_1[2]
  survtable$table_body$stat_1[3]
  loopDF  <- data.frame(matrix(0,ncol = 4, nrow = 1)) 
  colnames(loopDF) = c('Age','LowpCO2_Probabilty','ModpCO2_Probabilty','Diff')
  loopDF  <- loopDF %>% 
        dplyr::mutate(
                      Age                = x[i],
                      LowpCO2_Probabilty = survtable$table_body$stat_1[2], 
                      ModpCO2_Probabilty = survtable$table_body$stat_1[3],
                      Diff               = abs(
                                           as.numeric(substr(survtable$table_body$stat_1[2],1,2)) -
                                           as.numeric(substr(survtable$table_body$stat_1[3],1,2)) 
                                           )
                      ) 
  loopDF       <- data.frame(loopDF) # name dataframe for this single row
  summarytable <- rbind(summarytable,loopDF) #bind to a cumulative list dataframe
}
```


# Comparing survival times between groups (log-rank test)
* We can conduct between-group significance tests using a log-rank test. The log-rank test equally weights observations over the entire follow-up time and is the most common way to compare survival times between groups. There are versions that more heavily weight the early or late follow-up that could be more appropriate depending on the research question (see ?survdiff for different test options).

* We get the log-rank p-value using the survdiff function
* use binary_surv_df_MEANS
```{r log-rank test survdiff}


F1_logrank_test.all <- survdiff(formula = Surv(Age, Count_dead) ~ 
                              Treatment+(1|Replicate), data = binary_surv_df)
#                                            N Observed Expected (O-E)^2/E (O-E)^2/V
# Treatment=Low, 1 | Replicate=TRUE      23867     2995     3410      50.6       109
# Treatment=Moderate, 1 | Replicate=TRUE 24079     3907     3492      49.4       109
# Chisq= 109  on 1 degrees of freedom, p= <2e-16 

F1_logrank_test.means <- survdiff(formula = Surv(Age, Count_dead) ~ 
                                    Treatment, data = binary_surv_df_MEANS)
#                       N Observed Expected (O-E)^2/E (O-E)^2/V
# Treatment=Low      5686      651      748      12.5      26.8
# Treatment=Moderate 5739      862      765      12.2      26.8
# Chisq= 26.8  on 1 degrees of freedom, p= 2e-07
```


# The Cox regression model + Hazard Ratio

 * We may want to quantify an effect size for a single variable, or include **more than one variable** into a regression model to account for the effects of multiple variables.

* The Cox regression model is a semi-parametric model that can be used to fit univariable and multivariable regression models that have survival outcomes.

* use binary_surv_df - WE CAN ADDRESS REP HERE!


# Hazard ratio is equivalent to the exp(coef) in the coxpH model

  *  HR > 1 indicates an increased risk of death, An HR < 1, on the other hand, 
  indicates a decreased risk

  *  For example, a hazard ratio of 0.25 for treatment groups tells you 
  that individuals who received treatment  B have a reduced risk of dying compared 
  to patients who received treatment A

```{r cox  for multiple variables}

# Hazard ratio is equivalent to the exp(coef)
# HR > 1 indicates an increased risk of death, An HR < 1, on the other hand, indicates a decreased risk
# For example, a hazard ratio of 0.25 for treatment groups tells you that individuals who received treatment 
# B have a reduced risk of dying compared to patients who received treatment A



# run cox test on all data with replicate as a random factor
F1_coxph_test   <- coxph(formula = Surv(Age, Count_dead) ~ Treatment+(1|TankID), data = binary_surv_df)
summary(F1_coxph_test)
#                      coef exp(coef) se(coef)     z Pr(>|z|)    
# TreatmentModerate 0.24904   1.28280  0.02429 10.25   <2e-16 ***
# 1 | ReplicateTRUE      NA        NA  0.00000    NA       NA 
# Hazard ratio = 1.28280
ggforest(F1_coxph_test, data = binary_surv_df)
# Likelihood ratio test=106  on 1 df, p=< 2.2e-16
# n= 47946, number of events= 6902
F1_coxph_test_table <- coxph(Surv(Age, Count_dead) ~ Treatment+(1|TankID), data = binary_surv_df) %>% 
                              tbl_regression(exp = TRUE) 

# COXME IS THE PROPER WAY TO ADDRESS THE TANK REPLICATE AS A RANDOM FACTOR - ALITHOU GGFOREST IS NOT COMPTATIBLE
# THEREFORE, USE THE OUTPUT EXP AND c95 CI FROM THE COXME BUT PLOT THE COXPH HAZARD RATIO - ADJUST PDF MANUALLY OFF R
# run mixed cox model with replicate as a random factor 
F1_coxme_mixed_test   <- coxme(Surv(Age, Count_dead) ~ # using coxme, notice ther results are the same as coxpH
                                   Treatment + (1 | TankID), # note we cannot make a hazrd ratio plot using coxme
                                 data = binary_surv_df)
#                        coef exp(coef)  se(coef)    z    p
# TreatmentModerate 0.2097335  1.233349 0.1537181 1.36 0.17

F1_coxme_mixed_HR   <- coxme(Surv(Age, Count_dead) ~ # using coxme, notice ther results are the same as coxpH
                                   Treatment + (1 | TankID), # note we cannot make a hazrd ratio plot using coxme
                                 data = binary_surv_df) %>%  
                                        tbl_regression(exp = TRUE) # thi gives us what we need
# 1.23	0.91, 1.67	0.2 # THESE ARE THE CORRECT VALUES - OUTPUT THE COXPH HAZARD GGFIREST BUT MANUALLY ADJUST FOR THESE EXPONENTS!!



# run cox test on all data as a mean
# * no replicate tank, these are the binary data as a mean
F1_coxph_test.means    <- coxph(formula = Surv(Age, Count_dead) ~ Treatment, data = binary_surv_df_MEANS)
summary(F1_coxph_test.means)
#                      coef exp(coef) se(coef)     z Pr(>|z|)    
# TreatmentModerate 0.13669   1.14647  0.03066 4.459 8.25e-06 ***
HaxardRatio_plot <- ggforest(F1_coxph_test.means,
                               data = binary_surv_df_MEANS)

pdf(paste0("Output/Survival/F1/F1_Survival_hazardratio.pdf"),width=6, height=2)
print(HaxardRatio_plot)
dev.off()

# Likelihood ratio test=106  on 1 df, p=< 2.2e-16
# n= 47946, number of events= 6902
F1_coxph_test_table.mean <- coxph(Surv(Age, Count_dead) ~ Treatment, 
                                  data = binary_surv_df_MEANS) %>% 
                              tbl_regression(exp = TRUE) 

```


```{r 217dpf cox for multiple variables}

# Hazard ratio is equivalent to the exp(coef)
# HR > 1 indicates an increased risk of death, An HR < 1, on the other hand, indicates a decreased risk
# For example, a hazard ratio of 0.25 for treatment groups tells you that individuals who received treatment 
# B have a reduced risk of dying compared to patients who received treatment A



# run cox test on all data with replicate as a random factor
F1_coxph_217dpf   <- coxph(formula = Surv(Age, Count_dead) ~ 
                             Treatment+(1|TankID), 
                           data = binary_surv_df_217dpf)
summary(F1_coxph_217dpf)
#                      coef exp(coef) se(coef)     z Pr(>|z|)    
# TreatmentModerate 0.36187   1.43601  0.02225 16.27   <2e-16 ***
# 1 | TankIDTRUE         NA        NA  0.00000    NA       NA   
# Hazard ratio = 1.28280
ggforest(F1_coxph_217dpf, data = binary_surv_df_217dpf)
F1_coxph_217dpf_table <- coxph(Surv(Age, Count_dead) ~ 
                               Treatment+(1|TankID), 
                             data = binary_surv_df_217dpf) %>% 
                              tbl_regression(exp = TRUE) 
# 1.44	1.37, 1.50	<0.001 # tell sus that moderate had signicantly lower survival, however coxpH does NOT address
# the tank factor correctly, need to use coxme below, these data however output out of R (havenot found out how to 
# output coxme) therefore output, do not report but use as a template to report the coxme below!!


# COXME IS THE PROPER WAY TO ADDRESS THE TANK REPLICATE AS A RANDOM FACTOR - ALITHOU GGFOREST IS NOT COMPTATIBLE
# THEREFORE, USE THE OUTPUT EXP AND c95 CI FROM THE COXME BUT PLOT THE COXPH HAZARD RATIO - ADJUST PDF MANUALLY OFF R
# run mixed cox model with replicate as a random factor 
F1_coxme_mixed_217dpf   <- coxme(Surv(Age, Count_dead) ~ # using coxme, notice ther results are the same as coxpH
                                   Treatment + (1 | TankID), # note we cannot make a hazrd ratio plot using coxme
                                 data = binary_surv_df_217dpf)
#                       coef exp(coef)  se(coef)    z    p
# TreatmentModerate 0.439905   1.55256 0.3328382 1.32 0.19

F1_coxme_mixed_217dpf_HR   <- coxme(Surv(Age, Count_dead) ~ # using coxme, notice ther results are the same as coxpH
                                   Treatment + (1 | TankID), # note we cannot make a hazrd ratio plot using coxme
                                 data = binary_surv_df_217dpf) %>%  
                                        tbl_regression(exp = TRUE) # thi gives us what we need
# 1.55	0.81, 2.98	0.2 # THESE ARE THE CORRECT VALUES - OUTPUT THE COXPH HAZARD GGFIREST BUT MANUALLY ADJUST FOR THESE EXPONENTS!!



# run cox test on all data as a mean
# * no replicate tank, these are the binary data as a mean
F1_coxph_test.means    <- coxph(formula = Surv(Age, Count_dead) ~ Treatment, data = binary_surv_df_MEANS)
summary(F1_coxph_test.means)
#                      coef exp(coef) se(coef)     z Pr(>|z|)    
# TreatmentModerate 0.13669   1.14647  0.03066 4.459 8.25e-06 ***
HaxardRatio_plot <- ggforest(F1_coxph_test.means,
                               data = binary_surv_df_MEANS)

pdf(paste0("Output/Survival/F1/F1_Survival_hazardratio.pdf"),width=6, height=2)
print(HaxardRatio_plot)
dev.off()

# Likelihood ratio test=106  on 1 df, p=< 2.2e-16
# n= 47946, number of events= 6902
F1_coxph_test_table.mean <- coxph(Surv(Age, Count_dead) ~ Treatment, 
                                  data = binary_surv_df_MEANS) %>% 
                              tbl_regression(exp = TRUE) 

```

