---
title: "F1_F2_Juveniles_Popgen"
author: "Samuel Gurr"
date: "2024-02-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# SET WORKING DIRECTORY 
# knitr::opts_knit$set(root.dir = "C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB-Airradians_multigen_OA/larvae") # Katie's
# knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/HPC_analysis") # Sam's
knitr::opts_knit$set(root.dir = "C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/HPC_analysis") # Sam's

```

#### load packages

```{r load packages we need}
library(vcfR)
library(hierfstat)
library(pcadapt)
library(adegenet)
library(pegas)
library(LDlinkR)
install.packages(c("ldsep", "updog", "BiocManager"))
library(ldsep)
library(updog)
library(VariantAnnotation)
```


### Now lets load the total dataset of Juveniles 

* At this time (F3 still running), this includes the pH8 andpH75 data for F1s and F2s Juveniles 

 * I rand genotyping with SNP separately before converting the bcf (from angsd) for each of the four datasets and merging them. 
 

## load files

```{r load vcf file}

#INTERSECT 
F1_Juveniles_Intersect_vcf   <- read.vcfR("C:/Users/samuel.gurr/Documents/F1Juveniles_Intersect.vcf.gz")
F1F2_Juveniles_Intersect_vcf <- read.vcfR("C:/Users/samuel.gurr/Documents/F1F2Juvneiles_intersect.vcf.gz")

F3_Juveniles_Intersect_vcf   <- read.vcfR("C:/Users/samuel.gurr/Documents/F3Juveniles_Intersect.vcf.gz")


AllBroodstock_Intersect_vcf  <- read.vcfR("C:/Users/samuel.gurr/Documents/AllBroodstock_intersect.vcf.gz")
AllJuveniles_intersect_vcf   <- read.vcfR("C:/Users/samuel.gurr/Documents/AllJuveniles_intersect.vcf.gz")

F1F2_Juveniles_vcf           <- read.vcfR("C:/Users/samuel.gurr/Documents/F1_F2_Juveniles_Merged.vcf.gz")



# F0 - F1 merged and intersect


F0F1_intersect.vcf          <- read.vcfR("C:/Users/samuel.gurr/Documents/F0F1_intersect.vcf.gz")
F0F1_merged.vcf             <- read.vcfR("C:/Users/samuel.gurr/Documents/F0Brood_F1Juv_merged.vcf.gz")
F0F1_strata                 <- read.csv("C:/Users/samuel.gurr/Documents/strata.csv", sep =',', header=FALSE) %>% 
                                dplyr::rename(Individual = V1) %>% 
                                dplyr::mutate(Individual = gsub('*./','',Individual),
                                      Gen = dplyr::case_when(grepl("F0", Individual) ~ "F0",
                                                                     .default = "F1"),
                                      Treatment       = dplyr::case_when(grepl("F0", Individual) ~ "none",
                                      grepl(c("pH75|201|203|204|251|253|254|301|303|304|351|352|353|354"), Individual) ~ "Moderate",
                                      grepl(c("pH8|101|103|104|153|154|155|3_||.4_|.5_"), Individual) ~ "Low"))



F0BroodF1JuvenilespH75.vcf  <- read.vcfR("C:/Users/samuel.gurr/Documents/F0BroodF1JuvenilespH75.vcf.gz")
F0F1_strata_phH75           <- F0F1_strata %>% dplyr::filter(!Treatment %in% 'Low') # keep modrate, pH 75

F0BroodF1JuvenilespH8.vcf   <- read.vcfR("C:/Users/samuel.gurr/Documents/F0BroodF1JuvenilespH8.vcf.gz")
F0F1_strata_phH8            <- F0F1_strata %>% dplyr::filter(!Treatment %in% 'Moderate') # keep modrate, pH 75
```

```{r}

subuit <- readVcf(file = "C:/Users/samuel.gurr/Documents/F0BroodF1JuvenilespH8.vcf.gz")
class(subuit)
#> [1] "CollapsedVCF"
#> attr(,"package")
#> [1] "VariantAnnotation"

#> # A brief description of the genotype fields can be seen with
geno(header(subuit))
# DataFrame with 11 rows and 3 columns
#          Number        Type            Description
#     <character> <character>            <character>
# GT            1      String               Genotype
# DP4           4     Integer Number of high-quali..
# SP            1     Integer Phred-scaled strand ..
# AD            R     Integer         Allelic depths
# ADF           R     Integer Allelic depths on th..
# ADR           R     Integer Allelic depths on th..
# PL            G     Integer List of Phred-scaled..
# DP            1     Integer Number of high-quali..
# DV            1     Integer Number of high-quali..
# DPR           R     Integer Number of high-quali..
# GL            G       Float scaled Genotype Like..

sizemat <- geno(subuit)$DP
refmat  <- geno(subuit)$RA
?Seqinfo 
Seqinfo(genome="ASM985889v1")
registered_NCBI_assemblies()
?multidog

ploidy <- 4
?multidog
mout <- multidog(refmat = NA, 
                 sizemat = sizemat, 
                 ploidy = ploidy, 
                 model = "norm")

```

#### load .bed files (from plink)

* F1 and F2 Juveniles from pH 75 and pH 8 merged .bed from plink

```{r}

F1F2_pH8_bed <- read.pcadapt("C:/Users/samuel.gurr/Documents/plink/F1F2_pH8.bed", type = "bed")
F1F2_pH75_bed <- read.pcadapt("C:/Users/samuel.gurr/Documents/plink/F1F2_pH75.bed", type = "bed")

```

#### load vcf files

* F1 and F2 Juveniles from pH 75 and pH 8 merged vcf from angsd

```{r}

F1F2_pH8_vcf <- read.vcfR("C:/Users/samuel.gurr/Documents/F1F2_pH8_Merged.vcf.gz")
F1F2_pH75_vcf <- read.vcfR("C:/Users/samuel.gurr/Documents/F1F2_pH75_Merged.vcf.gz")

```


### load strata anf format 

```{r}
# table cntiaing the metadata for F1Broodstok
F1_Juv_strata_df <- as.data.frame(
              read.csv("../RAnalysis/Data/Genomics/strata/F1_Juveniles_strata.csv", header = TRUE)
              ) %>%  
              dplyr::select(!X) %>% 
              dplyr::mutate(Gen = "F1")

F2_Juv_strata_df <- as.data.frame(
              read.csv("../RAnalysis/Data/Genomics/strata/F2_Juveniles_strata.csv", header = TRUE)
              ) %>%  
              # dplyr::filter(! Treatment %in% 'High') %>% 
              dplyr::select(!X) %>% 
              dplyr::mutate(Gen = "F2")

F3_Juv_strata_df <- as.data.frame(
              read.csv("../RAnalysis/Data/Genomics/strata/F3_Juveniles_strata.csv", header = TRUE)
              ) %>%  
              # dplyr::filter(! Treatment %in% 'High') %>% 
              dplyr::select(!X) %>% 
              dplyr::mutate(Gen = "F3")

F1_F2_strata_df        <- rbind(F1_Juv_strata_df, F2_Juv_strata_df)
AllJuveniles_strata_df <- rbind(F1_Juv_strata_df, F2_Juv_strata_df, F3_Juv_strata_df)

F1_F2_pH8_strata_df <- F1_F2_strata_df %>%  dplyr::filter(Treatment %in% 'Low')


F1_F2_pH75_strata_df <- F1_F2_strata_df %>%  dplyr::filter(Treatment %in% 'Moderate')

# add a sample that is missing - a duplicate 
# note: that it may be best to ommit this duplicate from the SNP calls altogether, 
# view some sanity checks here before mocing forward and output rationale 
# strata[nrow(strata)+1,] = c("adapter_trim.F1_B6_pH7.5DUP.bam","Moderate", "6")

F0Broodstock <- as.data.frame(read.csv("../RAnalysis/Data/Genomics/strata/F0_Broodstock_strata.csv", header = TRUE))
F1Broodstock <- as.data.frame(read.csv("../RAnalysis/Data/Genomics/strata/F1_Broodstock_strata.csv", header = TRUE))
F2Broodstock <- as.data.frame(read.csv("../RAnalysis/Data/Genomics/strata/F2_Broodstock_strata.csv", header = TRUE))

```


# Screeplot of bed file

-   what to look for?   the 'elbow' of this plot infers the number of descriptive principle components

```{r screeplot}

pH8_res <- pcadapt(F1F2_pH8_bed, K = 8)

pH75_res <- pcadapt(F1F2_pH75_bed, K = 8)


plot(pH8_res, option = "screeplot") # looks like 3

plot(pH75_res, option = "screeplot") # looks like 3
```

# Look at the group variable 
- look a this! WTF?!?

```{r}
plot(pH8_res, option = "scores", pop = F1_F2_pH8_strata_df$Gen)

plot(pH75_res, option = "scores", pop = F1_F2_pH75_strata_df$Gen)
```

This might look normal, but you’ll notice that two of the populations are tightly grouped around PC1. We should check too make sure this pattern isn’t being driven by a linkage in the genome. To do this, we can look at the loading scores of the PCs. Loading scores show how much a particular SNP factors into a PC.

```{r View PCAs 1 through 4}

# pH 8
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH8_res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}


# pH 75 - this one looks wierd..
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH75_res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}
```

# Linkage disequilibrium

-   Linkage Disequilibrium can affect ascertainment of population structure (Abdellaoui et al. 2013). Users analyzing dense data such as SNP Array data should account for LD in their PCAs and PCA-based genome-scans.

-   PCAdapt has a built in feature that allows us to clump SNPs by LD, reducing the data to a more informative subset.

```{r address the LD baby!}
library(ggpubr)


# LD_clumping: 
#   Default is NULL and doesn't use any SNP thinning. If you want to use SNP thinning, provide a named list with parameters $size and $thr which corresponds respectively to the window radius and the squared correlation threshold. A good default value would be list(size = 500, thr = 0.1)
  
# pH 8
pH8_res_LD <- pcadapt(F1F2_pH8_bed, K = 10, LD.clumping = list(size = 500, thr = 0.1))
plot(pH8_res_LD, option = "screeplot") # looks like 2 PCAs
plot(pH8_res_LD, option = "scores", pop = F1_F2_pH8_strata_df$Gen) # F2 is wonky AF
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH8_res_LD$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}


ggarrange(
plot(pH8_res, option = "scores", pop = F1_F2_pH8_strata_df$Gen),
plot(pH8_res_LD, option = "scores", pop = F1_F2_pH8_strata_df$Gen))


# pH 75
?pcadapt
pH75_res_LD <- pcadapt(F1F2_pH75_bed, K = 10, min.ma= 0.01, LD.clumping = list(size = 100, thr = 0.18))
plot(pH75_res_LD, option = "screeplot") # looks like 2 PCAs
plot(pH75_res_LD, option = "scores", pop = F1_F2_pH75_strata_df$Gen) # F2 is wonky AF
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH75_res_LD$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}

ggarrange(
plot(pH75_res, option = "scores", pop = F1_F2_pH75_strata_df$Gen),
plot(pH75_res_LD, option = "scores", pop = F1_F2_pH75_strata_df$Gen))

```


-   Interestingly, we see that compensating for LD, the four groups are more distinct, but not by treatment

-   what other attributes could be responsible for this separation?

    -   we had 4 replicates per treatment (A, B, C, D), however the buckets were randomly distributed at random and rotated. Perhaps there was a tank position during a critical stage (on the seawater table) that caused this separation? Unforuntatley we do not have replicate info for the broodstock, as these were pooled from each replicate and positions on the spawning table.

    -   Look at the F2 Juveniles (here we have A-D information) to see if this arises also


## Build genid objects

```{r}
# create genind object from vcf file - use the LD object 

pH8_genind               <- vcfR2genind(F1F2_pH8_vcf)
F1F2_pH8_vcf_ld_filtered <- F1F2_pH8_vcf[!is.na(pH8_res_LD$loadings[,1]),]
pH8_genind_ld_filtered   <- vcfR2genind(F1F2_pH8_vcf_ld_filtered)

pH75_genind               <- vcfR2genind(F1F2_pH75_vcf)
F1F2_pH75_vcf_ld_filtered <- F1F2_pH75_vcf[!is.na(pH75_res_LD$loadings[,1]),]
pH75_genind_ld_filtered    <- vcfR2genind(F1F2_pH75_vcf_ld_filtered)

# assign metadata to these loci 

strata(pH8_genind) <- F1_F2_pH8_strata_df
setPop(pH8_genind) <- ~Gen

strata(pH8_genind_ld_filtered) <- F1_F2_pH8_strata_df
setPop(pH8_genind_ld_filtered) <- ~Gen




strata(pH75_genind) <- F1_F2_pH75_strata_df
setPop(pH75_genind) <- ~Gen

strata(pH75_genind_ld_filtered) <- F1_F2_pH75_strata_df
setPop(pH75_genind_ld_filtered) <- ~Gen

# PCA analysis 
pH8_tab          <- tab(pH8_genind, freq = TRUE, NA.method = "mean")
pH8_pca1         <- dudi.pca(pH8_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH8_pca1$eig[1:25], main = "PCA eigenvalues", col = heat.colors(25))
s.class(pH8_pca1$li, pop(pH8_genind))


pH8_tab_ld_filt  <- tab(pH8_genind_ld_filtered, freq = TRUE, NA.method = "mean")
pH8_ld_filt_pca1 <- dudi.pca(pH8_tab_ld_filt, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH8_ld_filt_pca1$eig[1:25], main = "PCA eigenvalues", col = heat.colors(25))
s.class(pH8_ld_filt_pca1$li, pop(pH8_genind_ld_filtered))
title("PCA of dataset\naxes 1-2")
add.scatter.eig(pH8_ld_filt_pca1$eig[1:20], 3,1,2)




# PCA analysis 
pH75_tab          <- tab(pH75_genind, freq = TRUE, NA.method = "mean")
pH75_pca1         <- dudi.pca(pH75_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH75_pca1$eig[1:25], main = "PCA eigenvalues", col = heat.colors(25))
s.class(pH75_pca1$li, pop(pH75_genind))


pH75_tab_ld_filt  <- tab(pH75_genind_ld_filtered, freq = TRUE, NA.method = "mean")
pH75_ld_filt_pca1 <- dudi.pca(pH75_tab_ld_filt, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH75_ld_filt_pca1$eig[1:25], main = "PCA eigenvalues", col = heat.colors(25))
s.class(pH75_ld_filt_pca1$li, pop(pH75_genind_ld_filtered))
title("PCA of dataset\naxes 1-2")
add.scatter.eig(pH75_ld_filt_pca1$eig[1:20], 3,1,2)


```



```{r load strata}
F1_Juv_strata_df # we will us this for the intersected juvenile data above
F1_F2_strata_df # for the merged data  we already laoded and fomatted this! THIS IS NOT NORMALIZED AND IS MERGED FOR ALL ALLELES!
F3_Juv_strata_df # 147 rows!
```

## build genind
* use adegent - genind class is a dataframe compatible iwth adegent based on usual genetic markers

```{r genid build}
F1F2_Juveniles_genid <- vcfR2genind(F1F2_Juveniles_vcf)
F1_F2_strata_df$pop <- paste0(F1_F2_strata_df$Gen, F1_F2_strata_df$Treatment)
strata(F1F2_Juveniles_genid) <- F1_F2_strata_df
setPop(F1F2_Juveniles_genid) <- ~pop



# F1 Low and moderate interect genes only 
F1_Juveniles_Intersect_genid <- vcfR2genind(F1_Juveniles_Intersect_vcf)
F1_Juv_strata_df$pop <- paste0(F1_Juv_strata_df$Gen, F1_Juv_strata_df$Treatment)
strata(F1_Juveniles_Intersect_genid) <- F1_Juv_strata_df
setPop(F1_Juveniles_Intersect_genid) <- ~pop





# F1 and F2 low nad moderate interect genes only 
F1F2_Juveniles_Intersect_genid <- vcfR2genind(F1F2_Juveniles_Intersect_vcf)
F1_F2_strata_df$pop <- paste0(F1_F2_strata_df$Gen, F1_F2_strata_df$Treatment)
strata(F1F2_Juveniles_Intersect_genid) <- F1_F2_strata_df
setPop(F1F2_Juveniles_Intersect_genid) <- ~pop


# F3 (low mod and high)  interect genes only 
F3_Juveniles_Intersect_genid <- vcfR2genind(F3_Juveniles_Intersect_vcf)
F3_Juv_strata_df$pop <- paste0(F3_Juv_strata_df$Gen, F3_Juv_strata_df$Treatment)
strata(F3_Juveniles_Intersect_genid) <- F3_Juv_strata_df
setPop(F3_Juveniles_Intersect_genid) <- ~Treatment

# All Juvneiles (low mod and high)  interect genes only 
AllJuveniles_Intersect_genid <- vcfR2genind(AllJuveniles_intersect_vcf)
AllJuveniles_strata_df$pop <- paste0(AllJuveniles_strata_df$Gen, AllJuveniles_strata_df$Treatment)
strata(AllJuveniles_Intersect_genid) <- AllJuveniles_strata_df
setPop(AllJuveniles_Intersect_genid) <- ~pop


# F0 - F1 Merged and Intersect
F0F1_Merged_genid <- vcfR2genind(F0F1_merged.vcf) # 81,325 loci
F0F1_merged.strata$pop <- paste0(F0F1_merged.strata$Gen, F0F1_merged.strata$Treatment)
strata(F0F1_Merged_genid) <- F0F1_merged.strata
setPop(F0F1_Merged_genid) <- ~pop



F0F1_Intersect_genid <- vcfR2genind(F0F1_intersect.vcf) # 6,048 loci;
F0F1_merged.strata$pop <- paste0(F0F1_merged.strata$Gen, F0F1_merged.strata$Treatment)
strata(F0F1_Intersect_genid) <- F0F1_merged.strata
setPop(F0F1_Intersect_genid) <- ~pop


F0F1_pH75_Intersect_genid <- vcfR2genind(F0BroodF1JuvenilespH75.vcf) # 6,048 loci;
F0F1_strata_phH75$pop <- paste0(F0F1_strata_phH75$Gen, F0F1_strata_phH75$Treatment)
strata(F0F1_pH75_Intersect_genid) <- F0F1_strata_phH75
setPop(F0F1_pH75_Intersect_genid) <- ~pop


F0F1_pH8_Intersect_genid <- vcfR2genind(F0BroodF1JuvenilespH8.vcf) # 6,048 loci;
F0F1_strata_phH8$pop <- paste0(F0F1_strata_phH8$Gen, F0F1_strata_phH8$Treatment)
strata(F0F1_pH8_Intersect_genid) <- F0F1_strata_phH8
setPop(F0F1_pH8_Intersect_genid) <- ~pop


```


### Discriminant analysis of principle components (DAPC) 

* find.clusters

  - what is this all about? Investigating genetic diversity using multivarate aprpoches 
  relies on synthetic variables build as linear combinations of alleles which relects the gnetic variation 
  amoung the studied individuals - this allows us in turn to study the diversity beween groups of individuals.
  One route is via genetic clusters where a standard multivariate ANOVA model is used 
  
  total variance = (variance between groups) + (variance within groups)
  
  - PCA focuses on the this total variance or global diveristy, overlooking the differences
  between groups (as the sum of between and within!). 
  
  - DAPC optimizes the between group variance while minimizing the within group variance. 
  Synthetic variables as discriminant functions show differenes between groups while minimizing variation within 
  the cluster
  
  - Note: this is from the adagement tutorial - I am curious, does this DAPC and creation of 
  discriminant functions *bias* the the outcome to focus on between-group variance? OR does it simply
  remove the background to easily discern the present, yet shrouded between-group variance from heavy 
  within-group variance? I hope my future self thinks this makes sence.. 
  
  
```{r find clusters genind object}

grp <- find.clusters(F3_Juveniles_Intersect_genid, max.n.clust=40)

# graph of cumulated variance explained by the eigenvalues of the PCA
# apart from computationa; time, no reason to keep a small number of components 
# we can specify to retain PCs 
table(pop(F3_Juveniles_Intersect_genid), grp$grp)



# run the cluster filters onthe intersect data for F1 pH75 and 8
grp_F1_Intersect <- find.clusters(F1_Juveniles_Intersect_genid, max.n.clust=40)
table(pop(F1_Juveniles_Intersect_genid), grp_F1_Intersect$grp)
table.value(table(pop(F1_Juveniles_Intersect_genid), grp_F1_Intersect$grp), 
            col.lab=paste("inf", 1:20),
            row.lab=paste("ori", 1:20))
# DAPC using function dapc transforms data using PCA and runs discriminant analysis on the retained 
# principle compoenents running on the inferred $grp groups
dapc1 <- dapc(F3_Juveniles_Intersect_genid, grp_F1_Intersect$grp)
scatter.dapc(dapc1, grp=F3_Juveniles_Intersect_genid$pop)
?scatter.dapc
scatter(dapc1, posi.da="topleft", bg="white",
        grp=F3_Juveniles_Intersect_genid$pop,
        pch=17:22, cstar=0,  scree.pca=TRUE,
        posi.pca="bottomleft")

scatter.dapc(dapc1,1,1, 
        grp=F3_Juveniles_Intersect_genid$pop,
        bg="white", scree.da=FALSE, legend=TRUE, solid=.4,
        txt.leg=paste("Cluster",1:6))


```


## build genlight 

* use adegent - genlight is a dataframe compatible with adegenet based on genome-wide SNP data
```{r build genlight}
F1F2_Juveniles_genlight <- vcfR2genlight(F1F2_Juveniles_vcf, n.cores = 4)

```


```{r}
# pairwise Fst
## wrapper for pegas pacakage
F1F1_pH8_perloci.fst     <- Fst(as.loci(F0F1_pH8_Intersect_genid, pop=pop))
F1F1_pH75_perloci.fst    <- Fst(as.loci(F0F1_pH75_Intersect_genid, pop=pop))

F1F1_pH8_perloci.fst_NA  <- F1F1_pH8_perloci.fst %>% na.omit()
F1F1_pH75_perloci.fst_NA <- F1F1_pH75_perloci.fst %>% na.omit()

## wrapper for heirfstat
mat.fst <- genet.dist(F1F2_Juveniles_genid) # (hierfstat): implements pairwise FST , which is also a Euclidean distance between populations.
mat.fst
is.euclid(mat.fst)

?genet.dist

# Fst using genet.dist
# “Dch” By default, Cavalli-Sforza and Edwards Chord distance (eqn 6 in the reference) is returned. This distance is used as default since Takezaki & Nei (1996) found that it was the best to retrieve the relation among samples
F1_intersect.fst      <- genet.dist(F1_Juveniles_Intersect_genid) # default is “Dch”
F1_intersect.fstNei87 <- genet.dist(F1_Juveniles_Intersect_genid, method = "Nei87")



F1F2_intersect.fst      <- genet.dist(F1F2_Juveniles_Intersect_genid) # default is “Dch”
F1F2_intersect.fstNei87 <- genet.dist(F1F2_Juveniles_Intersect_genid, method = "Nei87")



F3_intersect.fst      <- genet.dist(F3_Juveniles_Intersect_genid) # default is “Dch”
F3_intersect.fstNei87 <- genet.dist(F3_Juveniles_Intersect_genid, method = "Nei87")



AllJuveniles_intersect.fst      <- genet.dist(AllJuveniles_Intersect_genid) # default is “Dch”
F3_intersect.fstNei87 <- genet.dist(AllJuveniles_Intersect_genid, method = "Nei87")



F0F1_Merged.fst      <- genet.dist(F0F1_Merged_genid) # default is “Dch”
F3_intersect.fstNei87 <- genet.dist(AllJuveniles_Intersect_genid, method = "Nei87")


F0F1_Intersect.fst      <- genet.dist(F0F1_Intersect_genid) # default is “Dch”


```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

```{r}

```


```{r}

```


```{r}

```

-   F-statistics: a measure of genetic structure developed by Sewall Wright (1969, 1978). Related to statistical analysis of variance (ANOVA)

    -   FST is the proportion of the total genetic variance contained in a subpopulation (the S subscript) relative to the total genetic variance (the T subscript). Values can range from 0 to 1. High FST implies a considerable degree of differentiation among populations.

    -   FIS (inbreeding coefficient) is the proportion of the variance in the subpopulation contained in an individual. High FIS implies a considerable degree of inbreeding.

    -   Related measures: q (theta) of Weir and Cockerham (1984) and GST of Nei (1973, 1978). [See Weir, 1996; Avise, Box 6.3, p. 206].


```{r}
getwd()
my_vcf <- read.vcfR("C:/Users/samuel.gurr/Documents/F1_F2_Juveniles_Merged.vcf.gz")
ld_filtered_vcf <- my_vcf[!is.na(res$loadings[,1]),]

ld_filtered_vcf_LD <- my_vcf[!is.na(res_LD$loadings[,1]),]

```

-   Next, we will convert our vcfR file to a genlight input which can be used by the package adegenet. We will also use the strata and setPop function to enter population level information. Remember, we made the strata_df in the previous tutorial, but we will remake it here just in case.

```{r}
library(adegenet)
library(hierfstat)
mygl <- vcfR2genlight(ld_filtered_vcf_LD,n.cores =8)
strata(mygl) <- strata_df
setPop(mygl) <- ~Treatment

#  glPca (adegenet): implements PCA for genome-wide SNP data stored as genlight
# objects; see dedicated tutorial (genomics).

myglPCA <- glPca(mygl)
```


```{r Fst}
library(adegenet)
# create genind object from vcf file - use the LD object 
ld_genind <- vcfR2genind(my_vcf)
# assign metadata to these loci 
F1_F2_strata_df
strata(ld_genind) <- F1_F2_strata_df
setPop(ld_genind) <- ~Gen

# pairwise Fst
## wrapper for pegas pacakage
Fst(as.loci(ld_genind))
?Fst
## wrapper for heirfstat
mat.fst <- genet.dist(ld_genind) # (hierfstat): implements pairwise FST , which is also a Euclidean distance between populations.
mat.fst
is.euclid(mat.fst)



# PCS analysis 
X <- tab(ld_genind, freq = TRUE, NA.method = "mean")
class(X) # "matrix" "array"
dim(X) # 79 42782
pca1 <- dudi.pca(X, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pca1$eig[1:50], main = "PCA eigenvalues", col = heat.colors(50))
s.class(pca1$li, pop(ld_genind))
title("PCA of F1 Juvenile dataset\naxes 1-2")
add.scatter.eig(pca1$eig[1:20], 3,1,2)

```

Inbreeding 
refers to an excess of homozygosity in a given individual due to the mating of
genetically related parents. This excess of homozygosity is due to the fact that there are
non-negligible chances of inheriting two identical alleles from a recent common ancestor.
Inbreeding can be associated to a loss of fitness leading to ”inbreeding depression”. Typically,
loss of fitness is caused by recessive deleterious alleles which have usually low frequency in
the population, but for which inbred individuals are more likely to be homozygotes.

```{r inbreeding}

# use sepop to separate pops and explore inbreeding

F1_Low <- seppop(ld_genind)$Low

F1_Mod <- seppop(ld_genind)$Moderate

# compute the mean inbreeding for each individual, and plot the resulting distribution
F1_Low_temp <- inbreeding(F1_Low, N=100)
F1_Mod_temp <- inbreeding(F1_Mod, N=100)

# temp is a list of values sampled from the likelihood distribution of each individual; means
# values are obtained for all individuals using sapply

F1_Low_Fbar <- sapply(F1_Low_temp, mean)
hist(F1_Low_Fbar, col="firebrick", main="Average inbreeding in F1 Low")


# We can see that all  individuals  have higher inbreeding (>0.4).
# We can recompute inbreeding for them, asking for the likelihood function to be  returned

which(F1_Low_Fbar>0.4) # all of them
F1_Low_F <- inbreeding(F1_Low, res.type="function")[which(F1_Low_Fbar>0.4)]

plot(F1_Low_F$adapter_trim.201_querydupscoord.bam, 
     main=paste("Inbreeding of individual",
                names(F1_Low_F)),
     xlab="Inbreeding (F)", 
     ylab="Probability density")


```


-   Below, we use the PCA function of adegent to create a PCA.

```{r}
oyster.pca <- glPca(mygl, nf = 3)
```

-   Let’s look at how much variance each PC explains:

```{r}
barplot(100*oyster.pca$eig/sum(oyster.pca$eig),
        col = heat.colors(50), 
        main="PCA Variance Explained")
title(ylab="Percent of variance\nexplained", 
      line = 2)
title(xlab="PC", 
      line = 1)
```

-   We basically have TWO informative PCs here. Let’s plot the individuals on the first two PCs:

```{r}
myCol <- colorplot(oyster.pca$scores,oyster.pca$scores, 
                   transp=TRUE, 
                   cex=4)
abline(h=0,
       v=0, 
       col="grey")
add.scatter.eig(oyster.pca$eig[1:10],2,1,2, 
                posi="bottomright", 
                ratio=.16)
```

-   The plot above is combining information from the first 3 PCs to color dots, and using the first two for x,y coordinates. We can see possibly four groups across all PCs.

-   We can also port this to ggplot and color by population:

```{r}
library(ggplot2)
oyster.pca.df <- as.data.frame(oyster.pca$scores)
oyster.pca.df$pop <- pop(mygl)
cols <-c("#871a1a","#33A02C","#1F78B4")

p <- ggplot(oyster.pca.df, aes(x=PC1, y=PC2, colour=pop)) 
p <- p + geom_point(size=2)
p <- p + stat_ellipse(level = 0.95, size = 1)
p <- p + scale_color_manual(values = cols) 
p <- p + geom_hline(yintercept = 0) 
p <- p + geom_vline(xintercept = 0) 
p <- p + theme_bw()

p
```

# **DAPC**

-   Discriminant analysis of Principal Components (DAPC), allows us to either infer groups or put in groups *a priori*. DAPC seeks to maximize between group variance while minimizing within group variance. I’ll show you how this works both ways below.

### **Finding clusters**

-   'Adegenet' has a built in method for inferring population groupings or clusters. It runs interactively, so this code block below won’t run on it’s own. You need to paste it into the Console.

```{r}
grp <- find.clusters(mygl, max.n.clust=10)
# choose 40 for the number of OCs to retain
```

For the purpose of picking clusters, the more PCs the better. Pick any number greater than 40.

We’d like to see an elbow here, where the lowest point would be the correct number. This doesn’t always work well for subtle structure. I’m going to pick 3 given the results above.

```{r}
grp <- find.clusters(mygl, max.n.clust=10, n.pca =100, n.clust =3)
```

We can make a simple table to see the assignments:

```{r}
table(pop(mygl), grp$grp)
```


<take some time to interpret what this means here!>

## Discriminant Analysis

This is another interactive function. Run in the console.

```{r}
oyster.dapc <- dapc(mygl, grp$grp)
```

**Now this is different than finding clusters. You can overload the analysis with two many PCs.** For this, you want to choose the lowest number that gets you > 60% of the variance. 
  - I would choose 25 or 30.

This is picking the number of discriminant functions. Because we put in four groups, there are only three.(check this if true with our data) Truly, only the first two are informative. Let’s pick 2.

```{r}
oyster.dapc <- dapc(mygl, n.pca = 25, n.da = 2, grp$grp)
```

Now, let’s plot the analysis

```{r}
scatter(oyster.dapc,col=cols,bg="white", solid=1)
```

We can also plot membership probabilities:

```{r}
compoplot(oyster.dapc, 
          posi="bottom",
          txt.leg=paste("Cluster", 1:3), 
          lab="", 
          ncol=4, 
          xlab="individuals")
```

We can use ggplot to make this easier to read and put in the populations for each individual:

```{r}
library(tidyr)
dapc.df <- as.data.frame(oyster.dapc$posterior)
dapc.df$pop <- pop(mygl)
dapc.df$indNames <- rownames(dapc.df)
cols4 <-c("#871a1a","#33A02C","#1F78B4","#FDBF6F" )

dapc.df <- pivot_longer(dapc.df, -c(pop, indNames))
colnames(dapc.df) <- c("Original_Pop","Sample","Assigned_Pop","Posterior_membership_probability")

p <- ggplot(dapc.df, aes(x=Sample, y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity') 
p <- p + scale_fill_manual(values = cols4) 
p <- p + facet_grid(~Original_Pop, scales = "free")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
p <- p + ylab("Posterior membership probability")
p
```

## DAPC with original populations

Again, instead of inferring groups, we can use our original populations.

```{r}
oyster.dapc <- dapc(mygl, 
                    n.pca = 25, 
                    n.da = 2)
scatter(oyster.dapc,
        col = cols, 
        cex = 2, 
        legend = TRUE, 
        clabel = F, 
        posi.leg = "bottomleft", 
        scree.pca = TRUE,
        posi.pca = "topleft", 
        cleg = 0.75, 
        posi.da = "topright")
```

Let’s make this better with ggplot

```{r}
dapc.df <- as.data.frame(oyster.dapc$ind.coord)
dapc.df$pop <- pop(mygl)
dapc.df$indNames <- rownames(dapc.df)

p <- ggplot(dapc.df, aes(x=LD1, 
                         y=LD2, 
                         colour=pop)) 
p <- p + geom_point(size=2)
p <- p + scale_color_manual(values = cols) 
p <- p + geom_hline(yintercept = 0) 
p <- p + geom_vline(xintercept = 0) 
p <- p + theme_bw()+ xlab("DA 1") + ylab("DA 2")+ ggtitle("DAPC with populations as groups")

p
```

**Works cited and acknowledgements**
Code for this tutorial was adapted from the following sources:
https://knausb.github.io/vcfR_documentation/
https://grunwaldlab.github.io/Population_Genetics_in_R/gbs_analysis.html
Documentation from the Adegenet R Package