---
title: "All_Juveniles_Popgen"
author: "Samuel Gurr"
date: "2024-02-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# SET WORKING DIRECTORY 
# knitr::opts_knit$set(root.dir = "C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB-Airradians_multigen_OA/larvae") # Katie's
knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/HPC_analysis") # Sam's
#knitr::opts_knit$set(root.dir = "C:/Users/samuel.gurr/Documents/Github_repositories/EAD-ASEB-Airradians_multigen_OA/HPC_analysis") # Sam's

```

#### load packages

```{r load packages we need}

library(qqman)
library(vcfR)
library(hierfstat)
library(pcadapt)
library(adegenet)
library(remotes)
library(vcf2ploidy) # https://github.com/dandewaters/VCF2Ploidy
library(rPlant)
# library(pegas)
# library(LDlinkR)
# library(ldsep) # need a Seqinfo object  Airradians not registered in package
# library(updog) # need a Seqinfo object  Airradians not registered in package
# library(VariantAnnotation) # need a Seqinfo object  Airradians not registered in package
```


### Now lets load the total dataset of Juveniles 

* At this time (F3 still running), this includes the pH8 andpH75 data for F1s and F2s Juveniles 

 * I rand genotyping with SNP separately before converting the bcf (from angsd) for each of the four datasets and merging them. 
 

## load files

* vcf.gz files 

  - merged: contains all SNPs, using ```bcftools merge``` those that overlap between files and those that did not 
    *NOTE*: merge contains those that intersect and those that did not, however note that when there are >2 input files
    the intersection can be partial 
    
    
  - intersect: contains only SNPs *shared* amoung **all** *input vscf files* using ```bcftools isec -n=<#input>```
  
  
```{r load vcf and bed files}
path = "output/lcWGS/angsd/Merge_Intercept/All_Juveniles/"

pH8.vcf      <- read.vcfR(paste0(path,"pH8/Juveniles_pH8_merged.vcf.gz")) # 78283 variants
pH8.vcf_tidy <- vcfR2tidy(pH8.vcf)
pH8.bed      <- read.pcadapt(paste0(path,"pH8/Juveniles_merged_pH8.bed"), type = "bed") # 78283 variants

pH75.vcf      <- read.vcfR(paste0(path,"pH75/Juveniles_pH75_merged.vcf.gz")) # 54315 variants
pH75.vcf_tidy <- vcfR2tidy(pH75.vcf)
pH75.bed      <- read.pcadapt(paste0(path,"pH75/Juveniles_merged_pH75.bed"), type = "bed") # 54315 variants

path2 = "output/lcWGS/angsd/Merge_Intercept/F1_F3_Juveniles_Low_v_Mod/"

F1F3.vcf      <- read.vcfR(paste0(path2,"F1F3_LOWvMOD_merge.vcf.gz")) # 96703 variants
F1F3.vcf_tidy <- vcfR2tidy(F1F3.vcf)
F1F3.bed      <- read.pcadapt(paste0(path2,"F1F3_LOWvMOD.bed"), type = "bed") # 96703 variants

pH8.vcf      <- read.vcfR(paste0(path,"pH8/Juveniles_pH8_merged.vcf.gz")) # 78,283 variants
pH8.vcf_tidy <- vcfR2tidy(pH8.vcf)
pH8.bed      <- read.pcadapt(paste0(path,"pH8/Juveniles_merged_pH8.bed"), type = "bed") # 78,283 variants

pH75.vcf     <- read.vcfR(paste0(path,"pH75/Juveniles_pH75_merged.vcf.gz")) # 54,315 variants
pH75.bed     <- read.pcadapt(paste0(path,"pH75/Juveniles_merged_pH75.bed"), type = "bed") # 54,315 variants

```

* strata - metadata

  - note, this must be in the same order at which files were analyzed with angsd , these are the columns in the vcf file 
  you can get this information using ```bcftools query -l``` call, thats what I did to output the strata.csv file, this raw 
  file is then changes to a dataframe below with custom calls based on the raw input bam names.. tedious yet one and done!
  
  - can call subsets of this strata for the files with just F0brood and pH75 and F0 brood and pH , okay? okay.
  
```{r load and format strata as metadata}

path = "output/lcWGS/angsd/Merge_Intercept/All_Juveniles/"

pH8_strata   <- read.csv(paste0(path,"pH8/IDs.csv"), sep =',', header=FALSE) %>% 
                                dplyr::rename(Individual = V1) %>% 
                                dplyr::mutate(Individual = gsub('*./','',Individual),
                                      Gen = dplyr::case_when(grepl("F1", Individual) ~ "F1", # in SOME cases, juvenile F1s have 'F1' in the name
                                                             grepl("F2", Individual) ~ "F2", # in all cases, juvenile F2s have 'F2' in the name
                                                             grepl("F3", Individual) ~ "F3", # in all cases, juvenile F3s have 'F3' in the name
                                                                     .default = "F1"), # all other cases when not given, these are F1s
                                      Treatment       = "Low")


pH75_strata   <- read.csv(paste0(path,"pH75/IDs.csv"), sep =',', header=FALSE) %>% 
                                dplyr::rename(Individual = V1) %>% 
                                dplyr::mutate(Individual = gsub('*./','',Individual),
                                      Gen = dplyr::case_when(grepl("F1", Individual) ~ "F1", # in SOME cases, juvenile F1s have 'F1' in the name
                                                             grepl("F2", Individual) ~ "F2", # in all cases, juvenile F2s have 'F2' in the name
                                                             grepl("F3", Individual) ~ "F3", # in all cases, juvenile F3s have 'F3' in the name
                                                                     .default = "F1"), # all other cases when not given, these are F1s
                                      Treatment       = "Moderate")



path2 = "output/lcWGS/angsd/Merge_Intercept/F1_F3_Juveniles_Low_v_Mod/"

F1F3_strata   <- read.csv(paste0(path2,"IDs.csv"), sep =',', header=FALSE) %>% 
                               dplyr::rename(Individual = V1) %>% 
                                dplyr::mutate(Individual = gsub('*./','',Individual),
                                      Gen = dplyr::case_when(grepl("F3", Individual) ~ "F3",
                                                                     .default = "F1"), # some cases when F1 is not in am file
                                      Treatment       = dplyr::case_when(
                                      grepl(c("pH75|201|203|204|251|253|254|301|303|304|351|352|353|354"), Individual) ~ "Moderate",
                                      grepl(c("pH8|101|103|104|153|154|155|3_||.4_|.5_"), Individual) ~ "Low")) %>% 
                                dplyr::mutate(Gen_Treatment = paste0(Gen,'_',Treatment))

```



# Screeplot of bed file

-   what to look for?   the 'elbow' of this plot infers the number of descriptive principle components

-  assign the K value and rerun as '.res'

- Manhattan plot - regions involved in adaptation OR low recombination (high Linkage disequilibrium) affecting ascertainment of population structure,
when working with whole genome data we need to perform SNP thinning to acocutn for LD

  - What does LD look like on a Manhatttan plot? A regoin on the x axis SNPs with the same Y value (-log10 pvalues), appears 
  as a bar (many) or pair of points close/touching on the same Y-axis plane


```{r NO LD - screeplot diagnostic and plot PCA}
library(ggpubr)

path = "../RAnalysis/Output/PopGen/"

## pH8
pH8.diagnostic      <- pcadapt(pH8.bed, K = 20)
plot(pH8.diagnostic, option = "screeplot") # looks like 4 - elbow!
pH8.res             <- pcadapt(pH8.bed, K = 4) # assign PCA 
pdf("../RAnalysis/Output/Popgen/Juvenile_LowpCO2_ManPCA.pdf",width = 10, height = 8)
ggarrange( (plot(pH8.diagnostic, option = "screeplot")),
           (plot(pH8.res, option = "manhattan")), # manhattan plot 
           (plot(pH8.res, option = "scores", pop = pH8_strata$Gen)), # PCA
          nrow=3)
dev.off()

pdf(paste0(path,"AllJuv_pH8_interceptRAW.pdf"),width=8, height = 6)
ggarrange(
  plot(pH8.diagnostic, option = "screeplot"),
  plot(pH8.res, option = "screeplot"),
  plot(pH8.res, option = "manhattan"),
  plot(pH8.res, option = "scores", pop = pH8_strata$Gen),
  nrow = 2, ncol = 2
)
dev.off()

## pH75
pH75.diagnostic      <- pcadapt(pH75.bed, K = 20)
plot(pH75.diagnostic, option = "screeplot") # looks like 4 - elbow!
pH75.res             <- pcadapt(pH75.bed, K = 4) # assign PCA 
pdf("../RAnalysis/Output/Popgen/Juvenile_ModeratepCO2_ManPCA.pdf",width = 10, height = 8)
ggarrange( (plot(pH75.diagnostic, option = "screeplot")),
           (plot(pH75.res, option = "manhattan")), # manhattan plot 
           (plot(pH75.res, option = "scores", pop = pH75_strata$Gen)), # PCA
          nrow=3)
dev.off()



## F1 v F3 low v Mod
F1F3.diagnostic      <- pcadapt(F1F3.bed, K = 20)
plot(F1F3.diagnostic, option = "screeplot") # looks like 4 - elbow!
F1F3.res             <- pcadapt(F1F3.bed, K = 4) # assign PCA 

pdf(paste0(path,"AllJuv_pH75_interceptRAW.pdf"),width=8, height = 6)
ggarrange(
  plot(pH75.diagnostic, option = "screeplot"),
  plot(pH75.res, option = "screeplot"),
  plot(pH75.res, option = "manhattan"),
  plot(pH75.res, option = "scores", pop = pH75_strata$Gen),
  nrow = 2, ncol = 2
)
dev.off()
```


### Is there LD in my data, and is it problematic? (Evaluating loadings)

* To evaluate if LD might be an issue for your dataset... display the loadings (contributions of each SNP to the PC)
  
  - what do i look for? If the loadings are clustered in a single or several genomic regions.

```{r is there LD}


## pH 8
par(mfrow = c(2, 2))
for (i in 1:4) 
  plot(pH8.res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))


## pH 75
par(mfrow = c(2, 2))
for (i in 1:4) 
  plot(pH75.res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))


```

### Linkage disequilibrium thinning using ```pcadapt```

- ```size``` = window size (default 200 SNPs), window radius of which SNPs are lumped 

- ```thr``` = r^2 threshold (default 0.1, correlation threshold 


* Lets write a function to **optimize** ```LD.cliumping```

```{r clump4me}

clump4me <- function(data, LD.thr, LD.K, LD.minMaf, outputfilename) {
  
        # For loop ::::::::::: #
        outputfilename      <- data.frame()  # start dataframe 
        loop.table          <- data.frame(matrix(nrow = 1, ncol = 5)) # create dataframe, columns for the number of sampling days
        colnames(loop.table)<-c('output_PC1', 'input_MinMaf', 'input_Window', 'input_Threshold', 'input_NumPCAs') # names for comuns in the for loop
        LD.window_loop      <- seq(50,1000, by=50) # run the loop for CPM from 1 - 10 (counts per million) 
        LD.window_loop      <- data.frame(LD.window_loop)
        
        
        for (i in 1:nrow(LD.window_loop)) {
          
          LD.window <- LD.window_loop[i,1]
          res       <- pcadapt(input = data, 
                         K = LD.K, 
                         LD.clumping = list(size = LD.window, 
                                            thr = LD.thr),
                         min.maf= LD.minMaf)  
        
          loop.table$input_MinMaf    = LD.minMaf
          loop.table$input_Window    = LD.window
          loop.table$input_Threshold = LD.thr
          loop.table$input_NumPCAs   = LD.K
          loop.table$output_PC1      = abs(mean(res$scores[,1])) +abs(mean(res$scores[,2]))
        
            
          # df             <- data.frame(loop.table) # name dataframe for this singl e row
          outputfilename <- rbind(outputfilename,loop.table) #bind to a cumulative list dataframe
          #print(df_total) # print to monitor progress
        }
        
        return(outputfilename)
}



```




```{r output the results with and without LD}
library(ggpubr)

## pH 8

pdf("../RAnalysis/Output/Popgen/All_Juveniles/Juvenile_LowpCO2_res.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(pH8.diagnostic, option = "screeplot")),
          (plot(pH8.res, option = "qqplot")),
          (plot(pH8.res, option = "stat.distribution")),
          (plot(pH8.res, option = "scores", pop = pH8_strata$Gen)),
          nrow=2,
          ncol=2)),
  (plot(pH8.res , option = "manhattan")),
         nrow = 2)
dev.off()



pdf("../RAnalysis/Output/Popgen/All_Juveniles/Juvenile_LowpCO2_LDres.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(pH8.LDdiagnostics, option = "screeplot")),
          (plot(pH8.LDres, option = "qqplot")),
          (plot(pH8.LDres, option = "stat.distribution")),
          (plot(pH8.LDres, option = "scores", pop = pH8_strata$Gen)),
          nrow=2,
          ncol=2)),
  (plot(pH8.LDres , option = "manhattan")),
         nrow = 2)
dev.off()


## pH 75
pdf("../RAnalysis/Output/Popgen/All_Juveniles/Juvenile_ModeratepCO2_res.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(pH75.diagnostic, option = "screeplot")),
          (plot(pH75.res, option = "qqplot")),
          (plot(pH75.res, option = "stat.distribution")),
          (plot(pH75.res, option = "scores", pop = pH75_strata$Gen)),
          nrow=2,
          ncol=2)),
  (plot(pH75.res , option = "manhattan")),
         nrow = 2)
dev.off()



pdf("../RAnalysis/Output/Popgen/All_Juveniles/Juvenile_ModeratepCO2_LDres.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(pH75.LDdiagnostics, option = "screeplot")),
          (plot(pH75.LDres, option = "qqplot")),
          (plot(pH75.LDres, option = "stat.distribution")),
          (plot(pH75.LDres, option = "scores", pop = pH75_strata$Gen)),
          nrow=2,
          ncol=2)),
  (plot(pH75.LDres , option = "manhattan")),
         nrow = 2)
dev.off()




## F1 v F3 low v Mod
pdf("../RAnalysis/Output/Popgen/All_Juveniles/F1F3_LowvMod_res.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(F1F3.diagnostic, option = "screeplot")),
          (plot(F1F3.res, option = "qqplot")),
          (plot(F1F3.res, option = "stat.distribution")),
          (plot(F1F3.res, option = "scores", pop = F1F3_strata$Gen_Treatment)),
          nrow=2,
          ncol=2)),
  (plot(F1F3.res , option = "manhattan")),
         nrow = 2)
dev.off()



pdf("../RAnalysis/Output/Popgen/All_Juveniles/F1F3_LowvMod_LDres.pdf",width = 10, height = 8)
ggarrange( 
  (ggarrange(
          (plot(F1F3.LDdiagnostics, option = "screeplot")),
          (plot(F1F3.LDres, option = "qqplot")),
          (plot(F1F3.LDres, option = "stat.distribution")),
          (plot(F1F3.LDres, option = "scores", pop = F1F3_strata$Gen_Treatment)),
          nrow=2,
          ncol=2)),
  (plot(F1F3.LDres , option = "manhattan")),
         nrow = 2)
dev.off()

```


### Use the LD loadings to reduce the cvf file 

* ObjectiveL convert the large vcf to a smaller vcf , run the vcf tidy to create tidy object 

  - why? we need this for qqman! 
  

```{r LD loadings reduce vcf files}

pH8.vcf_LDfiltered  <- pH8.vcf[!is.na(pH8.LDres$loadings[,1]),] # 78,283 DOWN TO 21,555 variants
pH75.vcf_LDfiltered <- pH75.vcf[!is.na(pH75.LDres$loadings[,1]),] # 54,315 DOWN TO 18,203 variants!

```


```{r convert LDfiltered vcf to vcf_tidy}

pH8.vcf_LD_tidy <- vcfR2tidy(pH8.vcf_LDfiltered)
pH75.vcf_LD_tidy <- vcfR2tidy(pH75.vcf_LDfiltered)

```
## Manhattan using qqman (tidyr vcf objects!)

  * Objective: run the qqmanmanhattan plots on both res docs (with and without LD filtration!)

  * datasets: pH8.vcf_tidy, pH75.vcf_tidy, pH8.vcf_LD_tidy, pH75.vcf_LD_tidy
  
```{r qqman manhattan plots pH8 Low pCO2}
library(tidyr)


# low pCO2 (pH8) 
pH8Results_qqman            <- as.data.frame(matrix(nrow=length(pH8.vcf_tidy$fix$CHROM), ncol=4)) 
colnames(pH8Results_qqman) <- c('SNP','CHR', 'BP', 'P')
pH8Results_qqman            <- pH8Results_qqman[-c(1:4)] %>% 
                                    dplyr::mutate(
                                      SNP = paste0(pH8.vcf_tidy$fix$CHROM, '_',pH8.vcf_tidy$fix$POS),
                                      CHR = as.numeric(extract_numeric(pH8.vcf_tidy$fix$CHROM)),
                                      BP  = pH8.vcf_tidy$fix$POS,
                                      P   = pH8.LDres$pvalues
                                    ) %>% na.omit()
manhattan( (pH8Results_qqman %>% dplyr::filter(CHR < 90 & -log(pH8Results_qqman$P))),
            annotatePval = 0.001)


library(tidyr)
library(dplyr)
don <- pH8Results_qqman %>% 
  
  # Compute chromosome size
  group_by(CHR) %>% 
  summarise(chr_len=max(BP)) %>% 
  
  # Calculate cumulative position of each chromosome
  mutate(tot=cumsum(chr_len)-chr_len) %>%
  select(-chr_len) %>%
  
  # Add this info to the initial dataset
  left_join(pH8Results_qqman, ., by=c("CHR"="CHR")) %>%
  
  # Add a cumulative position of each SNP
  arrange(CHR, BP) %>%
  mutate( BPcum=BP+tot)

axisdf = don %>%
  group_by(CHR) %>%
  summarize(center=( max(BPcum) + min(BPcum) ) / 2 )

ggplot(don, aes(x=BPcum, y=-log10(P))) +
    
    # Show all points
    geom_point( aes(color=as.factor(CHR)), alpha=0.8, size=1.3) +
    scale_color_manual(values = rep(c("grey", "skyblue"), length(unique(don$CHR)) )) +
    
    # custom X axis:
    scale_x_continuous( label = axisdf$CHR, breaks= axisdf$center ) +
    scale_y_continuous(expand = c(0, 0) ) +     # remove space between plot area and x axis
  
    # Custom the theme:
    theme_bw() +
    theme( 
      legend.position="none",
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )


pH8Results_LD_qqman            <- as.data.frame(matrix(nrow=length(pH8.vcf_LD_tidy$fix$CHROM), ncol=4)) 
colnames(pH8Results_LD_qqman)  <- c('SNP','CHR', 'BP', 'P')
pH8pvals_LD <- as.data.frame(pH8.LDres$pvalues) # call the p values of the res as dataframe
pH8Results_LD_qqman            <- pH8Results_LD_qqman[-c(1:4)] %>% 
                                    dplyr::mutate(
                                      SNP = paste0(pH8.vcf_LD_tidy$fix$CHROM, '_',pH8.vcf_LD_tidy$fix$POS),
                                      CHR = as.numeric(extract_numeric(pH8.vcf_LD_tidy$fix$CHROM)),
                                      BP  = pH8.vcf_LD_tidy$fix$POS,
                                      P   = as.numeric(pH8pvals_LD[!is.na(pH8.LDres$loadings[,1]),]) # truncate the same, omit those with no loadings
                                    ) %>% na.omit()

manhattan( (pH8Results_LD_qqman %>% dplyr::filter(CHR < 400 & -log10(P) > 10)),
            annotatePval = 0.001)

manhattan( (pH8Results_LD_qqman %>% dplyr::filter(CHR < 400)),
            annotatePval = 0.001)
```

```{r qqman manhattan plots pH75 Moderate pCO2}
library(tidyr)


# low pCO2 (pH75) 
pH75Results_qqman            <- as.data.frame(matrix(nrow=length(pH75.vcf_tidy$fix$CHROM), ncol=4)) 
colnames(pH75Results_qqman) <- c('SNP','CHR', 'BP', 'P')
pH75Results_qqman            <- pH75Results_qqman[-c(1:4)] %>% 
                                    dplyr::mutate(
                                      SNP = paste0(pH75.vcf_tidy$fix$CHROM, '_',pH75.vcf_tidy$fix$POS),
                                      CHR = as.numeric(extract_numeric(pH75.vcf_tidy$fix$CHROM)),
                                      BP  = pH75.vcf_tidy$fix$POS,
                                      P   = pH75.LDres$pvalues
                                    ) %>% na.omit()
manhattan( (pH75Results_qqman %>% dplyr::filter(CHR < 90 & -log(pH75Results_qqman$P))),
            annotatePval = 0.001)


library(tidyr)
library(dplyr)
don <- pH75Results_qqman %>% 
  
  # Compute chromosome size
  group_by(CHR) %>% 
  summarise(chr_len=max(BP)) %>% 
  
  # Calculate cumulative position of each chromosome
  mutate(tot=cumsum(chr_len)-chr_len) %>%
  select(-chr_len) %>%
  
  # Add this info to the initial dataset
  left_join(pH75Results_qqman, ., by=c("CHR"="CHR")) %>%
  
  # Add a cumulative position of each SNP
  arrange(CHR, BP) %>%
  mutate( BPcum=BP+tot)

axisdf = don %>%
  group_by(CHR) %>%
  summarize(center=( max(BPcum) + min(BPcum) ) / 2 )

ggplot(don, aes(x=BPcum, y=-log10(P))) +
    
    # Show all points
    geom_point( aes(color=as.factor(CHR)), alpha=0.75, size=1.3) +
    scale_color_manual(values = rep(c("grey", "skyblue"), length(unique(don$CHR)) )) +
    
    # custom X axis:
    scale_x_continuous( label = axisdf$CHR, breaks= axisdf$center ) +
    scale_y_continuous(expand = c(0, 0) ) +     # remove space between plot area and x axis
  
    # Custom the theme:
    theme_bw() +
    theme( 
      legend.position="none",
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )







pH75Results_LD_qqman            <- as.data.frame(matrix(nrow=length(pH75.vcf_LD_tidy$fix$CHROM), ncol=4)) 
colnames(pH75Results_LD_qqman)  <- c('SNP','CHR', 'BP', 'P')
pH75pvals_LD <- as.data.frame(pH75.LDres$pvalues) # call the p values of the res as dataframe
pH75Results_LD_qqman            <- pH75Results_LD_qqman[-c(1:4)] %>% 
                                    dplyr::mutate(
                                      SNP = paste0(pH75.vcf_LD_tidy$fix$CHROM, '_',pH75.vcf_LD_tidy$fix$POS),
                                      CHR = as.numeric(extract_numeric(pH75.vcf_LD_tidy$fix$CHROM)),
                                      BP  = pH75.vcf_LD_tidy$fix$POS,
                                      P   = as.numeric(pH75pvals_LD[!is.na(pH75.LDres$loadings[,1]),]) # truncate the same, omit those with no loadings
                                    ) %>% na.omit()

manhattan( (pH75Results_LD_qqman %>% dplyr::filter(CHR > 40000)),
            annotatePval = 0.001)





don <- pH75Results_LD_qqman %>% 
  
  # Compute chromosome size
  group_by(CHR) %>% 
  summarise(chr_len=max(BP)) %>% 
  
  # Calculate cumulative position of each chromosome
  mutate(tot=cumsum(chr_len)-chr_len) %>%
  select(-chr_len) %>%
  
  # Add this info to the initial dataset
  left_join(pH75Results_LD_qqman, ., by=c("CHR"="CHR")) %>%
  
  # Add a cumulative position of each SNP
  arrange(CHR, BP) %>%
  mutate( BPcum=BP+tot)

axisdf = don %>%
  group_by(CHR) %>%
  summarize(center=( max(BPcum) + min(BPcum) ) / 2 )

ggplot(don, aes(x=BPcum, y=-log10(P))) +
    
    # Show all points
    geom_point( aes(color=as.factor(CHR)), alpha=0.75, size=1.3) +
    scale_color_manual(values = rep(c("grey", "skyblue"), length(unique(don$CHR)) )) +
    
    # custom X axis:
    scale_x_continuous( label = axisdf$CHR, breaks= axisdf$center ) +
    scale_y_continuous(expand = c(0, 0) ) +     # remove space between plot area and x axis
  
    # Custom the theme:
    theme_bw() +
    theme( 
      legend.position="none",
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )

```


This might look normal, but you’ll notice that two of the populations are tightly grouped around PC1. We should check too make sure this pattern isn’t being driven by a linkage in the genome. To do this, we can look at the loading scores of the PCs. Loading scores show how much a particular SNP factors into a PC.

```{r View PCAs 1 through 4}

# pH 8
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH8_res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}


# pH 75 - this one looks wierd..
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(pH75_res$loadings[, i], pch = 19, cex = .3, ylab = paste0("Loadings PC", i))
}
```

# Linkage disequilibrium

-   Linkage Disequilibrium can affect ascertainment of population structure (Abdellaoui et al. 2013). Users analyzing dense data such as SNP Array data should account for LD in their PCAs and PCA-based genome-scans.

-   PCAdapt has a built in feature that allows us to clump SNPs by LD, reducing the data to a more informative subset.

```{r address the LD baby!}
library(ggpubr)


# LD_clumping: 
#   Default is NULL and doesn't use any SNP thinning. If you want to use SNP thinning, provide a named list with parameters $size and $thr which corresponds respectively to the window radius and the squared correlation threshold. A good default value would be list(size = 500, thr = 0.1)
  

## pH 8
plot(pH8.LDres, option = "screeplot") # looks like 2 PCAs
plot(pH8.LDres, option = "scores", pop = pH8_strata$Gen) # 

## pH 75
plot(pH75.LDres, option = "screeplot") # looks like 2 PCAs
plot(pH75.LDres, option = "scores", pop = pH75_strata$Gen) # 


```


-   Interestingly, we see that compensating for LD, the four groups are more distinct, but not by treatment

-   what other attributes could be responsible for this separation?

    -   we had 4 replicates per treatment (A, B, C, D), however the buckets were randomly distributed at random and rotated. Perhaps there was a tank position during a critical stage (on the seawater table) that caused this separation? Unforuntatley we do not have replicate info for the broodstock, as these were pooled from each replicate and positions on the spawning table.

    -   Look at the F2 Juveniles (here we have A-D information) to see if this arises also


## Build genid objects

```{r}
# create genind object from vcf file - use the LD object 

# pH8
pH8.genind         <- vcfR2genind(pH8.vcf)
pH8.vcf_LDfiltered <- pH8.vcf[!is.na(pH8.LDres$loadings[,1]),]
pH8.genind_LD      <- vcfR2genind(pH8.vcf_LDfiltered)


strata(pH8.genind) <- pH8_strata
setPop(pH8.genind) <- ~Gen

strata(pH8.genind_LD) <- pH8_strata
setPop(pH8.genind_LD) <- ~Gen


pH8_tab        <- tab(pH8.genind, freq = TRUE, NA.method = "mean")
pH8_tab_pca1   <- dudi.pca(pH8_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH8_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(pH8_tab_pca1$li, pop(pH8.genind))


pH8_LD_tab        <- tab(pH8.genind_LD, freq = TRUE, NA.method = "mean")
pH8_LD_tab_pca1   <- dudi.pca(pH8_LD_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH8_LD_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(pH8_LD_tab_pca1$li, pop(pH8.genind_LD))



# pH75
pH75.genind         <- vcfR2genind(pH75.vcf)
pH75.vcf_LDfiltered <- pH75.vcf[!is.na(pH75.LDres$loadings[,1]),]
pH75.genind_LD      <- vcfR2genind(pH75.vcf_LDfiltered)

strata(pH75.genind) <- pH75_strata
setPop(pH75.genind) <- ~Gen

strata(pH75.genind_LD) <- pH75_strata
setPop(pH75.genind_LD) <- ~Gen

pH75_tab        <- tab(pH75.genind, freq = TRUE, NA.method = "mean")
pH75_tab_pca1   <- dudi.pca(pH75_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH75_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(pH75_tab_pca1$li, pop(pH75.genind))

?dudi.pca
pH75_LD_tab        <- tab(pH75.genind_LD, freq = TRUE, NA.method = "mean")
pH75_LD_tab_pca1   <- dudi.pca(pH75_LD_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pH75_LD_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(pH75_LD_tab_pca1$li, pop(pH75.genind_LD))








# F1F3
F1F3.genind         <- vcfR2genind(F1F3.vcf)
F1F3.vcf_LDfiltered <- F1F3.vcf[!is.na(F1F3.LDres$loadings[,1]),]
F1F3.genind_LD      <- vcfR2genind(F1F3.vcf_LDfiltered)

strata(F1F3.genind) <- F1F3_strata
setPop(F1F3.genind) <- ~Gen_Treatment

strata(F1F3.genind_LD) <- F1F3_strata
setPop(F1F3.genind_LD) <- ~Gen_Treatment

F1F3_tab        <- tab(F1F3.genind, freq = TRUE, NA.method = "mean")
F1F3_tab_pca1   <- dudi.pca(F1F3_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(F1F3_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(F1F3_tab_pca1$li, pop(F1F3.genind))

F1F3_LD_tab        <- tab(F1F3.genind_LD, freq = TRUE, NA.method = "mean")
F1F3_LD_tab_pca1   <- dudi.pca(F1F3_LD_tab, scale = FALSE, scannf = FALSE, nf = 3)
barplot(F1F3_LD_tab_pca1$eig[1:25], 
        main = "PCA eigenvalues", 
        col = heat.colors(25))
s.class(F1F3_LD_tab_pca1$li, pop(F1F3.genind_LD))


groups <- as.factor(F1F3.genind_LD$strata$Gen_Treatment)
s.class(F1F3_LD_tab_pca1$li,
        fac = groups,  # color by groups
        col = c("orange",  "skyblue","brown",  "turquoise"),
        # labels = NULL,
        # add.plot = TRUE,         # Add onto the scatter plot
        cstar = 0,               # Remove stars
        cellipse = 0             # Remove ellipses
        )
# DAPC using function dapc transforms data using PCA and runs discriminant analysis on the retained 
# principle compoenents running on the inferred $grp groups'
# run the cluster filters onthe intersect data for F1 pH75 and 8
grp_F1F3   <- find.clusters(F1F3.genind_LD, max.n.clust=40)
F1F3_dapc1 <- dapc(F1F3.genind_LD, grp_F1F3$grp)
scatter.dapc(F1F3_dapc1, grp=F1F3.genind_LD$pop)
scatter(F1F3_dapc1, posi.da="topleft", bg="white",
        grp=F1F3.genind_LD$pop,
        pch=17:22, cstar=0,  scree.pca=TRUE,
        posi.pca="bottomleft")

scatter.dapc(F1F3_dapc1,1,1, 
        grp=F1F3.genind_LD$pop,
        bg="white", scree.da=FALSE, legend=TRUE, solid=.4,
        txt.leg=paste("Cluster",1:4))
```



```{r load strata}
F1_Juv_strata_df # we will us this for the intersected juvenile data above
F1_F2_strata_df # for the merged data  we already laoded and fomatted this! THIS IS NOT NORMALIZED AND IS MERGED FOR ALL ALLELES!
F3_Juv_strata_df # 147 rows!
```

## build genind
* use adegent - genind class is a dataframe compatible iwth adegent based on usual genetic markers

```{r genid build}
F1F2_Juveniles_genid <- vcfR2genind(F1F2_Juveniles_vcf)
F1_F2_strata_df$pop <- paste0(F1_F2_strata_df$Gen, F1_F2_strata_df$Treatment)
strata(F1F2_Juveniles_genid) <- F1_F2_strata_df
setPop(F1F2_Juveniles_genid) <- ~pop



# F1 Low and moderate interect genes only 
F1_Juveniles_Intersect_genid <- vcfR2genind(F1_Juveniles_Intersect_vcf)
F1_Juv_strata_df$pop <- paste0(F1_Juv_strata_df$Gen, F1_Juv_strata_df$Treatment)
strata(F1_Juveniles_Intersect_genid) <- F1_Juv_strata_df
setPop(F1_Juveniles_Intersect_genid) <- ~pop





# F1 and F2 low nad moderate interect genes only 
F1F2_Juveniles_Intersect_genid <- vcfR2genind(F1F2_Juveniles_Intersect_vcf)
F1_F2_strata_df$pop <- paste0(F1_F2_strata_df$Gen, F1_F2_strata_df$Treatment)
strata(F1F2_Juveniles_Intersect_genid) <- F1_F2_strata_df
setPop(F1F2_Juveniles_Intersect_genid) <- ~pop


# F3 (low mod and high)  interect genes only 
F3_Juveniles_Intersect_genid <- vcfR2genind(F3_Juveniles_Intersect_vcf)
F3_Juv_strata_df$pop <- paste0(F3_Juv_strata_df$Gen, F3_Juv_strata_df$Treatment)
strata(F3_Juveniles_Intersect_genid) <- F3_Juv_strata_df
setPop(F3_Juveniles_Intersect_genid) <- ~Treatment

# All Juvneiles (low mod and high)  interect genes only 
AllJuveniles_Intersect_genid <- vcfR2genind(AllJuveniles_intersect_vcf)
AllJuveniles_strata_df$pop <- paste0(AllJuveniles_strata_df$Gen, AllJuveniles_strata_df$Treatment)
strata(AllJuveniles_Intersect_genid) <- AllJuveniles_strata_df
setPop(AllJuveniles_Intersect_genid) <- ~pop


# F0 - F1 Merged and Intersect
F0F1_Merged_genid <- vcfR2genind(F0F1_merged.vcf) # 81,325 loci
F0F1_merged.strata$pop <- paste0(F0F1_merged.strata$Gen, F0F1_merged.strata$Treatment)
strata(F0F1_Merged_genid) <- F0F1_merged.strata
setPop(F0F1_Merged_genid) <- ~pop



F0F1_Intersect_genid <- vcfR2genind(F0F1_intersect.vcf) # 6,048 loci;
F0F1_merged.strata$pop <- paste0(F0F1_merged.strata$Gen, F0F1_merged.strata$Treatment)
strata(F0F1_Intersect_genid) <- F0F1_merged.strata
setPop(F0F1_Intersect_genid) <- ~pop


F0F1_pH75_Intersect_genid <- vcfR2genind(F0BroodF1JuvenilespH75.vcf) # 6,048 loci;
F0F1_strata_phH75$pop <- paste0(F0F1_strata_phH75$Gen, F0F1_strata_phH75$Treatment)
strata(F0F1_pH75_Intersect_genid) <- F0F1_strata_phH75
setPop(F0F1_pH75_Intersect_genid) <- ~pop


F0F1_pH8_Intersect_genid <- vcfR2genind(F0BroodF1JuvenilespH8.vcf) # 6,048 loci;
F0F1_strata_phH8$pop <- paste0(F0F1_strata_phH8$Gen, F0F1_strata_phH8$Treatment)
strata(F0F1_pH8_Intersect_genid) <- F0F1_strata_phH8
setPop(F0F1_pH8_Intersect_genid) <- ~pop


```


### Discriminant analysis of principle components (DAPC) 

* find.clusters

  - what is this all about? Investigating genetic diversity using multivarate aprpoches 
  relies on synthetic variables build as linear combinations of alleles which relects the gnetic variation 
  amoung the studied individuals - this allows us in turn to study the diversity beween groups of individuals.
  One route is via genetic clusters where a standard multivariate ANOVA model is used 
  
  total variance = (variance between groups) + (variance within groups)
  
  - PCA focuses on the this total variance or global diveristy, overlooking the differences
  between groups (as the sum of between and within!). 
  
  - DAPC optimizes the between group variance while minimizing the within group variance. 
  Synthetic variables as discriminant functions show differenes between groups while minimizing variation within 
  the cluster
  
  - Note: this is from the adagement tutorial - I am curious, does this DAPC and creation of 
  discriminant functions *bias* the the outcome to focus on between-group variance? OR does it simply
  remove the background to easily discern the present, yet shrouded between-group variance from heavy 
  within-group variance? I hope my future self thinks this makes sence.. 
  
  
```{r find clusters genind object}

grp <- find.clusters(F3_Juveniles_Intersect_genid, max.n.clust=40)

# graph of cumulated variance explained by the eigenvalues of the PCA
# apart from computationa; time, no reason to keep a small number of components 
# we can specify to retain PCs 
table(pop(F3_Juveniles_Intersect_genid), grp$grp)



# run the cluster filters onthe intersect data for F1 pH75 and 8
grp_F1_Intersect <- find.clusters(F1_Juveniles_Intersect_genid, max.n.clust=40)
table(pop(F1_Juveniles_Intersect_genid), grp_F1_Intersect$grp)
table.value(table(pop(F1_Juveniles_Intersect_genid), grp_F1_Intersect$grp), 
            col.lab=paste("inf", 1:20),
            row.lab=paste("ori", 1:20))
# DAPC using function dapc transforms data using PCA and runs discriminant analysis on the retained 
# principle compoenents running on the inferred $grp groups
dapc1 <- dapc(F3_Juveniles_Intersect_genid, grp_F1_Intersect$grp)
scatter.dapc(dapc1, grp=F3_Juveniles_Intersect_genid$pop)
?scatter.dapc
scatter(dapc1, posi.da="topleft", bg="white",
        grp=F3_Juveniles_Intersect_genid$pop,
        pch=17:22, cstar=0,  scree.pca=TRUE,
        posi.pca="bottomleft")

scatter.dapc(dapc1,1,1, 
        grp=F3_Juveniles_Intersect_genid$pop,
        bg="white", scree.da=FALSE, legend=TRUE, solid=.4,
        txt.leg=paste("Cluster",1:6))


```


## build genlight 

* use adegent - genlight is a dataframe compatible with adegenet based on genome-wide SNP data
```{r build genlight}
F1F2_Juveniles_genlight <- vcfR2genlight(F1F2_Juveniles_vcf, n.cores = 4)

```


```{r}
# pairwise Fst
## wrapper for pegas pacakage
library(pegas)
pH8.genind_LD.fst     <- Fst(as.loci(pH8.genind_LD, pop=Gen))
pH8.genind_LD_NA <- F1F1_pH75_perloci.fst %>% na.omit()

## wrapper for heirfstat
mat.fst <- genet.dist(F1F2_Juveniles_genid) # (hierfstat): implements pairwise FST , which is also a Euclidean distance between populations.
mat.fst
is.euclid(mat.fst)

?genet.dist

# Fst using genet.dist
# “Dch” By default, Cavalli-Sforza and Edwards Chord distance (eqn 6 in the reference) is returned. This distance is used as default since Takezaki & Nei (1996) found that it was the best to retrieve the relation among samples
pH8.genind_LD.fst      <- genet.dist(pH8.genind_LD) # default is “Dch”
pH8.genind_LD.mat.fst  <- Fst(as.loci(pH8.genind_LD, pop=Gen))


pH75.genind_LD.fst     <- genet.dist(pH75.genind_LD) # default is “Dch”
pH75.genind_LD.mat.fst <-  Fst(as.loci(pH75.genind_LD, pop=Gen))
?Fst
as.data.frame(pH75.genind_LD.mat.fst) %>% dplyr::filter(Fst > .1) %>% dplyr::arrange()
max(pH75.genind_LD.mat.fst)
```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

```{r}

```


```{r}

```


```{r}

```

-   F-statistics: a measure of genetic structure developed by Sewall Wright (1969, 1978). Related to statistical analysis of variance (ANOVA)

    -   FST is the proportion of the total genetic variance contained in a subpopulation (the S subscript) relative to the total genetic variance (the T subscript). Values can range from 0 to 1. High FST implies a considerable degree of differentiation among populations.

    -   FIS (inbreeding coefficient) is the proportion of the variance in the subpopulation contained in an individual. High FIS implies a considerable degree of inbreeding.

    -   Related measures: q (theta) of Weir and Cockerham (1984) and GST of Nei (1973, 1978). [See Weir, 1996; Avise, Box 6.3, p. 206].


```{r}
getwd()
my_vcf <- read.vcfR("C:/Users/samuel.gurr/Documents/F1_F2_Juveniles_Merged.vcf.gz")
ld_filtered_vcf <- my_vcf[!is.na(res$loadings[,1]),]

ld_filtered_vcf_LD <- my_vcf[!is.na(res_LD$loadings[,1]),]

```

-   Next, we will convert our vcfR file to a genlight input which can be used by the package adegenet. We will also use the strata and setPop function to enter population level information. Remember, we made the strata_df in the previous tutorial, but we will remake it here just in case.

```{r}
library(adegenet)
library(hierfstat)
mygl <- vcfR2genlight(ld_filtered_vcf_LD,n.cores =8)
strata(mygl) <- strata_df
setPop(mygl) <- ~Treatment

#  glPca (adegenet): implements PCA for genome-wide SNP data stored as genlight
# objects; see dedicated tutorial (genomics).

myglPCA <- glPca(mygl)
```


```{r Fst}
library(adegenet)
# create genind object from vcf file - use the LD object 
ld_genind <- vcfR2genind(my_vcf)
# assign metadata to these loci 
F1_F2_strata_df
strata(ld_genind) <- F1_F2_strata_df
setPop(ld_genind) <- ~Gen

# pairwise Fst
## wrapper for pegas pacakage
Fst(as.loci(ld_genind))
?Fst
## wrapper for heirfstat
mat.fst <- genet.dist(ld_genind) # (hierfstat): implements pairwise FST , which is also a Euclidean distance between populations.
mat.fst
is.euclid(mat.fst)



# PCS analysis 
X <- tab(ld_genind, freq = TRUE, NA.method = "mean")
class(X) # "matrix" "array"
dim(X) # 79 42782
pca1 <- dudi.pca(X, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pca1$eig[1:50], main = "PCA eigenvalues", col = heat.colors(50))
s.class(pca1$li, pop(ld_genind))
title("PCA of F1 Juvenile dataset\naxes 1-2")
add.scatter.eig(pca1$eig[1:20], 3,1,2)

```

Inbreeding 
refers to an excess of homozygosity in a given individual due to the mating of
genetically related parents. This excess of homozygosity is due to the fact that there are
non-negligible chances of inheriting two identical alleles from a recent common ancestor.
Inbreeding can be associated to a loss of fitness leading to ”inbreeding depression”. Typically,
loss of fitness is caused by recessive deleterious alleles which have usually low frequency in
the population, but for which inbred individuals are more likely to be homozygotes.

```{r inbreeding}

# use sepop to separate pops and explore inbreeding

F1_Low <- seppop(ld_genind)$Low

F1_Mod <- seppop(ld_genind)$Moderate

# compute the mean inbreeding for each individual, and plot the resulting distribution
F1_Low_temp <- inbreeding(F1_Low, N=100)
F1_Mod_temp <- inbreeding(F1_Mod, N=100)

# temp is a list of values sampled from the likelihood distribution of each individual; means
# values are obtained for all individuals using sapply

F1_Low_Fbar <- sapply(F1_Low_temp, mean)
hist(F1_Low_Fbar, col="firebrick", main="Average inbreeding in F1 Low")


# We can see that all  individuals  have higher inbreeding (>0.4).
# We can recompute inbreeding for them, asking for the likelihood function to be  returned

which(F1_Low_Fbar>0.4) # all of them
F1_Low_F <- inbreeding(F1_Low, res.type="function")[which(F1_Low_Fbar>0.4)]

plot(F1_Low_F$adapter_trim.201_querydupscoord.bam, 
     main=paste("Inbreeding of individual",
                names(F1_Low_F)),
     xlab="Inbreeding (F)", 
     ylab="Probability density")


```


-   Below, we use the PCA function of adegent to create a PCA.

```{r}
oyster.pca <- glPca(mygl, nf = 3)
```

-   Let’s look at how much variance each PC explains:

```{r}
barplot(100*oyster.pca$eig/sum(oyster.pca$eig),
        col = heat.colors(50), 
        main="PCA Variance Explained")
title(ylab="Percent of variance\nexplained", 
      line = 2)
title(xlab="PC", 
      line = 1)
```

-   We basically have TWO informative PCs here. Let’s plot the individuals on the first two PCs:

```{r}
myCol <- colorplot(oyster.pca$scores,oyster.pca$scores, 
                   transp=TRUE, 
                   cex=4)
abline(h=0,
       v=0, 
       col="grey")
add.scatter.eig(oyster.pca$eig[1:10],2,1,2, 
                posi="bottomright", 
                ratio=.16)
```

-   The plot above is combining information from the first 3 PCs to color dots, and using the first two for x,y coordinates. We can see possibly four groups across all PCs.

-   We can also port this to ggplot and color by population:

```{r}
library(ggplot2)
oyster.pca.df <- as.data.frame(oyster.pca$scores)
oyster.pca.df$pop <- pop(mygl)
cols <-c("#871a1a","#33A02C","#1F78B4")

p <- ggplot(oyster.pca.df, aes(x=PC1, y=PC2, colour=pop)) 
p <- p + geom_point(size=2)
p <- p + stat_ellipse(level = 0.95, size = 1)
p <- p + scale_color_manual(values = cols) 
p <- p + geom_hline(yintercept = 0) 
p <- p + geom_vline(xintercept = 0) 
p <- p + theme_bw()

p
```

# **DAPC**

-   Discriminant analysis of Principal Components (DAPC), allows us to either infer groups or put in groups *a priori*. DAPC seeks to maximize between group variance while minimizing within group variance. I’ll show you how this works both ways below.

### **Finding clusters**

-   'Adegenet' has a built in method for inferring population groupings or clusters. It runs interactively, so this code block below won’t run on it’s own. You need to paste it into the Console.

```{r}
grp <- find.clusters(mygl, max.n.clust=10)
# choose 40 for the number of OCs to retain
```

For the purpose of picking clusters, the more PCs the better. Pick any number greater than 40.

We’d like to see an elbow here, where the lowest point would be the correct number. This doesn’t always work well for subtle structure. I’m going to pick 3 given the results above.

```{r}
grp <- find.clusters(mygl, max.n.clust=10, n.pca =100, n.clust =3)
```

We can make a simple table to see the assignments:

```{r}
table(pop(mygl), grp$grp)
```


<take some time to interpret what this means here!>

## Discriminant Analysis

This is another interactive function. Run in the console.

```{r}
oyster.dapc <- dapc(mygl, grp$grp)
```

**Now this is different than finding clusters. You can overload the analysis with two many PCs.** For this, you want to choose the lowest number that gets you > 60% of the variance. 
  - I would choose 25 or 30.

This is picking the number of discriminant functions. Because we put in four groups, there are only three.(check this if true with our data) Truly, only the first two are informative. Let’s pick 2.

```{r}
oyster.dapc <- dapc(mygl, n.pca = 25, n.da = 2, grp$grp)
```

Now, let’s plot the analysis

```{r}
scatter(oyster.dapc,col=cols,bg="white", solid=1)
```

We can also plot membership probabilities:

```{r}
compoplot(oyster.dapc, 
          posi="bottom",
          txt.leg=paste("Cluster", 1:3), 
          lab="", 
          ncol=4, 
          xlab="individuals")
```

We can use ggplot to make this easier to read and put in the populations for each individual:

```{r}
library(tidyr)
dapc.df <- as.data.frame(oyster.dapc$posterior)
dapc.df$pop <- pop(mygl)
dapc.df$indNames <- rownames(dapc.df)
cols4 <-c("#871a1a","#33A02C","#1F78B4","#FDBF6F" )

dapc.df <- pivot_longer(dapc.df, -c(pop, indNames))
colnames(dapc.df) <- c("Original_Pop","Sample","Assigned_Pop","Posterior_membership_probability")

p <- ggplot(dapc.df, aes(x=Sample, y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity') 
p <- p + scale_fill_manual(values = cols4) 
p <- p + facet_grid(~Original_Pop, scales = "free")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
p <- p + ylab("Posterior membership probability")
p
```

## DAPC with original populations

Again, instead of inferring groups, we can use our original populations.

```{r}
oyster.dapc <- dapc(mygl, 
                    n.pca = 25, 
                    n.da = 2)
scatter(oyster.dapc,
        col = cols, 
        cex = 2, 
        legend = TRUE, 
        clabel = F, 
        posi.leg = "bottomleft", 
        scree.pca = TRUE,
        posi.pca = "topleft", 
        cleg = 0.75, 
        posi.da = "topright")
```

Let’s make this better with ggplot

```{r}
dapc.df <- as.data.frame(oyster.dapc$ind.coord)
dapc.df$pop <- pop(mygl)
dapc.df$indNames <- rownames(dapc.df)

p <- ggplot(dapc.df, aes(x=LD1, 
                         y=LD2, 
                         colour=pop)) 
p <- p + geom_point(size=2)
p <- p + scale_color_manual(values = cols) 
p <- p + geom_hline(yintercept = 0) 
p <- p + geom_vline(xintercept = 0) 
p <- p + theme_bw()+ xlab("DA 1") + ylab("DA 2")+ ggtitle("DAPC with populations as groups")

p
```

**Works cited and acknowledgements**
Code for this tutorial was adapted from the following sources:
https://knausb.github.io/vcfR_documentation/
https://grunwaldlab.github.io/Population_Genetics_in_R/gbs_analysis.html
Documentation from the Adegenet R Package