---
title: "RespirationRates_calc_F1s"
author: "Samuel Gurr"
date: "3/16/2023"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
---

### Set up, load libraries and set the working directory for the entire script

```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(devtools)
library(ggpubr)
library(hrbrthemes)


# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
knitr::opts_knit$set(root.dir = 'C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis')
# getwd()
```

#### load data 

* Important: the raw data was already output with non-bias algorithm LoLinR - view RespirationRates_LoLin.R

* about raw data 

  * filter for solely relevant data by dates!  

```{r, load data} 

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
resp.data           <- read.csv(file="Output/Respiration/RR_LoLin_raw.csv", header=T) %>% 
                            dplyr::filter((Date %in% c("3/16/2023", # larvae from full reciprocal trial with F2s
                                                     "4/7/2023",  # larvae from full reciprocal trial with F3s
                                                     "4/12/2023", # larvae from full reciprocal trial with F3s 
                                                     "4/21/2023")))# larvae from full reciprocal trial with F3s 
                          
resp.ref            <- read.csv(file="Data/Physiology/Respiration/metadata/Reference_resp_ID.csv", header=T) %>% 
                              dplyr::filter((Date %in% c("3/16/2023", # larvae from full reciprocal trial with F2s
                                                     "4/7/2023",  # larvae from full reciprocal trial with F3s
                                                     "4/12/2023", # larvae from full reciprocal trial with F3s 
                                                     "4/21/2023")))# larvae from full reciprocal trial with F3s 
                          

```


### Merge master resp data frame with lengths

* view the first few lines to see if it merged well! 

* aso view the unique dates to make sure we have the right data!

```{r merge resp with length data and treatment IDs, echo=FALSE}

# merge the exp_metadata with the resp.data
resp.data_merged                       <- merge(resp.data, resp.ref) %>% # merge em! 
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% # edit the filetype string
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", 
                                                                                   "SDR_data", 
                                                                                   "LoLigo_data"))) %>% 
                                            dplyr::mutate(Date_formatted =  
                                                            gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                                            dplyr::arrange(Date_formatted,Run, Channel, .by_group = TRUE)
kable(head(resp.data_merged))
unique(resp.data_merged$Date)
# View(resp.data_merged)
```


#### Calculate blank rates, calc means by day pH_treatment

* what does this mean? 

  * we have blanks for each treatment and timepoint - blanks were run with the corresponding treated pCO2 seawater, the same seawater was used to fill the respiration chambers/plates
  
* important! below you will find custom lines where some blanks were filtered out, these were poor data (e.g. positive rates, high noise, etc.) viewed manually from viewing the raw data plots and 
the output non0bias rates

  * raw plots found in 'Output/Respiration/plots_raw'
  
  * LoLinR non-bias respiration rate data and additional raw plots found in 'Output/Respiration/plots_alpha0.4_increm15sec' 

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- resp.data_merged %>% # data.frame((merge(resp_all_raw, resp.ref)) %>%
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  dplyr::select(c('Date', 'Run', 'Channel','Filename', 'pH', 'pH','Lpc', 'Leq', 'Lz','filetype')) %>%
                  dplyr::arrange(Date, pH, .by_group = TRUE)

write.csv(blanks_all_raw, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_blanks_raw_larvae.csv")


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# mean blanks for the LoLinR output ('Lpc') ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

blanks_means <- blanks_all_raw %>% 
                       # filter out bad blanks 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_799_resp_Plate1.csv' & Channel %in% c('B3', 'D3', 'D4'))) %>% 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_873_resp_Plate2.csv' & Channel %in% ('C5'))) %>% 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_979_resp_Plate3.csv' & Channel %in% c('D1', 'D4', 'D5'))) %>% 
                       dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Run
                       #dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
                       dplyr::mutate(Lpc = case_when(Lpc > 0 & Lpc < 0.005 ~ 0,TRUE ~ Lpc)) %>% #  when LPC is positive but veery close to zero - assign as zero
                       dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)), n = n()) %>% 
                       dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                       dplyr::arrange(Date_formatted, Run, pH)

write.csv(blanks_means, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/RR_blanks_means_larvae.csv")


```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, 
                     blanks_means, 
# NOTE: this repeats for every distinct length value
                     by=c("Date", "pH", "Run", "filetype")) %>% 
# remove values with positive O2 - should be none here, double check by removing the '!' and run partial pipeline (found 9/14/2021	pH 8	LoLigo_data	CH1)
               dplyr::filter(!Lpc > 0) %>% 
# Lpc =  Lolin calculated resp (used for SMR actual rates), raw value is negative, take the absolute value and subtract from the mean blank Lpc (already abs value)
               dplyr::mutate(resp_blankStand = (abs(Lpc)) - BLANK.mean_Lpc) %>%  
               dplyr::filter(!Chamber_tank %in% 'blank')

head(Resp.Master)
```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' for larvae samples was ALWAYS 80 uL! (0.08 used below)
* 'pCO2_offspring' 'pCO2_parents'- remember this was the full reciprocal challenge - these metadata are needed for analysis!
* 'pCO2'- add pCO2 categories in replace of the categorical pH 

NOTE: all resp runs for larvae in this R script were completed with 80ul-well SDR dishes (as 'dplyr::mutate(volume = 0.08)' called below!)
```{r master resp file, echo=FALSE}
# View(Resp.Master[!is.na(Resp.Master$Length_um),])
Resp.Master_OM <- Resp.Master %>% 
                    
                    dplyr::filter(!resp_blankStand < 0) %>% # omit respiration values that are positive  
                    
                    dplyr::mutate(volume = 0.08) %>% # F2 data
                    # corrected for volume of the chamber and time (respblankstand is in minutes!)
                    dplyr::mutate(resp_mg_hr = ( (abs(resp_blankStand)) *  # currently as just mg O2 per minute - DOUBLE CHECK
                                                        (volume/1000) * # correct Liters - mg per L per min
                                                         60) )  %>% # convert rate per minutes to rate per hour
                    # convert mg L to minutes L
                    dplyr::mutate(resp_umol_hr = (resp_mg_hr*1000) / 32) %>% # convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)            
  
                    #  convert to rate per individual
                    dplyr::mutate(resp_umol_hr_indiv = (resp_umol_hr) / Num_indivs) %>% # convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)
                    
                    # pH is the pH exposed during the expeirment - dub here as pH_offspring 
                    dplyr::rename(pH_offspring = pH) %>% 
                    
                    # creant pCO2 variable for the offspring condition based on the variable pH_offspring
                    dplyr::mutate(pCO2_offspring = 
                                    case_when(pH_offspring == 8.0 ~ "500 uatm", 
                                              pH_offspring == 7.5 ~ "800 uatm",
                                              pH_offspring == 7 ~ "1200 uatm")) %>% 
                  
                    # creant pCO2 variable for the parental condition
                    dplyr::mutate(pCO2_parents = 
                                    case_when(pH_parents == 8.0 ~ "500 uatm", 
                                              pH_parents == 7.5 ~ "800 uatm",
                                              pH_parents == 7 ~ "1200 uatm")) %>% 
                    
                    dplyr::select(c(Date,
                                    pCO2_parents,pH_parents,
                                    pCO2_offspring, pH_offspring,
                                    Channel,
                                    Chamber_tank,
                                    Num_indivs,
                                    Lpc,
                                    BLANK.mean_Lpc,
                                    resp_blankStand,
                                    resp_mg_hr,
                                    resp_umol_hr,
                                    resp_umol_hr_indiv,
                                    Filename
                                    ))


```

### filter out the bad data

* what is 'bad' data and why omit? 

  * these data omitted from our master file contained rates that were **less than** the blank, this can be due to an array of demonic intrusions (air bubbles for example) or the animal simply did not respire (less likely)
  
  * Remember- we already filtered out the unreliable blanks, we can trust our corrected respiration rate values are true
  
  * we output these larvae-specific 'bad' data to view later if requested
  
```{r, diagnositcs- bad data!}
# diagnostics..
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_blankStand < 0) # call negatives - 92
nrow(Resp.outliers) # 92
write.csv(Resp.outliers, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/RR_bad_data_larvae.csv")

```


```{r Calculate Resp Rates & WRTIE CSV, echo=TRUE, message = FALSE, warning = FALSE}

#write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/RR_calc_raw_larvae.csv")

View(Resp.Master_OM)
```

