---
title: "RespirationRates_Analysis"
author: "Samuel Gurr"
date: "2023-04-20"
output: pdf_document
---

# Objectives: 

* (i) view the mean, variation, and number of samples

* (ii) plot the data 

* (ii) 

### set up load libraries and set working dir for the script 
```{r setup, include= FALSE, echo = FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(Rmisc)
library(devtools)
library(ggpubr)
library(SciViews)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis")


```

# load the data 

* these data are the calculated rates, not the raw! 

  * 'raw' rates achieved from the script RespirationRates_LoLin.R

  * 'calc_raw' meaning subtracted from blanks and corrected for vessel volume - view the script RespirationRates_calc_larvae.Rmd


```{r}
# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

RR_master <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/data/RR_calc_raw_larvae.csv", header=T)

RR_master_F2_Dhinge <- RR_master %>% dplyr::filter(Date %in% '3/16/2023')
RR_master_F3_Dhinge <- RR_master %>% dplyr::filter(Date %in% '4/7/2023')
RR_master_F3_7day   <- RR_master %>% dplyr::filter(Date %in% '4/12/2023')
RR_master_F3_16day   <- RR_master %>% dplyr::filter(Date %in% '4/21/2023')
```

# DATA ANALYSIS

### Summary tables

* lets look at the means, variation, and replication within each stage!

```{r respiration rates at each time point, echo = FALSE}

F2_Dhinge_SumTable <- RR_master_F2_Dhinge %>%  
            summarySE(measurevar="resp_umol_hr_indiv", groupvars=c("Date","pCO2_parents", "pCO2_offspring")) %>% 
            dplyr::arrange(resp_umol_hr_indiv)
F2_Dhinge_SumTable # lowest are naive parents under mid and high; highest are habituated parents under low!

F3_Dhinge_SumTable <- RR_master_F3_Dhinge %>%  
            summarySE(measurevar="resp_umol_hr_indiv", groupvars=c("Date","pCO2_parents", "pCO2_offspring")) %>% 
            dplyr::arrange(resp_umol_hr_indiv)
F3_Dhinge_SumTable


F3_7day_SumTable <- RR_master_F3_7day %>%  
            summarySE(measurevar="resp_umol_hr_indiv", groupvars=c("Date","pCO2_parents", "pCO2_offspring")) %>% 
            dplyr::arrange(resp_umol_hr_indiv)
F3_7day_SumTable


F3_16day_SumTable <- RR_master_F3_16day %>%  
            summarySE(measurevar="resp_umol_hr_indiv", groupvars=c("Date","pCO2_parents", "pCO2_offspring")) %>% 
            dplyr::arrange(resp_umol_hr_indiv)
F3_16day_SumTable

```


# F2 D hinge figures 

###  Date 20230316 

```{r, Fig F2 larvae RR per indiv, echo = FALSE, results='hide',message = FALSE, warning = FALSE}

RR_master_F2_Dhinge$pCO2_parents   <- factor(RR_master_F2_Dhinge$pCO2_parents, levels = c("500 uatm", "800 uatm"))
RR_master_F2_Dhinge$pCO2_offspring <- factor(RR_master_F2_Dhinge$pCO2_offspring, levels = c("500 uatm", "800 uatm", "1200 uatm"))
 
# PLOT
F2_Dinge_BOXPLOT <- RR_master_F2_Dhinge %>% 
                    dplyr::filter(!resp_umol_hr_indiv > 0.0002) %>% 
                    ggplot(aes(x = factor(pCO2_parents), 
                               y = resp_umol_hr_indiv, 
                               colour = pCO2_offspring,
                               fill = pCO2_parents)) +
                           geom_boxplot(alpha = 0.5,  # color hue
                               width=0.6, # boxplot width
                               outlier.size=0, # make outliers small
                               position = position_dodge(preserve = "single")) + 
                           geom_point(pch = 19, 
                                      position = position_jitterdodge(0.5), 
                                      size=1) +
                           scale_fill_manual(values=c("white", "grey75")) +
                           scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                           theme_classic() + 
                           ggtitle("F2 Dhinge 20230316 (parent pCO2)") +
                           theme(axis.title.y=element_text(size=7),
                                 axis.title.x=element_text(size=7),
                                 axis.text.x=element_text(size=7)) +
                           #ylim(0, 0.2) +
                           stat_summary(fun.y=mean, 
                                        geom = "errorbar", 
                                        aes(ymax = ..y.., ymin = ..y..), 
                                        width = 0.6, 
                                        size=0.4, 
                                        linetype = "dashed", 
                                        position = position_dodge(preserve = "single")) +
                           facet_wrap(~pCO2_offspring) #, scales = "free)



F2_Dinge_BOXPLOT_Parent <- RR_master_F2_Dhinge %>% 
                            dplyr::filter(!resp_umol_hr_indiv > 0.0002) %>% 
                            ggplot(aes(x = factor(pCO2_parents), 
                                       y = resp_umol_hr_indiv, 
                                       fill = pCO2_parents)) +
                                   geom_boxplot(alpha = 0.5, # color hue
                                       width=0.6, # boxplot width
                                       outlier.size=0, # make outliers small
                                       position = position_dodge(preserve = "single")) + 
                                   geom_point(pch = 19, 
                                              position = position_jitterdodge(0.5), 
                                              size=1) +
                                   # geom_jitter(width=0.2, size=2) +
                                   scale_fill_manual(values=c("white", "grey75")) +
                                   #scale_colour_manual(values=c("forestgreen","orange")) +
                                   theme_classic() + 
                                   ggtitle("F2 Dhinge 20230316 (larvaepCO2 x parentpCO2)") +
                                   xlab("Respiration rates - Dhinge larvae") +
                                   theme(axis.title.y=element_text(size=7),
                                         axis.title.x=element_text(size=7),
                                         axis.text.x=element_text(size=7)) +
                                   #ylim(0, 0.2) +
                                   stat_summary(fun.y=mean, 
                                                geom = "errorbar", 
                                                aes(ymax = ..y.., ymin = ..y..), 
                                                width = 0.6, 
                                                size=0.4, 
                                                linetype = "dashed", 
                                                position = position_dodge(preserve = "single")) 

# VIEW THE PLOT 
ggarrange(F2_Dinge_BOXPLOT_Parent, F2_Dinge_BOXPLOT, nrow = 2)

# OUTPUT THE PLOT
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/plots/F2_RR_larvae.pdf"), width = 8, height = 8)
ggarrange(F2_Dinge_BOXPLOT_Parent, F2_Dinge_BOXPLOT, nrow = 2)
dev.off()
```


# F3 D hinge figures

###  Date 20230407 - 2 DPF (days post fertilization)

```{r, Fig F3 larvae RR per indiv, echo = FALSE, results='hide',message = FALSE, warning = FALSE}

RR_master_F3_Dhinge$pCO2_parents   <- factor(RR_master_F3_Dhinge$pCO2_parents, levels = c("500 uatm", "800 uatm", "1200 uatm"))
RR_master_F3_Dhinge$pCO2_offspring <- factor(RR_master_F3_Dhinge$pCO2_offspring, levels = c("500 uatm", "800 uatm", "1200 uatm"))


F3_Dinge_BOXPLOT_Parent <- RR_master_F3_Dhinge %>% 
                            dplyr::filter(!resp_umol_hr_indiv > 0.0004) %>% # omits a single dramatic outlier
                            ggplot(aes(x = factor(pCO2_parents), 
                                       y = resp_umol_hr_indiv, 
                                       fill = pCO2_parents)) +
                                   geom_boxplot(alpha = 0.5, # color hue
                                       width=0.6, # boxplot width
                                       outlier.size=0, # make outliers small
                                       position = position_dodge(preserve = "single")) + 
                                   geom_point(pch = 19, 
                                              position = position_jitterdodge(0.5), 
                                              size=1) +
                                   scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                   #scale_colour_manual(values=c("forestgreen","orange")) +
                                   theme_classic() + 
                                   ggtitle("F3 Dhinge 20230407 (parentpCO2)") +
                                   theme(axis.title.y=element_text(size=7),
                                         axis.title.x=element_text(size=7),
                                         axis.text.x=element_text(size=7),
                                         legend.position = "none") +
                                   #ylim(0, 0.2) +
                                   stat_summary(fun.y=mean, 
                                                geom = "errorbar", 
                                                aes(ymax = ..y.., ymin = ..y..), 
                                                width = 0.6, 
                                                size=0.4, 
                                                linetype = "dashed", 
                                                position = position_dodge(preserve = "single")) 


F3_Dhinge_BOXPLOT_Offspring <- RR_master_F3_Dhinge %>% 
                                dplyr::filter(!resp_umol_hr_indiv > 0.0004) %>% # omits a single dramatic outlier
                                ggplot(aes(x = factor(pCO2_offspring), 
                                           y = resp_umol_hr_indiv, 
                                           colour = pCO2_offspring)) +
                                       geom_boxplot(alpha = 0.5, # color hue
                                           width=0.6, # boxplot width
                                           outlier.size=0, # make outliers small
                                           position = position_dodge(preserve = "single")) + 
                                       geom_point(pch = 19, 
                                                  position = position_jitterdodge(0.5), 
                                                  size=1) +
                                       scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                       ggtitle("F3 Dhinge 20230407 (larvaepCO2)") +
                                       theme_classic() + 
                                       theme(axis.title.y=element_text(size=7),
                                             axis.title.x=element_text(size=7),
                                             axis.text.x=element_text(size=7),
                                             legend.position = "none") +
                                       #ylim(0, 0.2) +
                                       stat_summary(fun.y=mean, 
                                                    geom = "errorbar", 
                                                    aes(ymax = ..y.., ymin = ..y..), 
                                                    width = 0.6, 
                                                    size=0.4, 
                                                    linetype = "dashed", 
                                                    position = position_dodge(preserve = "single")) 

F3_Dinge_BOXPLOT_ParentxOffspring <- RR_master_F3_Dhinge %>% 
                                        dplyr::filter(!resp_umol_hr_indiv > 0.0004) %>%  # omits a single dramatic outlier
                                        ggplot(aes(x = factor(pCO2_parents), 
                                                   y = resp_umol_hr_indiv, 
                                                   colour = pCO2_offspring,
                                                   fill = pCO2_parents)) +
                                               geom_boxplot(alpha = 0.5,  # color hue
                                                   width=0.6, # boxplot width
                                                   outlier.size=0, # make outliers small
                                                   position = position_dodge(preserve = "single")) + 
                                               geom_point(pch = 19, 
                                                          position = position_jitterdodge(0.5), 
                                                          size=1) +
                                               scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                               scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                               theme_classic() + 
                                               ggtitle("F3 Dhinge 20230407 (larvaepCO2 x parentpCO2)") +
                                               # ggtitle("F3 Respiration rates - Dhinge larvae 20230407") +
                                               theme(axis.title.y=element_text(size=7),
                                                     axis.title.x=element_text(size=7),
                                                     axis.text.x=element_text(size=7)) +
                                               #ylim(0, 0.2) +
                                               stat_summary(fun.y=mean, 
                                                            geom = "errorbar", 
                                                            aes(ymax = ..y.., ymin = ..y..), 
                                                            width = 0.6, 
                                                            size=0.4, 
                                                            linetype = "dashed", 
                                                            position = position_dodge(preserve = "single")) +
                                               facet_wrap(~pCO2_offspring) #, scales = "free)


# VIEW PLOTS 
ggarrange( (ggarrange(F3_Dinge_BOXPLOT_Parent, F3_Dhinge_BOXPLOT_Offspring, ncol=2)),
           F3_Dinge_BOXPLOT_ParentxOffspring, nrow = 2)
# save plots 
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/plots/F3_RR_larvae_2DPF.pdf"), width = 8, height = 8)
ggarrange( (ggarrange(F3_Dinge_BOXPLOT_Parent, F3_Dhinge_BOXPLOT_Offspring, ncol=2)),
           F3_Dinge_BOXPLOT_ParentxOffspring, nrow = 2)
dev.off()

```


### Date 20230412 - 7 DPF (days post fertilization)


#### Figures 20230412, F3 7 DPF

```{r, Fig F3 larvae RR 7 DPF, echo = FALSE, results='hide',message = FALSE, warning = FALSE}

# Prep data for the  7 day larvae from 20230412
RR_master_F3_7day$pCO2_parents   <- factor(RR_master_F3_7day$pCO2_parents, levels = c("500 uatm", "800 uatm", "1200 uatm"))
RR_master_F3_7day$pCO2_offspring <- factor(RR_master_F3_7day$pCO2_offspring, levels = c("500 uatm", "800 uatm", "1200 uatm"))
 
# two data points near 0 
RR_master_F3_7day %>% dplyr::filter(resp_umol_hr_indiv > 0.0005)


# PLOT 7 day larvae from 20230412
F3_7day_BOXPLOT_Parent <- RR_master_F3_7day %>% 
                            dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>%  # omits two dramatic outliers CHECK THESE!
                            ggplot(aes(x = factor(pCO2_parents), 
                                       y = resp_umol_hr_indiv, 
                                       fill = pCO2_parents)) +
                                   geom_boxplot(alpha = 0.5, # color hue
                                       width=0.6, # boxplot width
                                       outlier.size=0, # make outliers small
                                       position = position_dodge(preserve = "single")) + 
                                   geom_point(pch = 19, 
                                              position = position_jitterdodge(0.5), 
                                              size=1) +
                                   scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                   #scale_colour_manual(values=c("forestgreen","orange")) +
                                   theme_classic() + 
                                   ggtitle("F3 7 DPF 20230412 (parentpCO2)") +
                                   xlab("Respiration rates - 7 day larvae") +
                                   theme(axis.title.y=element_text(size=7),
                                         axis.title.x=element_text(size=7),
                                         axis.text.x=element_text(size=7),
                                         legend.position = "none") +
                                   #ylim(0, 0.2) +
                                   stat_summary(fun.y=mean, 
                                                geom = "errorbar", 
                                                aes(ymax = ..y.., ymin = ..y..), 
                                                width = 0.6, 
                                                size=0.4, 
                                                linetype = "dashed", 
                                                position = position_dodge(preserve = "single")) 

F3_7day_BOXPLOT_Offspring <- RR_master_F3_7day %>% 
                              dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>%  # omits two dramatic outliers CHECK THESE!
                              ggplot(aes(x = factor(pCO2_offspring), 
                                         y = resp_umol_hr_indiv, 
                                         colour = pCO2_offspring)) +
                                     geom_boxplot(alpha = 0.5, # color hue
                                         width=0.6, # boxplot width
                                         outlier.size=0, # make outliers small
                                         position = position_dodge(preserve = "single")) + 
                                     geom_point(pch = 19, 
                                                position = position_jitterdodge(0.01), 
                                                size=1) +
                                     scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                     ggtitle("F3 7 DPF 20230412 (larvaepCO2)") +
                                     theme_classic() + 
                                     theme(axis.title.y=element_text(size=7),
                                           axis.title.x=element_text(size=7),
                                           axis.text.x=element_text(size=7),
                                           legend.position = "none") +
                                     #ylim(0, 0.2) +
                                     stat_summary(fun.y=mean, 
                                                  geom = "errorbar", 
                                                  aes(ymax = ..y.., ymin = ..y..), 
                                                  width = 0.6, 
                                                  size=0.4, 
                                                  linetype = "dashed", 
                                                  position = position_dodge(preserve = "single")) 

F3_7day_BOXPLOT_ParentxOffspring <- RR_master_F3_7day %>% 
                                        dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>%  # omits two dramatic outliers CHECK THESE!
                                        ggplot(aes(x = factor(pCO2_offspring), 
                                                   y = resp_umol_hr_indiv, 
                                                   colour = pCO2_offspring,
                                                   fill = pCO2_parents)) +
                                               geom_boxplot(alpha = 0.5,  # color hue
                                                   width=0.6, # boxplot width
                                                   outlier.size=0, # make outliers small
                                                   position = position_dodge(preserve = "single")) + 
                                               geom_point(pch = 19, 
                                                          position = position_jitterdodge(0.5), 
                                                          size=1) +
                                               scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                               scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                               theme_classic() + 
                                               ggtitle("F3 7 DPF 20230412 (larvaepCO2 x parentpCO2)") +
                                               # ggtitle("F3 Respiration rates - 7 day larvae 20230412") +
                                               theme(axis.title.y=element_text(size=7),
                                                     axis.title.x=element_text(size=7),
                                                     axis.text.x=element_text(size=7)) +
                                               #ylim(0, 0.2) +
                                               stat_summary(fun.y=mean, 
                                                            geom = "errorbar", 
                                                            aes(ymax = ..y.., ymin = ..y..), 
                                                            width = 0.6, 
                                                            size=0.4, 
                                                            linetype = "dashed", 
                                                            position = position_dodge(preserve = "single")) +
                                               facet_wrap(~pCO2_parents) #, scales = "free)

# VIEW PLOTS 
ggarrange( (ggarrange(F3_7day_BOXPLOT_Parent, F3_7day_BOXPLOT_Offspring, ncol=2)),
           F3_7day_BOXPLOT_ParentxOffspring, nrow = 2)
# sdve plots 
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/plots/F3_RR_larvae_7DPF.pdf"), width = 8, height = 8)
ggarrange( (ggarrange(F3_7day_BOXPLOT_Parent, F3_7day_BOXPLOT_Offspring, ncol=2)),
           F3_7day_BOXPLOT_ParentxOffspring, nrow = 2)
dev.off()

```


#### Stats 20230412, F3 7 DPF


```{r, stats F3 7 DPF}




# full model



RR_F3_7DPF_full.mod <- lm(resp_umol_hr_indiv ~ pCO2_parents * pCO2_offspring,
                          data = (RR_master_F3_7day %>% dplyr::filter(!resp_umol_hr_indiv > 0.0005)) )

shapiro.test(resid(RR_F3_7DPF_full.mod)) # 0.03848 - non-normal
leveneTest(RR_F3_7DPF_full.mod) # 0.2965 - homogeneity of variance pass
summary(aov(RR_F3_7DPF_full.mod))
#                             Df    Sum Sq   Mean Sq F value Pr(>F)
# pCO2_parents                 2 2.773e-08 1.386e-08   1.390  0.278
# pCO2_offspring               2 2.370e-08 1.185e-08   1.188  0.330
# pCO2_parents:pCO2_offspring  4 1.614e-08 4.034e-09   0.404  0.803
# Residuals                   16 1.596e-07 9.978e-09





# within histories 




### low pCO2
RR_F3_7DPF_Lowhist.mod <- lm(resp_umol_hr_indiv ~ pCO2_offspring,
                          data = (RR_master_F3_7day %>% 
                                    dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>% 
                                    dplyr::filter(pCO2_parents %in% '500 uatm')) )

shapiro.test(resid(RR_F3_7DPF_Lowhist.mod)) # 0.2857 - normal
leveneTest(RR_F3_7DPF_Lowhist.mod) # 0.3293 - homogeneity of variance pass
summary(aov(RR_F3_7DPF_Lowhist.mod))
#                Df    Sum Sq   Mean Sq F value Pr(>F)
# pCO2_offspring  2 2.078e-08 1.039e-08   0.791  0.495
# Residuals       6 7.878e-08 1.313e-08





### moderate pCO2
RR_F3_7DPF_Moderatehist.mod <- lm(resp_umol_hr_indiv ~ pCO2_offspring,
                          data = (RR_master_F3_7day %>% 
                                    dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>% 
                                    dplyr::filter(pCO2_parents %in% '800 uatm')) )

shapiro.test(resid(RR_F3_7DPF_Moderatehist.mod)) # 0.9895 - normal
leveneTest(RR_F3_7DPF_Moderatehist.mod) # 0.4294 - homogeneity of variance pass
summary(aov(RR_F3_7DPF_Moderatehist.mod))
#                Df    Sum Sq   Mean Sq F value Pr(>F)  
# pCO2_offspring  2 1.426e-08 7.129e-09   13.09 0.0176 *
# Residuals       4 2.179e-09 5.450e-10
TukeyHSD(aov(RR_F3_7DPF_Moderatehist.mod))
# $pCO2_offspring
#                             diff           lwr          upr     p adj
# 800 uatm-500 uatm  -2.592220e-06 -7.852437e-05 7.333993e-05 0.9918885
# 1200 uatm-500 uatm  9.832117e-05  1.514167e-05 1.815007e-04 0.0292334
# 1200 uatm-800 uatm  1.009134e-04  2.498124e-05 1.768455e-04 0.0196851




### high pCO2
RR_F3_7DPF_Highhist.mod <- lm(resp_umol_hr_indiv ~ pCO2_offspring,
                          data = (RR_master_F3_7day %>% 
                                    dplyr::filter(!resp_umol_hr_indiv > 0.0005) %>% 
                                    dplyr::filter(pCO2_parents %in% '1200 uatm')) )

shapiro.test(resid(RR_F3_7DPF_Highhist.mod)) # 0.8153 - normal
leveneTest(RR_F3_7DPF_Highhist.mod) # 0.3722 - homogeneity of variance pass
summary(aov(RR_F3_7DPF_Highhist.mod))
#                Df    Sum Sq   Mean Sq F value Pr(>F)
# pCO2_offspring  2 4.800e-09 2.398e-09   0.183  0.837
# Residuals       6 7.868e-08 1.311e-08

```



### Date 20230421 - 16 DPF (pdays post fertilization)


```{r, Fig F3 larvae RR 16 DPF, echo = FALSE, results='hide',message = FALSE, warning = FALSE}

# Prep data for the  16 day larvae from 20230421

RR_master_F3_16day$pCO2_parents   <- factor(RR_master_F3_16day$pCO2_parents, levels = c("500 uatm", "800 uatm", "1200 uatm"))
RR_master_F3_16day$pCO2_offspring <- factor(RR_master_F3_16day$pCO2_offspring, levels = c("500 uatm", "800 uatm", "1200 uatm"))

 
# PLOT 16 day larvae from 20230421

F3_16day_BOXPLOT_Parent <- RR_master_F3_16day %>% 
                            ggplot(aes(x = factor(pCO2_parents), 
                                       y = resp_umol_hr_indiv, 
                                       fill = pCO2_parents)) +
                                   geom_boxplot(alpha = 0.5, # color hue
                                       width=0.6, # boxplot width
                                       outlier.size=0, # make outliers small
                                       position = position_dodge(preserve = "single")) + 
                                   geom_point(pch = 19, 
                                              position = position_jitterdodge(0.5), 
                                              size=1) +
                                   scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                   #scale_colour_manual(values=c("forestgreen","orange")) +
                                   theme_classic() + 
                                   ggtitle("F3 Dhinge 20230421 (parentpCO2)") +
                                   xlab("Respiration rates - 16 day larvae") +
                                   theme(axis.title.y=element_text(size=7),
                                         axis.title.x=element_text(size=7),
                                         axis.text.x=element_text(size=7),
                                         legend.position = "none") +
                                   #ylim(0, 0.2) +
                                   stat_summary(fun.y=mean, 
                                                geom = "errorbar", 
                                                aes(ymax = ..y.., ymin = ..y..), 
                                                width = 0.6, 
                                                size=0.4, 
                                                linetype = "dashed", 
                                                position = position_dodge(preserve = "single")) 

F3_16day_BOXPLOT_Offspring <- RR_master_F3_16day %>% 
                                    ggplot(aes(x = factor(pCO2_offspring), 
                                               y = resp_umol_hr_indiv, 
                                               colour = pCO2_offspring)) +
                                           geom_boxplot(alpha = 0.5, # color hue
                                               width=0.6, # boxplot width
                                               outlier.size=0, # make outliers small
                                               position = position_dodge(preserve = "single")) + 
                                           geom_point(pch = 19, 
                                                      position = position_jitterdodge(0.5), 
                                                      size=1) +
                                           scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                           ggtitle("F3 Dhinge 20230421 larvaepCO2)") +
                                           theme_classic() + 
                                           theme(axis.title.y=element_text(size=7),
                                                 axis.title.x=element_text(size=7),
                                                 axis.text.x=element_text(size=7),
                                                 legend.position = "none") +
                                           #ylim(0, 0.2) +
                                           stat_summary(fun.y=mean, 
                                                        geom = "errorbar", 
                                                        aes(ymax = ..y.., ymin = ..y..), 
                                                        width = 0.6, 
                                                        size=0.4, 
                                                        linetype = "dashed", 
                                                        position = position_dodge(preserve = "single")) 

F3_16day_BOXPLOT_ParentxOffspring <- RR_master_F3_16day %>% 
                                      ggplot(aes(x = factor(pCO2_parents), 
                                                 y = resp_umol_hr_indiv, 
                                                 colour = pCO2_offspring,
                                                 fill = pCO2_parents)) +
                                             geom_boxplot(alpha = 0.5,  # color hue
                                                 width=0.6, # boxplot width
                                                 outlier.size=0, # make outliers small
                                                 position = position_dodge(preserve = "single")) + 
                                             geom_point(pch = 19, 
                                                        position = position_jitterdodge(0.5), 
                                                        size=1) +
                                             scale_fill_manual(values=c("white", "grey60", "grey15")) +
                                             scale_colour_manual(values=c("forestgreen","orange", "purple")) +
                                             theme_classic() + 
                                             ggtitle("F3 Dhinge 20230421 (larvae x parentpCO2)") +
                                             theme(axis.title.y=element_text(size=7),
                                                   axis.title.x=element_text(size=7),
                                                   axis.text.x=element_text(size=7)) +
                                             #ylim(0, 0.2) +
                                             stat_summary(fun.y=mean, 
                                                          geom = "errorbar", 
                                                          aes(ymax = ..y.., ymin = ..y..), 
                                                          width = 0.6, 
                                                          size=0.4, 
                                                          linetype = "dashed", 
                                                          position = position_dodge(preserve = "single")) +
                                             facet_wrap(~pCO2_offspring) #, scales = "free)

# VIEW PLOTS 
ggarrange( (ggarrange(F3_16day_BOXPLOT_Parent, F3_16day_BOXPLOT_Offspring, ncol=2)),
           F3_16day_BOXPLOT_ParentxOffspring, nrow = 2)
# sdve plots 
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/Larvae/plots/F3_RR_larvae_16DPF.pdf"), width = 8, height = 8)
ggarrange( (ggarrange(F3_16day_BOXPLOT_Parent, F3_16day_BOXPLOT_Offspring, ncol=2)),
           F3_16day_BOXPLOT_ParentxOffspring, nrow = 2)
dev.off()

```


# STANDARDIZE AND STATISTICAL ANALYSIS 


``` {r, standardize & ANOVA stats,echo = FALSE, results='hide',message = FALSE, warning = FALSE}
par(mfrow = c(2, 2)) # a two by two grid for model diagnostics! 

aov_mod <- aov(lm(resp_umol_hr_indiv~ pCO2_parents*pCO2_offspring, data = RR_master))
plot(aov_mod)
shapiro.test(resid(aov_mod)) # 0.003548
leveneTest(aov_mod) # 0.6297
hist(resid(aov_mod)) # left skew
qqnorm(resid(aov_mod))


RR_master_outlierOM <- RR_master %>% dplyr::filter(!resp_umol_hr_indiv > 0.0002) 
aov_mod_outlierOM <- aov(lm((resp_umol_hr_indiv)~ pCO2_parents*pCO2_offspring, data = RR_master_outlierOM))
shapiro.test(resid(aov_mod_outlierOM)) # 0.3301
leveneTest(aov_mod_outlierOM) # 0.706
hist(resid(aov_mod_outlierOM)) # left skew

summary(aov_mod_outlierOM)
#                              Df    Sum Sq   Mean Sq F value Pr(>F)
# pCO2_parents                 1 1.399e-09 1.399e-09   2.243  0.145
# pCO2_offspring               2 1.016e-09 5.078e-10   0.814  0.453
# pCO2_parents:pCO2_offspring  2 9.720e-10 4.862e-10   0.780  0.468
# Residuals                   28 1.747e-08 6.237e-10

aov_mod_parents <- aov(lm(resp_umol_hr_indiv~ pCO2_parents, data = RR_master))
summary(aov_mod_parents)



RR_master_800uatm_parents <- RR_master %>%  dplyr::filter(pCO2_parents %in% "800 uatm") %>% dplyr::filter(!resp_umol_hr_indiv > 0.0002) 
aov_mod_800uatmParents <- aov(lm(resp_umol_hr_indiv~ pCO2_offspring, data = RR_master_800uatm_parents))
shapiro.test(resid(aov_mod_800uatmParents)) # 0.2078
leveneTest(aov_mod_800uatmParents) # 0.5813
summary(aov_mod_800uatmParents)

aov_mod_800uatmParents_SQRT <- aov(lm(sqrt(resp_umol_hr_indiv)~ pCO2_offspring, data = RR_master_800uatm_parents))
shapiro.test(resid(aov_mod_800uatmParents_SQRT)) # 0.3995
leveneTest(aov_mod_800uatmParents_SQRT) # 0.824
summary(aov_mod_800uatmParents_SQRT)


```