---
title: "RespirationRates_calc_F1s"
author: "Samuel Gurr"
date: "3/16/2023"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::
library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(devtools)
library(ggpubr)
library(hrbrthemes)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis") # personal computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_parentXoffspring_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
resp.data           <- read.csv(file="Output/Respiration/RR_LoLin_raw.csv", header=T) %>% 
                            dplyr::filter((Date %in% c("3/16/2023", # larvae from full reciprocal trial with F2s
                                                     "4/7/2023",  # larvae from full reciprocal trial with F3s
                                                     "4/12/2023")))# larvae from full reciprocal trial with F3s 
                          
resp.ref            <- read.csv(file="Data/Physiology/Respiration/Reference_resp_ID.csv", header=T) %>% 
                              dplyr::filter((Date %in% c("3/16/2023", # larvae from full reciprocal trial with F2s
                                                     "4/7/2023",  # larvae from full reciprocal trial with F3s
                                                     "4/12/2023")))# larvae from full reciprocal trial with F3s 
                          

```


### Merge master resp data frame with lengths

```{r merge resp with length data and treatment IDs, echo=FALSE}


# merge the exp_metadata with the resp.data
resp.data_merged                       <- merge(resp.data, resp.ref) %>% 
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", 
                                                                                   "SDR_data", 
                                                                                   "LoLigo_data"))) %>% 
                                            dplyr::mutate(Date_formatted =  
                                                            gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                                            dplyr::arrange(Date_formatted,Run, Channel, .by_group = TRUE)
kable(head(resp.data_merged))
unique(resp.data_merged$Date)
# View(resp.data_merged)
```


#### Calculate blank rates, view means by day pH_treatment and instrument

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- resp.data_merged %>% # data.frame((merge(resp_all_raw, resp.ref)) %>%
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  dplyr::select(c('Date', 'Run', 'Channel','Filename', 'pH', 'pH','Lpc', 'Leq', 'Lz','filetype')) %>%
                  dplyr::arrange(Date, pH, .by_group = TRUE)

write.csv(blanks_all_raw, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_blanks_raw_larvae.csv")


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# mean blanks for the LoLinR output ('Lpc') ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

blanks_means <- blanks_all_raw %>% 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_799_resp_Plate1.csv' & Channel %in% c('B3', 'D3', 'D4'))) %>% 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_873_resp_Plate2.csv' & Channel %in% ('C5'))) %>% 
                       dplyr::filter(!(Date %in% "3/16/2023" & Filename == 'SDR_979_resp_Plate3.csv' & Channel %in% c('D1', 'D4', 'D5'))) %>% 
                       dplyr::group_by(Date, pH, Run, filetype) %>% # grouped by date, pH, and instrument - similar among Run
                       #dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
                       dplyr::mutate(Lpc = case_when(Lpc > 0 & Lpc < 0.005 ~ 0,TRUE ~ Lpc)) %>% #  when LPC is positive but veery close to zero - assign as zero
                       dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)), n = n()) %>% 
                       dplyr::mutate(Date_formatted =  gsub("-", "", substr( (strptime(Date, "%m/%d/%Y")), 1,10)) ) %>% 
                       dplyr::arrange(Date_formatted, Run, pH)

write.csv(blanks_means, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_blanks_means_larvae.csv")


```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH", "Run", "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::filter(!Lpc > 0) %>% # remove values with positive O2 - should be none here, double check by removing the '!' and run partial pipeline (found 9/14/2021	pH 8	LoLigo_data	CH1)
  dplyr::mutate(resp_blankStand = (abs(Lpc)) - BLANK.mean_Lpc) %>%  # Lpc =  Lolin calculated resp (used for SMR actual rates), raw value is negative, take the absolute value and subtract from the mean blank Lpc (already abs value)
  dplyr::filter(!Chamber_tank %in% 'blank')
```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
* 'Fed_unfed'
* 'pCO2'

NOTE: all resp runs for larva ein this R script were completed with 80ul-well SDR dishes (as 'dplyr::mutate(volume = 0.08)' called below!)
```{r master resp file, echo=FALSE}
# View(Resp.Master[!is.na(Resp.Master$Length_um),])
Resp.Master_OM <- Resp.Master %>% 
  
  dplyr::filter(!resp_blankStand < 0) %>% # ommit respiration values that are positive  
  
  dplyr::mutate(volume = 0.08) %>% # F2 data
  # corrected for volume of the chamber and time (respblankstand is in minutes!)
  dplyr::mutate(resp_mg_hr   = ( (abs(resp_blankStand)) *  # currently as just mg O2 per minute - DOUBLE CHECK
                                      (volume/1000) * # correct Liters - mg per L per min
                                       60) )  %>% # convert rate per minutes to rate per hour
  # convert mg L to minutes L
  dplyr::mutate(resp_umol_hr = (resp_mg_hr*1000) / 32) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                                
  #  convert to rate per individual
  dplyr::mutate(resp_umol_hr_indiv = (resp_umol_hr) / Num_indivs) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)     
  
  # pH is the pH exposed during the expeirment - dub here as pH_offspring 
  dplyr::rename(pH_offspring = pH) %>% 
  
  # creant pCO2 variable for the offspring condition based on the variable pH_offspring
  dplyr::mutate(pCO2_offspring = 
                  case_when(pH_offspring == 8.0 ~ "500 uatm", 
                            pH_offspring == 7.5 ~ "800 uatm",
                            pH_offspring == 7 ~ "1200 uatm")) %>% 

  # creant pCO2 variable for the parental condition
  dplyr::mutate(pCO2_parents = 
                  case_when(pH_parents == 8.0 ~ "500 uatm", 
                            pH_parents == 7.5 ~ "800 uatm",
                            pH_parents == 7 ~ "1200 uatm")) %>% 
  
  dplyr::select(c(Date,
                  pCO2_parents,pH_parents,
                  pCO2_offspring, pH_offspring,
                  Channel,
                  Chamber_tank,
                  Num_indivs,
                  Lpc,
                  BLANK.mean_Lpc,
                  resp_blankStand,
                  resp_mg_hr,
                  resp_umol_hr,
                  resp_umol_hr_indiv,
                  Filename
                  ))
# diagnostics..
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_blankStand < 0) # call negatives - 66
nrow(Resp.outliers) # 66
write.csv(Resp.outliers, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_bad_data_larvae.csv")

```


```{r Calculate Resp Rates & WRTIE CSV, echo=TRUE, message = FALSE, warning = FALSE}

#write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Output/Respiration/RR_calc_raw_larvae.csv")


View(Resp.Master_OM)
```

