---
title: "Bay Scallop Larve - D Stage Abnormality Rates"
author: "Katie McFarland"
date: "12/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(rcompanion)
library(FSA)
library(car)
```


```{r}
#Set Path
# setwd("C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB-Airradians_multigen_OA/larvae")
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_multigen_OA/RAnalysis/Larvae")
```

### Load Data
```{r}
#Here we are assing our data fram the name "df" so that we do not have to type out the full file name everytime we want to call it.
df<-read.csv("Dstage.data.csv", header = T)

df$Percent.deformed=as.numeric(df$Percent.deformed)

dfParent=as.factor(df$Parent)
dfTtreatment=as.factor(df$Treatment)
df$Rep=as.factor(df$Rep)
df$Year=as.factor(df$Year)
df$Run=as.factor(df$Run)

df$Treatment <- factor(df$Treatment,levels = c("Low OA", "Moderate OA", "High OA"))

df$Parent <- factor(df$Parent,levels = c("Wild", "LOW", "MODERATE", "HIGH"))

#to look at columns names of your data frame
head(df)

#Sturcture of the data - to check that variables are properly assigned to facotr or variable
str(df)
```

```{r}

#df$Par_Off <- paste("Par:",df$Parent, " ", "Off:", df$Treatment)


ggplot(data=df, aes(x=Run, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed, grouped by parentage (2023: F3 Larvae) ", x ="Generation", y = "Percent Deformed")+
 # facet_wrap(~Par_Off)
  facet_wrap(~Parent+Treatment)
```

```{r}
df$Percent.deformed_trans <- asin(sqrt(df$Percent.deformed))

leveneTest(Percent.deformed_trans ~ Treatment, data=df)
shapiro.test(df$Percent.deformed_trans)
```



# Stats across genrations
Data did not meet the assumptions of normality so the non parametric Scheirer Ray Hare test was used to test for signifcance among treatments and prental exposures.
```{r}
scheirerRayHare(Percent.deformed ~ Treatment*Run,
                data = df)

scheirerRayHare(Percent.deformed ~ Treatment*Parent,
                data = df)

scheirerRayHare(Percent.deformed ~ Run*Parent,
                data = df)

dunnTest(Percent.deformed ~ Run,
                data = df,
              method="bh")
```


### Low parental exposure across generations (all larval treatmeents)
```{r}
df_low <- df%>%
  filter(Parent %in% c("LOW"))

leveneTest(Percent.deformed_trans ~ Run, data=df_low)
shapiro.test(df_low$Percent.deformed_trans)

scheirerRayHare(Percent.deformed ~ Treatment*Run,
                data = df_low)


dunnTest(Percent.deformed ~ Run,
                data = df_low,
              method="bh")
```

### Low larval exposure and Low parental exposure ("control") across generations
```{r}

df_low_low <- df_low%>%
  filter(Treatment %in% c("Low OA"))

leveneTest(Percent.deformed_trans ~ Run, data=df_low_low)
shapiro.test(df_low_low$Percent.deformed_trans)

mod <- aov(Percent.deformed_trans ~Run, data = df_low_low)
summary(mod)

TukeyHSD(mod)
```


################## 

# Broken down for each experiment 

### F1: Two runs

```{r}

df_2021 <- df%>%
  filter(Year=="2021")

ggplot(data=df_2021, aes(x=Treatment, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed (2021: F1 Larvae) ", x ="Treatment", y = "Percent Deformed")+
  facet_wrap("Run")
```


```{r}
df_run1 <- df%>%
  filter(Run=="1")

leveneTest(Percent.deformed_trans ~ Treatment, data=df_run1)
shapiro.test(df_run1$Percent.deformed_trans)

df_run2 <- df%>%
  filter(Run=="2")

leveneTest(Percent.deformed_trans ~ Treatment, data=df_run2)
shapiro.test(df_run2$Percent.deformed_trans)
```


```{r}
dunnTest(Percent.deformed ~ Treatment,
                data = df_run1,
              method="bh")
dunnTest(Percent.deformed ~ Treatment,
                data = df_run2,
              method="bh")
```


```{r}
leveneTest(Percent.deformed_trans ~ Treatment, data=df_2021)
shapiro.test(df_2021$Percent.deformed_trans)
```

### F2 April 2022

```{r}
df_2022 <- df%>%
  filter(Year=="2022")

df_2022_3 <- df_2022%>%
  filter(Run=="3")

ggplot(data=df_2022_3, aes(x=Treatment, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed, grouped by parentage (2022: F2 Larvae) ", x ="Treatment", y = "Percent Deformed")+
  facet_wrap("Parent")
```


```{r}
leveneTest(Percent.deformed_trans ~ Treatment, data=df_2022_3)
shapiro.test(df_2022_3$Percent.deformed_trans)
```


```{r}
scheirerRayHare(Percent.deformed ~ Treatment*Parent,
                data = df_2022_3)

dunnTest(Percent.deformed ~ Treatment,
                data = df_2022_3,
              method="bh")

dunnTest(Percent.deformed ~ Parent,
                data = df_2022_3,
              method="bh")
```


### F2 August 2022

```{r}
df_2022 <- df%>%
  filter(Year=="2022")

df_2022_4 <- df_2022%>%
  filter(Run=="4")

ggplot(data=df_2022_4, aes(x=Treatment, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed (2022: F2 Larvae) ", x ="Treatment", y = "Percent Deformed")
```

```{r}

leveneTest(Percent.deformed_trans ~ Treatment, data=df_2022_4)
shapiro.test(df_2022_4$Percent.deformed_trans)
```

```{r}

res.kruskal <- kruskal.test(Percent.deformed ~ Treatment, data = df_2022_4)
res.kruskal

```


### F3 Larval April 2023

```{r}
df_6 <- df%>%
  filter(Run=="6")

ggplot(data=df_6, aes(x=Treatment, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed, grouped by parentage (2023: F3 Larvae) ", x ="Treatment", y = "Percent Deformed")+
  facet_wrap("Parent")



Run6_mean_deformaties <- df_6 %>% 
                dplyr::select(Treatment,Parent,Percent.deformed) %>% 
                na.omit() %>% 
                dplyr::group_by(Treatment,Parent) %>% 
                dplyr::summarise(mean_Perc_def = mean(Percent.deformed), 
                                 n           = n(),
                                 sd_Perc_def   = sd(Percent.deformed),
                                 se_Perc_def   = sd_Perc_def/(sqrt(n)))

library(forcats)

ggplot(Run6_mean_deformaties) +
  geom_errorbar(aes(x=Treatment, 
                     ymin=mean_Perc_def-se_Perc_def, 
                     ymax=mean_Perc_def+se_Perc_def), 
                 width=0, # removes the horizontal line
                 colour="black", 
                 size=1) +
  geom_bar(aes(x=Treatment, y=mean_Perc_def,fill=factor(Treatment)), 
            stat="identity",
           width = 0.75,
           alpha = 0.5) +
  labs(title="F3 Abnormalities- Full cross exposure", 
      x ="pCO2 Offspring Exposure", 
      y = "Percent Abnormalities") +
   scale_fill_manual(breaks=c("Low OA", "Moderate OA", "High OA"), 
                       values=c("forestgreen","orange", "purple")) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.text=element_text(size=12),
        legend.position="none") +
  facet_wrap(~Parent)


Run6PLot_MeanSE_deformaties <- ggplot(data=Run6_mean_deformaties, 
                                       aes(x=fct_relevel(Treatment, c("Low OA", "Moderate OA", "High OA")), 
                                           y=Percent.deformed_trans, 
                                           colour=fct_relevel(Treatment, c("Low OA", "Moderate OA", "High OA")))) +
                                       # scale_linetype(c("dotted","solid")) +
                                       # scale_linetype_manual(breaks=c("Low", "High"), values=c("dashed","solid")) +
                                       scale_colour_manual(breaks=c("Low OA", "Moderate OA", "High OA"), 
                                                           values=c("forestgreen","orange", "purple")) +
                                       geom_bar() + 
                                       stat_summary(fun.y="mean", size = 0.8, 
                                                    position = position_dodge2(width = 1)) +
                                       stat_summary(fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)), 
                                                    fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
                                                    geom = 'errorbar', 
                                                    width = 0,
                                                    position = position_dodge2(width = 1)) +
                                       labs(title="F3 Abnormalities- Full cross exposure", 
                                            x ="pCO2 Offspring Exposure", 
                                            y = "Percent Abnormalities") +
                                       theme_classic() +
                                       theme(panel.grid.major = element_blank(), 
                                             panel.grid.minor = element_blank(), 
                                             axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                                             axis.text=element_text(size=12),
                                            legend.position="none") +
                                       facet_wrap(~Parent)
Run6PLot_MeanSE_deformaties

```


```{r, F3 run 6 stats by history}

df_6_HIGH     <- df_6 %>% dplyr::filter(Parent %in% "HIGH")
df_6_MODERATE <- df_6 %>% dplyr::filter(Parent %in% "MODERATE")
df_6_LOW      <- df_6 %>% dplyr::filter(Parent %in% "LOW")


anova_HIGH <- lm(Percent.deformed_trans ~ Treatment, data = df_6_HIGH)
shapiro.test(resid(anova_HIGH)) # 0.7455
leveneTest(anova_HIGH) # 0.865
summary(aov(anova_HIGH))
#             Df   Sum Sq  Mean Sq F value Pr(>F)
# Treatment    2 0.000305 0.000152   0.033  0.968
# Residuals    6 0.027538 0.004590

anova_MODERATE <- lm(Percent.deformed_trans ~ Treatment, data = df_6_MODERATE)
shapiro.test(resid(anova_MODERATE)) # 0.5231
leveneTest(anova_MODERATE) # 0.7784
summary(aov(anova_MODERATE))
#             Df Sum Sq Mean Sq F value Pr(>F)
# Treatment    2 0.1244 0.06218   2.761  0.141
# Residuals    6 0.1351 0.02252

anova_LOW <- lm(Percent.deformed_trans ~ Treatment, data = df_6_LOW)
shapiro.test(resid(anova_LOW)) # 0.9679
leveneTest(anova_LOW) # 0.102
summary(aov(anova_LOW))
#             Df Sum Sq Mean Sq F value Pr(>F)  
# Treatment    2 0.2222 0.11108   5.188 0.0603 .
# Residuals    5 0.1071 0.02141

```


```{r}
leveneTest(Percent.deformed_trans ~ Treatment, data=df_6)
shapiro.test(df_6$Percent.deformed_trans)
```

```{r}
mod <- aov(Percent.deformed_trans ~Treatment * Parent, data = df_6)
summary(mod)
```


```{r}
scheirerRayHare(Percent.deformed ~ Treatment*Parent,
                data = df_6)

dunnTest(Percent.deformed ~ Treatment,
                data = df_6,
              method="bh")

dunnTest(Percent.deformed ~ Parent,
                data = df_6,
              method="bh")
```



### Trimming the F3 to look at differences
```{r}

df_6_trim <- df_6%>%
  filter(Parent %in% c("MODERATE", "LOW"))

ggplot(data=df_6_trim, aes(x=Treatment, y=Percent.deformed, fill=Treatment)) +
  geom_boxplot()+  scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Percent Deformed, grouped by parentage (2023: F3 Larvae) ", x ="Treatment", y = "Percent Deformed")+
  facet_wrap("Parent")
```

```{r}
scheirerRayHare(Percent.deformed ~ Treatment*Parent,
                data = df_6_trim)

#dunnTest(Percent.deformed ~ Treatment,
#                data = df_6_trim,
 #             method="bh")

#dunnTest(Percent.deformed ~ Parent,
  #              data = df_6_trim,
   #           method="bh")
```







Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
