---
title: "Temp by OA - Heatwave - Conidtion Index"
author: "Katie McFarland"
date: "7/14/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## install libraries (only run this code if you do not already have these libraries installed)
```{r, include=FALSE}
install.packages("ggplot2")
install.packages("car")
install.packages("nlme")
install.packages("Rmisc")
```


## Load libraries
```{r, include=FALSE}
library("ggplot2")
library("car")
library("nlme")
library(Rmisc)

```


## Set Path. This is there the csv data file is stored on your computer. AKA set working directory so that your computer knows where to look for files
```{r}
#Set Path - telling R where to look for files

setwd("C:/Users/katherine.mcfarland/Documents/4. GitHub/EAD-ASEB-Airradians_multigen_OA/RAnalysis/Heatwave")
```

### Load Data -

```{r}
#Here we are assigning our data frame the name "df" so that we do not have to type out the full file name everytime we want to call it.

df<-read.csv("Condition_Index_Heatwave.csv", header = T)
#

#to look at columns names of your data frame
head(df)

# assigning our controlled variables as factors 
df$pH=as.factor(df$pH)
df$Temp=as.factor(df$Temp)
df$Rep=as.factor(df$Rep)


#Sturcture of the data - to check that variables are properly assigned to facotr or variable
str(df)
```

```{r, echo=FALSE}
ggplot(data=df, aes(x=pH, y=Condition.Index, fill=pH)) +
  geom_boxplot()+  
     #scale_fill_manual(values=c("forestgreen","orange"))+
  #scale_fill_manual(values=c("gray90","gray54"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Condition Index", x ="pH", y = "Condition Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~Temp)

                        #labels=c("500 µatm", "800 µatm"))
  
```

# Quick summary of the average condition index for each treatment 
    sd = standard deviation
    se = standard error
    ci = confidence interval
```{r}
stL <- summarySE(df, measurevar="Condition.Index", groupvars=c("pH", "Temp"))
stL 
```



#testing assumptions for statisitcal analysis
```{r}
#Lavene's test for Homogeneity (want p > 0.05)
leveneTest(Condition.Index ~ pH*Temp, data=df)

#Shapiro-Wilk test for normality (want p > 0.05)
shapiro.test(df$Condition.Index)
```


# Running an Analysis of Variance to test statistical Significance of the main effects (temperature and pH) and their interaction
```{r}
mod <- aov(Condition.Index ~pH*Temp, data=df)

summary(mod)

```

# Post hoc analysis to test among which treatments within the main effects the significance lies
```{r}
TukeyHSD(mod, conf.level = .95)
```

# This prints out the R version information which is helpful for when you report your statisical methods
```{r}
sessionInfo()
```

